### 2021-06-07 AggregateCounts.Rmd
changed folder and got aggregates files import

---
title: "AggregateCounts"
author: "Juan P Barraza"
date: "6/4/2021"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
library(conflicted)
library(tidyverse)
filter <- dplyr::filter

conditionlist= list('wt','pqsL', 'phz', 'mono')

ReadAggregateFile(fileList[1], "Pa", "1", "wt")
GetAggregates()

datos <-read.csv(fileList[1], header = F)
colnames(datos)<-c('Size')
datos1<-datos %>% filter(!Size<0.5) #first filter the size

ReadAggregateFile<-function(file, species, timepoint, condition){#make a dataframe of the aggregate size list and add experimental parameters
  datos <-read.csv(file, header = F)
  colnames(datos)<-c('Size')
  datos<-datos %>% filter(!Size<0.5) #first filter the size
  datos<-datos %>% mutate(Species = species)#add parameters
  datos<-datos %>% mutate(TimePoint = timepoint)
  datos<-datos %>% mutate(Condition = condition)
  return(datos)
}

GetAggregates<-function(){#import all experiments at once
  folder<- paste0('/Volumes/raw_data/Confocal/Carolyn/2020/Chronic wounds/Aggregate lists')
  fileList<-list.files(path = folder, full.names = TRUE)
  growthDf<-data.frame()
  for (condition in 1:length(conditionlist)){
    currentCondition<-fileList[grep(conditionlist[condition],fileList)] #find files for each condition
    print(currentCondition)
    for (species in 1:3){
      currentTimePoint<-currentPosition[grep(paste0("t_",GetNumber(timepoint),"p_"),currentPosition)]
      print(currentTimePoint)
      #growthDf<-rbind(growthDf,ReadAggregateFile(currentTimePoint, position, timepoint))
    }
  }
  return(growthDf)
}

for (i in 0:3){
  print(i)
  }

```

## R Markdown

This is an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

### 2021-06-07 R/AggregateCounts.Rmd
changed folder and got aggregates files import

---
title: "AggregateCounts"
author: "Juan P Barraza"
date: "6/4/2021"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
library(conflicted)
library(tidyverse)
filter <- dplyr::filter

ReadAggregateFile(fileList[1], "Pa", "1", "wt")
blah<-GetAggregates()

datos <-read.csv(fileList[1], header = F)
colnames(datos)<-c('Size')
datos1<-datos %>% filter(!Size<0.5) #first filter the size

ReadAggregateFile<-function(file, species, timepoint, condition, replicate){#make a dataframe of the aggregate size list and add experimental parameters
   datos <-read.csv(file, header = F)
   colnames(datos)<-c('Size')
   datos<-datos %>% filter(!Size<0.5) #first filter the size
   datos<-datos %>% mutate(Species = species)#add parameters
   datos<-datos %>% mutate(TimePoint = timepoint)
   datos<-datos %>% mutate(Condition = condition)
   datos<-datos %>% mutate(Replicate = replicate)
   datos$Species<-as.factor(datos$Species)
   datos$Replicate<-as.factor(datos$Replicate)
   datos$Condition<-as.factor(datos$Condition)
   datos$TimePoint<-as.factor(datos$TimePoint)
   return(datos)
}

GetAggregates<-function(){#import all experiments at once
   folder<- paste0('/Volumes/raw_data/Confocal/Carolyn/2020/Chronic wounds/Aggregate lists')
   fileList<-list.files(path = folder, full.names = TRUE)
   growthDf<-data.frame()
   for (aggList in 1:length(fileList)){
     fileName<-str_split(basename(fileList[aggList]), "\\.")[[1]][1]#this selects the base file name and removes the ".csv"
     attrList<-str_split(fileName,"_")[[1]]
     growthDf<-rbind(growthDf,ReadAggregateFile(fileList[aggList],attrList[4],attrList[2],attrList[1],attrList[3]))
     }
   return(growthDf)
}
```

### 2021-06-07 R/Raw Img Data.Rmd
changed folder and got aggregates files import

--- 2021-06-07 AggregateCounts.Rmd
@@
 ---
-title: "AggregateCounts"
+title: "Raw img Data"
 author: "Juan P Barraza"
-date: "6/4/2021"
+date: "4/23/2021"
 output: html_document
-editor_options: 
-  chunk_output_type: console
 ---
@@
 ```{r setup, include=FALSE}
-library(conflicted)
-library(tidyverse)
-filter <- dplyr::filter
 
-conditionlist= list('wt','pqsL', 'phz', 'mono')
-
-ReadAggregateFile(fileList[1], "Pa", "1", "wt")
-GetAggregates()
-
-datos <-read.csv(fileList[1], header = F)
-colnames(datos)<-c('Size')
-datos1<-datos %>% filter(!Size<0.5) #first filter the size
-
-ReadAggregateFile<-function(file, species, timepoint, condition){#make a dataframe of the aggregate size list and add experimental parameters
-  datos <-read.csv(file, header = F)
-  colnames(datos)<-c('Size')
-  datos<-datos %>% filter(!Size<0.5) #first filter the size
-  datos<-datos %>% mutate(Species = species)#add parameters
-  datos<-datos %>% mutate(TimePoint = timepoint)
-  datos<-datos %>% mutate(Condition = condition)
-  return(datos)
-}
-
-GetAggregates<-function(){#import all experiments at once
-  folder<- paste0('/Volumes/raw_data/Confocal/Carolyn/2020/Chronic wounds/Aggregate lists')
-  fileList<-list.files(path = folder, full.names = TRUE)
-  growthDf<-data.frame()
-  for (condition in 1:length(conditionlist)){
-    currentCondition<-fileList[grep(conditionlist[condition],fileList)] #find files for each condition
-    print(currentCondition)
-    for (species in 1:3){
-      currentTimePoint<-currentPosition[grep(paste0("t_",GetNumber(timepoint),"p_"),currentPosition)]
-      print(currentTimePoint)
-      #growthDf<-rbind(growthDf,ReadAggregateFile(currentTimePoint, position, timepoint))
-    }
-  }
-  return(growthDf)
-}
-
-for (i in 0:3){
-  print(i)
-  }
+#####
+imgHisData<-read.csv("/Users/jupabago/Documents/Whiteley/PROJECTS/SaPa Chronic Wounds/Images data/Image histogram data/cowtd1m2p2a_1.csv",header = F)
+NewNames <- c('zeroInt','zeroPercent','maxInt','firstZero','totalZeroes','level','calculatedG2','tailBins', 'numtailEnd','optimalG','meanIntensity','sdIntensity')
+names(imgHisData) <- NewNames
 

### 2021-06-07 R/AggregateCounts.Rmd
import and fancy histogram working for 1 sample

@@
 library(tidyverse)
+library(plotrix)#for std error
+library(cowplot)
 filter <- dplyr::filter
 
-ReadAggregateFile(fileList[1], "Pa", "1", "wt")
-blah<-GetAggregates()
+aggregateList<-GetAggregates()
+# mutate(Strain = recode(Position, "0" = "Pa14 wt", "1"= "Pa14 -PA1414","2" = "Pa14 wt", "3"= "Pa14 -PA1414")) #this is to change the names
 
-datos <-read.csv(fileList[1], header = F)
-colnames(datos)<-c('Size')
-datos1<-datos %>% filter(!Size<0.5) #first filter the size
-
+#agregate input functions
+#####
 ReadAggregateFile<-function(file, species, timepoint, condition, replicate){#make a dataframe of the aggregate size list and add experimental parameters
@@
 }
+#####
 ```
+```{r aggregate wrangling}
+aggregateListSummary<-aggregateList %>% group_by(Species, TimePoint, Condition) %>% 
+  summarise(Aggs = n(), biomass = sum(Size), meanAggSize = mean(Size), seAggSize = std.error(Size), maxSize = max(Size), minSize = min(Size)) %>%
+  ungroup() %>% mutate(RatioMaxTotal = maxSize/biomass )
+
+#plot agg summary
+#####
+ggplot()+
+  geom_point(data = aggregateListSummary, aes(x = TimePoint, y= meanAggSize, color = Species,shape = "MeanSize"))+
+  geom_point(data = aggregateListSummary, aes(x = TimePoint, y= maxSize, color = Species, shape = "MaxSize"))+
+  geom_point(data = aggregateListSummary, aes(x = TimePoint, y= biomass, color = Species, shape = "TotalBiomass"))+  
+  scale_y_log10( breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
+  facet_grid(. ~ Condition, scales = "free", space = "free") +
+  ggtitle('Aggregates: Mean, largest and total biomass (wild type)')+
+  labs(x = "",y = "Aggregate size (um3)")+
+  scale_shape_manual(name="Metric",values=c(MeanSize=1, MaxSize=2, TotalBiomass=17))+
+  theme_cowplot()+
+  theme(plot.title = element_text(hjust = 0.5))
+#####
+
+#create histograms, this takes a long time, so consider cutting them in chunks
+allDataGrouped<-aggregateList %>% group_by(Species, TimePoint, Condition)#first do the correct grouping
+allDataList<- group_split(allDataGrouped)#create list of dataframes
+allDataHistograms.5<-map2(allDataList, 5,TotalFancyHistogram)#apply histogram function to all items in the list
+
+allDataHistograms.5df<- bind_rows(allDataHistograms.5)
+
+```
+```{r Histogram fucntions}
+FancyHistogram<-function(df, sec){#my own way of doing histograms which includes the sum and mean of values whitin each bin
+  results<-data.frame()
+  for( i in 1:(length(sec)-1)){ 
+    blah<-df %>% filter(Size > sec[i] &Size<=sec[i+1])%>%summarise(frequency = n(), avg = mean(Size),suma = sum(Size)) %>% mutate(bin = i, min = sec[i],max = sec[i+1])
+    if(blah$frequency>0){ 
+      results<-rbind(results, blah)} 
+  }
+  return(results) 
+}
+TotalFancyHistogram<-function(df,binsize){
+  totalbiomass<-sum(df$Size)#total biomass per sample
+  totalfrequency<-length(df$Size)#total number of objects
+  upperLim<-max(df$Size)+binsize-(max(df$Size)%%binsize)#largest bin size based in largest object
+  breaksSequence<-seq(0,upperLim,binsize)#this makes breaks every "binsize" 
+  histogram<-FancyHistogram(df,breaksSequence)#apply "fancy histogram" to get distributions
+  histogram%>%mutate(BiomassBin=suma/totalbiomass)->histogram#add column with proportion of biomas per bin
+  histogram%>%mutate(Density=frequency/totalfrequency)->histogram#add column with proportion of counts per bin
+  histogram%>%mutate(Species=df$Species[1])->histogram#add column maintaining sample and so on...
+  histogram%>%mutate(Condition=df$Condition[1])->histogram
+  histogram%>%mutate(TimePoint=df$TimePoint[1])->histogram
+  histogram%>%mutate(Sample=df$Sample[1])->histogram
+  return(histogram)
+}
+```

### 2021-06-07 R/AggregateCounts.Rmd
plotting aggregate vs planktonics for wtd1_02

@@
 
-#create histograms, this takes a long time, so consider cutting them in chunks
+#Create histograms
+##this takes a long time, so consider running them in parts
 allDataGrouped<-aggregateList %>% group_by(Species, TimePoint, Condition)#first do the correct grouping
+#allDataGrouped<-aggregateList %>% group_by(Species, TimePoint, Condition, Sample)# this is to include sample on the distribution or keep it out
 allDataList<- group_split(allDataGrouped)#create list of dataframes
 allDataHistograms.5<-map2(allDataList, 5,TotalFancyHistogram)#apply histogram function to all items in the list
+allDataHistograms.5df<- bind_rows(allDataHistograms.5)#bring them together
 
-allDataHistograms.5df<- bind_rows(allDataHistograms.5)
+#Separating aggregates vs planktonic
+hist.plank.Agg.Sumary<-allDataHistograms.5df %>%  mutate(Aggregation = case_when(max == 5 ~ "Planktonic",max>5 ~ "Aggregate")) %>%
+  ungroup() %>%group_by(Species, TimePoint, Condition,Aggregation) %>% 
+  summarize(FrequencyAggregation = sum(frequency), BiomassAggregation = sum(BiomassBin), DensityAggregation = sum(Density))
+
+hist.plank.Agg.Stats<-hist.plank.Agg.Sumary %>% group_by(Species,TimePoint, Condition,Aggregation) %>%
+  summarise(MeanFreq = mean(FrequencyAggregation), SEFreq = std.error(FrequencyAggregation), MeanBiomass = mean(BiomassAggregation),
+            SEBiomass = std.error(BiomassAggregation),MeanDensity = mean(DensityAggregation), SEDensity = std.error(DensityAggregation))
+
+#Plotting these guys
+PlotAggsPlank<- function(){
+  ggplot()+
+    geom_col(data = hist.plank.Agg.Stats,aes(x=TimePoint,y=MeanBiomass, fill = Aggregation),size=3,position = position_dodge( width = .9))+
+    geom_errorbar(data = hist.plank.Agg.Stats,aes(x=TimePoint,ymin=MeanBiomass-SEBiomass, ymax = MeanBiomass+SEBiomass),size=.5,position = position_dodge2( width = .6))+
+    facet_grid(.~Species)+
+    labs(title = "Chronic Wounds", x = "", y = "Biomass contribution")+
+    theme_cowplot()+
+    theme(plot.title = element_text(hjust = 0.5))
+}
+PlotAggsPlank()
 
 ```
-```{r Histogram fucntions}
+```{r Histogram functions}
 FancyHistogram<-function(df, sec){#my own way of doing histograms which includes the sum and mean of values whitin each bin

### 2021-06-08 Matlab/adaptiveThreshold.m
testing the pipeline on multiple images

@@ -1,7 +1,23 @@
-rawTifPath = '/Volumes/raw_data/Confocal/Carolyn/2020/Chronic wounds/Tiff Stacks/wtd1-02/';
-binTifPath = '/Volumes/raw_data/Confocal/Carolyn/2020/Chronic wounds/Binary Images larger wiener2/wtd1-02/';
-aggsFilePath = '/Volumes/raw_data/Confocal/Carolyn/2020/Chronic wounds/Aggregate lists/wtd1-02';
-%
+rawTifPathBase = '/Volumes/raw_data/Confocal/Carolyn/2020/Chronic wounds/Tiff Stacks/';
+binTifPathBase = '/Volumes/raw_data/Confocal/Carolyn/2020/Chronic wounds/Binary Images/';
+aggsFilePathBase = '/Volumes/raw_data/Confocal/Carolyn/2020/Chronic wounds/Aggregate lists/'; %names are different
+
+
+for image= 4:15
+rawTifPath = [rawTifPathBase,'wtd1-',GetNum(image),'/'];
+binTifPath = [binTifPathBase,'wtd1-',GetNum(image),'/'];
+aggsFilePath = [aggsFilePathBase,'wt_d1_',GetNum(image)];
+Tiff2Data (rawTifPath,binTifPath,aggsFilePath);
+end
+
+for image= 1:6
+rawTifPath = [rawTifPathBase,'wtd4-',GetNum(image),'/'];
+binTifPath = [binTifPathBase,'wtd4-',GetNum(image),'/'];
+aggsFilePath = [aggsFilePathBase,'wt_d4_',GetNum(image)];
+Tiff2Data (rawTifPath,binTifPath,aggsFilePath);
+end
+
+function Tiff2Data (rawTifPath,binTifPath, aggsFilePath)
 tic
 [ch1,ch2,ch3] = Stack2volume(rawTifPath);%split the image by the 3 channels.
 toc
@@ -16,10 +32,9 @@ filtered3 = imbinarize(FilterImage(ch3));
 toc
 disp('combining and saving')
 
-%now remove bleeding from red into the green channel and isolated pixels
-%and create a clean volume
-[cleanRed, cleanGreen, cleanBlue] = CleanExportVolume(binTifPath, filtered3,filtered1, filtered2);%Order is really important here
-%{
+%now remove bleeding from red into the green channel and isolated pixels and create a clean volume
+%%!!!Order is really important here, it is input as red, green blue
[…]

### 2021-06-15 R/AggregateCounts.Rmd
added new histogram function

--- 2021-06-07 R/AggregateCounts.Rmd
@@
 library(tidyverse)
+library(plotrix)#for std error
+library(dplyr)
+library(cowplot)
 filter <- dplyr::filter
+source("~/Documents/Whiteley/PROJECTS/SaPa Chronic Wounds/PaSaChronicWounds/R/readTiff.R")
+library(EBImage) #for rtiff
 
-ReadAggregateFile(fileList[1], "Pa", "1", "wt")
-blah<-GetAggregates()
+aggregateList<-GetAggregates()#this reads the data from Matlab
+# mutate(Strain = recode(Position, "0" = "Pa14 wt", "1"= "Pa14 -PA1414","2" = "Pa14 wt", "3"= "Pa14 -PA1414")) #this is to change the names
 
-datos <-read.csv(fileList[1], header = F)
-colnames(datos)<-c('Size')
-datos1<-datos %>% filter(!Size<0.5) #first filter the size
-
+#agregate input functions
+#####
 ReadAggregateFile<-function(file, species, timepoint, condition, replicate){#make a dataframe of the aggregate size list and add experimental parameters 
@@
 }
+#####
 ```
+```{r aggregate wrangling}
+#Statistics from all aggregates
+
+#Get aggregate summary per sample
+aggregateListSummaryReplicate<-aggregateList %>% group_by(Species, TimePoint, Condition, Replicate) %>% 
+  summarise(Aggs = n(), biomass = sum(Size), meanAggSize = mean(Size), seAggSize = std.error(Size), maxSize = max(Size), minSize = min(Size)) %>%
+  ungroup() %>% mutate(RatioMaxTotal = maxSize/biomass )
+
+#Plot agg summary per sample
+#####
+ggplot()+
+  geom_jitter(data = aggregateListSummaryReplicate, aes(x = TimePoint, y= meanAggSize, color = Species,shape = "MeanSize"),size = 3, height = 0, width = .1)+
+  geom_jitter(data = aggregateListSummaryReplicate, aes(x = TimePoint, y= maxSize, color = Species, shape = "MaxSize"),size = 3, height = 0, width = .1)+
+  geom_jitter(data = aggregateListSummaryReplicate, aes(x = TimePoint, y= biomass, color = Species, shape = "TotalBiomass"),size = 3, height = 0, width = .1)+  
+  scale_y_log10( breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
+  facet_grid(. ~ Condition, scales = "free", space = "free") +
+  ggtitle('Mean size and largest aggregate and total biomass per sample')+
+  labs(x = "",y = "um3")+
+  scale_shape_manual(name="Metric",values=c(MeanSize=1, MaxSize=2, TotalBiomass=17))+
+  theme_cowplot()+
+  theme(plot.title = element_text(hjust = 0.5))
+#####
+
+#Get aggregate Summary per condition
+aggregateListSummary<-aggregateList %>% group_by(Species, TimePoint, Condition) %>% 
+  summarise(Aggs = n(), biomass = sum(Size), meanAggSize = mean(Size), seAggSize = std.error(Size), maxSize = max(Size), minSize = min(Size)) %>%
+  ungroup() %>% mutate(RatioMaxTotal = maxSize/biomass ) 
+#plot agg summary per condition
+#####
+ggplot()+
+  geom_jitter(data = aggregateListSummary, aes(x = TimePoint, y= meanAggSize, color = Species,shape = "MeanSize"),size = 3, height = 0, width = .1)+
+  geom_jitter(data = aggregateListSummary, aes(x = TimePoint, y= maxSize, color = Species, shape = "MaxSize"),size = 3, height = 0, width = .1)+
+  geom_jitter(data = aggregateListSummary, aes(x = TimePoint, y= biomass, color = Species, shape = "TotalBiomass"),size = 3, height = 0, width = .1)+  
+  scale_y_log10( breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
+  facet_grid(. ~ Condition, scales = "free", space = "free") +
+  ggtitle('Mean size and largest aggregate and total biomass per sample')+
+  labs(x = "",y = "um3")+
+  scale_shape_manual(name="Metric",values=c(MeanSize=1, MaxSize=2, TotalBiomass=17))+
+  theme_cowplot()+
+  theme(plot.title = element_text(hjust = 0.5))
+#####
+```
+```{r non-fancy histogram}
+#histogram<- hist(aggregateList$Size, breaks = c(0, 5, 10, 100, 1000, 10^9))#this is a simple way to do a histogram
+
+#this pipe essentially gets to the producto of what fancy histograms do but more efficiently
+#First including all sizes
+#####
+newHistogram.df<-aggregateList %>% mutate(LogBin = case_when(Size <= 5 ~ 5,
+                        Size<= 10 ~ 10,
+                        Size<= 100    ~ 100,
+                        Size<= 1000   ~ 1000,
+                        Size<= 10000  ~ 10000,
+                        Size<= 100000 ~ 100000,
+                        Size > 100000 ~ 1000000)) %>% group_by(Species,Condition,TimePoint, Replicate)%>% 
+  mutate(TotalBiomass = sum(Size), TotalFrequency = n()) %>% ungroup() %>% group_by(Species,Condition,TimePoint, Replicate, LogBin)%>%
+  mutate(BinBiomass = sum(Size), BinFrequency = n()) %>% ungroup() %>%
+  mutate(NormalizedFrequency = BinFrequency/TotalFrequency*100, NormalizedBiomass = BinBiomass/TotalBiomass*100)
+
+#This is weird, but I want to have the histogram above with all the data, and the one below with only the bins
+newHistogramSummary.df<-newHistogram.df %>% group_by(Species,Condition,TimePoint, Replicate, LogBin,NormalizedFrequency,NormalizedBiomass) %>% summarize() %>%  unique()%>%ungroup() %>%  group_by(Species,Condition,TimePoint, Replicate) %>% mutate(checkSumFreq =sum(NormalizedFrequency), checkSumBiomass = sum(NormalizedBiomass))
+
+#now plot it
+ggplot()+
+    geom_jitter(data = newHistogramSummary.df,aes(x=as.factor(LogBin),y=NormalizedFrequency,  color =Species, ),size=3, height = 0, width = .2)+
+    scale_y_log10(breaks = c(100, 10, 1, .1, .01), labels = c(100, 10, 1, .1, .01))+
+    facet_grid(.~TimePoint)+
+    labs(y = "Frequency",x = bquote(paste("Aggregate Volume (", mu*"m"^3*")")))+
+    theme_cowplot()+
+    theme(plot.title = element_text(hjust = 0.5))  
+#####
+#now only aggregates 5 microns or larger
+#####
+aggsOnlyHist.df<-aggregateList %>% mutate(LogBin = case_when(Size <= 5 ~ 5,
+                        Size<= 10 ~ 10,
+                        Size<= 100    ~ 100,
+                        Size<= 1000   ~ 1000,
+                        Size<= 10000  ~ 10000,
+                        Size<= 100000 ~ 100000,
+                        Size > 100000 ~ 1000000)) %>% filter(!LogBin == 5) %>% group_by(Species,Condition,TimePoint, Replicate)%>% 
+  mutate(TotalBiomass = sum(Size), TotalFrequency = n()) %>% ungroup() %>% group_by(Species,Condition,TimePoint, Replicate, LogBin)%>%
+  mutate(BinBiomass = sum(Size), BinFrequency = n()) %>% ungroup() %>%
+  mutate(NormalizedFrequency = BinFrequency/TotalFrequency*100, NormalizedBiomass = BinBiomass/TotalBiomass*100)
+
+#This is weird, but I want to have the histogram above with all the data, and the one below with only the bins
+aggsOnlyHistSummary.df<-aggsOnlyHist.df %>% group_by(Species,Condition,TimePoint, Replicate, LogBin,NormalizedFrequency,NormalizedBiomass) %>% summarize() %>%  unique()%>%ungroup() %>%  group_by(Species,Condition,TimePoint, Replicate) %>% mutate(checkSumFreq =sum(NormalizedFrequency), checkSumBiomass = sum(NormalizedBiomass))
+
+#now plot it
+#normalized frequency
+ggplot()+
+    geom_jitter(data = aggsOnlyHistSummary.df,aes(x=as.factor(LogBin),y=NormalizedFrequency,  color =Species, ),size=3, height = 0, width = .2)+
+    scale_y_log10(breaks = c(100, 10, 1, .1, .01), labels = c(100, 10, 1, .1, .01))+
+    facet_grid(.~TimePoint)+
+    labs(y = "Frequency",x = bquote(paste("Aggregate Volume (", mu*"m"^3*")")))+
+    theme_cowplot()+
+    theme(plot.title = element_text(hjust = 0.5)) 
+#Normalized Biomass facet timepoint, color species
+ggplot()+
+    geom_jitter(data = aggsOnlyHistSummary.df,aes(x=as.factor(LogBin),y=NormalizedBiomass,  color =Species, ),size=3, height = 0, width = .2)+
+    scale_y_log10(breaks = c(100, 10, 1, .1, .01), labels = c(100, 10, 1, .1, .01))+
+    facet_grid(.~TimePoint)+
+    labs(y = "Normalized Biomass",x = bquote(paste("Aggregate Volume (", mu*"m"^3*")")))+
+    theme_cowplot()+
+    theme(plot.title = element_text(hjust = 0.5)) 
+#Normalized Biomass facet species, color timepoint
+ggplot()+
+    geom_jitter(data = aggsOnlyHistSummary.df,aes(x=as.factor(LogBin),y=NormalizedBiomass,  color =TimePoint, ),size=3, height = 0, width = .2)+
+    #scale_y_log10(breaks = c(100, 10, 1, .1, .01), labels = c(100, 10, 1, .1, .01))+
+    facet_grid(.~Species)+
+    labs(y = "Normalized Biomass",x = bquote(paste("Aggregate Volume (", mu*"m"^3*")")))+
+    theme_cowplot()+
+    theme(plot.title = element_text(hjust = 0.5)) 
+#Normalized Biomass facet species and Timepoint, color Replicate
+ggplot()+
+    geom_line(data = aggsOnlyHistSummary.df,aes(x=as.factor(LogBin),y=NormalizedBiomass, color = Replicate, group = Replicate ),size=1)+
+    #scale_y_log10(breaks = c(100, 10, 1, .1, .01), labels = c(100, 10, 1, .1, .01))+
+    guides(color = FALSE)+
+    facet_grid(TimePoint~Species)+
+    labs(y = "Normalized Biomass",x = bquote(paste("Aggregate Volume (", mu*"m"^3*")")))+
+    theme_cowplot()+
+    scale_colour_grey()+
+    theme(plot.title = element_text(hjust = 0.5))
+
+#####
+#Planktonic vs aggregates
+#####
+#Add agregation value to the dataframe
+newHistogram.df<-newHistogram.df %>%  mutate(Aggregation = case_when(LogBin == 5 ~ "Planktonic",LogBin>5 ~ "Aggregate")) %>%
+  group_by(Species,Condition,TimePoint, Replicate, Aggregation)%>% 
+  mutate(AgPlBiomass = sum(Size), AgPlFreq = n()) %>% ungroup() %>%
+  mutate(AgPlNormFrequency = AgPlFreq/TotalFrequency*100, AgPlNormBiomass = AgPlBiomass/TotalBiomass*100)
+#Sumarize in dataframe
+plankAggHist<-newHistogram.df %>% group_by(Species,Condition,TimePoint, Replicate, Aggregation,AgPlNormFrequency,AgPlNormBiomass) %>% summarize() %>%  unique()%>%ungroup() %>%  group_by(Species,Condition,TimePoint, Replicate) %>% mutate(checkAggFreq =sum(AgPlNormFrequency), checkAggBiomass = sum(AgPlNormBiomass))
+#plot Frequency
+ggplot()+
+    geom_jitter(data = plankAggHist,aes(x=as.factor(Aggregation),y=AgPlNormFrequency,  color =Species, ),size=3, height = 0, width = .2)+
+    #scale_y_log10(breaks = c(100, 10, 1, .1, .01), labels = c(100, 10, 1, .1, .01))+
+    facet_grid(.~TimePoint)+
+    labs(y = "Frequency",x = bquote(paste("Aggregate Volume (", mu*"m"^3*")")))+
+    theme_cowplot()+
+    theme(plot.title = element_text(hjust = 0.5)) 
+ggplot()+
+    geom_jitter(data = plankAggHist,aes(x=as.factor(Aggregation),y=AgPlNormBiomass,  color =Species, ),size=3, height = 0, width = .2)+
+    #scale_y_log10(breaks = c(100, 10, 1, .1, .01), labels = c(100, 10, 1, .1, .01))+
+    facet_grid(.~TimePoint)+
+    labs(y = "Normalized Biomass",x = bquote(paste("Aggregate Volume (", mu*"m"^3*")")))+
+    theme_cowplot()+
+    theme(plot.title = element_text(hjust = 0.5))
+
+#####
+```
+
+```{r fancy histogram of aggregates}
+#Create histograms
+##this takes a long time, so consider running them in parts
+allDataGrouped<-aggregateList %>% group_by(Species, TimePoint, Condition)#first do the correct grouping
+#allDataGrouped<-aggregateList %>% group_by(Species, TimePoint, Condition, Sample)# this is to include sample on the distribution or keep it out
+allDataList<- group_split(allDataGrouped)#create list of dataframes
+allDataHistograms.5<-map2(allDataList, 5,TotalFancyHistogram)#apply histogram function to all items in the list
+allDataHistograms.5df<- bind_rows(allDataHistograms.5)#bring them together
+
+#plotting histogram data
+hist.5.LogBinSummarize<-allDataHistograms.5df %>% 
+  filter(!max == 5)%>% #remove planktonic cells, but this changes the nortmalization of aggregate counts, so the normalization needs to be done later for aggs only
+  group_by(Species,Condition,TimePoint)%>% mutate(LogBin = case_when(max <= 10 ~ 10,
+                        max<= 100    ~ 100,
+                        max<= 1000   ~ 1000,
+                        max<= 10000  ~ 10000,
+                        max<= 100000 ~ 100000,
+                        max > 100000 ~ 1000000)) %>% ungroup() %>% 
+  group_by(Species, Condition,TimePoint,LogBin) %>% summarise(FrequencyLogBin = sum(frequency), BiomassLogBin = sum(BiomassBin), DensityLogBin = sum(Density))
+
+#plot frequency  
+ggplot()+
+    geom_point(data = hist.5.LogBinSummarize,aes(x=as.factor(LogBin),y=FrequencyLogBin,  color =Species ),size=4)+
+    #labs(title = titulo)+
+    scale_y_log10(breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
+    facet_grid(.~TimePoint)+
+    labs(y = "Frequency",x = bquote(paste("Aggregate Volume (", mu*"m"^3*")")))+
+    #guides(color = FALSE)+
+    theme_cowplot()+
+    theme(plot.title = element_text(hjust = 0.5))
+
+  ggplot()+
+    geom_point(data = hist.5.LogBinSummarize,aes(x=as.factor(LogBin),y=BiomassLogBin,  color =Species ),size=4)+
+    scale_y_log10(breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
+    facet_grid(.~TimePoint)+
+    labs(y = "Biomass fraction per bin",x = bquote(paste("Aggregate Volume (", mu*"m"^3*")")))+
+    theme_cowplot()+
+    theme(plot.title = element_text(hjust = 0.5))
+
+  ggplot()+
+    geom_point(data = hist.5.LogBinSummarize,aes(x=as.factor(LogBin),y=DensityLogBin,  color =Species ),size=4)+
+    scale_y_log10(breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
+    facet_grid(.~TimePoint)+
+    labs(y = "Biomass fraction per bin",x = bquote(paste("Aggregate Volume (", mu*"m"^3*")")))+
+    theme_cowplot()+
+    theme(plot.title = element_text(hjust = 0.5))
+
+#Separating aggregates vs planktonic
+hist.plank.Agg.Sumary<-allDataHistograms.5df %>%  mutate(Aggregation = case_when(max == 5 ~ "Planktonic",max>5 ~ "Aggregate")) %>%
+  ungroup() %>%group_by(Species, TimePoint, Condition,Aggregation) %>% 
+  summarize(FrequencyAggregation = sum(frequency), BiomassAggregation = sum(BiomassBin), DensityAggregation = sum(Density))
+
+hist.plank.Agg.Stats<-hist.plank.Agg.Sumary %>% group_by(Species,TimePoint, Condition,Aggregation) %>%
+  summarise(MeanFreq = mean(FrequencyAggregation), SEFreq = std.error(FrequencyAggregation), MeanBiomass = mean(BiomassAggregation),
+            SEBiomass = std.error(BiomassAggregation),MeanDensity = mean(DensityAggregation), SEDensity = std.error(DensityAggregation))
+
+#Plotting these guys
+PlotAggsPlank<- function(){
+  ggplot()+
+    geom_col(data = hist.plank.Agg.Stats,aes(x=TimePoint,y=MeanBiomass, fill = Aggregation),size=3,position = position_dodge( width = .9))+
+    geom_errorbar(data = hist.plank.Agg.Stats,aes(x=TimePoint,ymin=MeanBiomass-SEBiomass, ymax = MeanBiomass+SEBiomass),size=.5,position = position_dodge2( width = .6))+
+    facet_grid(.~Species)+
+    labs(title = "Chronic Wounds", x = "", y = "Biomass contribution")+
+    theme_cowplot()+
+    theme(plot.title = element_text(hjust = 0.5))
+}
+PlotAggsPlank()
+```
+
+```{r biomass per slice}
+#this was taken from "Microscopy data clean.Rmd"
+GetResults<-function(sample,){#points to folder with files. Folder is hardcoded, unfortunately
+  #folder<- paste0('/Volumes/raw_data/Confocal/Carolyn/2020/Chronic wounds/Binary Images/', sample)
+  folder<- paste0('/Volumes/raw_data/Confocal/Carolyn/2020/Chronic wounds/Binary Images/wtd1-02')
+  fileList<-list.files(path = folder, full.names = TRUE)
+  growthDf<-data.frame()
+  blueChannel<-fileList[grep('B_',fileList)]
+  for(slice in 1:length(filesList)/3){
+    counts<-sum(as.array(readImage(fileList[1], convert = TRUE)))
+    growthDf<-rbind(growthDf,c(counts, slice,species))
+    growthDf<-growthDf %>% mutate(Sample = samplename)
+return(growthDf)
+} }
+#this was taken from the PropOc package
+SlicesTo3D<-function(filesList,side){
+  image1<-readTiff(filesList[1])#read first image to get its dimensions
+  image3D <- array(0, c(image1@size[1], image1@size[2], length(filesList)))#preallocate array for image given using image dimensions
+  for(i in 1:length(filesList)/3){#keep in mind that it is not zero-index
+    #print(paste("loading ch1...", i, "/", length(filesList), filesList[i]))
+    image3D[,,i]<-as.array(readImage(fileList[1], convert = TRUE))
+  }
+  return(image3D)
+}
+
+```
+
+```{r Histogram functions}
+FancyHistogram<-function(df, sec){#my own way of doing histograms which includes the sum and mean of values whitin each bin
+  results<-data.frame()
+  for( i in 1:(length(sec)-1)){ 
+    blah<-df %>% filter(Size > sec[i] &Size<=sec[i+1])%>%summarise(frequency = n(), avg = mean(Size),suma = sum(Size)) %>% mutate(bin = i, min = sec[i],max = sec[i+1])
+    if(blah$frequency>0){ 
+      results<-rbind(results, blah)} 
+  }
+  return(results) 
+}
+TotalFancyHistogram<-function(df,binsize){
+  totalbiomass<-sum(df$Size)#total biomass per sample
+  totalfrequency<-length(df$Size)#total number of objects
+  upperLim<-max(df$Size)+binsize-(max(df$Size)%%binsize)#largest bin size based in largest object
+  breaksSequence<-seq(0,upperLim,binsize)#this makes breaks every "binsize" 
+  histogram<-FancyHistogram(df,breaksSequence)#apply "fancy histogram" to get distributions
+  histogram%>%mutate(BiomassBin=suma/totalbiomass)->histogram#add column with proportion of biomass per bin
+  histogram%>%mutate(Density=frequency/totalfrequency)->histogram#add column with proportion of counts per bin
+  histogram%>%mutate(Species=df$Species[1])->histogram#add column maintaining sample and so on...
+  histogram%>%mutate(Condition=df$Condition[1])->histogram
+  histogram%>%mutate(TimePoint=df$TimePoint[1])->histogram
+  histogram%>%mutate(Sample=df$Sample[1])->histogram
+  return(histogram)
+}
+```

### 2021-06-15 Matlab/adaptiveThreshold.m
added comments to code

@@ -56,8 +56,8 @@ function filteredVolume = FilterImage(volume)
 [width, height,slices] = size(volume);
 filteredVolume = zeros(width, height, slices);
 for slice= 1:slices
-    stretchedImg = imadjust(volume(:,:,slice));
-    weinerImage = wiener2(stretchedImg, [10 10]);
+    stretchedImg = imadjust(volume(:,:,slice));%maximizes range of intensity
+    weinerImage = wiener2(stretchedImg, [10 10]);%smooths image when it's low contrast and leaves it if high contrast
     filteredVolume(:,:,slice)= weinerImage;
 end
 end
@@ -82,11 +82,11 @@ function [cleanRedVol,cleanGreenVol,cleanBlueVol]=CleanExportVolume(directory,re
 [width, height,slices] = size(redVolume);
 [cleanRedVol, cleanGreenVol, cleanBlueVol]= deal(zeros(width, height, slices));
 for slice= 1:slices
-redImage = bwareaopen(redVolume(:,:,slice),10);
+redImage = bwareaopen(redVolume(:,:,slice),10);%remove isolated voxels
 cleanRedVol(:,:,slice) = redImage;
 greenImage = greenVolume(:,:,slice);
 greenImage = greenImage - redImage; %correct for bleeding
-idx = greenImage < 0;%this identifies zeros
+idx = greenImage < 0;%this identifies -1's
 greenImage(idx) = 0;
 greenImage = bwareaopen(greenImage,10);
 cleanGreenVol(:,:,slice) = greenImage; 
@@ -109,7 +109,7 @@ end
 
 function objectSize = GetObjectSize(threeDStructure,aggNumber)
 objectSize = numel(threeDStructure.PixelIdxList{aggNumber});
-objectSize = objectSize*.415*.415*.52;
+objectSize = objectSize*.415*.415*.52;%conversion of voxels to um^3
 end
 
 function slice = GetSlice(idx)

### 2021-06-16 R/AggregateCounts.Rmd
Added figures from previous paper and got the readTiff function to work

@@
 
-#now plot it
+#Plot Normalized Frequency
 ggplot()+
@@
     facet_grid(.~TimePoint)+
-    labs(y = "Frequency",x = bquote(paste("Aggregate Volume (", mu*"m"^3*")")))+
+    labs(y = "Normalized Frequency (%)",x = bquote(paste("Aggregate Volume (", mu*"m"^3*")")))+
     theme_cowplot()+
+    theme(plot.title = element_text(hjust = 0.5))
+#Plot Normalized Biomass
+ggplot()+
+    geom_jitter(data = newHistogramSummary.df,aes(x=as.factor(LogBin),y=NormalizedBiomass,  color =Species, ),size=3, height = 0, width = .2)+
+    scale_y_log10(breaks = c(100, 10, 1, .1, .01), labels = c(100, 10, 1, .1, .01))+
+    facet_grid(.~TimePoint)+
+    labs(y = "Normalized Biomass (%)",x = bquote(paste("Aggregate Volume (", mu*"m"^3*")")))+
+    theme_cowplot()+
+    theme(plot.title = element_text(hjust = 0.5))
+
+#Plot normalized Biomass per sample
+ggplot()+
+    geom_line(data = newHistogramSummary.df,aes(x=as.factor(LogBin),y=NormalizedBiomass, color = Replicate, group = Replicate ),size=1)+
+    #scale_y_log10(breaks = c(100, 10, 1, .1, .01), labels = c(100, 10, 1, .1, .01))+
+    guides(color = FALSE)+
+    facet_grid(TimePoint~Species)+
+    labs(y = "Normalized Biomass",x = bquote(paste("Aggregate Volume (", mu*"m"^3*")")))+
+    theme_cowplot()+
+    scale_colour_grey()+
     theme(plot.title = element_text(hjust = 0.5)) 
@@
     facet_grid(.~TimePoint)+
-    labs(y = "Frequency",x = bquote(paste("Aggregate Volume (", mu*"m"^3*")")))+
+    labs(y = "Normalized Frequency (%)",x = bquote(paste("Aggregate Volume (", mu*"m"^3*")")))+
     theme_cowplot()+
@@
     facet_grid(.~TimePoint)+
-    labs(y = "Normalized Biomass",x = bquote(paste("Aggregate Volume (", mu*"m"^3*")")))+
+    labs(y = "Normalized Biomass (%)",x = bquote(paste("Aggregate Volume (", mu*"m"^3*")")))+
     theme_cowplot()+
@@
   mutate(AgPlNormFrequency = AgPlFreq/TotalFrequency*100, AgPlNormBiomass = AgPlBiomass/TotalBiomass*100)
-#Sumarize in dataframe
+#Collapse to only values per replicate
 plankAggHist<-newHistogram.df %>% group_by(Species,Condition,TimePoint, Replicate, Aggregation,AgPlNormFrequency,AgPlNormBiomass) %>% summarize() %>%  unique()%>%ungroup() %>%  group_by(Species,Condition,TimePoint, Replicate) %>% mutate(checkAggFreq =sum(AgPlNormFrequency), checkAggBiomass = sum(AgPlNormBiomass))
@@
     facet_grid(.~TimePoint)+
-    labs(y = "Frequency",x = bquote(paste("Aggregate Volume (", mu*"m"^3*")")))+
+    labs(y = "Normalized Frequency (%)",x = bquote(paste("Aggregate Volume (", mu*"m"^3*")")))+
     theme_cowplot()+
     theme(plot.title = element_text(hjust = 0.5)) 
+#Plot Biomass
 ggplot()+
@@
     facet_grid(.~TimePoint)+
-    labs(y = "Normalized Biomass",x = bquote(paste("Aggregate Volume (", mu*"m"^3*")")))+
+    labs(y = "Normalized Biomass (%)",x = bquote(paste("Aggregate Volume (", mu*"m"^3*")")))+
     theme_cowplot()+
     theme(plot.title = element_text(hjust = 0.5)) 
-
 #####
@@
 
+```{r Figures from Pasa SCFM2 Paper}
+#Biomass contribution of Planktonic vs Aggregates
+#####
+#Collapse dataframe to values per condition
+plankAggHistSummary<-plankAggHist %>% group_by(Species,TimePoint, Condition,Aggregation) %>%
+  summarise(MeanFreq = mean(AgPlNormFrequency), SEFreq = std.error(AgPlNormFrequency), MeanBiomass = mean(AgPlNormBiomass),
+            SEBiomass = std.error(AgPlNormBiomass))
+#Plot using the code from the paper
+ggplot()+
+  geom_col(data = plankAggHistSummary,aes(x=Aggregation,y=MeanBiomass, fill = TimePoint),
+           size=3,position = position_dodge( width = .9))+
+  geom_jitter(data = plankAggHist,aes(x=Aggregation,y=AgPlNormBiomass, group = TimePoint),shape = 1,size=2,position = position_dodge(width = .9),show.legend = FALSE)+
+  geom_errorbar(data = plankAggHistSummary,aes(x=Aggregation,ymin=(MeanBiomass-SEBiomass), ymax = (MeanBiomass+SEBiomass), group = TimePoint),width = 0, size=.5,position = position_dodge(width = .9))+
+  scale_y_continuous(limits = c(0,103),expand = expand_scale(mult = c(0, 0)))+
+  facet_grid(.~Species)+
+  scale_fill_grey()+
+  labs(title = '', x = "", y = "Biomass contribution (%)")+
+  theme_cowplot()+
+  theme(plot.title = element_text(hjust = 0.5),strip.text = element_text(size = 9, face = "italic",margin = margin(.1,0,.1,0, "cm")),
+        strip.background = element_rect(color="black", fill="white", size=.5, linetype="solid"),
+        axis.title.x = element_text(margin = margin(0,0,0,0),size=13),axis.text.x = element_text(margin = margin(1,0,0,0),size=13),
+        axis.title.y = element_text(margin = margin(0,4,0,0),size=13),axis.text.y = element_text(margin = margin(0,0,2,0),size=11),
+        legend.title = element_text(size=13),legend.text = element_text(size = 11),
+          legend.position = c(0.79, 0.60))
+#####
+#Normalized Frequency and Biomass contribution of Aggregate bins
+#####
+#Collapse to data per condition
+AggsOnlySummary<-aggsOnlyHistSummary.df %>% group_by(Species,TimePoint, Condition,LogBin) %>%
+  summarise(MeanFreq = mean(NormalizedFrequency), SEFreq = std.error(NormalizedFrequency), MeanBiomass = mean(NormalizedBiomass),
+            SEBiomass = std.error(NormalizedBiomass))
+#Plot Frequency using code from the paper
+ggplot()+
+    geom_col(data = AggsOnlySummary, aes(x=as.factor(LogBin),y=MeanFreq,  fill =TimePoint ),size=4,position = position_dodge( width = .9))+
+    geom_jitter(data = aggsOnlyHistSummary.df, aes(x=as.factor(LogBin),y=NormalizedFrequency, group = TimePoint),shape = 1,size=2,position = position_dodge( width = .9))+
+    geom_errorbar(data = AggsOnlySummary,aes(x=as.factor(LogBin),ymin=(MeanFreq-SEFreq), ymax = (MeanFreq+SEFreq), group = TimePoint),width = 0, size= .5,position = position_dodge( width = .9))+
+    facet_grid(.~Species)+
+    labs(fill = "",y = "Aggregates per bin (% of total)",x = bquote(paste("Aggregate Volume (", mu*"m"^3*")")))+
+    #guides(color = FALSE)+
+    scale_y_continuous(limits = c(0,70), expand = expand_scale(mult = c(0, 0)))+
+    scale_fill_grey()+
+    theme_half_open()+
+    theme(plot.title = element_text(hjust = 0.5),
+          strip.text = element_text(size = 9, face = "italic",margin = margin(.1,0,.1,0, "cm")),#this is for the facets
+          strip.background = element_rect(color="black", fill="white", size=.5, linetype="solid"),
+          plot.margin = unit(c(0,.5,0,.5), "cm"),
+          axis.title.x = element_text(margin = margin(0,0,0,0),size=13),axis.text.x = element_text(margin = margin(1,0,0,0),size=11),
+          axis.title.y = element_text(margin = margin(0,4,0,0),size=13),axis.text.y = element_text(margin = margin(0,2,2,0),size=11),
+          legend.title = element_text(size=13),legend.text = element_text(size = 11),
+          legend.position = c(0.79, 0.60))
+#Plot Normalized Biomass
+ggplot()+
+    geom_col(data = AggsOnlySummary, aes(x=as.factor(LogBin),y=MeanBiomass,  fill =TimePoint ),size=4,position = position_dodge( width = .9))+
+    #geom_jitter(data = aggsOnlyHistSummary.df, aes(x=as.factor(LogBin),y=NormalizedBiomass, group = TimePoint),shape = 1,size=2,position = position_dodge( width = .9))+
+    geom_errorbar(data = AggsOnlySummary,aes(x=as.factor(LogBin),ymin=(MeanBiomass-SEBiomass), ymax = (MeanBiomass+SEBiomass), group = TimePoint),width = 0, size= .5,position = position_dodge( width = .9))+
+    facet_grid(.~Species)+
+    labs(fill = "",y = "Aggregates per bin (% of total)",x = bquote(paste("Aggregate Volume (", mu*"m"^3*")")))+
+    #guides(color = FALSE)+
+    scale_y_continuous(limits = c(0,100), expand = expand_scale(mult = c(0, 0)))+
+    scale_fill_grey()+
+    theme_half_open()+
+    theme(plot.title = element_text(hjust = 0.5),
+          strip.text = element_text(size = 9, face = "italic",margin = margin(.1,0,.1,0, "cm")),#this is for the facets
+          strip.background = element_rect(color="black", fill="white", size=.5, linetype="solid"),
+          plot.margin = unit(c(0,.5,0,.5), "cm"),
+          axis.title.x = element_text(margin = margin(0,0,0,0),size=13),axis.text.x = element_text(margin = margin(1,0,0,0),size=11),
+          axis.title.y = element_text(margin = margin(0,4,0,0),size=13),axis.text.y = element_text(margin = margin(0,2,2,0),size=11),
+          legend.title = element_text(size=13),legend.text = element_text(size = 11),
+          legend.position = c(0.79, 0.60))
+#####
+```
 ```{r fancy histogram of aggregates}
@@
 #this was taken from "Microscopy data clean.Rmd"
-GetResults<-function(sample,){#points to folder with files. Folder is hardcoded, unfortunately
-  #folder<- paste0('/Volumes/raw_data/Confocal/Carolyn/2020/Chronic wounds/Binary Images/', sample)
+GetResults<-function(){
   folder<- paste0('/Volumes/raw_data/Confocal/Carolyn/2020/Chronic wounds/Binary Images/wtd1-02')
   fileList<-list.files(path = folder, full.names = TRUE)
-  growthDf<-data.frame()
   blueChannel<-fileList[grep('B_',fileList)]
-  for(slice in 1:length(filesList)/3){
-    counts<-sum(as.array(readImage(fileList[1], convert = TRUE)))
-    growthDf<-rbind(growthDf,c(counts, slice,species))
-    growthDf<-growthDf %>% mutate(Sample = samplename)
+  redChannel<-fileList[grep('R_',fileList)]
+  greenChannel<-fileList[grep('G_',fileList)]
+  Results<-rbind(blueChannel,redChannel,greenChannel)
+  Results<-Results %>% mutate(Sample = sample)
+IterateTiff<-function(fileList, species)
+  growth<-matrix(ncol=3, nrow=length(fileList))
+  for(slice in 1:(length(fileList))){
+    counts<-sum(as.array(readImage(fileList[slice], convert = TRUE)))
+    growth[slice,]<-c(counts, slice, species)
+  }
+  growthDf<-data.fram(growth)
 return(growthDf) 
-} }
+  }
+
+testGetResults<-GetResults()
+testGetResults.df<- data.frame(testGetResults)
 #this was taken from the PropOc package

### 2021-06-22 Matlab/adaptiveThreshold.m
updated to take tiffs from Imaris

@@ -1,4 +1,4 @@
-rawTifPathBase = '/Volumes/raw_data/Confocal/Carolyn/2020/Chronic wounds/Tiff Stacks/';
+rawTifPathBase = '/Volumes/raw_data/Confocal/Carolyn/2020/Chronic wounds/Tiff Stacks New/';
 binTifPathBase = '/Volumes/raw_data/Confocal/Carolyn/2020/Chronic wounds/Binary Images/';
 aggsFilePathBase = '/Volumes/raw_data/Confocal/Carolyn/2020/Chronic wounds/Aggregate lists/'; %names are different
 slicedAggsFilePathBase = '/Volumes/raw_data/Confocal/Carolyn/2020/Chronic wounds/Results per slice/'; %names are different
@@ -19,10 +19,10 @@ Tiff2Data (rawTifPath,binTifPath,aggsFilePath);
 end
 %}
 
-rawTifPath = [rawTifPathBase,'phzd1-07/'];
-binTifPath = [binTifPathBase,'phz_d1_07/'];
-aggsFilePath = [aggsFilePathBase,'phz_d1_07'];
-slicedAggsFilePath = [slicedAggsFilePathBase,'phz_d1_07'];
+rawTifPath = [rawTifPathBase,'monod4-01/'];
+binTifPath = [binTifPathBase,'mono_d4_01/'];
+aggsFilePath = [aggsFilePathBase,'mono_d4_01'];
+slicedAggsFilePath = [slicedAggsFilePathBase,'mono_d4_01'];
 Tiff2Data (rawTifPath,binTifPath,aggsFilePath,slicedAggsFilePath);
 
 
@@ -43,7 +43,7 @@ disp('combining and saving')
 
 %now remove bleeding from red into the green channel and isolated pixels and create a clean volume
 %%!!!Order is really important here, it is input as red, green blue, but matlab doesnt let you do it in the actual function
-[cleanRed, cleanGreen, cleanBlue] = CleanExportVolume(binTifPath, filtered3,filtered1, filtered2, slicedAggsPath);
+[cleanRed, cleanGreen, cleanBlue] = CleanExportVolume(binTifPath, filtered1,filtered2, filtered3, slicedAggsPath);
 %Use clean volumes created to get aggregate sizes
 toc
 disp('creating aggregate structure red');

### 2021-06-22 Matlab/adaptiveThreshold.m
deprecated functions

@@ -154,7 +154,7 @@ end
 end
 
 
-
+%deprecated functions
 function threshold = CollectThresholds(volume)
 [~,~,slices]=size(volume);
 totalCounts = 0;

### 2021-06-22 R/readTiff.R

@@ -1,0 +1,57 @@
+"readTiff" <-
+function(fn, page=0, reduce=0, pixmap=TRUE) {
+  w <- integer(1)
+  h <- integer(1)
+
+  w <- .C("C_TiffGetWidth", as.character(fn), w=as.integer(w), PACKAGE="rtiff")$w
+  h <- .C("C_TiffGetHeight", as.character(fn), h=as.integer(h), PACKAGE="rtiff")$h
+  nw <- ceiling((1-reduce)*w)
+  nh <- ceiling((1-reduce)*h)
+  if (w > 0 && h > 0) {
+    r <- integer(w * h)
+    g <- integer(w * h)
+    b <- integer(w * h)
+
+    spp <- integer(1);
+    pm <- integer(1);
+    bps <- integer(1);
+    tiled <- integer(1);
+
+      tiff <- .C("C_TiffReadTIFFRGBA", as.character(fn), page=page, r=as.integer(r), g=as.integer(g), b=as.integer(b), PACKAGE="rtiff");
+      if(reduce < 1) {
+        rr <- integer(nw * nh)
+        rg <- integer(nw * nh)
+        rb <- integer(nw * nh)
+        tiff$r <- .C("C_reduce", as.integer(tiff$r), rr=as.integer(rr), as.integer(w), as.integer(h), as.double(reduce), PACKAGE="rtiff")$rr
+        tiff$g <- .C("C_reduce", as.integer(tiff$g), rg=as.integer(rg), as.integer(w), as.integer(h), as.double(reduce), PACKAGE="rtiff")$rg
+        tiff$b <- .C("C_reduce", as.integer(tiff$b), rb=as.integer(rb), as.integer(w), as.integer(h), as.double(reduce), PACKAGE="rtiff")$rb
+      }
+
+      r <- matrix(tiff$r, nrow=nh, ncol=nw, byrow=TRUE)
+      g <- matrix(tiff$g, nrow=nh, ncol=nw, byrow=TRUE)
+      b <- matrix(tiff$b, nrow=nh, ncol=nw, byrow=TRUE)
+      rm(tiff);
+     
+      rmx <- max(r)
+      gmx <- max(g)
+      bmx <- max(b)
+      rm(rr)
+      rm(rg)
+      rm(rb)
+
+      if(pixmap) {
+            pmap <- pixmapRGB(data=array(data = c(r, g, b), dim = c(nh, nw, 3)), nrow=nh, ncol=nw,
[…]

### 2021-06-22 Matlab/adaptiveThreshold.m
added the voxel size to pipeline and correction for wiener filtersize

@@ -18,26 +18,30 @@ aggsFilePath = [aggsFilePathBase,'wt_d4_',GetNum(image)];
 Tiff2Data (rawTifPath,binTifPath,aggsFilePath);
 end
 %}
+for sampleName = 3:5
 
-rawTifPath = [rawTifPathBase,'monod4-01/'];
-binTifPath = [binTifPathBase,'mono_d4_01/'];
-aggsFilePath = [aggsFilePathBase,'mono_d4_01'];
-slicedAggsFilePath = [slicedAggsFilePathBase,'mono_d4_01'];
-Tiff2Data (rawTifPath,binTifPath,aggsFilePath,slicedAggsFilePath);
+rawTifPath = [rawTifPathBase,'mono_d4_',GetNum(sampleName),'/'];
+binTifPath = [binTifPathBase,'mono_d4_',GetNum(sampleName),'/'];
+aggsFilePath = [aggsFilePathBase,'mono_d4_',GetNum(sampleName)];
+slicedAggsFilePath = [slicedAggsFilePathBase,'mono_d4_',GetNum(sampleName)];
+xySize = .415; %.208 or .132
+zSize = .52; %.365 or .361
+Tiff2Data (rawTifPath,binTifPath,aggsFilePath,slicedAggsFilePath, xySize, zSize);
+end
 
-
-function Tiff2Data (rawTifPath,binTifPath, aggsFilePath,slicedAggsPath)
+function Tiff2Data (rawTifPath,binTifPath, aggsFilePath,slicedAggsPath, xySize, zSize)
+wienerSize = ceil(5/xySize); %image filter neighborhod set at 5 microns
 tic
 [ch1,ch2,ch3] = Stack2volume(rawTifPath);%split the image by the 3 channels.
 toc
 disp('filtering and stretching channel 1')
-filtered1 = imbinarize(FilterImage(ch1));
+filtered1 = imbinarize(FilterImage(ch1, wienerSize));
 toc
 disp('filtering and stretching channel 2')
-filtered2 = imbinarize(FilterImage(ch2));
+filtered2 = imbinarize(FilterImage(ch2, wienerSize));
 toc
 disp('filtering and stretching channel 3')
-filtered3 = imbinarize(FilterImage(ch3));
+filtered3 = imbinarize(FilterImage(ch3, wienerSize));
 toc
 disp('combining and saving')
 
@@ -47,13 +51,12 @@ disp('combining and saving')
[…]

### 2021-06-22 Matlab/adaptiveThreshold.m
added function to parent function to run samples

@@ -1,32 +1,44 @@
+%{
 rawTifPathBase = '/Volumes/raw_data/Confocal/Carolyn/2020/Chronic wounds/Tiff Stacks New/';
 binTifPathBase = '/Volumes/raw_data/Confocal/Carolyn/2020/Chronic wounds/Binary Images/';
 aggsFilePathBase = '/Volumes/raw_data/Confocal/Carolyn/2020/Chronic wounds/Aggregate lists/'; %names are different
 slicedAggsFilePathBase = '/Volumes/raw_data/Confocal/Carolyn/2020/Chronic wounds/Results per slice/'; %names are different
 
-%{
-for image= 4:15
-rawTifPath = [rawTifPathBase,'wtd1-',GetNum(image),'/'];
-binTifPath = [binTifPathBase,'wt_d1_',GetNum(image),'/'];
-aggsFilePath = [aggsFilePathBase,'wt_d1_',GetNum(image)];
-Tiff2Data (rawTifPath,binTifPath,aggsFilePath);
-end
-
-for image= 1:6
-rawTifPath = [rawTifPathBase,'wtd4-',GetNum(image),'/'];
-binTifPath = [binTifPathBase,'wt_d4_',GetNum(image),'/'];
-aggsFilePath = [aggsFilePathBase,'wt_d4_',GetNum(image)];
-Tiff2Data (rawTifPath,binTifPath,aggsFilePath);
-end
-%}
-for sampleName = 3:5
-
-rawTifPath = [rawTifPathBase,'mono_d4_',GetNum(sampleName),'/'];
-binTifPath = [binTifPathBase,'mono_d4_',GetNum(sampleName),'/'];
-aggsFilePath = [aggsFilePathBase,'mono_d4_',GetNum(sampleName)];
-slicedAggsFilePath = [slicedAggsFilePathBase,'mono_d4_',GetNum(sampleName)];
+for sampleNumber = 1:2
+rawTifPath = [rawTifPathBase,'mono_d1_',GetNum(sampleNumber),'/'];
+binTifPath = [binTifPathBase,'mono_d1_',GetNum(sampleNumber),'/'];
+aggsFilePath = [aggsFilePathBase,'mono_d1_',GetNum(sampleNumber)];
+slicedAggsFilePath = [slicedAggsFilePathBase,'mono_d1_',GetNum(sampleNumber)];
 xySize = .415; %.208 or .132
 zSize = .52; %.365 or .361
[…]

### 2021-06-22 Matlab/adaptiveThreshold.m
getting ready for running without memory array limits

@@ -15,11 +15,7 @@ Tiff2Data (rawTifPath,binTifPath,aggsFilePath,slicedAggsFilePath, xySize, zSize)
 end
 %}
 
-for sampleNumber = 1:2
-iterateSamples('mono_d1_',sampleNumber,.415,.52)
-end
-
-for sampleNumber = 3:8
+for sampleNumber = 4:8
 iterateSamples('mono_d1_',sampleNumber,.208,.52)
 end
 
@@ -38,6 +34,7 @@ rawTifPath = [rawTifPathBase,sampleName,GetNum(sampleNum),'/'];
 binTifPath = [binTifPathBase,sampleName,GetNum(sampleNum),'/'];
 aggsFilePath = [aggsFilePathBase,sampleName,GetNum(sampleNum)];
 slicedAggsFilePath = [slicedAggsFilePathBase,sampleName,GetNum(sampleNum)];
+disp(['Sample ',sampleName,GetNum(sampleNum)])
 Tiff2Data (rawTifPath,binTifPath,aggsFilePath,slicedAggsFilePath, xy, z);
 end
 
@@ -48,12 +45,15 @@ tic
 toc
 disp('filtering and stretching channel 1')
 filtered1 = imbinarize(FilterImage(ch1, wienerSize));
+clear ch1
 toc
 disp('filtering and stretching channel 2')
 filtered2 = imbinarize(FilterImage(ch2, wienerSize));
+clear ch2
 toc
 disp('filtering and stretching channel 3')
 filtered3 = imbinarize(FilterImage(ch3, wienerSize));
+clear ch3
 toc
 disp('combining and saving')
 
@@ -84,6 +84,7 @@ for slice= 1:slices
     weinerImage = wiener2(stretchedImg, [wienerSize wienerSize]);%smooths image when it's low contrast and leaves it if high contrast
     filteredVolume(:,:,slice)= weinerImage;
 end
+clear volume %empty original volume from memory
 end
 
 function [ch1Volume, ch2Volume, ch3Volume] = Stack2volume(directory)%takes a folder with tiffs and returns a 3d-volume/matrix

### 2021-06-22 R/AggregateCounts.Rmd
trying to setup biomass per slice here

@@
 ```
-```{r fancy histogram of aggregates}
+```{r fancy histogram of aggregates !!!deprecated}
 #Create histograms
@@
 GetResults<-function(){
-  folder<- paste0('/Volumes/raw_data/Confocal/Carolyn/2020/Chronic wounds/Binary Images/wtd1-02')
-  fileList<-list.files(path = folder, full.names = TRUE)
+  folder<- '/Volumes/raw_data/Confocal/Carolyn/2020/Chronic wounds/Binary Images'
+  samplesList<-list.files(path = folder, full.names = TRUE)
+  imagesList<-mapply(list.files,samplesList)
+
+separateColors
   blueChannel<-fileList[grep('B_',fileList)]
@@
   Results<-Results %>% mutate(Sample = sample)
+
+   fileList<-list.files(path = folder, full.names = TRUE)
+   growthDf<-data.frame()
+   for (aggList in 1:length(fileList)){
+     fileName<-str_split(basename(fileList[aggList]), "\\.")[[1]][1]#this selects the base file name and removes the ".csv"
+     attrList<-str_split(fileName,"_")[[1]]
+     growthDf<-rbind(growthDf,ReadAggregateFile(fileList[aggList],attrList[4],attrList[2],attrList[1],attrList[3]))
+     }
+   return(growthDf)
+}
+
+  VectorizeTiff<-function(file){
+    counts<-sum(as.array(readImage(fileList[slice], convert = TRUE)))
+    growth[slice,]<-c(counts, slice, species)
+  }
+
   IterateTiff<-function(fileList, species)

### 2021-06-25 R/AggregateCounts.Rmd
Added functions for plotting basica aggregates distributions for all the strains

@@
 library(EBImage) #for rtiff
+```
 
+```{r aggregate input}
 aggregateList<-GetAggregates()#this reads the data from Matlab
 # mutate(Strain = recode(Position, "0" = "Pa14 wt", "1"= "Pa14 -PA1414","2" = "Pa14 wt", "3"= "Pa14 -PA1414")) #this is to change the names
+removable <- aggregateList %>% filter(Species == "Pa" & Condition == "mono")
+aggregateList <- anti_join(aggregateList, removable)
 
@@
 ReadAggregateFile<-function(file, species, timepoint, condition, replicate){#make a dataframe of the aggregate size list and add experimental parameters
+  print(file)
    datos <-read.csv(file, header = F)  
@@
 ```
-```{r aggregate wrangling}
+```{r aggregate wrangling and overview plots}
 #Statistics from all aggregates
@@
 #Get aggregate summary per sample
-aggregateListSummaryReplicate<-aggregateList %>% group_by(Species, TimePoint, Condition, Replicate) %>% 
+aggregateListSummaryReplicate<-aggregateList%>% group_by(Species, TimePoint, Condition, Replicate) %>% 
   summarise(Aggs = n(), biomass = sum(Size), meanAggSize = mean(Size), seAggSize = std.error(Size), maxSize = max(Size), minSize = min(Size)) %>%
@@
   ggtitle('Mean size and largest aggregate and total biomass per sample')+
-  labs(x = "",y = "um3")+
+  labs(x = "",y = bquote(paste("Volume (", mu*"m"^3*")")))+
   scale_shape_manual(name="Metric",values=c(MeanSize=1, MaxSize=2, TotalBiomass=17))+
@@
 
-#this pipe essentially gets to the producto of what fancy histograms do but more efficiently
+#this pipe essentially gets to the product of what fancy histograms do but more efficiently
 #First including all sizes
 #####
-newHistogram.df<-aggregateList %>% mutate(LogBin = case_when(Size <= 5 ~ 5,
+
+#There are two ways to normalize the Bin Frequncy and Bin Biomass, per condition and per sample, so I'll do both
+#First per replicate:
+HistReplicate<-aggregateList %>% mutate(LogBin = case_when(Size <= 5 ~ 5,
                         Size<= 10 ~ 10,
@@
 #This is weird, but I want to have the histogram above with all the data, and the one below with only the bins
-newHistogramSummary.df<-newHistogram.df %>% group_by(Species,Condition,TimePoint, Replicate, LogBin,NormalizedFrequency,NormalizedBiomass) %>% summarize() %>%  unique()%>%ungroup() %>%  group_by(Species,Condition,TimePoint, Replicate) %>% mutate(checkSumFreq =sum(NormalizedFrequency), checkSumBiomass = sum(NormalizedBiomass))
+HistReplicateSummary<-HistReplicate %>% group_by(Species,Condition,TimePoint, Replicate, LogBin,NormalizedFrequency,NormalizedBiomass) %>% summarize() %>%  unique()%>%ungroup() %>%  group_by(Species,Condition,TimePoint, Replicate) %>% mutate(checkSumFreq =sum(NormalizedFrequency), checkSumBiomass = sum(NormalizedBiomass))
+
+#Now per condition. The difference is int the "group_by" part
+HistCondition<-aggregateList %>% mutate(LogBin = case_when(Size <= 5 ~ 5,
+                        Size<= 10 ~ 10,
+                        Size<= 100    ~ 100,
+                        Size<= 1000   ~ 1000,
+                        Size<= 10000  ~ 10000,
+                        Size<= 100000 ~ 100000,
+                        Size > 100000 ~ 1000000)) %>% group_by(Species,Condition,TimePoint)%>% 
+  mutate(TotalBiomass = sum(Size), TotalFrequency = n()) %>% ungroup() %>%
+  group_by(Species,Condition,TimePoint,LogBin)%>%
+  mutate(BinBiomass = sum(Size), BinFrequency = n()) %>% ungroup() %>%
+  mutate(NormalizedFrequency = BinFrequency/TotalFrequency*100, NormalizedBiomass = BinBiomass/TotalBiomass*100)
+
+#Summary data frame
+HistConditionSummary<-HistCondition %>%
+  group_by(Species,Condition,TimePoint,LogBin,NormalizedFrequency,NormalizedBiomass) %>% summarize() %>% 
+  unique()%>%ungroup() %>%  group_by(Species,Condition,TimePoint) %>% 
+  mutate(checkSumFreq =sum(NormalizedFrequency), checkSumBiomass = sum(NormalizedBiomass))
 
 #Plot Normalized Frequency
+#this isn't useful as the normalized Frequency changes with replicate, so it's better to pool all samples together
+PlotHistSum<-function(rep.df,cond.df, y_var, title){
 ggplot()+
-    geom_jitter(data = newHistogramSummary.df,aes(x=as.factor(LogBin),y=NormalizedFrequency,  color =Species, ),size=3, height = 0, width = .2)+
+    geom_jitter(data = HistReplicateSummary,aes(x=as.factor(LogBin),y=.data[[y_var]],  color =Species ),size=3, height = 0, width = .2, shape = 1)+
+    geom_point(data = HistConditionSummary,aes(x=as.factor(LogBin),y=.data[[y_var]],  color =Species,group = Species),size=4, shape = 16, position = position_dodge(width = .3) )+
     scale_y_log10(breaks = c(100, 10, 1, .1, .01), labels = c(100, 10, 1, .1, .01))+
-    facet_grid(.~TimePoint)+
-    labs(y = "Normalized Frequency (%)",x = bquote(paste("Aggregate Volume (", mu*"m"^3*")")))+
+    facet_grid(Condition~TimePoint)+
+    ggtitle(title)+
+    labs(y = paste(y_var,"(%)"),x = bquote(paste("Aggregate Volume (", mu*"m"^3*")")))+
     theme_cowplot()+
     theme(plot.title = element_text(hjust = 0.5))
-#Plot Normalized Biomass
-ggplot()+
-    geom_jitter(data = newHistogramSummary.df,aes(x=as.factor(LogBin),y=NormalizedBiomass,  color =Species, ),size=3, height = 0, width = .2)+
-    scale_y_log10(breaks = c(100, 10, 1, .1, .01), labels = c(100, 10, 1, .1, .01))+
-    facet_grid(.~TimePoint)+
-    labs(y = "Normalized Biomass (%)",x = bquote(paste("Aggregate Volume (", mu*"m"^3*")")))+
-    theme_cowplot()+
-    theme(plot.title = element_text(hjust = 0.5))
+}
+
+PlotHistSum(HistReplicateSummary,HistConditionSummary,"NormalizedFrequency", "Normalized Frequency all sizes")
+
+PlotHistSum(HistReplicateSummary,HistConditionSummary,"NormalizedBiomass", "Normalized Biomass all sizes")
 
 #Plot normalized Biomass per sample
+##Pa
+PlotHistRepBioTrend<-function(rep.df,species){
 ggplot()+
-    geom_line(data = newHistogramSummary.df,aes(x=as.factor(LogBin),y=NormalizedBiomass, color = Replicate, group = Replicate ),size=1)+
-    #scale_y_log10(breaks = c(100, 10, 1, .1, .01), labels = c(100, 10, 1, .1, .01))+
+    geom_line(data = rep.df %>% filter(Species==species),aes(x=as.factor(LogBin),y=NormalizedBiomass, color = Replicate, group = Replicate ),size=1)+
     guides(color = FALSE)+
-    facet_grid(TimePoint~Species)+
+    facet_grid(Condition~TimePoint)+
     labs(y = "Normalized Biomass",x = bquote(paste("Aggregate Volume (", mu*"m"^3*")")))+
+    ggtitle(paste('Normalized Biomass per Sample', species))+
     theme_cowplot()+
     scale_colour_grey()+
-    theme(plot.title = element_text(hjust = 0.5)) 
+    theme(plot.title = element_text(hjust = 0.5)) }
+PlotHistRepBioTrend(HistReplicateSummary, "Pa")
+PlotHistRepBioTrend(HistReplicateSummary, "Sa")
+
 #####
@@
 #####
-aggsOnlyHist.df<-aggregateList %>% mutate(LogBin = case_when(Size <= 5 ~ 5,
+#Separating the replicates
+aggsHistRep<-aggregateList %>% mutate(LogBin = case_when(Size <= 5 ~ 5,
                         Size<= 10 ~ 10,
@@
 
-#This is weird, but I want to have the histogram above with all the data, and the one below with only the bins
-aggsOnlyHistSummary.df<-aggsOnlyHist.df %>% group_by(Species,Condition,TimePoint, Replicate, LogBin,NormalizedFrequency,NormalizedBiomass) %>% summarize() %>%  unique()%>%ungroup() %>%  group_by(Species,Condition,TimePoint, Replicate) %>% mutate(checkSumFreq =sum(NormalizedFrequency), checkSumBiomass = sum(NormalizedBiomass))
+##Summary df
+aggsHistRepSum<-aggsHistRep %>% group_by(Species,Condition,TimePoint, Replicate, LogBin,NormalizedFrequency,NormalizedBiomass) %>% summarize() %>%  unique()%>%ungroup() %>%  group_by(Species,Condition,TimePoint, Replicate) %>% mutate(checkSumFreq =sum(NormalizedFrequency), checkSumBiomass = sum(NormalizedBiomass))
+
+#Pooling replicates together
+aggsHistCond<-aggregateList %>% mutate(LogBin = case_when(Size <= 5 ~ 5,
+                        Size<= 10 ~ 10,
+                        Size<= 100    ~ 100,
+                        Size<= 1000   ~ 1000,
+                        Size<= 10000  ~ 10000,
+                        Size<= 100000 ~ 100000,
+                        Size > 100000 ~ 1000000)) %>% filter(!LogBin == 5) %>% group_by(Species,Condition,TimePoint)%>% 
+  mutate(TotalBiomass=sum(Size),TotalFrequency=n()) %>% ungroup() %>% group_by(Species,Condition,TimePoint, LogBin)%>%
+  mutate(BinBiomass = sum(Size), BinFrequency = n()) %>% ungroup() %>%
+  mutate(NormalizedFrequency = BinFrequency/TotalFrequency*100, NormalizedBiomass = BinBiomass/TotalBiomass*100)
+
+##Summary df
+aggsHistCondSum<-aggsHistCond %>% group_by(Species,Condition,TimePoint, Replicate, LogBin,NormalizedFrequency,NormalizedBiomass) %>% summarize() %>%  unique()%>%ungroup() %>%  group_by(Species,Condition,TimePoint, Replicate) %>% mutate(checkSumFreq =sum(NormalizedFrequency), checkSumBiomass = sum(NormalizedBiomass))
 
@@
 #normalized frequency
-ggplot()+
-    geom_jitter(data = aggsOnlyHistSummary.df,aes(x=as.factor(LogBin),y=NormalizedFrequency,  color =Species, ),size=3, height = 0, width = .2)+
-    scale_y_log10(breaks = c(100, 10, 1, .1, .01), labels = c(100, 10, 1, .1, .01))+
-    facet_grid(.~TimePoint)+
-    labs(y = "Normalized Frequency (%)",x = bquote(paste("Aggregate Volume (", mu*"m"^3*")")))+
-    theme_cowplot()+
-    theme(plot.title = element_text(hjust = 0.5)) 
-#Normalized Biomass facet timepoint, color species
-ggplot()+
-    geom_jitter(data = aggsOnlyHistSummary.df,aes(x=as.factor(LogBin),y=NormalizedBiomass,  color =Species, ),size=3, height = 0, width = .2)+
-    scale_y_log10(breaks = c(100, 10, 1, .1, .01), labels = c(100, 10, 1, .1, .01))+
-    facet_grid(.~TimePoint)+
-    labs(y = "Normalized Biomass (%)",x = bquote(paste("Aggregate Volume (", mu*"m"^3*")")))+
-    theme_cowplot()+
-    theme(plot.title = element_text(hjust = 0.5)) 
-#Normalized Biomass facet species, color timepoint
-ggplot()+
-    geom_jitter(data = aggsOnlyHistSummary.df,aes(x=as.factor(LogBin),y=NormalizedBiomass,  color =TimePoint, ),size=3, height = 0, width = .2)+
-    #scale_y_log10(breaks = c(100, 10, 1, .1, .01), labels = c(100, 10, 1, .1, .01))+
-    facet_grid(.~Species)+
-    labs(y = "Normalized Biomass",x = bquote(paste("Aggregate Volume (", mu*"m"^3*")")))+
-    theme_cowplot()+
-    theme(plot.title = element_text(hjust = 0.5)) 
-#Normalized Biomass facet species and Timepoint, color Replicate
-ggplot()+
-    geom_line(data = aggsOnlyHistSummary.df,aes(x=as.factor(LogBin),y=NormalizedBiomass, color = Replicate, group = Replicate ),size=1)+
-    #scale_y_log10(breaks = c(100, 10, 1, .1, .01), labels = c(100, 10, 1, .1, .01))+
-    guides(color = FALSE)+
-    facet_grid(TimePoint~Species)+
-    labs(y = "Normalized Biomass",x = bquote(paste("Aggregate Volume (", mu*"m"^3*")")))+
-    theme_cowplot()+
-    scale_colour_grey()+
-    theme(plot.title = element_text(hjust = 0.5))
+
+PlotHistSum(aggsHistRepSum,aggsHistCondSum,"NormalizedFrequency", "Normalized Frequency aggregates only")
+PlotHistSum(aggsHistRepSum,aggsHistCondSum,"NormalizedBiomass","Normalized Biomass aggregates only")
+PlotHistRepBioTrend(aggsHistRepSum, "Pa")
+PlotHistRepBioTrend(aggsHistRepSum, "Sa")
 
@@
 #Add agregation value to the dataframe
-newHistogram.df<-newHistogram.df %>%  mutate(Aggregation = case_when(LogBin == 5 ~ "Planktonic",LogBin>5 ~ "Aggregate")) %>%
+##Normalize using replicates
+HistReplicate<-HistReplicate %>%  mutate(Aggregation = case_when(LogBin == 5 ~"Planktonic",LogBin>5 ~ "Aggregate")) %>%
   group_by(Species,Condition,TimePoint, Replicate, Aggregation)%>% 
@@
 #Collapse to only values per replicate
-plankAggHist<-newHistogram.df %>% group_by(Species,Condition,TimePoint, Replicate, Aggregation,AgPlNormFrequency,AgPlNormBiomass) %>% summarize() %>%  unique()%>%ungroup() %>%  group_by(Species,Condition,TimePoint, Replicate) %>% mutate(checkAggFreq =sum(AgPlNormFrequency), checkAggBiomass = sum(AgPlNormBiomass))
-#plot Frequency
+plankAggHistRep<-HistReplicate %>% group_by(Species,Condition,TimePoint, Replicate, Aggregation,AgPlNormFrequency,AgPlNormBiomass) %>% summarize() %>%  unique()%>%ungroup() %>%  group_by(Species,Condition,TimePoint, Replicate) %>% mutate(checkAggFreq =sum(AgPlNormFrequency), checkAggBiomass = sum(AgPlNormBiomass))
+
+##Normalize using Condition
+HistCondition<-HistCondition %>%  mutate(Aggregation = case_when(LogBin == 5 ~"Planktonic",LogBin>5 ~ "Aggregate")) %>%
+  group_by(Species,Condition,TimePoint, Aggregation)%>% 
+  mutate(AgPlBiomass = sum(Size), AgPlFreq = n()) %>% ungroup() %>%
+  mutate(AgPlNormFrequency = AgPlFreq/TotalFrequency*100, AgPlNormBiomass = AgPlBiomass/TotalBiomass*100)
+#Collapse to only values per replicate
+plankAggHistCond<-HistCondition %>% group_by(Species,Condition,TimePoint, Aggregation,AgPlNormFrequency,AgPlNormBiomass) %>% summarize() %>%  unique()%>%ungroup() %>%  group_by(Species,Condition,TimePoint) %>% mutate(checkAggFreq =sum(AgPlNormFrequency), checkAggBiomass = sum(AgPlNormBiomass))
+
+#Plot Frequency
 ggplot()+
-    geom_jitter(data = plankAggHist,aes(x=as.factor(Aggregation),y=AgPlNormFrequency,  color =Species, ),size=3, height = 0, width = .2)+ 
-    #scale_y_log10(breaks = c(100, 10, 1, .1, .01), labels = c(100, 10, 1, .1, .01))+
-    facet_grid(.~TimePoint)+
+  geom_jitter(data = plankAggHistRep,aes(x=as.factor(Aggregation),y=AgPlNormFrequency,  color =Species, ),size=3, height = 0, width = .2, shape = 1)+ 
+  geom_point(data = plankAggHistCond,aes(x=as.factor(Aggregation),y=AgPlNormFrequency,  color =Species,group = Species),size=4, shape = 16, position = position_dodge(width = .3) )+
+  facet_grid(Condition~TimePoint)+
+  ggtitle("Normalized Frequency (%) Aggs vs Plank")+
   labs(y = "Normalized Frequency (%)",x = bquote(paste("Aggregate Volume (", mu*"m"^3*")")))+
-    theme_cowplot()+
+  theme_half_open()+
+  panel_border() +
+  #background_grid(major = "y")+
   theme(plot.title = element_text(hjust = 0.5)) 
@@
 ggplot()+
-    geom_jitter(data = plankAggHist,aes(x=as.factor(Aggregation),y=AgPlNormBiomass,  color =Species, ),size=3, height = 0, width = .2)+
-    #scale_y_log10(breaks = c(100, 10, 1, .1, .01), labels = c(100, 10, 1, .1, .01))+
-    facet_grid(.~TimePoint)+
-    labs(y = "Normalized Biomass (%)",x = bquote(paste("Aggregate Volume (", mu*"m"^3*")")))+
+    geom_jitter(data = plankAggHistRep,aes(x=as.factor(Aggregation),y=AgPlNormBiomass,  color =Condition ),size=2, height = 0, width = .2, shape = 1)+
+  geom_jitter(data = plankAggHistCond,aes(x=as.factor(Aggregation),y=AgPlNormBiomass,  color =Condition,group = Species),size=5, shape = 16,height = 0, width = .2) +
+    facet_grid(Species~TimePoint)+
+  ggtitle("Normalized Biomass (%) Aggs vs Plank")+
+    labs(y = "Normalized Biomass (%)",x = bquote(paste("Aggregate Volume (", mu*"m"^3*")")))+  scale_color_manual( values = c( "red","blue","green", "gray"),labels = c("Sa Mono", "phz co", "pqsL co", "wt co"))+
     theme_cowplot()+
+    panel_border() +
     theme(plot.title = element_text(hjust = 0.5)) 

### 2021-06-28 R/AggregateCounts.Rmd
Added code to remove bad samples, labels, compared across conditions and not species and color palette

@@
 aggregateList<-GetAggregates()#this reads the data from Matlab
-# mutate(Strain = recode(Position, "0" = "Pa14 wt", "1"= "Pa14 -PA1414","2" = "Pa14 wt", "3"= "Pa14 -PA1414")) #this is to change the names
+#remove bad samples and irrelevant conditions
+##first remove irrelevant conditions
 removable <- aggregateList %>% filter(Species == "Pa" & Condition == "mono")
 aggregateList <- anti_join(aggregateList, removable)
+##bad samples
+aggregateListRemoved<-aggregateList %>% filter(!SampleCode == "mono_d1_03_Pa" & !SampleCode == "mono_d1_03_Sa")
+aggregateListRemoved<-aggregateList %>% filter(!SampleCode == "phz_d4_14_Pa" & !SampleCode == "phz_d4_14_Sa")
+aggregateListRemoved<-aggregateList %>% filter(!SampleCode == "pqsL_d4_02_Pa" & !SampleCode == "pqsL_d4_02_Sa")
+aggregateListRemoved<-aggregateList %>% filter(!SampleCode == "pqsL_d4_04_Pa" & !SampleCode == "pqsL_d4_04_Sa")
+aggregateListRemoved<-aggregateList %>% filter(!SampleCode == "pqsL_d4_10_Pa" & !SampleCode == "pqsL_d4_10_Sa")
+aggregateListRemoved<-aggregateList %>% filter(!SampleCode == "wt_d4_07_Pa" & !SampleCode == "wt_d4_07_Sa")
 
+#add proper labels for plots
+aggregateList$Species <- factor(aggregateList$Species, levels = c("Pa", "Sa"),labels = c('P. aeruginosa','S. aureus'))
+aggregateList$Condition <- factor(aggregateList$Condition, levels = c("mono", "wt", "pqsL", "phz"),labels = c('Sa mono','wt co', 'pqsL co', 'phz co'))
+aggregateList$TimePoint <- factor(aggregateList$TimePoint, levels = c("d1", "d4"),labels = c('Day 1','Day 4'))
 #agregate input functions
-#####
-ReadAggregateFile<-function(file, species, timepoint, condition, replicate){#make a dataframe of the aggregate size list and add experimental parameters
+ReadAggregateFile<-function(file, species, timepoint, condition, replicate, sampleCode){#make a dataframe of the aggregate size list and add experimental parameters
   print(file)
@@
    datos<-datos %>% mutate(Replicate = replicate)
+   datos<-datos %>% mutate(SampleCode = sampleCode)
    datos$Species<-as.factor(datos$Species)
@@
 }
-
 GetAggregates<-function(){#import all experiments at once
@@
      attrList<-str_split(fileName,"_")[[1]]
-     growthDf<-rbind(growthDf,ReadAggregateFile(fileList[aggList],attrList[4],attrList[2],attrList[1],attrList[3]))
+     growthDf<-rbind(growthDf,ReadAggregateFile(fileList[aggList],attrList[4],attrList[2],attrList[1],attrList[3], fileName))
      }
@@
 }
-#####
 ```
+
 ```{r aggregate wrangling and overview plots}
@@
 #####
+
 ggplot()+ 
-  geom_jitter(data = aggregateListSummaryReplicate, aes(x = TimePoint, y= meanAggSize, color = Species,shape = "MeanSize"),size = 3, height = 0, width = .1)+
-  geom_jitter(data = aggregateListSummaryReplicate, aes(x = TimePoint, y= maxSize, color = Species, shape = "MaxSize"),size = 3, height = 0, width = .1)+
-  geom_jitter(data = aggregateListSummaryReplicate, aes(x = TimePoint, y= biomass, color = Species, shape = "TotalBiomass"),size = 3, height = 0, width = .1)+  
+  geom_jitter(data = aggregateListSummaryReplicate, aes(x = TimePoint, y= meanAggSize, color = Condition,shape = "MeanSize"),size = 3, height = 0, width = .3)+
+  geom_jitter(data = aggregateListSummaryReplicate, aes(x = TimePoint, y= maxSize, color = Condition, shape = "MaxSize"),size = 3, height = 0, width = .3)+
+  geom_jitter(data = aggregateListSummaryReplicate, aes(x = TimePoint, y= biomass, color = Condition, shape = "TotalBiomass"),size = 3, height = 0,width= .3)+
   scale_y_log10( breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
-  facet_grid(. ~ Condition, scales = "free", space = "free") +
+  facet_grid(.~Species, scales = "free", space = "free") +
   ggtitle('Mean size and largest aggregate and total biomass per sample')+
@@
   scale_shape_manual(name="Metric",values=c(MeanSize=1, MaxSize=2, TotalBiomass=17))+
+  scale_color_brewer(palette = "Set1")+
   theme_cowplot()+
-  theme(plot.title = element_text(hjust = 0.5))
+  panel_border() +
+  theme(plot.title = element_text(hjust = 0.5), 
+        strip.text = element_text(size = 11, face = "italic",margin = margin(.1,0,.1,0, "cm")),#this is for the facet text
+        strip.background = element_rect(color="black", fill="white", size=1, linetype="solid"))#facet background
+
 #####
@@
 ggplot()+ 
-  geom_jitter(data = aggregateListSummary, aes(x = TimePoint, y= meanAggSize, color = Species,shape = "MeanSize"),size = 3, height = 0, width = .1)+
-  geom_jitter(data = aggregateListSummary, aes(x = TimePoint, y= maxSize, color = Species, shape = "MaxSize"),size = 3, height = 0, width = .1)+
-  geom_jitter(data = aggregateListSummary, aes(x = TimePoint, y= biomass, color = Species, shape = "TotalBiomass"),size = 3, height = 0, width = .1)+ 
+  geom_jitter(data = aggregateListSummary, aes(x = TimePoint, y= meanAggSize, color = Condition,shape = "MeanSize"),size = 3, height = 0, width = .3)+
+  geom_jitter(data = aggregateListSummary, aes(x = TimePoint, y= maxSize, color = Condition, shape = "MaxSize"),size = 3, height = 0, width = .3)+
+  geom_jitter(data = aggregateListSummary, aes(x = TimePoint, y= biomass, color = Condition, shape = "TotalBiomass"),size = 3, height = 0,width= .3)+
   scale_y_log10( breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
-  facet_grid(. ~ Condition, scales = "free", space = "free") +
-  ggtitle('Mean size and largest aggregate and total biomass per sample')+
+  facet_grid(. ~ Species, scales = "free", space = "free") +
+  ggtitle('Mean size and largest aggregate and total biomass per condition')+
   labs(x = "",y = bquote(paste("Volume (", mu*"m"^3*")")))+
   scale_shape_manual(name="Metric",values=c(MeanSize=1, MaxSize=2, TotalBiomass=17))+
+  scale_color_brewer(palette = "Set1")+
   theme_cowplot()+
-  theme(plot.title = element_text(hjust = 0.5))
+  theme(plot.title = element_text(hjust = 0.5),strip.text = element_text(size = 11, face = "italic",margin = margin(.1,0,.1,0, "cm")),#this is for the facets
+          strip.background = element_rect(color="black", fill="white", size=1, linetype="solid"))
 #####
 ```
-```{r non-fancy histogram}
+
+```{r Aggregate size bins}
 #histogram<- hist(aggregateList$Size, breaks = c(0, 5, 10, 100, 1000, 10^9))#this is a simple way to do a histogram
@@
 ggplot()+
-    geom_jitter(data = HistReplicateSummary,aes(x=as.factor(LogBin),y=.data[[y_var]],  color =Species ),size=3, height = 0, width = .2, shape = 1)+
-    geom_point(data = HistConditionSummary,aes(x=as.factor(LogBin),y=.data[[y_var]],  color =Species,group = Species),size=4, shape = 16, position = position_dodge(width = .3) )+
+    geom_jitter(data = HistReplicateSummary,aes(x=as.factor(LogBin),y=.data[[y_var]],  color =Condition ),size=3, height = 0, width = .2, shape = 1)+
+    geom_point(data = HistConditionSummary,aes(x=as.factor(LogBin),y=.data[[y_var]],  color =Condition,group = Condition),size=4, shape = 16, position = position_dodge(width = .5) )+
     scale_y_log10(breaks = c(100, 10, 1, .1, .01), labels = c(100, 10, 1, .1, .01))+
-    facet_grid(Condition~TimePoint)+
+    facet_grid(Species~TimePoint)+
     ggtitle(title)+
     labs(y = paste(y_var,"(%)"),x = bquote(paste("Aggregate Volume (", mu*"m"^3*")")))+
+    scale_color_brewer(palette = "Set1")+
     theme_cowplot()+
-    theme(plot.title = element_text(hjust = 0.5))
+    panel_border() +
+    theme(plot.title = element_text(hjust = 0.5), 
+        strip.text = element_text(size = 11, face = "italic",margin = margin(.1,0,.1,0, "cm")),#this is for the facet text
+        strip.background = element_rect(color="black", fill="white", size=1, linetype="solid"))#facet background
 }
@@
     scale_colour_grey()+
+    panel_border() +
     theme(plot.title = element_text(hjust = 0.5)) }
-PlotHistRepBioTrend(HistReplicateSummary, "Pa")
-PlotHistRepBioTrend(HistReplicateSummary, "Sa")
+PlotHistRepBioTrend(HistReplicateSummary, "P. aeruginosa")
+PlotHistRepBioTrend(HistReplicateSummary, "S. aureus")
 
@@
 ##Summary df
-aggsHistCondSum<-aggsHistCond %>% group_by(Species,Condition,TimePoint, Replicate, LogBin,NormalizedFrequency,NormalizedBiomass) %>% summarize() %>%  unique()%>%ungroup() %>%  group_by(Species,Condition,TimePoint, Replicate) %>% mutate(checkSumFreq =sum(NormalizedFrequency), checkSumBiomass = sum(NormalizedBiomass))
+aggsHistCondSum<-aggsHistCond %>% group_by(Species,Condition,TimePoint, Replicate, LogBin,NormalizedFrequency,NormalizedBiomass) %>% summarize() %>%  unique()%>%ungroup() %>%  group_by(Species,Condition,TimePoint, Replicate) %>% mutate(checkSumFreq =sum(NormalizedFrequency), checkSumBiomass = sum(NormalizedBiomass))%>%ungroup()
 
@@
 PlotHistSum(aggsHistRepSum,aggsHistCondSum,"NormalizedBiomass","Normalized Biomass aggregates only")
-PlotHistRepBioTrend(aggsHistRepSum, "Pa")
-PlotHistRepBioTrend(aggsHistRepSum, "Sa")
+PlotHistRepBioTrend(aggsHistRepSum, "P. aeruginosa")
+PlotHistRepBioTrend(aggsHistRepSum, "S. aureus")
 
@@
 ggplot()+
-  geom_jitter(data = plankAggHistRep,aes(x=as.factor(Aggregation),y=AgPlNormFrequency,  color =Species, ),size=3, height = 0, width = .2, shape = 1)+ 
-  geom_point(data = plankAggHistCond,aes(x=as.factor(Aggregation),y=AgPlNormFrequency,  color =Species,group = Species),size=4, shape = 16, position = position_dodge(width = .3) )+
-  facet_grid(Condition~TimePoint)+
+  geom_jitter(data = plankAggHistRep,aes(x=as.factor(Aggregation),y=AgPlNormFrequency,  color =Condition ),size=3, height = 0, width = .2, shape = 1)+ 
+  geom_point(data = plankAggHistCond,aes(x=as.factor(Aggregation),y=AgPlNormFrequency,  color =Condition,group = Condition),size=4, shape = 16, position = position_dodge(width = .3) )+
+  facet_grid(Species~TimePoint)+
   ggtitle("Normalized Frequency (%) Aggs vs Plank")+
@@
   panel_border() +
-  #background_grid(major = "y")+
+  scale_color_brewer(palette = "Set1")+
   theme(plot.title = element_text(hjust = 0.5)) 
@@
   geom_jitter(data = plankAggHistRep,aes(x=as.factor(Aggregation),y=AgPlNormBiomass,  color =Condition ),size=2, height = 0, width = .2, shape = 1)+
-  geom_jitter(data = plankAggHistCond,aes(x=as.factor(Aggregation),y=AgPlNormBiomass,  color =Condition,group = Species),size=5, shape = 16,height = 0, width = .2) +
+  geom_point(data = plankAggHistCond,aes(x=as.factor(Aggregation),y=AgPlNormBiomass,  color =Condition),size=5, shape = 16, position = position_dodge2(width = .5)) +
   facet_grid(Species~TimePoint)+
   ggtitle("Normalized Biomass (%) Aggs vs Plank")+
-    labs(y = "Normalized Biomass (%)",x = bquote(paste("Aggregate Volume (", mu*"m"^3*")")))+  scale_color_manual( values = c( "red","blue","green", "gray"),labels = c("Sa Mono", "phz co", "pqsL co", "wt co"))+
+  labs(y = "Normalized Biomass (%)",x = bquote(paste("Aggregate Volume (", mu*"m"^3*")")))+ 
   theme_cowplot()+
   panel_border() +
-    theme(plot.title = element_text(hjust = 0.5)) 
+  scale_color_brewer(palette = "Set1")+
+  theme(plot.title = element_text(hjust = 0.3)) 
 #####
@@
 #Collapse dataframe to values per condition
-plankAggHistSummary<-plankAggHist %>% group_by(Species,TimePoint, Condition,Aggregation) %>%
+plankAggHistSummary<-plankAggHistRep %>% group_by(Species,TimePoint, Condition,Aggregation) %>%
   summarise(MeanFreq = mean(AgPlNormFrequency), SEFreq = std.error(AgPlNormFrequency), MeanBiomass = mean(AgPlNormBiomass),
@@
 ggplot()+
-  geom_col(data = plankAggHistSummary,aes(x=Aggregation,y=MeanBiomass, fill = TimePoint),
+  geom_col(data = plankAggHistSummary %>% filter(Aggregation=="Aggregate"),aes(x=Aggregation,y=MeanBiomass, fill = Condition),
            size=3,position = position_dodge( width = .9))+
-  geom_jitter(data = plankAggHist,aes(x=Aggregation,y=AgPlNormBiomass, group = TimePoint),shape = 1,size=2,position = position_dodge(width = .9),show.legend = FALSE)+
-  geom_errorbar(data = plankAggHistSummary,aes(x=Aggregation,ymin=(MeanBiomass-SEBiomass), ymax = (MeanBiomass+SEBiomass), group = TimePoint),width = 0, size=.5,position = position_dodge(width = .9))+
+  geom_jitter(data = plankAggHistRep%>% filter(Aggregation=="Aggregate"),aes(x=Aggregation,y=AgPlNormBiomass, group = Condition),shape = 1,size=2,position = position_dodge(width = .9),show.legend = FALSE)+
+  geom_errorbar(data = plankAggHistSummary%>% filter(Aggregation=="Aggregate"),aes(x=Aggregation,ymin=(MeanBiomass-SEBiomass), ymax = (MeanBiomass+SEBiomass), group = Condition),width = 0, size=.5,position = position_dodge(width = .9))+
   scale_y_continuous(limits = c(0,103),expand = expand_scale(mult = c(0, 0)))+
-  facet_grid(.~Species)+
-  scale_fill_grey()+
+  facet_grid(TimePoint~Species)+
+  scale_fill_brewer(palette = "Set1")+
   labs(title = '', x = "", y = "Biomass contribution (%)")+
@@
         legend.title = element_text(size=13),legend.text = element_text(size = 11),
-          legend.position = c(0.79, 0.60))
+        legend.position = c(.45, 0.60))
 #####
@@
 #Collapse to data per condition
-AggsOnlySummary<-aggsOnlyHistSummary.df %>% group_by(Species,TimePoint, Condition,LogBin) %>%
+AggsOnlySummary<-aggsHistRepSum %>% group_by(Species,TimePoint, Condition,LogBin) %>%
   summarise(MeanFreq = mean(NormalizedFrequency), SEFreq = std.error(NormalizedFrequency), MeanBiomass = mean(NormalizedBiomass),
@@
 ggplot()+
-    geom_col(data = AggsOnlySummary, aes(x=as.factor(LogBin),y=MeanFreq,  fill =TimePoint ),size=4,position = position_dodge( width = .9))+
-    geom_jitter(data = aggsOnlyHistSummary.df, aes(x=as.factor(LogBin),y=NormalizedFrequency, group = TimePoint),shape = 1,size=2,position = position_dodge( width = .9))+
-    geom_errorbar(data = AggsOnlySummary,aes(x=as.factor(LogBin),ymin=(MeanFreq-SEFreq), ymax = (MeanFreq+SEFreq), group = TimePoint),width = 0, size= .5,position = position_dodge( width = .9))+
-    facet_grid(.~Species)+
-    labs(fill = "",y = "Aggregates per bin (% of total)",x = bquote(paste("Aggregate Volume (", mu*"m"^3*")")))+
+    geom_col(data = AggsOnlySummary, aes(x=as.factor(LogBin),y=MeanFreq,  fill =Condition ),size=4,position = position_dodge( width = .9))+
+    geom_jitter(data = aggsHistRepSum, aes(x=as.factor(LogBin),y=NormalizedFrequency, group = Condition),shape = 1,size=2,position = position_dodge( width = .9))+
+    geom_errorbar(data = AggsOnlySummary,aes(x=as.factor(LogBin),ymin=(MeanFreq-SEFreq), ymax = (MeanFreq+SEFreq), group = Condition),width = 0, size= .5,position = position_dodge( width = .9))+
+    facet_grid(TimePoint~Species)+
+    labs(fill = "",y = "Aggregates Frequency per bin (% of total)",x = bquote(paste("Aggregate Volume (", mu*"m"^3*")")))+
     #guides(color = FALSE)+
-    scale_y_continuous(limits = c(0,70), expand = expand_scale(mult = c(0, 0)))+
-    scale_fill_grey()+
+    #scale_y_continuous(limits = c(0,180), expand = expand_scale(mult = c(0, 0)))+
+    theme_half_open()+
+    scale_fill_brewer(palette = "Set1")+
+    theme(plot.title = element_text(hjust = 0.5),
+          strip.text = element_text(size = 9, face = "italic",margin = margin(.1,0,.1,0, "cm")),#this is for the facets
+          strip.background = element_rect(color="black", fill="white", size=.5, linetype="solid"),
+          plot.margin = unit(c(0,.5,0,.5), "cm"),
+          axis.title.x = element_text(margin = margin(0,0,0,0),size=13),axis.text.x = element_text(margin = margin(1,0,0,0),size=11),
+          axis.title.y = element_text(margin = margin(0,4,0,0),size=13),axis.text.y = element_text(margin = margin(0,2,2,0),size=11),
+          legend.title = element_text(size=13),legend.text = element_text(size = 11),
+          legend.position = c(0.79, 0.80))
+#Plot Normalized Biomass
+AggsOnlySummaryRep<-aggsHistRepSum %>% group_by(Species,TimePoint, Replicate, Condition,LogBin) %>%
+  summarise(MeanFreq = mean(NormalizedFrequency), SEFreq = std.error(NormalizedFrequency), MeanBiomass = mean(NormalizedBiomass),
+            SEBiomass = std.error(NormalizedBiomass))
+ggplot()+
+    geom_col(data = AggsOnlySummary, aes(x=as.factor(LogBin),y=MeanBiomass,  fill =Condition ),size=4,position = position_dodge( width = .9))+
+    #geom_jitter(data = aggsOnlyHistSummary.df, aes(x=as.factor(LogBin),y=NormalizedBiomass, group = TimePoint),shape = 1,size=2,position = position_dodge( width = .9))+
+    geom_errorbar(data = AggsOnlySummary,aes(x=as.factor(LogBin),ymin=(MeanBiomass-SEBiomass), ymax = (MeanBiomass+SEBiomass), group = Condition),width = 0, size= .5,position = position_dodge( width = .9))+
+    facet_grid(TimePoint~Species)+
+    labs(fill = "",y = "Biomass contribution per bin (% of total)",x = bquote(paste("Aggregate Volume (", mu*"m"^3*")")))+
+    #guides(color = FALSE)+
+    scale_y_continuous(limits = c(0,100), expand = expand_scale(mult = c(0, 0)))+
+    scale_fill_brewer(palette = "Set1")+
     theme_half_open()+
@@
           legend.title = element_text(size=13),legend.text = element_text(size = 11),
-          legend.position = c(0.79, 0.60))
-#Plot Normalized Biomass
-ggplot()+
-    geom_col(data = AggsOnlySummary, aes(x=as.factor(LogBin),y=MeanBiomass,  fill =TimePoint ),size=4,position = position_dodge( width = .9))+
-    #geom_jitter(data = aggsOnlyHistSummary.df, aes(x=as.factor(LogBin),y=NormalizedBiomass, group = TimePoint),shape = 1,size=2,position = position_dodge( width = .9))+
-    geom_errorbar(data = AggsOnlySummary,aes(x=as.factor(LogBin),ymin=(MeanBiomass-SEBiomass), ymax = (MeanBiomass+SEBiomass), group = TimePoint),width = 0, size= .5,position = position_dodge( width = .9))+
-    facet_grid(.~Species)+
-    labs(fill = "",y = "Aggregates per bin (% of total)",x = bquote(paste("Aggregate Volume (", mu*"m"^3*")")))+
-    #guides(color = FALSE)+
-    scale_y_continuous(limits = c(0,100), expand = expand_scale(mult = c(0, 0)))+
-    scale_fill_grey()+
-    theme_half_open()+
-    theme(plot.title = element_text(hjust = 0.5),
-          strip.text = element_text(size = 9, face = "italic",margin = margin(.1,0,.1,0, "cm")),#this is for the facets
-          strip.background = element_rect(color="black", fill="white", size=.5, linetype="solid"),
-          plot.margin = unit(c(0,.5,0,.5), "cm"),
-          axis.title.x = element_text(margin = margin(0,0,0,0),size=13),axis.text.x = element_text(margin = margin(1,0,0,0),size=11),
-          axis.title.y = element_text(margin = margin(0,4,0,0),size=13),axis.text.y = element_text(margin = margin(0,2,2,0),size=11),
-          legend.title = element_text(size=13),legend.text = element_text(size = 11),
-          legend.position = c(0.79, 0.60))
+          legend.position = c(0.79, 0.80))
 #####
 ```
+
 ```{r fancy histogram of aggregates !!!deprecated}
@@
 ```
+```{r Test color palettes}
+library(RColorBrewer)
+brewer.pal(n = 4, name = 'Set1')
+```

### 2021-06-28 R/AggregateCounts.Rmd
added z-slice figure

@@
 #this was taken from "Microscopy data clean.Rmd" 
-GetResults<-function(){
-  folder<- '/Volumes/raw_data/Confocal/Carolyn/2020/Chronic wounds/Binary Images'
-  samplesList<-list.files(path = folder, full.names = TRUE)
-  imagesList<-mapply(list.files,samplesList)
-
-separateColors
-  blueChannel<-fileList[grep('B_',fileList)]
-  redChannel<-fileList[grep('R_',fileList)]
-  greenChannel<-fileList[grep('G_',fileList)]
-  Results<-rbind(blueChannel,redChannel,greenChannel)
-  Results<-Results %>% mutate(Sample = sample)
-
+GetSliceData<-function(){#import all experiments at once
+  folder<- '/Volumes/raw_data/Confocal/Carolyn/2020/Chronic wounds/Results per slice'
    fileList<-list.files(path = folder, full.names = TRUE)
@@
      attrList<-str_split(fileName,"_")[[1]]
-     growthDf<-rbind(growthDf,ReadAggregateFile(fileList[aggList],attrList[4],attrList[2],attrList[1],attrList[3]))
+     growthDf<-rbind(growthDf,ReadSliceFile(fileList[aggList],attrList[2],attrList[1],attrList[3], fileName))
      }
@@
 }
+
+ReadSliceFile<-function(file, timepoint, condition, replicate, sampleCode){#make a dataframe of the aggregate size list and add experimental parameters
+  print(file)
+   datos <-read.csv(file, header = F)  
+   colnames(datos)<-c('Biomass', 'Channel', 'Slice') 
+   datos<-datos %>% mutate(TimePoint = timepoint) 
+   datos<-datos %>% mutate(Condition = condition)
+   datos<-datos %>% mutate(Replicate = replicate)
+   datos<-datos %>% mutate(SampleCode = sampleCode)
+   datos$Replicate<-as.factor(datos$Replicate)
+   datos$Condition<-as.factor(datos$Condition)
+   datos$TimePoint<-as.factor(datos$TimePoint)
+   return(datos)
+}
+
+slicedData<-GetSliceData()
+
+#merge with metadata
+metaData.df <-read.csv('/Volumes/raw_data/Confocal/Carolyn/2020/Chronic wounds/image data copy.csv', header = TRUE)
+
+metaData.df<-metaData.df %>% select(SampleCode, mouse, Position, size, Voxel.size,Region, Zdim)
+sliceDataMeta<-metaData.df %>%  merge(slicedData, by = "SampleCode")
+remove <- sliceDataMeta %>% filter(Channel == 2 & Condition == "mono")
+sliceDataMeta <- anti_join(sliceDataMeta, remove)
+
+sliceDataMeta$Channel <- factor(sliceDataMeta$Channel, levels = c(1, 2, 3),labels = c('S. aureus','P. aeruginosa','host'))
+sliceDataMeta<-sliceDataMeta %>% mutate(Height = Zdim*Slice)
+sliceDataMeta<-sliceDataMeta %>% group_by(SampleCode, Channel) %>% mutate(TotalBiomass = sum(Biomass)) %>% ungroup() %>% mutate(NormBiomass = Biomass/TotalBiomass*100)
+
+ggplot()+
+  geom_point(data = sliceDataMeta,aes(x=NormBiomass,y=Height, color = Condition, shape = TimePoint ),size=2)+
+
+  theme_cowplot()+
+  scale_color_brewer(palette = "Set1")+
+  facet_grid(Channel~Condition)+
+  theme(plot.title = element_text(hjust = 0.5))
+
+```
+
+```{r read Tiff functions}
 
@@
 
-  IterateTiff<-function(fileList, species)
+  IterateTiff<-function(fileList, species){
   growth<-matrix(ncol=3, nrow=length(fileList))

### 2021-06-29 R/PropOcDataThor.Rmd
Thor version of the Proportional occupancy code

---
title: "Proportional Occupancy"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
library(pixmap)
library(rtiff)
library(reshape2)
library(gplots)
library(gdata)
library(plyr)
library(dplyr)
library(ggplot2)
library(cowplot)
library(tidyr)
library(purrr)
library(plotrix)
library(ggsignif)
library(rdist)

```

```{r functions to get data}
#using the new 3D script with capped spheres.
source('/home/jbarraza6/Documents/RScripts/PropOcFunctions2.0.R') 
GetPropOcData<-function(sample, timepoints, positions){
  #folder<- paste0('/media/jbarraza6/Seagate Backup Plus Drive/Good images/',sample,'/images1')
  folder<- paste0('~/Desktop/Seagate Backup Plus Drive/Good images/',sample,'/imagesSubtractRed1')
  growthDf<-data.frame()#data frame to add all timepoints and positions
  fileList<-list.files(path = folder, full.names = TRUE)
  print(folder)
  for (position in 2:positions){
    currentPosition<-fileList[grep(paste0("p",position,"_"),fileList)]
    print(paste0('analyzing position ', position))
    for (timepoint in 0:timepoints){
      currentTimePoint<-currentPosition[grep(paste0("t",GetSlice(timepoint),"_"),currentPosition)]
      dataTimePoint<-AllDataPipeline(SlicesTo3D(currentTimePoint,"red"),SlicesTo3D(currentTimePoint,"green"), 
                                     xydimSearch=114,zdimSearch = 70, sampleSize=1000,xyRealDim=0.264,
                                     zRealDim = 0.44, pipeBinSize = 1)
      dataTimePoint$TimePoint <- timepoint
      dataTimePoint$Position <- position
      growthDf<-rbind(growthDf,dataTimePoint)
      }
    }
  return(growthDf)
  }
GetSlice<-function(idx){
  if (idx<10){num = paste0(0,idx)}
  else
  {num = idx}
  return(num)}
```

```{r running functions}
wt1.1000<-GetPropOcData("3-13-19", 6, 2)
write.csv(wt1.1000, "~/Desktop/Seagate Backup Plus Drive/Good images/PropOcDataAll/wt1-1000-3.csv")

wt2.1000<-GetPropOcData("3-19-19", 6, 2)
write.csv(wt2.1000, "~/Desktop/Seagate Backup Plus Drive/Good images/PropOcDataAll/wt2-1000-3.csv")

wt3.1000<-GetPropOcData("4-17-19", 6, 2)
write.csv(wt3.1000, "~/Desktop/Seagate Backup Plus Drive/Good images/PropOcDataAll/wt3-1000-3.csv")

mut1.1000<-GetPropOcData("4-24-19", 6, 2)
write.csv(mut1.1000, "~/Desktop/Seagate Backup Plus Drive/Good images/PropOcDataAll/mut1-1000-3.csv")

mut2.1000<-GetPropOcData("4-25-19", 6, 2)
write.csv(mut2.1000, "~/Desktop/Seagate Backup Plus Drive/Good images/PropOcDataAll/mut2-1000-3.csv")
mut3.1000<-GetPropOcData("5-8-19", 6, 2)
write.csv(mut3.1000, "~/Desktop/Seagate Backup Plus Drive/Good images/PropOcDataAll/mut3-1000-3.csv")

```

### 2021-06-29 Matlab/adaptiveThreshold.m
more samples

@@ -15,15 +15,17 @@ Tiff2Data (rawTifPath,binTifPath,aggsFilePath,slicedAggsFilePath, xySize, zSize)
 end
 %}
 
-for sampleNumber = 4:8
-iterateSamples('mono_d1_',sampleNumber,.208,.52)
+for sampleNumber = 1:7
+iterateSamples('phz_d1_',sampleNumber,.415,.52)
 end
 
-for sampleNumber = 9:15
-iterateSamples('mono_d1_',sampleNumber,.208,.365)
+for sampleNumber = 1:14
+iterateSamples('phz_d4_',sampleNumber,.208,.52)
 end
 
-
+for sampleNumber = 1:16
+iterateSamples('pqsL_d4_',sampleNumber,.208,.52)
+end
 
 function iterateSamples(sampleName, sampleNum,xy,z)
 rawTifPathBase = '/Volumes/raw_data/Confocal/Carolyn/2020/Chronic wounds/Tiff Stacks New/';

### 2021-06-29 R/AggregateCounts.Rmd
Added figures for z-slice

@@
 
+#Input data
+#####
+#get data from csv file
 slicedData<-GetSliceData()
-
-#merge with metadata
+#get metadata
 metaData.df <-read.csv('/Volumes/raw_data/Confocal/Carolyn/2020/Chronic wounds/image data copy.csv', header = TRUE)
-
+#merge files
 metaData.df<-metaData.df %>% select(SampleCode, mouse, Position, size, Voxel.size,Region, Zdim)
 sliceDataMeta<-metaData.df %>%  merge(slicedData, by = "SampleCode")
+#clean up
 remove <- sliceDataMeta %>% filter(Channel == 2 & Condition == "mono")
 sliceDataMeta <- anti_join(sliceDataMeta, remove)
+#rename variables
+sliceDataMeta$Channel <- factor(sliceDataMeta$Channel, levels = c(1, 2, 3),labels = c('S. aureus','P. aeruginosa','host'))
+sliceDataMeta$Condition<- factor(sliceDataMeta$Condition, levels = c("mono", "wt", "pqsL", "phz"),labels = c('Sa mono','wt co', 'pqsL co', 'phz co'))
+sliceDataMeta$TimePoint <- factor(sliceDataMeta$TimePoint, levels = c("d1", "d4"),labels = c('Day 1','Day 4'))
+#calculate relative biomass
+sliceDataMeta<-sliceDataMeta%>% filter(!Channel == "host") %>% mutate(Height = Zdim*Slice) %>% group_by(SampleCode, Channel) %>% mutate(TotalBiomass = sum(Biomass)) %>% ungroup() %>% mutate(NormBiomass = Biomass/TotalBiomass*100)
 
-sliceDataMeta$Channel <- factor(sliceDataMeta$Channel, levels = c(1, 2, 3),labels = c('S. aureus','P. aeruginosa','host'))
-sliceDataMeta<-sliceDataMeta %>% mutate(Height = Zdim*Slice)
-sliceDataMeta<-sliceDataMeta %>% group_by(SampleCode, Channel) %>% mutate(TotalBiomass = sum(Biomass)) %>% ungroup() %>% mutate(NormBiomass = Biomass/TotalBiomass*100)
+#####
+#Plot Data
+#####
+ggplot()+
+  #geom_point(data = sliceDataMeta ,aes(y=NormBiomass,x=Height, color = Condition, group = Replicate),size=.5)+
+  geom_smooth(data = sliceDataMeta ,aes(y=NormBiomass,x=Height, color = Condition),size=2)+
+  geom_hline(yintercept = 0, linetype = "dashed", color = "gray")+
+  theme_cowplot()+
+  scale_color_brewer(palette = "Set1")+
+  facet_grid(Channel~TimePoint)+
+  panel_border() +
+  coord_flip()
+  theme(plot.title = element_text(hjust = 0.5))
+#####
+#Max slice?
+sliceDataMeta<-sliceDataMeta %>% group_by(SampleCode, Condition, Replicate, TimePoint) %>% mutate(MaxHeight = max(Height))
+ggplot()+
+  geom_point(data = maxSlice%>% filter(MaxHeight<120 & MaxHeight>50),aes(x=Replicate,y=MaxHeight, color = Condition),size=4)+
+facet_grid(.~TimePoint, scales = "free", space = "free")+
+  scale_color_brewer(palette = "Set1")+
+  geom_hline(yintercept = 120)+
+  geom_hline(yintercept = 50)+
+  theme_cowplot()+
+  theme(plot.title = element_text(hjust = 0.5),axis.text.x = element_text(angle = 70, hjust = 1))
 
 ggplot()+
-  geom_point(data = sliceDataMeta,aes(x=NormBiomass,y=Height, color = Condition, shape = TimePoint ),size=2)+
-
+  #geom_point(data = sliceDataMeta ,aes(y=NormBiomass,x=Height, color = Condition, group = Replicate),size=.5)+
+  geom_smooth(data = sliceDataMeta %>% filter(MaxHeight>50 & MaxHeight<120) ,aes(y=NormBiomass,x=Height, color = Condition),size=2)+
+  geom_hline(yintercept = 0, linetype = "dashed", color = "gray")+
   theme_cowplot()+
   scale_color_brewer(palette = "Set1")+
-  facet_grid(Channel~Condition)+
+  facet_grid(Channel~TimePoint)+
+  panel_border() +
+  coord_flip()
   theme(plot.title = element_text(hjust = 0.5))

### 2021-06-30 R/PropOcDataThor.Rmd
fixed propOc function to map and take tiffs

@@
 source('/home/jbarraza6/Documents/RScripts/PropOcFunctions2.0.R') 
+source('/Users/jupabago/Documents/Whiteley/PROJECTS/Rpackage/PropOc Package/R/PropOcFunctions2.0.R') 
 GetPropOcData<-function(sample, timepoints, positions){
-  #folder<- paste0('/media/jbarraza6/Seagate Backup Plus Drive/Good images/',sample,'/images1')
-  folder<- paste0('~/Desktop/Seagate Backup Plus Drive/Good images/',sample,'/imagesSubtractRed1')
+  folder<- paste0('/Volumes/raw_data/Confocal/Carolyn/2020/Chronic wounds/Aggregate lists')
   growthDf<-data.frame()#data frame to add all timepoints and positions
@@
       currentTimePoint<-currentPosition[grep(paste0("t",GetSlice(timepoint),"_"),currentPosition)]
-      dataTimePoint<-AllDataPipeline(SlicesTo3D(currentTimePoint,"red"),SlicesTo3D(currentTimePoint,"green"), 
-                                     xydimSearch=114,zdimSearch = 70, sampleSize=1000,xyRealDim=0.264,
+      dataTimePoint<-AllDataPipeline(SlicesTo3D(redVolume),SlicesTo3D(greenVolume), 
+                                     xydimSearch=114,zdimSearch = 70,
+                                     sampleSize=1000,xyRealDim=0.264,
                                      zRealDim = 0.44, pipeBinSize = 1)
-      dataTimePoint$TimePoint <- timepoint
-      dataTimePoint$Position <- position
+      dataTimePoint$Condition <- 
+      dataTimePoint$TimePoint <- 
       growthDf<-rbind(growthDf,dataTimePoint)
@@
 }
+
+GetPropOcData<-function(sampleName, xyDim,zDim){
+  parentFolder<- '/Volumes/raw_data/Confocal/Carolyn/2020/Chronic wounds/Binary Images/'
+  sampleFolder<-paste0(parentFolder, sampleName)
+  attrList<-str_split(sampleName,"_")[[1]]
+  fileList<-list.files(path = sampleFolder, full.names = TRUE)
+  greenImg<-fileList[grep("G_",fileList)]
+  redImg<-fileList[grep("R_",fileList)]
+  propOcData<-AllDataPipeline(SlicesTo3D(redImg),SlicesTo3D(greenImg), 
+                                     xydimSearch=round(30/xyDim),zdimSearch =round(30/zDim),
+                                     sampleSize=10,xyRealDim=xyDim,
+                                     zRealDim = zDim, pipeBinSize = 1)
+  propOcData$Condition <- attrList[1]
+  propOcData$TimePoint <- attrList[2]
+  propOcData$Replicate <- attrList[3]
+  write.csv(propOcData, paste0("/Volumes/raw_data/Confocal/Carolyn/2020/Chronic wounds/PropOc Data/",sampleName,".csv"))
+}
+
+testGetPropOcData<-GetPropOcData("mono_d1_01", .415,.52)
+testPmap<-pmap(list(metaData.df$SampleCode, metaData.df$xyDim, metaData.df$Zdim),GetPropOcData)
+boundPmapTest<-bind_rows(testPmap)
+
+testGrep<-list.files(path = '/Volumes/raw_data/Confocal/Carolyn/2020/Chronic wounds/Binary Images/mono_d1_02', full.names = TRUE)
+testGrepG<-testGrep[grep("G_",testGrep)]
+
 GetSlice<-function(idx){
@@
   return(num)}
+
+Slices2threeD<-function(fileList){
+  image1<-as.array(readImage(fileList[1], convert = TRUE))#read first image to get its dimensions
+  image3D <- array(0, c(dim(image1)[1], dim(image1)[2], length(fileList)))#preallocate array for image given using image dimensions
+  for(i in 1:length(fileList)){#keep in mind that it is not zero-index
+    #print(paste("loading ch1...", i, "/", length(filesList), filesList[i]))
+    image3D[,,i]<-as.array(readImage(fileList[i], convert = TRUE))
+  }
+  return(image3D)
+}
+testSlices2threeD<-Slices2threeD(testGrepG)
+testGrepG[1]
+testImage1<-as.array(readImage(testGrepG[1], convert = TRUE))
+
 ```

### 2021-07-06 R/PropOcDataThor.Rmd
tests for empty folder prop oc

--- 2021-06-29 R/PropOcDataThor.Rmd
@@
 source('/home/jbarraza6/Documents/RScripts/PropOcFunctions2.0.R') 
-GetPropOcData<-function(sample, timepoints, positions){
-  #folder<- paste0('/media/jbarraza6/Seagate Backup Plus Drive/Good images/',sample,'/images1')
-  folder<- paste0('~/Desktop/Seagate Backup Plus Drive/Good images/',sample,'/imagesSubtractRed1')
-  growthDf<-data.frame()#data frame to add all timepoints and positions
-  fileList<-list.files(path = folder, full.names = TRUE)
-  print(folder)
-  for (position in 2:positions){
-    currentPosition<-fileList[grep(paste0("p",position,"_"),fileList)]
-    print(paste0('analyzing position ', position))
-    for (timepoint in 0:timepoints){
-      currentTimePoint<-currentPosition[grep(paste0("t",GetSlice(timepoint),"_"),currentPosition)]
-      dataTimePoint<-AllDataPipeline(SlicesTo3D(currentTimePoint,"red"),SlicesTo3D(currentTimePoint,"green"), 
-                                     xydimSearch=114,zdimSearch = 70, sampleSize=1000,xyRealDim=0.264,
-                                     zRealDim = 0.44, pipeBinSize = 1)
-      dataTimePoint$TimePoint <- timepoint
-      dataTimePoint$Position <- position
-      growthDf<-rbind(growthDf,dataTimePoint)
+source('/Users/jupabago/Documents/Whiteley/PROJECTS/Rpackage/PropOc Package/R/PropOcFunctions2.0.R')
+
+GetPropOcData<-function(sampleName, xyDim,zDim){
+  tic()
+  #parentFolder<- '/run/user/937561/gvfs/smb-share:server=130.207.66.142,share=raw_data/Confocal/Carolyn/2020/Chronic wounds/Binary Images/'
+  parentFolder<- '/Volumes/raw_data/Confocal/Carolyn/2020/Chronic wounds/Binary Images/'
+  sampleFolder<-paste0(parentFolder, sampleName)
+  attrList<-str_split(sampleName,"_")[[1]]
+  print(sampleName)
+  fileList<-list.files(path = sampleFolder, full.names = TRUE)
+  print(paste("# of files:", length(fileList)))
+  if(length(fileList)<1){
+    print("empty set")
+    return(data.frame())
+  }else{
+  greenImg<-fileList[grep("G_",fileList)]
+  redImg<-fileList[grep("R_",fileList)]
+  propOcData<-AllDataPipeline(Slices2threeD(redImg),Slices2threeD(greenImg), 
+                                     xydimSearch=round(30/xyDim),zdimSearch =round(30/zDim),
+                                     sampleSize=10,xyRealDim=xyDim,
+                                     zRealDim = zDim, pipeBinSize = 1)
+  propOcData$Condition <- attrList[1]
+  propOcData$TimePoint <- attrList[2]
+  propOcData$Replicate <- attrList[3]
+  toc()
+  write.csv(propOcData, paste0("/Volumes/raw_data/Confocal/Carolyn/2020/Chronic wounds/PropOc Data/",sampleName,".csv"))
+  return(propOcData)}
+  }
+
+testGetPropOcData<-GetPropOcData("mono_d1_02", .415,.52)
+
+testGetPropOcDataemptyFolder<-GetPropOcData("wt_d1_01", .415,.52)
+testPmap<-pmap(list(metaData.df$SampleCode,metaData.df$xyDim, metaData.df$Zdim),
+               GetPropOcData)
+boundPmapTest<-bind_rows(testPmap)
+
+#Dummy function
+GetDummyOcData<-function(sampleName, xyDim,zDim){
+  parentFolder<- '/Volumes/raw_data/Confocal/Carolyn/2020/Chronic wounds/Binary Images/'
+  sampleFolder<-paste0(parentFolder, sampleName)
+  attrList<-str_split(sampleName,"_")[[1]]
+  print(sampleName)
+  fileList<-list.files(path = sampleFolder, full.names = TRUE)
+  print(paste("# of files:", length(fileList)))
+  if(length(fileList)<1){
+    print("empty set")
+    return(data.frame())
+  }else{
+  greenImg<-fileList[grep("G_",fileList)]
+  redImg<-fileList[grep("R_",fileList)]
+  return(as.data.frame(list(length(greenImg), length(redImg))))
   }
   }
-  return(growthDf)
+testDummyData<-GetDummyOcData("mono_d1_02", .415,.52)
+testDummyEmptyFolder<-GetDummyOcData("wt_d1_01", .415,.52)
+dummyBind<-bind_rows(list(testDummyData,testDummyEmptyFolder))
+
+testGrep<-list.files(path = '/Volumes/raw_data/Confocal/Carolyn/2020/Chronic wounds/Binary Images/mono_d1_02', full.names = TRUE)
+testGrepG<-testGrep[grep("G_",testGrep)]
+
+Slices2threeD<-function(fileList){
+  image1<-as.array(readImage(fileList[1], convert = TRUE))#read first image to get its dimensions
+  image3D <- array(0, c(dim(image1)[1], dim(image1)[2], length(fileList)))#preallocate array for image given using image dimensions
+  for(i in 1:length(fileList)){#keep in mind that it is not zero-index
+    #print(paste("loading ch1...", i, "/", length(filesList), filesList[i]))
+    image3D[,,i]<-as.array(readImage(fileList[i], convert = TRUE))
   }
-GetSlice<-function(idx){
-  if (idx<10){num = paste0(0,idx)}
-  else
-  {num = idx}
-  return(num)}
+  return(image3D)
+}
+
+testSlices2threeD<-Slices2threeD(testGrepG)
+testGrepG[1]
+testImage1<-as.array(readImage(testGrepG[1], convert = TRUE))
+
 ```

### 2021-07-06 R/PropOcDataThor.Rmd
fixing names

--- 2021-06-29 R/PropOcDataThor.Rmd
@@
 library(rdist)
+library(EBImage)
 
@@
 source('/home/jbarraza6/Documents/RScripts/PropOcFunctions2.0.R') 
-GetPropOcData<-function(sample, timepoints, positions){
-  #folder<- paste0('/media/jbarraza6/Seagate Backup Plus Drive/Good images/',sample,'/images1')
-  folder<- paste0('~/Desktop/Seagate Backup Plus Drive/Good images/',sample,'/imagesSubtractRed1')
-  growthDf<-data.frame()#data frame to add all timepoints and positions
-  fileList<-list.files(path = folder, full.names = TRUE)
-  print(folder)
-  for (position in 2:positions){
-    currentPosition<-fileList[grep(paste0("p",position,"_"),fileList)]
-    print(paste0('analyzing position ', position))
-    for (timepoint in 0:timepoints){
-      currentTimePoint<-currentPosition[grep(paste0("t",GetSlice(timepoint),"_"),currentPosition)]
-      dataTimePoint<-AllDataPipeline(SlicesTo3D(currentTimePoint,"red"),SlicesTo3D(currentTimePoint,"green"), 
-                                     xydimSearch=114,zdimSearch = 70, sampleSize=1000,xyRealDim=0.264,
-                                     zRealDim = 0.44, pipeBinSize = 1)
-      dataTimePoint$TimePoint <- timepoint
-      dataTimePoint$Position <- position
-      growthDf<-rbind(growthDf,dataTimePoint)
+source('/Users/jupabago/Documents/Whiteley/PROJECTS/Rpackage/PropOc Package/R/PropOcFunctions2.0.R')
+
+GetPropOcData<-function(sampleName, xyDim,zDim){
+  parentFolder<- '/run/user/937561/gvfs/smb-share:server=130.207.66.142,share=raw_data/Confocal/Carolyn/2020/Chronic wounds/Binary Images/'
+  sampleFolder<-paste0(parentFolder, sampleName)
+  attrList<-str_split(sampleName,"_")[[1]]
+  fileList<-list.files(path = sampleFolder, full.names = TRUE)
+  greenImg<-fileList[grep("G_",fileList)]
+  redImg<-fileList[grep("R_",fileList)]
+  propOcData<-AllDataPipeline(SlicesTo3D(redImg),SlicesTo3D(greenImg), 
+                                     xydimSearch=round(30/xyDim),zdimSearch =round(30/zDim),
+                                     sampleSize=10,xyRealDim=xyDim,
+                                     zRealDim = zDim, pipeBinSize = 1)
+  propOcData$Condition <- attrList[1]
+  propOcData$TimePoint <- attrList[2]
+  propOcData$Replicate <- attrList[3]
+  write.csv(propOcData, paste0("/run/user/937561/gvfs/smb-share:server=130.207.66.142,share=raw_data/Confocal/Carolyn/2020/Chronic wounds/Chronic wounds/PropOc Data/",sampleName,".csv"))
   }
+
+testGetPropOcData<-GetPropOcData("mono_d1_01", .415,.52)
+testPmap<-pmap(list(metaData.df$SampleCode, metaData.df$xyDim, metaData.df$Zdim),GetPropOcData)
+boundPmapTest<-bind_rows(testPmap)
+
+testGrep<-list.files(path = '/run/user/937561/gvfs/smb-share:server=130.207.66.142,share=raw_data/Confocal/Carolyn/2020/Chronic wounds/Binary Images/mono_d1_02', full.names = TRUE)
+testGrepG<-testGrep[grep("G_",testGrep)]
+
+Slices2threeD<-function(fileList){
+  image1<-as.array(readImage(fileList[1], convert = TRUE))#read first image to get its dimensions
+  image3D <- array(0, c(dim(image1)[1], dim(image1)[2], length(fileList)))#preallocate array for image given using image dimensions
+  for(i in 1:length(fileList)){#keep in mind that it is not zero-index
+    #print(paste("loading ch1...", i, "/", length(filesList), filesList[i]))
+    image3D[,,i]<-as.array(readImage(fileList[i], convert = TRUE))
   }
-  return(growthDf)
+  return(image3D)
 }
-GetSlice<-function(idx){
-  if (idx<10){num = paste0(0,idx)}
-  else
-  {num = idx}
-  return(num)}
+testSlices2threeD<-Slices2threeD(testGrepG)
+testGrepG[1]
+testImage1<-as.array(readImage(testGrepG[1], convert = TRUE))
+install.packages("BiocManager")
+BiocManager::install("EBImage")
 ```

### 2021-07-06 R/AggregateCounts.Rmd

--- 2021-06-28 R/AggregateCounts.Rmd
@@
 filter <- dplyr::filter
-source("~/Documents/Whiteley/PROJECTS/SaPa Chronic Wounds/PaSaChronicWounds/R/readTiff.R")
 library(EBImage) #for rtiff
@@
 
+#Input data
+#####
+#get data from csv file
 slicedData<-GetSliceData()
-
-#merge with metadata
-metaData.df <-read.csv('/Volumes/raw_data/Confocal/Carolyn/2020/Chronic wounds/image data copy.csv', header = TRUE)
-
-metaData.df<-metaData.df %>% select(SampleCode, mouse, Position, size, Voxel.size,Region, Zdim)
+#get metadata
+metaData.df <-read.csv('/Volumes/raw_data/Confocal/Carolyn/2020/Chronic wounds/images metadata.csv', header = TRUE)
+#merge files
+metaData.df<-metaData.df %>% select(SampleCode, mouse, Position, size, Region, Zdim, xyDim)
 sliceDataMeta<-metaData.df %>%  merge(slicedData, by = "SampleCode")
+#clean up
 remove <- sliceDataMeta %>% filter(Channel == 2 & Condition == "mono")
@@
 
+aggregateListRemoved<-aggregateList %>% filter(!SampleCode == "mono_d1_03_Pa" & !SampleCode == "mono_d1_03_Sa")
+aggregateListRemoved<-aggregateList %>% filter(!SampleCode == "phz_d4_14_Pa" & !SampleCode == "phz_d4_14_Sa")
+aggregateListRemoved<-aggregateList %>% filter(!SampleCode == "pqsL_d4_02_Pa" & !SampleCode == "pqsL_d4_02_Sa")
+aggregateListRemoved<-aggregateList %>% filter(!SampleCode == "pqsL_d4_04_Pa" & !SampleCode == "pqsL_d4_04_Sa")
+aggregateListRemoved<-aggregateList %>% filter(!SampleCode == "pqsL_d4_10_Pa" & !SampleCode == "pqsL_d4_10_Sa")
+aggregateListRemoved<-aggregateList %>% filter(!SampleCode == "wt_d4_07_Pa" & !SampleCode == "wt_d4_07_Sa")
+
+#rename variables
 sliceDataMeta$Channel <- factor(sliceDataMeta$Channel, levels = c(1, 2, 3),labels = c('S. aureus','P. aeruginosa','host'))
-sliceDataMeta<-sliceDataMeta %>% mutate(Height = Zdim*Slice)
-sliceDataMeta<-sliceDataMeta %>% group_by(SampleCode, Channel) %>% mutate(TotalBiomass = sum(Biomass)) %>% ungroup() %>% mutate(NormBiomass = Biomass/TotalBiomass*100)
+sliceDataMeta$Condition<- factor(sliceDataMeta$Condition, levels = c("mono", "wt", "pqsL", "phz"),labels = c('Sa mono','wt co', 'pqsL co', 'phz co'))
+sliceDataMeta$TimePoint <- factor(sliceDataMeta$TimePoint, levels = c("d1", "d4"),labels = c('Day 1','Day 4'))
+#calculate relative biomass
+sliceDataMeta<-sliceDataMeta%>% filter(!Channel == "host") %>% mutate(Height = Zdim*Slice) %>% group_by(SampleCode, Channel) %>% mutate(TotalBiomass = sum(Biomass)) %>% ungroup() %>% mutate(NormBiomass = Biomass/TotalBiomass*100)
+
+#####
+#Plot Data
+#####
+ggplot()+
+  #geom_point(data = sliceDataMeta ,aes(y=NormBiomass,x=Height, color = Condition, group = Replicate),size=.5)+
+  geom_smooth(data = sliceDataMeta ,aes(y=NormBiomass,x=Height, color = Condition),size=2)+
+  geom_hline(yintercept = 0, linetype = "dashed", color = "gray")+
+  theme_cowplot()+
+  scale_color_brewer(palette = "Set1")+
+  facet_grid(Channel~TimePoint)+
+  panel_border() +
+  coord_flip()
+  theme(plot.title = element_text(hjust = 0.5))
+#####
+#Filter by Max height of the sample
+#####  
+sliceDataMeta<-sliceDataMeta %>% group_by(SampleCode, Condition, Replicate, TimePoint) %>% mutate(MaxHeight = max(Height))
+ggplot()+
+  geom_point(data = maxSlice%>% filter(MaxHeight<120 & MaxHeight>50),aes(x=Replicate,y=MaxHeight, color = Condition),size=4)+
+facet_grid(.~TimePoint, scales = "free", space = "free")+
+  scale_color_brewer(palette = "Set1")+
+  geom_hline(yintercept = 120)+
+  geom_hline(yintercept = 50)+
+  theme_cowplot()+
+  theme(plot.title = element_text(hjust = 0.5),axis.text.x = element_text(angle = 70, hjust = 1))
 
 ggplot()+
-  geom_point(data = sliceDataMeta,aes(x=NormBiomass,y=Height, color = Condition, shape = TimePoint ),size=2)+
-
+  geom_smooth(data = sliceDataMeta %>% filter(MaxHeight>50 & MaxHeight<120) ,aes(y=NormBiomass,x=Height, color = Condition),size=2)+
+  geom_hline(yintercept = 0, linetype = "dashed", color = "gray")+
   theme_cowplot()+
   scale_color_brewer(palette = "Set1")+
-  facet_grid(Channel~Condition)+
+  facet_grid(Channel~TimePoint)+
+  panel_border() +
+  coord_flip()
   theme(plot.title = element_text(hjust = 0.5))
@@
 ```
+```{r Metadata info}
+#How many samples have been binarized?
+GetTiffNum<-function(sampleName){
+  parentFolder<- '/Volumes/raw_data/Confocal/Carolyn/2020/Chronic wounds/Binary Images/'
+  sampleFolder<-paste0(parentFolder, sampleName)
+  attrList<-str_split(sampleName,"_")[[1]]
+  fileList<-list.files(path = sampleFolder, full.names = TRUE)
+  tiffSlices<-(length(fileList))/3
+  results<-as.data.frame(list(sampleName, attrList[1],attrList[2],attrList[3], tiffSlices))
+  colnames(results)<- c("SampleCode","Condition", "TimePoint","Replicate","TiffSlices")
+  return(results)
+}
+tiffNum<-map(metaData.df$SampleCode, GetTiffNum)
+tiffNum<-bind_rows(tiffNum)
+sortedMetaData<-tiffNum %>% filter(TiffSlices==0)%>% select(SampleCode)
+sortedMetaData[order(sortedMetaData),]
 
-```{r read Tiff functions}
-
-VectorizeTiff<-function(file){
-    counts<-sum(as.array(readImage(fileList[slice], convert = TRUE)))
-    growth[slice,]<-c(counts, slice, species)
-  }
-
-  IterateTiff<-function(fileList, species){
-  growth<-matrix(ncol=3, nrow=length(fileList))
-  for(slice in 1:(length(fileList))){
-    counts<-sum(as.array(readImage(fileList[slice], convert = TRUE)))
-    growth[slice,]<-c(counts, slice, species)
-  }
-  growthDf<-data.fram(growth)
-return(growthDf) 
-  }
-
-testGetResults<-GetResults()
-testGetResults.df<- data.frame(testGetResults)
-#this was taken from the PropOc package
-SlicesTo3D<-function(filesList,side){
-  image1<-readTiff(filesList[1])#read first image to get its dimensions
-  image3D <- array(0, c(image1@size[1], image1@size[2], length(filesList)))#preallocate array for image given using image dimensions
-  for(i in 1:length(filesList)/3){#keep in mind that it is not zero-index
-    #print(paste("loading ch1...", i, "/", length(filesList), filesList[i]))
-    image3D[,,i]<-as.array(readImage(fileList[1], convert = TRUE))
-  }
-  return(image3D)
-}
+tiffStacksNew<-map(metaData.df$SampleCode, GetTiffNum)
+tiffStacksNew<-bind_rows(tiffStacksNew)
+tiffStacksNew %>% filter(TiffSlices==0) %>% select(SampleCode)
 

### 2021-07-06 R/PropOcDataThor.Rmd
this runs now on Thor

--- 2021-07-06 R/PropOcDataThor.Rmd
@@
 library(rdist)
-
+library(EBImage)
+library(tictoc)
+library(stringr)
 ```
@@
 #using the new 3D script with capped spheres.
-source('/home/jbarraza6/Documents/RScripts/PropOcFunctions2.0.R') 
-source('/Users/jupabago/Documents/Whiteley/PROJECTS/Rpackage/PropOc Package/R/PropOcFunctions2.0.R')
+source('/home/jbarraza6/Documents/RScripts/PropOcFunctions2.0.R') #for Thor
+source('/Users/jupabago/Documents/Whiteley/PROJECTS/Rpackage/PropOc Package/R/PropOcFunctions2.0.R') #for laptop
+
+metaData.df <-read.csv('/run/user/937561/gvfs/smb-share:server=130.207.66.142,share=raw_data/Confocal/Carolyn/2020/Chronic wounds/images metadata.csv', header = TRUE)
 
@@
   tic()
-  #parentFolder<- '/run/user/937561/gvfs/smb-share:server=130.207.66.142,share=raw_data/Confocal/Carolyn/2020/Chronic wounds/Binary Images/'
-  parentFolder<- '/Volumes/raw_data/Confocal/Carolyn/2020/Chronic wounds/Binary Images/'
+  parentFolder<- '/run/user/937561/gvfs/smb-share:server=130.207.66.142,share=raw_data/Confocal/Carolyn/2020/Chronic wounds/Binary Images/'
+  #parentFolder<- '/Volumes/raw_data/Confocal/Carolyn/2020/Chronic wounds/Binary Images/'
   sampleFolder<-paste0(parentFolder, sampleName)
@@
     print("empty set")
-    return(data.frame())
   }else{
@@
   propOcData$Replicate <- attrList[3]
-  toc()
-  write.csv(propOcData, paste0("/Volumes/raw_data/Confocal/Carolyn/2020/Chronic wounds/PropOc Data/",sampleName,".csv"))
-  return(propOcData)}
+  write.csv(propOcData, paste0("/run/user/937561/gvfs/smb-share:server=130.207.66.142,share=raw_data/Confocal/Carolyn/2020/Chronic wounds/PropOc Data/",sampleName,".csv"))
+  toc()}
   }
 
-testGetPropOcData<-GetPropOcData("mono_d1_02", .415,.52)
+testGetPropOcData<-GetPropOcData("wt_d1_02", .415,.52)
+testGetPropOcDataemptyFolder<-GetPropOcData("wt_d1_01", .415,.52)
 
-testGetPropOcDataemptyFolder<-GetPropOcData("wt_d1_01", .415,.52)
-testPmap<-pmap(list(metaData.df$SampleCode,metaData.df$xyDim, metaData.df$Zdim),
+blah<-pmap(list(metaData.df$SampleCode,metaData.df$xyDim, metaData.df$Zdim),
                GetPropOcData)
@@
 
-testGrep<-list.files(path = '/Volumes/raw_data/Confocal/Carolyn/2020/Chronic wounds/Binary Images/mono_d1_02', full.names = TRUE)
+testGrep<-list.files(path = '/run/user/937561/gvfs/smb-share:server=130.207.66.142,share=raw_data/Confocal/Carolyn/2020/Chronic wounds/Binary Images/mono_d1_02', full.names = TRUE)
 testGrepG<-testGrep[grep("G_",testGrep)]
@@
 testImage1<-as.array(readImage(testGrepG[1], convert = TRUE))
-
+install.packages("BiocManager")
+BiocManager::install("EBImage")
 ```

### 2021-07-07 R/AggregateCounts.Rmd
added accurate counts for total voxels in slice

--- 2021-06-28 R/AggregateCounts.Rmd
@@
 ##first remove irrelevant conditions
-removable <- aggregateList %>% filter(Species == "Pa" & Condition == "mono")
+removable <- bind_rows(aggregateList %>% filter(Species == "Pa" & Condition == "mono"), #Pa in Sa mono culture
+                       aggregateList%>% filter(Species == "Sa" & Condition == "pawt"),#Sa in all Pa mono cultures
+                       aggregateList%>% filter(Species == "Sa" & Condition == "papqsL"),
+                       aggregateList%>% filter(Species == "Sa" & Condition == "paphz"))
 aggregateList <- anti_join(aggregateList, removable)
-##bad samples
+##then, bad samples
 aggregateListRemoved<-aggregateList %>% filter(!SampleCode == "mono_d1_03_Pa" & !SampleCode == "mono_d1_03_Sa")
@@
 aggregateListRemoved<-aggregateList %>% filter(!SampleCode == "wt_d4_07_Pa" & !SampleCode == "wt_d4_07_Sa")
+aggregateListRemoved<-aggregateList %>% filter(!SampleCode == "papqsL_d4_02_Pa" & !SampleCode == "papqsL_d4_02_Sa")
+aggregateListRemoved<-aggregateList %>% filter(!SampleCode == "pawt_d4_05_Pa" & !SampleCode == "pawt_d4_05_Sa")
+aggregateListRemoved<-aggregateList %>% filter(!SampleCode == "phz_d4_06_Pa" & !SampleCode == "phz_d4_06_Sa")
 
@@
 aggregateList$Species <- factor(aggregateList$Species, levels = c("Pa", "Sa"),labels = c('P. aeruginosa','S. aureus'))
-aggregateList$Condition <- factor(aggregateList$Condition, levels = c("mono", "wt", "pqsL", "phz"),labels = c('Sa mono','wt co', 'pqsL co', 'phz co'))
+aggregateList$Condition <- factor(aggregateList$Condition, levels = c("mono", "pawt","papqsL", "paphz", "wt", "pqsL", "phz"),
+                                  labels = c('Sa mono', 'Pa wt mono','pqsL mono','phz mono','wt co', 'pqsL co', 'phz co'))
 aggregateList$TimePoint <- factor(aggregateList$TimePoint, levels = c("d1", "d4"),labels = c('Day 1','Day 4'))
@@
    datos$TimePoint<-as.factor(datos$TimePoint)
+   datos$SampleCode<-as.factor(datos$SampleCode)
    return(datos)
@@
 
+#Input data
+#####
+#get data from csv file
 slicedData<-GetSliceData()
+#get metadata
+metaData.df <-read.csv('/Volumes/raw_data/Confocal/Carolyn/2020/Chronic wounds/images metadata.csv', header = TRUE)
+metaData.df$SampleCode<-as.factor(metaData.df$SampleCode)
 
-#merge with metadata
-metaData.df <-read.csv('/Volumes/raw_data/Confocal/Carolyn/2020/Chronic wounds/image data copy.csv', header = TRUE)
+#merge files
+metaData.df<-metaData.df %>% select(SampleCode, mouse, Position, size, Region, Zdim, xyDim,xySize)
+sliceDataMeta<-metaData.df %>%  merge(slicedData, by = "SampleCode")
+#clean up
+remove <- bind_rows(sliceDataMeta %>% filter(Channel == 2 & Condition == "mono"),
+                    sliceDataMeta %>% filter(Channel == 1 & Condition == "pawt"),
+                    sliceDataMeta %>% filter(Channel == 1 & Condition == "paphz"),
+                    sliceDataMeta %>% filter(Channel == 1 & Condition == "papqsL"))
 
-metaData.df<-metaData.df %>% select(SampleCode, mouse, Position, size, Voxel.size,Region, Zdim)
-sliceDataMeta<-metaData.df %>%  merge(slicedData, by = "SampleCode")
-remove <- sliceDataMeta %>% filter(Channel == 2 & Condition == "mono")
 sliceDataMeta <- anti_join(sliceDataMeta, remove)
 
+sliceDataMeta<-sliceDataMeta %>% filter(!SampleCode == "mono_d1_03")
+sliceDataMeta<-sliceDataMeta %>% filter(!SampleCode == "phz_d4_14") #didnt make it to this dataset but still making sure
+sliceDataMeta<-sliceDataMeta %>% filter(!SampleCode == "pqsL_d4_02")
+sliceDataMeta<-sliceDataMeta %>% filter(!SampleCode == "pqsL_d4_04")
+sliceDataMeta<-sliceDataMeta %>% filter(!SampleCode == "pqsL_d4_10")
+sliceDataMeta<-sliceDataMeta %>% filter(!SampleCode == "wt_d4_07")
+sliceDataMeta<-sliceDataMeta %>% filter(!SampleCode == "papqsL_d4_02")
+sliceDataMeta<-sliceDataMeta %>% filter(!SampleCode == "pawt_d4_05")
+sliceDataMeta<-sliceDataMeta %>% filter(!SampleCode == "phz_d4_06")
+
+#rename variables
 sliceDataMeta$Channel <- factor(sliceDataMeta$Channel, levels = c(1, 2, 3),labels = c('S. aureus','P. aeruginosa','host'))
-sliceDataMeta<-sliceDataMeta %>% mutate(Height = Zdim*Slice)
-sliceDataMeta<-sliceDataMeta %>% group_by(SampleCode, Channel) %>% mutate(TotalBiomass = sum(Biomass)) %>% ungroup() %>% mutate(NormBiomass = Biomass/TotalBiomass*100)
+sliceDataMeta$Condition<- factor(sliceDataMeta$Condition, levels = c("mono", "pawt","papqsL", "paphz", "wt", "pqsL", "phz"),
+                                  labels = c('Sa mono', 'Pa wt mono','pqsL mono','phz mono','wt co', 'pqsL co', 'phz co'))
+sliceDataMeta$TimePoint <- factor(sliceDataMeta$TimePoint, levels = c("d1", "d4"),labels = c('Day 1','Day 4'))
+#calculate relative biomass
+sliceDataMeta<-sliceDataMeta%>% filter(!Channel == "host") %>% mutate(Height = Zdim*Slice) %>% group_by(SampleCode, Channel) %>% mutate(TotalBiomass = sum(Biomass)) %>% ungroup() %>% mutate(NormBiomass = Biomass/TotalBiomass*100)
+
+#####
+#Plot Data
+#####
+ggplot()+
+  #geom_point(data = sliceDataMeta ,aes(y=NormBiomass,x=Height, color = Condition, group = Replicate),size=.5)+
+  geom_smooth(data = sliceDataMeta ,aes(y=NormBiomass,x=Height, color = Condition),size=2)+
+  geom_hline(yintercept = 0, linetype = "dashed", color = "gray")+
+  theme_cowplot()+
+  scale_color_brewer(palette = "Set1")+
+  facet_grid(Channel~TimePoint)+
+  panel_border() +
+  coord_flip()
+  theme(plot.title = element_text(hjust = 0.5))
+#####
+#Filter by Max height of the sample
+#####  
+sliceDataSum<-sliceDataMeta %>% group_by(SampleCode, Condition, Replicate, TimePoint,xySize) %>% summarise(MaxHeight = max(Height)) %>% ungroup()
 
 ggplot()+
-  geom_point(data = sliceDataMeta,aes(x=NormBiomass,y=Height, color = Condition, shape = TimePoint ),size=2)+
-
+  geom_smooth(data = sliceDataSum %>% filter(MaxHeight>50 & MaxHeight<120) ,aes(y=NormBiomass,x=Height, color = Condition),size=2)+
+  geom_hline(yintercept = 0, linetype = "dashed", color = "gray")+
   theme_cowplot()+
   scale_color_brewer(palette = "Set1")+
-  facet_grid(Channel~Condition)+
+  facet_grid(Channel~TimePoint)+
+  panel_border() +
+  coord_flip()
   theme(plot.title = element_text(hjust = 0.5))
@@
 ```
+```{r Metadata info}
+#How many samples have been binarized?
+GetTiffNum<-function(sampleName){
+  parentFolder<- '/Volumes/raw_data/Confocal/Carolyn/2020/Chronic wounds/Binary Images/'
+  sampleFolder<-paste0(parentFolder, sampleName)
+  attrList<-str_split(sampleName,"_")[[1]]
+  fileList<-list.files(path = sampleFolder, full.names = TRUE)
+  tiffSlices<-(length(fileList))/3
+  results<-as.data.frame(list(sampleName, attrList[1],attrList[2],attrList[3], tiffSlices))
+  colnames(results)<- c("SampleCode","Condition", "TimePoint","Replicate","TiffSlices")
+  results$SampleCode<-as.factor(results$SampleCode)
+  return(results)
+}
+tiffNum<-map(metaData.df$SampleCode, GetTiffNum)
+tiffNum<-bind_rows(tiffNum)
+totalVoxels2<-metaData.df %>%  merge(tiffNum, by = "SampleCode") %>% mutate(SizeVoxels = xySize*xySize*TiffSlices)
 
-```{r read Tiff functions}
+sortedMetaData<-tiffNum %>% filter(TiffSlices==0)%>% select(SampleCode)
+sortedMetaData[order(sortedMetaData),]
 
-VectorizeTiff<-function(file){
-    counts<-sum(as.array(readImage(fileList[slice], convert = TRUE)))
-    growth[slice,]<-c(counts, slice, species)
-  }
+tiffStacksNew<-map(metaData.df$SampleCode, GetTiffNum)
+tiffStacksNew<-bind_rows(tiffStacksNew)
+tiffStacksNew %>% filter(TiffSlices==0) %>% select(SampleCode)
 
-  IterateTiff<-function(fileList, species){
-  growth<-matrix(ncol=3, nrow=length(fileList))
-  for(slice in 1:(length(fileList))){
-    counts<-sum(as.array(readImage(fileList[slice], convert = TRUE)))
-    growth[slice,]<-c(counts, slice, species)
-  }
-  growthDf<-data.fram(growth)
-return(growthDf) 
-  }
-
-testGetResults<-GetResults()
-testGetResults.df<- data.frame(testGetResults)
-#this was taken from the PropOc package
-SlicesTo3D<-function(filesList,side){
-  image1<-readTiff(filesList[1])#read first image to get its dimensions
-  image3D <- array(0, c(image1@size[1], image1@size[2], length(filesList)))#preallocate array for image given using image dimensions
-  for(i in 1:length(filesList)/3){#keep in mind that it is not zero-index
-    #print(paste("loading ch1...", i, "/", length(filesList), filesList[i]))
-    image3D[,,i]<-as.array(readImage(fileList[1], convert = TRUE))
-  }
-  return(image3D)
-}
-
+#How big are each of the image in bits?
+totalVoxels<-sliceDataMeta %>% group_by(SampleCode, Condition, Replicate, TimePoint,xySize) %>% summarise(MaxSlice = max(Slice)) %>% ungroup() %>% mutate(ImageVoxels = MaxSlice*xySize)
 ```

### 2021-07-12 R/PropOcDataThor.Rmd

@@
 
-GetPropOcData<-function(sampleName, xyDim,zDim){
+for(row in 1:length(metaData.df[[1]])){
+  metaData.df$Condition[[row]] = str_split(metaData.df$SampleCode[[row]],"_")[[1]][[1]]
+}
+metaData.df<-metaData.df %>% filter(!is.na(mouse))#removes the last row
+
+metaData.df<- metaData.df %>% #remove samples that have already ran
+  filter(!SampleCode == "pqsL_d4_16") %>%
+  filter(!SampleCode == "mono_d1_03") %>%#stalled
+  filter(!SampleCode == "mono_d1_02") %>% #ran
+  filter(!SampleCode == "mono_d1_01") %>% #ran
+  filter(!SampleCode == "mono_d1_04") %>% #ran
+  filter(!SampleCode == "mono_d1_05") %>% #ran
+  filter(!SampleCode == "mono_d1_06") %>%  #seemed to have stalled but data file is saved
+  filter(!SampleCode == "mono_d1_07") %>% #seemed to have stalled but data file is saved
+  filter(!SampleCode == "mono_d1_08") %>%
+  filter(!SampleCode == "mono_d1_09") %>%
+  filter(!SampleCode == "mono_d1_10") %>%
+  filter(!SampleCode == "mono_d1_11") %>%
+  filter(!SampleCode == "mono_d1_12") %>%
+  filter(!SampleCode == "mono_d1_13") %>%
+  filter(!SampleCode == "mono_d1_14") %>%
+  filter(!SampleCode == "mono_d1_15") %>%
+  filter(!SampleCode == "mono_d4_01") %>%
+  filter(!SampleCode == "mono_d4_02") %>%
+  filter(!SampleCode == "mono_d4_03") %>%
+  filter(!SampleCode == "mono_d4_04")
+
+metaData.df<-metaData.df %>% filter(!Condition == "mono") %>% 
+  filter(!Condition == "pawt") %>% 
+  filter(!Condition == "paphz") %>% 
+  filter(!Condition == "papqsL")
+
   tic()
@@
                                      xydimSearch=round(30/xyDim),zdimSearch =round(30/zDim),
-                                     sampleSize=10,xyRealDim=xyDim,
+                                     sampleSize=1000,xyRealDim=xyDim,
                                      zRealDim = zDim, pipeBinSize = 1)
@@
 
-testGetPropOcData<-GetPropOcData("wt_d1_02", .415,.52)
+testGetPropOcData<-GetPropOcData("phz_d4_08", .415,.52)
 testGetPropOcDataemptyFolder<-GetPropOcData("wt_d1_01", .415,.52)
@@
 
-testSlices2threeD<-Slices2threeD(testGrepG)
-testGrepG[1]
-testImage1<-as.array(readImage(testGrepG[1], convert = TRUE))
-install.packages("BiocManager")
-BiocManager::install("EBImage")
 ```

### 2021-07-14 R/AggregateCounts.Rmd
added culture and strain columns to data and all worked

@@
 ```{r aggregate input}
-aggregateList<-GetAggregates()#this reads the data from Matlab
-#remove bad samples and irrelevant conditions
-##first remove irrelevant conditions
-removable <- bind_rows(aggregateList %>% filter(Species == "Pa" & Condition == "mono"), #Pa in Sa mono culture
-                       aggregateList%>% filter(Species == "Sa" & Condition == "pawt"),#Sa in all Pa mono cultures
-                       aggregateList%>% filter(Species == "Sa" & Condition == "papqsL"),
-                       aggregateList%>% filter(Species == "Sa" & Condition == "paphz"))
-aggregateList <- anti_join(aggregateList, removable)
-##then, bad samples
-aggregateListRemoved<-aggregateList %>% filter(!SampleCode == "mono_d1_03_Pa" & !SampleCode == "mono_d1_03_Sa")
-aggregateListRemoved<-aggregateList %>% filter(!SampleCode == "phz_d4_14_Pa" & !SampleCode == "phz_d4_14_Sa")
-aggregateListRemoved<-aggregateList %>% filter(!SampleCode == "pqsL_d4_02_Pa" & !SampleCode == "pqsL_d4_02_Sa")
-aggregateListRemoved<-aggregateList %>% filter(!SampleCode == "pqsL_d4_04_Pa" & !SampleCode == "pqsL_d4_04_Sa")
-aggregateListRemoved<-aggregateList %>% filter(!SampleCode == "pqsL_d4_10_Pa" & !SampleCode == "pqsL_d4_10_Sa")
-aggregateListRemoved<-aggregateList %>% filter(!SampleCode == "wt_d4_07_Pa" & !SampleCode == "wt_d4_07_Sa")
-aggregateListRemoved<-aggregateList %>% filter(!SampleCode == "papqsL_d4_02_Pa" & !SampleCode == "papqsL_d4_02_Sa")
-aggregateListRemoved<-aggregateList %>% filter(!SampleCode == "pawt_d4_05_Pa" & !SampleCode == "pawt_d4_05_Sa")
-aggregateListRemoved<-aggregateList %>% filter(!SampleCode == "phz_d4_06_Pa" & !SampleCode == "phz_d4_06_Sa")
-
-#add proper labels for plots
-aggregateList$Species <- factor(aggregateList$Species, levels = c("Pa", "Sa"),labels = c('P. aeruginosa','S. aureus'))
-aggregateList$Condition <- factor(aggregateList$Condition, levels = c("mono", "pawt","papqsL", "paphz", "wt", "pqsL", "phz"),
-                                  labels = c('Sa mono', 'Pa wt mono','pqsL mono','phz mono','wt co', 'pqsL co', 'phz co'))
-aggregateList$TimePoint <- factor(aggregateList$TimePoint, levels = c("d1", "d4"),labels = c('Day 1','Day 4'))
 #agregate input functions
@@
 }
+
+#run functions
+aggregateList<-GetAggregates()#this reads the data from Matlab
+#remove bad samples and irrelevant conditions
+##first remove irrelevant conditions
+removable <- bind_rows(aggregateList %>% filter(Species == "Pa" & Condition == "mono"), #Pa in Sa mono culture
+                       aggregateList%>% filter(Species == "Sa" & Condition == "pawt"),#Sa in all Pa mono cultures
+                       aggregateList%>% filter(Species == "Sa" & Condition == "papqsL"),
+                       aggregateList%>% filter(Species == "Sa" & Condition == "paphz"))
+aggregateList <- anti_join(aggregateList, removable)
+##then, bad samples
+aggregateList<-aggregateList %>% filter(!SampleCode == "mono_d1_03_Pa" & !SampleCode == "mono_d1_03_Sa")
+aggregateList<-aggregateList %>% filter(!SampleCode == "phz_d4_14_Pa" & !SampleCode == "phz_d4_14_Sa")
+aggregateList<-aggregateList %>% filter(!SampleCode == "pqsL_d4_02_Pa" & !SampleCode == "pqsL_d4_02_Sa")
+aggregateList<-aggregateList %>% filter(!SampleCode == "pqsL_d4_04_Pa" & !SampleCode == "pqsL_d4_04_Sa")
+aggregateList<-aggregateList %>% filter(!SampleCode == "pqsL_d4_10_Pa" & !SampleCode == "pqsL_d4_10_Sa")
+aggregateList<-aggregateList %>% filter(!SampleCode == "wt_d4_07_Pa" & !SampleCode == "wt_d4_07_Sa")
+aggregateList<-aggregateList %>% filter(!SampleCode == "papqsL_d4_02_Pa" & !SampleCode == "papqsL_d4_02_Sa")
+aggregateList<-aggregateList %>% filter(!SampleCode == "pawt_d4_05_Pa" & !SampleCode == "pawt_d4_05_Sa")
+aggregateList<-aggregateList %>% filter(!SampleCode == "phz_d4_06_Pa" & !SampleCode == "phz_d4_06_Sa")
+
+#add proper labels for plots
+aggregateList$Species <- factor(aggregateList$Species, levels = c("Pa", "Sa"),labels = c('P. aeruginosa','S. aureus'))
+aggregateList$Condition <- factor(aggregateList$Condition, levels = c("mono", "pawt","papqsL", "paphz", "wt", "pqsL", "phz"),
+                                  labels = c('Sa mono', 'Pa wt mono','pqsL mono','phz mono','wt co', 'pqsL co', 'phz co'))
+aggregateList$TimePoint <- factor(aggregateList$TimePoint, levels = c("d1", "d4"),labels = c('Day 1','Day 4'))
+
+aggregateList<-aggregateList %>% mutate(Culture = recode(Condition, 'Sa mono' = "mono", 'Pa wt mono' = "mono",'pqsL mono'= "mono",'phz mono'= "mono",'wt co'= "co", 'pqsL co'= "co", 'phz co'= "co"))
+aggregateList<-aggregateList%>% mutate(Strain = recode(Condition, 'Sa mono' = "Sa", 'Pa wt mono' = "wt",'pqsL mono'= "pqsL",'phz mono'= "phz",'wt co'= "wt", 'pqsL co'= "pqsL", 'phz co'= "phz"))
+
 ```
@@
 #Get aggregate summary per sample
-aggregateListSummaryReplicate<-aggregateList%>% group_by(Species, TimePoint, Condition, Replicate) %>% 
+aggregateListSummaryReplicate<-aggregateList%>% group_by(Species, Strain, Culture,TimePoint, Condition, Replicate) %>% 
   summarise(Aggs = n(), biomass = sum(Size), meanAggSize = mean(Size), seAggSize = std.error(Size), maxSize = max(Size), minSize = min(Size)) %>%
@@
 ggplot()+ 
-  geom_jitter(data = aggregateListSummaryReplicate, aes(x = TimePoint, y= meanAggSize, color = Condition,shape = "MeanSize"),size = 3, height = 0, width = .3)+
-  geom_jitter(data = aggregateListSummaryReplicate, aes(x = TimePoint, y= maxSize, color = Condition, shape = "MaxSize"),size = 3, height = 0, width = .3)+
-  geom_jitter(data = aggregateListSummaryReplicate, aes(x = TimePoint, y= biomass, color = Condition, shape = "TotalBiomass"),size = 3, height = 0,width= .3)+
+  geom_jitter(data = aggregateListSummaryReplicate, aes(x = TimePoint, y= meanAggSize, color = Strain,shape = "MeanSize"),size = 3, height = 0, width = .3)+
+  geom_jitter(data = aggregateListSummaryReplicate, aes(x = TimePoint, y= maxSize, color = Strain, shape = "MaxSize"),size = 3, height = 0, width = .3)+
+  geom_jitter(data = aggregateListSummaryReplicate, aes(x = TimePoint, y= biomass, color = Strain, shape = "TotalBiomass"),size = 3, height = 0,width= .3)+
   scale_y_log10( breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
-  facet_grid(.~Species, scales = "free", space = "free") +
+  facet_grid(Species~Culture, scales = "free", space = "free") +
   ggtitle('Mean size and largest aggregate and total biomass per sample')+
@@
 #Get aggregate Summary per condition
-aggregateListSummary<-aggregateList %>% group_by(Species, TimePoint, Condition) %>% 
+aggregateListSummary<-aggregateList %>% group_by(Species, Strain, Culture,TimePoint, Condition) %>% 
   summarise(Aggs = n(), biomass = sum(Size), meanAggSize = mean(Size), seAggSize = std.error(Size), maxSize = max(Size), minSize = min(Size)) %>%
@@
 #####
+#Version 1
 ggplot()+ 
@@
           strip.background = element_rect(color="black", fill="white", size=1, linetype="solid"))
+#Version 2
+ggplot()+ 
+  geom_jitter(data = aggregateListSummary, aes(x = TimePoint, y= meanAggSize, color = Strain,shape = "MeanSize"),size = 3, height = 0, width = .3)+
+  geom_jitter(data = aggregateListSummary, aes(x = TimePoint, y= maxSize, color = Strain, shape = "MaxSize"),size = 3, height = 0, width = .3)+
+  geom_jitter(data = aggregateListSummary, aes(x = TimePoint, y= biomass, color = Strain, shape = "TotalBiomass"),size = 3, height = 0,width= .3)+
+  scale_y_log10( breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
+  facet_grid(Species~Culture, scales = "free", space = "free") +
+  ggtitle('Mean size and largest aggregate and total biomass per condition')+
+  labs(x = "",y = bquote(paste("Volume (", mu*"m"^3*")")))+
+  scale_shape_manual(name="Metric",values=c(MeanSize=1, MaxSize=2, TotalBiomass=17))+
+  scale_color_brewer(palette = "Set1")+
+  theme_cowplot()+
+  theme(plot.title = element_text(hjust = 0.5),strip.text = element_text(size = 11, face = "italic",margin = margin(.1,0,.1,0, "cm")),#this is for the facets
+          strip.background = element_rect(color="black", fill="white", size=1, linetype="solid"))
+
 #####
@@
                         Size<= 100000 ~ 100000,
-                        Size > 100000 ~ 1000000)) %>% group_by(Species,Condition,TimePoint, Replicate)%>% 
-  mutate(TotalBiomass = sum(Size), TotalFrequency = n()) %>% ungroup() %>% group_by(Species,Condition,TimePoint, Replicate, LogBin)%>%
+                        Size > 100000 ~ 1000000)) %>% group_by(Species,Culture,Strain, Condition,TimePoint, Replicate)%>% 
+  mutate(TotalBiomass = sum(Size), TotalFrequency = n()) %>% ungroup() %>% 
+  group_by(Species,Culture,Strain, Condition,TimePoint, Replicate, LogBin)%>%
   mutate(BinBiomass = sum(Size), BinFrequency = n()) %>% ungroup() %>%
@@
 #This is weird, but I want to have the histogram above with all the data, and the one below with only the bins
-HistReplicateSummary<-HistReplicate %>% group_by(Species,Condition,TimePoint, Replicate, LogBin,NormalizedFrequency,NormalizedBiomass) %>% summarize() %>%  unique()%>%ungroup() %>%  group_by(Species,Condition,TimePoint, Replicate) %>% mutate(checkSumFreq =sum(NormalizedFrequency), checkSumBiomass = sum(NormalizedBiomass))
+HistReplicateSummary<-HistReplicate %>% 
+  group_by(Species,Culture,Strain, Condition,TimePoint, Replicate, LogBin,NormalizedFrequency,NormalizedBiomass) %>% summarize() %>%
+  unique()%>%ungroup() %>%  group_by(Species,Culture,Condition,TimePoint, Replicate) %>% 
+  mutate(checkSumFreq =sum(NormalizedFrequency), checkSumBiomass = sum(NormalizedBiomass))
 
@@
                         Size<= 100000 ~ 100000,
-                        Size > 100000 ~ 1000000)) %>% group_by(Species,Condition,TimePoint)%>% 
+                        Size > 100000 ~ 1000000)) %>% group_by(Species,Culture,Strain, Condition,TimePoint)%>% 
   mutate(TotalBiomass = sum(Size), TotalFrequency = n()) %>% ungroup() %>%
-  group_by(Species,Condition,TimePoint,LogBin)%>%
+  group_by(Species,Culture,Strain, Condition,TimePoint,LogBin)%>%
   mutate(BinBiomass = sum(Size), BinFrequency = n()) %>% ungroup() %>%
@@
 HistConditionSummary<-HistCondition %>%
-  group_by(Species,Condition,TimePoint,LogBin,NormalizedFrequency,NormalizedBiomass) %>% summarize() %>% 
-  unique()%>%ungroup() %>%  group_by(Species,Condition,TimePoint) %>% 
+  group_by(Species,Culture,Strain, Condition,TimePoint,LogBin,NormalizedFrequency,NormalizedBiomass) %>% summarize() %>% 
+  unique()%>%ungroup() %>%  group_by(Species,Culture,Condition,TimePoint) %>% 
   mutate(checkSumFreq =sum(NormalizedFrequency), checkSumBiomass = sum(NormalizedBiomass))
@@
 ggplot()+
-    geom_jitter(data = HistReplicateSummary,aes(x=as.factor(LogBin),y=.data[[y_var]],  color =Condition ),size=3, height = 0, width = .2, shape = 1)+
-    geom_point(data = HistConditionSummary,aes(x=as.factor(LogBin),y=.data[[y_var]],  color =Condition,group = Condition),size=4, shape = 16, position = position_dodge(width = .5) )+
+    geom_jitter(data = rep.df,aes(x=as.factor(LogBin),y=.data[[y_var]],  color =Condition),size=3, height = 0, width = .2, shape = 1)+
+    geom_point(data = cond.df,aes(x=as.factor(LogBin),y=.data[[y_var]],  color =Condition,group = Condition),size=4, shape = 16, position = position_dodge(width = .5) )+
     scale_y_log10(breaks = c(100, 10, 1, .1, .01), labels = c(100, 10, 1, .1, .01))+
@@
                         Size<= 100000 ~ 100000,
-                        Size > 100000 ~ 1000000)) %>% filter(!LogBin == 5) %>% group_by(Species,Condition,TimePoint, Replicate)%>% 
-  mutate(TotalBiomass = sum(Size), TotalFrequency = n()) %>% ungroup() %>% group_by(Species,Condition,TimePoint, Replicate, LogBin)%>%
+                        Size > 100000 ~ 1000000)) %>% filter(!LogBin == 5) %>% group_by(Species,Culture,Strain,Condition,TimePoint, Replicate)%>% 
+  mutate(TotalBiomass = sum(Size), TotalFrequency = n()) %>% ungroup() %>% group_by(Species,Culture,Strain,Condition,TimePoint, Replicate, LogBin)%>%
   mutate(BinBiomass = sum(Size), BinFrequency = n()) %>% ungroup() %>%
@@
 ##Summary df
-aggsHistRepSum<-aggsHistRep %>% group_by(Species,Condition,TimePoint, Replicate, LogBin,NormalizedFrequency,NormalizedBiomass) %>% summarize() %>%  unique()%>%ungroup() %>%  group_by(Species,Condition,TimePoint, Replicate) %>% mutate(checkSumFreq =sum(NormalizedFrequency), checkSumBiomass = sum(NormalizedBiomass))
+aggsHistRepSum<-aggsHistRep %>% group_by(Species,Culture,Strain,Condition,TimePoint, Replicate, LogBin,NormalizedFrequency,NormalizedBiomass) %>% summarize() %>%  unique()%>%ungroup() %>%  group_by(Species,Culture,Strain,Condition,TimePoint, Replicate) %>% mutate(checkSumFreq =sum(NormalizedFrequency), checkSumBiomass = sum(NormalizedBiomass))
 
@@
                         Size<= 100000 ~ 100000,
-                        Size > 100000 ~ 1000000)) %>% filter(!LogBin == 5) %>% group_by(Species,Condition,TimePoint)%>% 
-  mutate(TotalBiomass=sum(Size),TotalFrequency=n()) %>% ungroup() %>% group_by(Species,Condition,TimePoint, LogBin)%>%
+                        Size > 100000 ~ 1000000)) %>% filter(!LogBin == 5) %>% group_by(Species,Culture,Strain,Condition,TimePoint)%>% 
+  mutate(TotalBiomass=sum(Size),TotalFrequency=n()) %>% ungroup() %>% group_by(Species,Culture,Strain,Condition,TimePoint, LogBin)%>%
   mutate(BinBiomass = sum(Size), BinFrequency = n()) %>% ungroup() %>%
@@
 ##Summary df
-aggsHistCondSum<-aggsHistCond %>% group_by(Species,Condition,TimePoint, Replicate, LogBin,NormalizedFrequency,NormalizedBiomass) %>% summarize() %>%  unique()%>%ungroup() %>%  group_by(Species,Condition,TimePoint, Replicate) %>% mutate(checkSumFreq =sum(NormalizedFrequency), checkSumBiomass = sum(NormalizedBiomass))%>%ungroup()
+aggsHistCondSum<-aggsHistCond %>% group_by(Species,Culture,Strain,Condition,TimePoint, Replicate, LogBin,NormalizedFrequency,NormalizedBiomass) %>% summarize() %>%  unique()%>%ungroup() %>%  group_by(Species,Culture,Strain,Condition,TimePoint, Replicate) %>% mutate(checkSumFreq =sum(NormalizedFrequency), checkSumBiomass = sum(NormalizedBiomass))%>%ungroup()
 
@@
 HistReplicate<-HistReplicate %>%  mutate(Aggregation = case_when(LogBin == 5 ~"Planktonic",LogBin>5 ~ "Aggregate")) %>%
-  group_by(Species,Condition,TimePoint, Replicate, Aggregation)%>% 
+  group_by(Species,Culture,Condition,Strain,TimePoint, Replicate, Aggregation)%>% 
   mutate(AgPlBiomass = sum(Size), AgPlFreq = n()) %>% ungroup() %>%
@@
 #Collapse to only values per replicate
-plankAggHistRep<-HistReplicate %>% group_by(Species,Condition,TimePoint, Replicate, Aggregation,AgPlNormFrequency,AgPlNormBiomass) %>% summarize() %>%  unique()%>%ungroup() %>%  group_by(Species,Condition,TimePoint, Replicate) %>% mutate(checkAggFreq =sum(AgPlNormFrequency), checkAggBiomass = sum(AgPlNormBiomass))
+plankAggHistRep<-HistReplicate %>% group_by(Species,Culture,Condition,Strain,TimePoint, Replicate, Aggregation,AgPlNormFrequency,AgPlNormBiomass) %>% summarize() %>%  unique()%>%ungroup() %>%  group_by(Species,Culture,Strain,Condition,TimePoint, Replicate) %>% mutate(checkAggFreq =sum(AgPlNormFrequency), checkAggBiomass = sum(AgPlNormBiomass))
 
@@
 HistCondition<-HistCondition %>%  mutate(Aggregation = case_when(LogBin == 5 ~"Planktonic",LogBin>5 ~ "Aggregate")) %>%
-  group_by(Species,Condition,TimePoint, Aggregation)%>% 
+  group_by(Species,Culture,Condition,Strain, TimePoint, Aggregation)%>% 
   mutate(AgPlBiomass = sum(Size), AgPlFreq = n()) %>% ungroup() %>%
@@
 #Collapse to only values per replicate
-plankAggHistCond<-HistCondition %>% group_by(Species,Condition,TimePoint, Aggregation,AgPlNormFrequency,AgPlNormBiomass) %>% summarize() %>%  unique()%>%ungroup() %>%  group_by(Species,Condition,TimePoint) %>% mutate(checkAggFreq =sum(AgPlNormFrequency), checkAggBiomass = sum(AgPlNormBiomass))
+plankAggHistCond<-HistCondition %>% group_by(Species,Culture,Condition,Strain,TimePoint, Aggregation,AgPlNormFrequency,AgPlNormBiomass) %>% summarize() %>%  unique()%>%ungroup() %>%  group_by(Species,Culture,Strain, Condition,TimePoint) %>% mutate(checkAggFreq =sum(AgPlNormFrequency), checkAggBiomass = sum(AgPlNormBiomass))
 
@@
 #####
-#Collapse dataframe to values per condition
-plankAggHistSummary<-plankAggHistRep %>% group_by(Species,TimePoint, Condition,Aggregation) %>%
+#Do stats on the df that has each replicate
+plankAggHistSummary<-plankAggHistRep %>% group_by(Species,TimePoint,Culture,Strain,Condition,Aggregation) %>%
   summarise(MeanFreq = mean(AgPlNormFrequency), SEFreq = std.error(AgPlNormFrequency), MeanBiomass = mean(AgPlNormBiomass),
             SEBiomass = std.error(AgPlNormBiomass))
+
 #Plot using the code from the paper
+
+PlotAggregateBiomassContribution<-function(species){
 ggplot()+
-  geom_col(data = plankAggHistSummary %>% filter(Aggregation=="Aggregate"),aes(x=Aggregation,y=MeanBiomass, fill = Condition),
+  geom_col(data = plankAggHistSummary %>% filter(Aggregation=="Aggregate") %>% filter(Species==species), aes(x=Strain,y=MeanBiomass, fill = Culture),
            size=3,position = position_dodge( width = .9))+
-  geom_jitter(data = plankAggHistRep%>% filter(Aggregation=="Aggregate"),aes(x=Aggregation,y=AgPlNormBiomass, group = Condition),shape = 1,size=2,position = position_dodge(width = .9),show.legend = FALSE)+
-  geom_errorbar(data = plankAggHistSummary%>% filter(Aggregation=="Aggregate"),aes(x=Aggregation,ymin=(MeanBiomass-SEBiomass), ymax = (MeanBiomass+SEBiomass), group = Condition),width = 0, size=.5,position = position_dodge(width = .9))+
+  geom_jitter(data = plankAggHistRep%>% filter(Aggregation=="Aggregate")%>% filter(Species==species), aes(x=Strain,y=AgPlNormBiomass, group = Culture),
+              shape = 1,size=2,position = position_dodge(width = .9),show.legend = FALSE)+
+  geom_errorbar(data = plankAggHistSummary%>% filter(Aggregation=="Aggregate")%>% filter(Species==species), aes(x=Strain,ymin=(MeanBiomass-SEBiomass), ymax = (MeanBiomass+SEBiomass), group = Culture),width = 0, size=.5,position = position_dodge(width = .9))+
   scale_y_continuous(limits = c(0,103),expand = expand_scale(mult = c(0, 0)))+
-  facet_grid(TimePoint~Species)+
-  scale_fill_brewer(palette = "Set1")+
-  labs(title = '', x = "", y = "Biomass contribution (%)")+
+  facet_grid(.~TimePoint)+
+  scale_fill_grey()+
+  labs(title = '', x = "", y = "Aggregate Biomass contribution (%)")+
   theme_cowplot()+
@@
         legend.title = element_text(size=13),legend.text = element_text(size = 11),
-        legend.position = c(.45, 0.60))
+        legend.position = c(.25, 0.60))
+}
+PlotAggregateBiomassContribution("P. aeruginosa")
+PlotAggregateBiomassContribution("S. aureus")
+
 #####
@@
 #Collapse to data per condition
-AggsOnlySummary<-aggsHistRepSum %>% group_by(Species,TimePoint, Condition,LogBin) %>%
+AggsOnlySummary<-aggsHistRepSum %>% group_by(Species,TimePoint,Culture, Strain, Condition,LogBin) %>%
   summarise(MeanFreq = mean(NormalizedFrequency), SEFreq = std.error(NormalizedFrequency), MeanBiomass = mean(NormalizedBiomass),
@@
 #Plot Frequency using code from the paper
+PlotFrequencyAggregateSize<-function(species){
 ggplot()+
-    geom_col(data = AggsOnlySummary, aes(x=as.factor(LogBin),y=MeanFreq,  fill =Condition ),size=4,position = position_dodge( width = .9))+
-    geom_jitter(data = aggsHistRepSum, aes(x=as.factor(LogBin),y=NormalizedFrequency, group = Condition),shape = 1,size=2,position = position_dodge( width = .9))+
-    geom_errorbar(data = AggsOnlySummary,aes(x=as.factor(LogBin),ymin=(MeanFreq-SEFreq), ymax = (MeanFreq+SEFreq), group = Condition),width = 0, size= .5,position = position_dodge( width = .9))+
-    facet_grid(TimePoint~Species)+
+    geom_col(data = AggsOnlySummary %>% filter(Species == species), aes(x=as.factor(LogBin),y=MeanFreq,  fill =Condition ),size=4,position = position_dodge( width = .9))+
+    geom_jitter(data = aggsHistRepSum%>% filter(Species == species), aes(x=as.factor(LogBin),y=NormalizedFrequency, group = Condition),shape = 1,size=2,position = position_dodge( width = .9))+
+    geom_errorbar(data = AggsOnlySummary%>% filter(Species == species),aes(x=as.factor(LogBin),ymin=(MeanFreq-SEFreq), ymax = (MeanFreq+SEFreq), group = Condition),width = 0, size= .5,position = position_dodge( width = .9))+
+    facet_grid(.~TimePoint)+
     labs(fill = "",y = "Aggregates Frequency per bin (% of total)",x = bquote(paste("Aggregate Volume (", mu*"m"^3*")")))+
@@
           legend.position = c(0.79, 0.80))
-#Plot Normalized Biomass
-AggsOnlySummaryRep<-aggsHistRepSum %>% group_by(Species,TimePoint, Replicate, Condition,LogBin) %>%
+}
+PlotFrequencyAggregateSize("S. aureus")
+PlotFrequencyAggregateSize("P. aeruginosa")#add culture to facets
+
+PlotFrequencyAggregateSize2<-function(species){
+ggplot()+
+    geom_col(data = aggsHistCondSum %>% filter(Species == species), aes(x=as.factor(LogBin),y=NormalizedFrequency,  fill =Condition ),size=4,position = position_dodge( width = .9))+
+    geom_jitter(data = aggsHistRepSum%>% filter(Species == species), aes(x=as.factor(LogBin),y=NormalizedFrequency, group = Condition),shape = 1,size=2,position = position_dodge( width = .9))+
+    #geom_errorbar(data = AggsOnlySummary%>% filter(Species == species),aes(x=as.factor(LogBin),ymin=(MeanFreq-SEFreq), ymax = (MeanFreq+SEFreq), group = Condition),width = 0, size= .5,position = position_dodge( width = .9))+
+    facet_grid(.~TimePoint)+
+    labs(fill = "",y = "Aggregates Frequency per bin (% of total)",x = bquote(paste("Aggregate Volume (", mu*"m"^3*")")))+
+    #guides(color = FALSE)+
+    #scale_y_continuous(limits = c(0,180), expand = expand_scale(mult = c(0, 0)))+
+    theme_half_open()+
+    scale_fill_brewer(palette = "Set1")+
+    theme(plot.title = element_text(hjust = 0.5),
+          strip.text = element_text(size = 9, face = "italic",margin = margin(.1,0,.1,0, "cm")),#this is for the facets
+          strip.background = element_rect(color="black", fill="white", size=.5, linetype="solid"),
+          plot.margin = unit(c(0,.5,0,.5), "cm"),
+          axis.title.x = element_text(margin = margin(0,0,0,0),size=13),axis.text.x = element_text(margin = margin(1,0,0,0),size=11),
+          axis.title.y = element_text(margin = margin(0,4,0,0),size=13),axis.text.y = element_text(margin = margin(0,2,2,0),size=11),
+          legend.title = element_text(size=13),legend.text = element_text(size = 11),
+          legend.position = c(0.79, 0.80))
+}
+PlotFrequencyAggregateSize2("S. aureus")
+PlotFrequencyAggregateSize2("P. aeruginosa")#add culture to facets and change condition for strain on fill and group
+
+#Plot Normalized Biomass #I am not using this one
+AggsOnlySummaryRep<-aggsHistRepSum %>% group_by(Species,TimePoint, Replicate, Condition,Culture, Strain,LogBin) %>%
   summarise(MeanFreq = mean(NormalizedFrequency), SEFreq = std.error(NormalizedFrequency), MeanBiomass = mean(NormalizedBiomass),
             SEBiomass = std.error(NormalizedBiomass))
+PlotBiomassAggregateSize<-function( species){
 ggplot()+
-    geom_col(data = AggsOnlySummary, aes(x=as.factor(LogBin),y=MeanBiomass,  fill =Condition ),size=4,position = position_dodge( width = .9))+
-    #geom_jitter(data = aggsOnlyHistSummary.df, aes(x=as.factor(LogBin),y=NormalizedBiomass, group = TimePoint),shape = 1,size=2,position = position_dodge( width = .9))+
-    geom_errorbar(data = AggsOnlySummary,aes(x=as.factor(LogBin),ymin=(MeanBiomass-SEBiomass), ymax = (MeanBiomass+SEBiomass), group = Condition),width = 0, size= .5,position = position_dodge( width = .9))+
-    facet_grid(TimePoint~Species)+
+    geom_col(data = AggsOnlySummary %>% filter(Species == species), aes(x=as.factor(LogBin),y=MeanBiomass,  fill =Condition ),size=4,position = position_dodge( width = .9))+
+    geom_jitter(data = aggsHistRepSum%>% filter(Species == species), aes(x=as.factor(LogBin),y=NormalizedBiomass, group = Condition),shape = 1,size=1,position = position_dodge( width = .9))+
+    geom_errorbar(data = AggsOnlySummary%>% filter(Species == species),aes(x=as.factor(LogBin),ymin=(MeanBiomass-SEBiomass), ymax = (MeanBiomass+SEBiomass), group = Condition),width = 0, size= .5,position = position_dodge( width = .9))+
+    facet_grid(.~TimePoint)+
     labs(fill = "",y = "Biomass contribution per bin (% of total)",x = bquote(paste("Aggregate Volume (", mu*"m"^3*")")))+
@@
           legend.position = c(0.79, 0.80))
+}
+PlotBiomassAggregateSize("P. aeruginosa")
+PlotBiomassAggregateSize("S. aureus")
+
+#the other way to do it is using aggsHistCondSum and normalized biomass
+PlotBiomassAggregateSize2<-function( species){
+ggplot()+
+    geom_col(data = aggsHistCondSum %>% filter(Species == species), aes(x=as.factor(LogBin),y=NormalizedBiomass,  fill =Condition ),size=4,position = position_dodge( width = .9))+
+    geom_jitter(data = aggsHistRepSum%>% filter(Species == species), aes(x=as.factor(LogBin),y=NormalizedBiomass, group = Condition),shape = 1,size=1,position = position_dodge( width = .9))+
+    #geom_errorbar(data = aggsHistCondSum%>% filter(Species == species),aes(x=as.factor(LogBin),ymin=(MeanBiomass-SEBiomass), ymax = (MeanBiomass+SEBiomass), group = Condition),width = 0, size= .5,position = position_dodge( width = .9))+
+    facet_grid(.~TimePoint)+
+    labs(fill = "",y = "Biomass contribution per bin (% of total)",x = bquote(paste("Aggregate Volume (", mu*"m"^3*")")))+
+    #guides(color = FALSE)+
+    scale_y_continuous(limits = c(0,100), expand = expand_scale(mult = c(0, 0)))+
+    scale_fill_brewer(palette = "Set1")+
+    theme_half_open()+
+    theme(plot.title = element_text(hjust = 0.5),
+          strip.text = element_text(size = 9, face = "italic",margin = margin(.1,0,.1,0, "cm")),#this is for the facets
+          strip.background = element_rect(color="black", fill="white", size=.5, linetype="solid"),
+          plot.margin = unit(c(0,.5,0,.5), "cm"),
+          axis.title.x = element_text(margin = margin(0,0,0,0),size=13),axis.text.x = element_text(margin = margin(1,0,0,0),size=11),
+          axis.title.y = element_text(margin = margin(0,4,0,0),size=13),axis.text.y = element_text(margin = margin(0,2,2,0),size=11),
+          legend.title = element_text(size=13),legend.text = element_text(size = 11),
+          legend.position = c(0.79, 0.80))
+}
+PlotBiomassAggregateSize2("P. aeruginosa")
+PlotBiomassAggregateSize2("S. aureus")
+
 #####
@@
 
+```{r biomass per slice}
+#this was taken from "Microscopy data clean.Rmd" 
+GetSliceData<-function(){#import all experiments at once
+  folder<- '/Volumes/raw_data/Confocal/Carolyn/2020/Chronic wounds/Results per slice'
+   fileList<-list.files(path = folder, full.names = TRUE)
+   growthDf<-data.frame()
+   for (aggList in 1:length(fileList)){
+     fileName<-str_split(basename(fileList[aggList]), "\\.")[[1]][1]#this selects the base file name and removes the ".csv"
+     attrList<-str_split(fileName,"_")[[1]]
+     growthDf<-rbind(growthDf,ReadSliceFile(fileList[aggList],attrList[2],attrList[1],attrList[3], fileName))
+     }
+   return(growthDf)
+}
+
+ReadSliceFile<-function(file, timepoint, condition, replicate, sampleCode){#make a dataframe of the aggregate size list and add experimental parameters
+  print(file)
+   datos <-read.csv(file, header = F)  
+   colnames(datos)<-c('Biomass', 'Channel', 'Slice') 
+   datos<-datos %>% mutate(TimePoint = timepoint) 
+   datos<-datos %>% mutate(Condition = condition)
+   datos<-datos %>% mutate(Replicate = replicate)
+   datos<-datos %>% mutate(SampleCode = sampleCode)
+   datos$Replicate<-as.factor(datos$Replicate)
+   datos$Condition<-as.factor(datos$Condition)
+   datos$TimePoint<-as.factor(datos$TimePoint)
+   datos$SampleCode<-as.factor(datos$SampleCode)
+   return(datos)
+}
+
+#Input data
+#####
+#get data from csv file
+slicedData<-GetSliceData()
+#get metadata
+metaData.df <-read.csv('/Volumes/raw_data/Confocal/Carolyn/2020/Chronic wounds/images metadata.csv', header = TRUE)
+metaData.df$SampleCode<-as.factor(metaData.df$SampleCode)
+
+#merge files
+metaData.df<-metaData.df %>% select(SampleCode, mouse, Position, size, Region, Zdim, xyDim,xySize)
+sliceDataMeta<-metaData.df %>%  merge(slicedData, by = "SampleCode")
+#clean up
+remove <- bind_rows(sliceDataMeta %>% filter(Channel == 2 & Condition == "mono"),
+                    sliceDataMeta %>% filter(Channel == 1 & Condition == "pawt"),
+                    sliceDataMeta %>% filter(Channel == 1 & Condition == "paphz"),
+                    sliceDataMeta %>% filter(Channel == 1 & Condition == "papqsL"))
+
+sliceDataMeta <- anti_join(sliceDataMeta, remove)
+
+sliceDataMeta<-sliceDataMeta %>% filter(!SampleCode == "mono_d1_03")
+sliceDataMeta<-sliceDataMeta %>% filter(!SampleCode == "phz_d4_14") #didnt make it to this dataset but still making sure
+sliceDataMeta<-sliceDataMeta %>% filter(!SampleCode == "pqsL_d4_02")
+sliceDataMeta<-sliceDataMeta %>% filter(!SampleCode == "pqsL_d4_04")
+sliceDataMeta<-sliceDataMeta %>% filter(!SampleCode == "pqsL_d4_10")
+sliceDataMeta<-sliceDataMeta %>% filter(!SampleCode == "wt_d4_07")
+sliceDataMeta<-sliceDataMeta %>% filter(!SampleCode == "papqsL_d4_02")
+sliceDataMeta<-sliceDataMeta %>% filter(!SampleCode == "pawt_d4_05")
+sliceDataMeta<-sliceDataMeta %>% filter(!SampleCode == "phz_d4_06")
+
+#rename variables
+sliceDataMeta$Channel <- factor(sliceDataMeta$Channel, levels = c(1, 2, 3),labels = c('S. aureus','P. aeruginosa','host'))
+sliceDataMeta$Condition<- factor(sliceDataMeta$Condition, levels = c("mono", "pawt","papqsL", "paphz", "wt", "pqsL", "phz"),
+                                  labels = c('Sa mono', 'Pa wt mono','pqsL mono','phz mono','wt co', 'pqsL co', 'phz co'))
+sliceDataMeta$TimePoint <- factor(sliceDataMeta$TimePoint, levels = c("d1", "d4"),labels = c('Day 1','Day 4'))
+sliceDataMeta<-sliceDataMeta %>% mutate(Culture = recode(Condition, 'Sa mono' = "mono", 'Pa wt mono' = "mono",'pqsL mono'= "mono",'phz mono'= "mono",'wt co'= "co", 'pqsL co'= "co", 'phz co'= "co"))
+sliceDataMeta<-sliceDataMeta%>% mutate(Strain = recode(Condition, 'Sa mono' = "Sa", 'Pa wt mono' = "wt",'pqsL mono'= "pqsL",'phz mono'= "phz",'wt co'= "wt", 'pqsL co'= "pqsL", 'phz co'= "phz"))
+
+#calculate relative biomass
+sliceDataMeta<-sliceDataMeta%>% filter(!Channel == "host") %>% mutate(Height = Zdim*Slice) %>% group_by(SampleCode, Channel) %>% mutate(TotalBiomass = sum(Biomass)) %>% ungroup() %>% mutate(NormBiomass = Biomass/TotalBiomass*100)
+
+#####
+#Plot Data
+#####
+ggplot()+
+  #geom_point(data = sliceDataMeta ,aes(y=NormBiomass,x=Height, color = Condition, group = Replicate),size=.5)+
+  geom_smooth(data = sliceDataMeta ,aes(y=NormBiomass,x=Height, color =Condition),size=2)+
+  geom_hline(yintercept = 0, linetype = "dashed", color = "gray")+
+  theme_cowplot()+
+  scale_color_brewer(palette = "Set1")+
+  ylim(0,26)+
+  facet_grid(Channel~TimePoint)+
+  panel_border() +
+  coord_flip()
+  theme(plot.title = element_text(hjust = 0.5))
+#####
+#Filter by Max height of the sample
+#####  
+sliceDataSum<-sliceDataMeta %>% group_by(SampleCode) %>% mutate(MaxHeight = max(Height)) %>% ungroup()
+
+ggplot()+
+  geom_smooth(data = sliceDataSum %>% filter(MaxHeight>50 & MaxHeight<120) ,aes(y=NormBiomass,x=Height, color = Strain, linetype = Culture),size=2)+
+  geom_hline(yintercept = 0, linetype = "dashed", color = "gray")+
+  theme_cowplot()+
+  scale_color_brewer(palette = "Set1")+
+  facet_grid(Channel~TimePoint)+
+  panel_border() +
+  coord_flip()+
+  theme(plot.title = element_text(hjust = 0.5))
+
+```
+
+```{r Metadata info}
+#How many samples have been binarized?
+GetTiffNum<-function(sampleName){
+  parentFolder<- '/Volumes/raw_data/Confocal/Carolyn/2020/Chronic wounds/Binary Images/'
+  sampleFolder<-paste0(parentFolder, sampleName)
+  attrList<-str_split(sampleName,"_")[[1]]
+  fileList<-list.files(path = sampleFolder, full.names = TRUE)
+  tiffSlices<-(length(fileList))/3
+  results<-as.data.frame(list(sampleName, attrList[1],attrList[2],attrList[3], tiffSlices))
+  colnames(results)<- c("SampleCode","Condition", "TimePoint","Replicate","TiffSlices")
+  results$SampleCode<-as.factor(results$SampleCode)
+  return(results)
+}
+tiffNum<-map(metaData.df$SampleCode, GetTiffNum)
+tiffNum<-bind_rows(tiffNum)
+totalVoxels2<-metaData.df %>%  merge(tiffNum, by = "SampleCode") %>% mutate(SizeVoxels = xySize*xySize*TiffSlices)
+
+sortedMetaData<-tiffNum %>% filter(TiffSlices==0)%>% select(SampleCode)
+sortedMetaData[order(sortedMetaData),]
+
+tiffStacksNew<-map(metaData.df$SampleCode, GetTiffNum)
+tiffStacksNew<-bind_rows(tiffStacksNew)
+tiffStacksNew %>% filter(TiffSlices==0) %>% select(SampleCode)
+
+#How big are each of the image in bits?
+totalVoxels<-sliceDataMeta %>% group_by(SampleCode, Condition, Replicate, TimePoint,xySize) %>% summarise(MaxSlice = max(Slice)) %>% ungroup() %>% mutate(ImageVoxels = MaxSlice*xySize)
+```
+
 ```{r fancy histogram of aggregates !!!deprecated}
+FancyHistogram<-function(df, sec){#my own way of doing histograms which includes the sum and mean of values whitin each bin
+  results<-data.frame()
+  for( i in 1:(length(sec)-1)){ 
+    blah<-df %>% filter(Size > sec[i] &Size<=sec[i+1])%>%summarise(frequency = n(), avg = mean(Size),suma = sum(Size)) %>% mutate(bin = i, min = sec[i],max = sec[i+1])
+    if(blah$frequency>0){ 
+      results<-rbind(results, blah)} 
+  }
+  return(results) 
+}
+TotalFancyHistogram<-function(df,binsize){
+  totalbiomass<-sum(df$Size)#total biomass per sample
+  totalfrequency<-length(df$Size)#total number of objects
+  upperLim<-max(df$Size)+binsize-(max(df$Size)%%binsize)#largest bin size based in largest object
+  breaksSequence<-seq(0,upperLim,binsize)#this makes breaks every "binsize" 
+  histogram<-FancyHistogram(df,breaksSequence)#apply "fancy histogram" to get distributions
+  histogram%>%mutate(BiomassBin=suma/totalbiomass)->histogram#add column with proportion of biomass per bin
+  histogram%>%mutate(Density=frequency/totalfrequency)->histogram#add column with proportion of counts per bin
+  histogram%>%mutate(Species=df$Species[1])->histogram#add column maintaining sample and so on...
+  histogram%>%mutate(Condition=df$Condition[1])->histogram
+  histogram%>%mutate(TimePoint=df$TimePoint[1])->histogram
+  histogram%>%mutate(Sample=df$Sample[1])->histogram
+  return(histogram)
+}
+
 #Create histograms
@@
 
-```{r biomass per slice}
-#this was taken from "Microscopy data clean.Rmd" 
-GetSliceData<-function(){#import all experiments at once
-  folder<- '/Volumes/raw_data/Confocal/Carolyn/2020/Chronic wounds/Results per slice'
-   fileList<-list.files(path = folder, full.names = TRUE)
-   growthDf<-data.frame()
-   for (aggList in 1:length(fileList)){
-     fileName<-str_split(basename(fileList[aggList]), "\\.")[[1]][1]#this selects the base file name and removes the ".csv"
-     attrList<-str_split(fileName,"_")[[1]]
-     growthDf<-rbind(growthDf,ReadSliceFile(fileList[aggList],attrList[2],attrList[1],attrList[3], fileName))
-     }
-   return(growthDf)
-}
-
-ReadSliceFile<-function(file, timepoint, condition, replicate, sampleCode){#make a dataframe of the aggregate size list and add experimental parameters
-  print(file)
-   datos <-read.csv(file, header = F)  
-   colnames(datos)<-c('Biomass', 'Channel', 'Slice') 
-   datos<-datos %>% mutate(TimePoint = timepoint) 
-   datos<-datos %>% mutate(Condition = condition)
-   datos<-datos %>% mutate(Replicate = replicate)
-   datos<-datos %>% mutate(SampleCode = sampleCode)
-   datos$Replicate<-as.factor(datos$Replicate)
-   datos$Condition<-as.factor(datos$Condition)
-   datos$TimePoint<-as.factor(datos$TimePoint)
-   datos$SampleCode<-as.factor(datos$SampleCode)
-   return(datos)
-}
-
-#Input data
-#####
-#get data from csv file
-slicedData<-GetSliceData()
-#get metadata
-metaData.df <-read.csv('/Volumes/raw_data/Confocal/Carolyn/2020/Chronic wounds/images metadata.csv', header = TRUE)
-metaData.df$SampleCode<-as.factor(metaData.df$SampleCode)
-
-#merge files
-metaData.df<-metaData.df %>% select(SampleCode, mouse, Position, size, Region, Zdim, xyDim,xySize)
-sliceDataMeta<-metaData.df %>%  merge(slicedData, by = "SampleCode")
-#clean up
-remove <- bind_rows(sliceDataMeta %>% filter(Channel == 2 & Condition == "mono"),
-                    sliceDataMeta %>% filter(Channel == 1 & Condition == "pawt"),
-                    sliceDataMeta %>% filter(Channel == 1 & Condition == "paphz"),
-                    sliceDataMeta %>% filter(Channel == 1 & Condition == "papqsL"))
-
-sliceDataMeta <- anti_join(sliceDataMeta, remove)
-
-sliceDataMeta<-sliceDataMeta %>% filter(!SampleCode == "mono_d1_03")
-sliceDataMeta<-sliceDataMeta %>% filter(!SampleCode == "phz_d4_14") #didnt make it to this dataset but still making sure
-sliceDataMeta<-sliceDataMeta %>% filter(!SampleCode == "pqsL_d4_02")
-sliceDataMeta<-sliceDataMeta %>% filter(!SampleCode == "pqsL_d4_04")
-sliceDataMeta<-sliceDataMeta %>% filter(!SampleCode == "pqsL_d4_10")
-sliceDataMeta<-sliceDataMeta %>% filter(!SampleCode == "wt_d4_07")
-sliceDataMeta<-sliceDataMeta %>% filter(!SampleCode == "papqsL_d4_02")
-sliceDataMeta<-sliceDataMeta %>% filter(!SampleCode == "pawt_d4_05")
-sliceDataMeta<-sliceDataMeta %>% filter(!SampleCode == "phz_d4_06")
-
-#rename variables
-sliceDataMeta$Channel <- factor(sliceDataMeta$Channel, levels = c(1, 2, 3),labels = c('S. aureus','P. aeruginosa','host'))
-sliceDataMeta$Condition<- factor(sliceDataMeta$Condition, levels = c("mono", "pawt","papqsL", "paphz", "wt", "pqsL", "phz"),
-                                  labels = c('Sa mono', 'Pa wt mono','pqsL mono','phz mono','wt co', 'pqsL co', 'phz co'))
-sliceDataMeta$TimePoint <- factor(sliceDataMeta$TimePoint, levels = c("d1", "d4"),labels = c('Day 1','Day 4'))
-#calculate relative biomass
-sliceDataMeta<-sliceDataMeta%>% filter(!Channel == "host") %>% mutate(Height = Zdim*Slice) %>% group_by(SampleCode, Channel) %>% mutate(TotalBiomass = sum(Biomass)) %>% ungroup() %>% mutate(NormBiomass = Biomass/TotalBiomass*100)
-
-#####
-#Plot Data
-#####
-ggplot()+
-  #geom_point(data = sliceDataMeta ,aes(y=NormBiomass,x=Height, color = Condition, group = Replicate),size=.5)+
-  geom_smooth(data = sliceDataMeta ,aes(y=NormBiomass,x=Height, color = Condition),size=2)+
-  geom_hline(yintercept = 0, linetype = "dashed", color = "gray")+
-  theme_cowplot()+
-  scale_color_brewer(palette = "Set1")+
-  facet_grid(Channel~TimePoint)+
-  panel_border() +
-  coord_flip()
-  theme(plot.title = element_text(hjust = 0.5))
-#####
-#Filter by Max height of the sample
-#####  
-sliceDataSum<-sliceDataMeta %>% group_by(SampleCode, Condition, Replicate, TimePoint,xySize) %>% summarise(MaxHeight = max(Height)) %>% ungroup()
-
-ggplot()+
-  geom_smooth(data = sliceDataSum %>% filter(MaxHeight>50 & MaxHeight<120) ,aes(y=NormBiomass,x=Height, color = Condition),size=2)+
-  geom_hline(yintercept = 0, linetype = "dashed", color = "gray")+
-  theme_cowplot()+
-  scale_color_brewer(palette = "Set1")+
-  facet_grid(Channel~TimePoint)+
-  panel_border() +
-  coord_flip()
-  theme(plot.title = element_text(hjust = 0.5))
-
-```
-```{r Metadata info}
-#How many samples have been binarized?
-GetTiffNum<-function(sampleName){
-  parentFolder<- '/Volumes/raw_data/Confocal/Carolyn/2020/Chronic wounds/Binary Images/'
-  sampleFolder<-paste0(parentFolder, sampleName)
-  attrList<-str_split(sampleName,"_")[[1]]
-  fileList<-list.files(path = sampleFolder, full.names = TRUE)
-  tiffSlices<-(length(fileList))/3
-  results<-as.data.frame(list(sampleName, attrList[1],attrList[2],attrList[3], tiffSlices))
-  colnames(results)<- c("SampleCode","Condition", "TimePoint","Replicate","TiffSlices")
-  results$SampleCode<-as.factor(results$SampleCode)
-  return(results)
-}
-tiffNum<-map(metaData.df$SampleCode, GetTiffNum)
-tiffNum<-bind_rows(tiffNum)
-totalVoxels2<-metaData.df %>%  merge(tiffNum, by = "SampleCode") %>% mutate(SizeVoxels = xySize*xySize*TiffSlices)
-
-sortedMetaData<-tiffNum %>% filter(TiffSlices==0)%>% select(SampleCode)
-sortedMetaData[order(sortedMetaData),]
-
-tiffStacksNew<-map(metaData.df$SampleCode, GetTiffNum)
-tiffStacksNew<-bind_rows(tiffStacksNew)
-tiffStacksNew %>% filter(TiffSlices==0) %>% select(SampleCode)
-
-#How big are each of the image in bits?
-totalVoxels<-sliceDataMeta %>% group_by(SampleCode, Condition, Replicate, TimePoint,xySize) %>% summarise(MaxSlice = max(Slice)) %>% ungroup() %>% mutate(ImageVoxels = MaxSlice*xySize)
-```
-
-```{r Histogram functions}
-FancyHistogram<-function(df, sec){#my own way of doing histograms which includes the sum and mean of values whitin each bin
-  results<-data.frame()
-  for( i in 1:(length(sec)-1)){ 
-    blah<-df %>% filter(Size > sec[i] &Size<=sec[i+1])%>%summarise(frequency = n(), avg = mean(Size),suma = sum(Size)) %>% mutate(bin = i, min = sec[i],max = sec[i+1])
-    if(blah$frequency>0){ 
-      results<-rbind(results, blah)} 
-  }
-  return(results) 
-}
-TotalFancyHistogram<-function(df,binsize){
-  totalbiomass<-sum(df$Size)#total biomass per sample
-  totalfrequency<-length(df$Size)#total number of objects
-  upperLim<-max(df$Size)+binsize-(max(df$Size)%%binsize)#largest bin size based in largest object
-  breaksSequence<-seq(0,upperLim,binsize)#this makes breaks every "binsize" 
-  histogram<-FancyHistogram(df,breaksSequence)#apply "fancy histogram" to get distributions
-  histogram%>%mutate(BiomassBin=suma/totalbiomass)->histogram#add column with proportion of biomass per bin
-  histogram%>%mutate(Density=frequency/totalfrequency)->histogram#add column with proportion of counts per bin
-  histogram%>%mutate(Species=df$Species[1])->histogram#add column maintaining sample and so on...
-  histogram%>%mutate(Condition=df$Condition[1])->histogram
-  histogram%>%mutate(TimePoint=df$TimePoint[1])->histogram
-  histogram%>%mutate(Sample=df$Sample[1])->histogram
-  return(histogram)
-}
-```
 ```{r Test color palettes}

### 2021-07-18 R/PropOc Data 3D.Rmd
proportional occupancy script based on the one for the mBio paper

---
title: "PropOcData2"
author: "Juan P Barraza"
date: "3/5/2020"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
library(pixmap)
library(rtiff)
library(reshape2)
library(gplots)
library(gdata)
library(plyr)
library(dplyr)
library(ggplot2)
library(cowplot)
library(tidyr)
library(purrr)
library(plotrix)
library(ggsignif)
library(rdist)
library("vcd")#this is fro fitting models to data
library(viridis)#color palette
library(gganimate)#gifs for ggplot

lseq <- function(from, to, length.out) {
  # logarithmic spaced sequence
  # blatantly stolen from library("emdbook"), because need only this
  exp(seq(log(from), log(to), length.out = length.out))}

source('/Users/jupabago/Documents/Whiteley/PROJECTS/Rpackage/PropOc Package/R/PropOcFunctions2.0.R') 
#using the new 3D script with capped spheres.
```

```{r functions to get PropOc Data}
GetPropOcData<-function(sample, timepoints, positions){
  folder<- paste0('/Volumes/Seagate Backup Plus Drive/Good images/',sample,'/imagesSubtractRed')
  growthDf<-data.frame()#data frame to add all timepoints and positions
  fileList<-list.files(path = folder, full.names = TRUE)
  print(folder)
  for (position in 0:positions){
    currentPosition<-fileList[grep(paste0("p",position,"_"),fileList)]
    print(paste0('analyzing position ', position))
    for (timepoint in 0:timepoints){
      currentTimePoint<-currentPosition[grep(paste0("t",GetSlice(timepoint),"_"),currentPosition)]
      dataTimePoint<-NormRawPipeline(SlicesTo3D(currentTimePoint,"red"),SlicesTo3D(currentTimePoint,"green"), 
                                     xydimSearch=114,zdimSearch = 70, sampleSize=1000,xyRealDim=0.264,
                                     zRealDim = 0.44, pipeBinSize = 1)
      dataTimePoint$TimePoint <- timepoint
      dataTimePoint$Position <- position
      growthDf<-rbind(growthDf,dataTimePoint)
      }
    }
  return(growthDf)
  }

GetSlice<-function(idx){
if (idx<10){num = paste0(0,idx)}
  else
    {num = idx}
  return(num)}
```
```{r run functions}
wt1<-GetPropOcData("3-13-19",6,2)
wt2<-GetPropOcData("3-19-19",6,2)
wt3<-GetPropOcData("4-17-19",6,2)
mut1<-GetPropOcData("4-24-19",6,2)
mut2<-GetPropOcData("4-25-19",6,2)
mut3<-GetPropOcData("5-8-19",6,2)

```
```{r Read data files}

Get3DPropOcData<-function(sampleName){
  propOcData1<-read.csv(paste0("/Volumes/raw_data/Confocal/Carolyn/2020/Chronic wounds/Aggregate lists", sampleName,".csv"),header = T)
  propOcData1<-propOcData1 %>% mutate(Strain = strain,BioRep = biologicalRep, RunRep = 1)
  propOcData2<-read.csv(paste0("/Users/jupabago/Documents/Whiteley/PROJECTS/PaSaProject/Spatial paper Data/Microscopy Data/PropOcDataRedSub1/", strain,biologicalRep,"-1000-",2,".csv"),header = T)
  propOcData2<-propOcData2 %>% mutate(Strain = strain,BioRep = biologicalRep, RunRep = 2)
  propOcData3<-read.csv(paste0("/Users/jupabago/Documents/Whiteley/PROJECTS/PaSaProject/Spatial paper Data/Microscopy Data/PropOcDataRedSub1/", strain,biologicalRep,"-1000-",3,".csv"),header = T)
  propOcData3<-propOcData3 %>% mutate(Strain = strain,BioRep = biologicalRep, RunRep = 3)
  allData<-bind_rows(propOcData1,propOcData2,propOcData3)
  allData<-allData %>%  mutate(CV = SDPropOcc/MeanPropOcc) %>% mutate(Experiment = experiment)
  allData<-allData %>% 
    mutate(Relation = recode(source, "finalGG" = "Pa->Pa","finalRG" = "Sa->Pa","finalRR" = "Sa->Sa","finalGR" = "Pa->Sa")) %>%
    mutate(Condition = recode(Position, "2" = "Pa:Sa 1:1")) %>%
    mutate(Interaction = recode(source, "finalGG" = "Self","finalRG" = "Other","finalRR" = "Self","finalGR" = "Other")) %>%
    mutate(FocusSpecies = recode(source, "finalGG" = "Pa","finalRG" = "Sa","finalRR" = "Sa","finalGR" = "Pa")) %>%
    mutate(TargetSpecies = recode(source, "finalGG" = "Pa","finalRG" = "Pa","finalRR" = "Sa","finalGR" = "Sa")) %>% 
    mutate(Time = recode(TimePoint, "0" = "Hour 1","1" = "Hour 2","2" = "Hour 3","3" = "Hour 4","4" = "Hour 5","5" = "Hour 6"))

  allData<-allData %>% filter(TimePoint<6 & Distance<30)#last distance is always off for some reason =(
  }

wt1<-Get3DPropOcData("wt", 1, "wt1")
wt2<-Get3DPropOcData("wt", 2, "wt2")
wt3<-Get3DPropOcData("wt", 3, "wt3")
wt3<-wt3 %>% filter(!RunRep==2|!TimePoint==1)

mut1<-Get3DPropOcData("mut", 1, "mut1")
mut2<-Get3DPropOcData("mut", 2, "mut2")
mut3<-Get3DPropOcData("mut", 3, "mut3")

combinedData<-bind_rows(wt1,wt2,wt3,mut1,mut2,mut3)
combinedData<-combinedData %>% filter(RunRep==1)#I just saw that theyr are all the same, so no point on dragging that much data
```
```{r checking the replicate runs}
PlotPropOcAll <- function(df, name) {
  ggplot()+
    geom_point(data=df, aes(x=Distance,y=MeanPropOcc, color = Relation, shape = factor(RunRep)),size=4)+
    geom_errorbar(data=df, aes(x=Distance,ymin=MeanPropOcc-SDPropOcc,ymax=MeanPropOcc+SDPropOcc, color = Relation, linetype = factor(RunRep)),size=4)+
    facet_wrap(TimePoint~Relation, ncol = 4)+
    scale_y_log10( breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
    labs(title =name)+
    theme_cowplot()+
    background_grid()
  }
PlotPropOcAll(wt1,"wt1")
PlotPropOcAll(wt2,"wt2")
PlotPropOcAll(wt3,"wt3")
PlotPropOcAll(mut1,"mut1 ")
PlotPropOcAll(mut2,"mut2")
PlotPropOcAll(mut3,"mut3")
```
```{r Plot comparison of prop oc between Strains}
ggplot()+ 
  geom_point(data = combinedData %>% filter(Relation == "Pa->Pa"),aes(x=Distance,y=MeanPropOcc, color = Strain, shape =factor(BioRep) ),size=4)+
  scale_y_log10( breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
  facet_wrap( ~ TimePoint, ncol = 3)+
  labs(title ="Pa->Pa")+  
  theme_cowplot()

ggplot()+
  geom_point(data = combinedData %>% filter(Relation == "Sa->Pa"),aes(x=Distance,y=MeanPropOcc, color = Strain, shape =factor(BioRep) ),size=4)+
  scale_y_log10( breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
  facet_wrap( ~ TimePoint, ncol = 3)+
  labs(title ="Sa->Pa")+
  theme_cowplot()

ggplot()+
  geom_point(data = combinedData %>% filter(Relation == "Pa->Sa"),aes(x=Distance,y=MeanPropOcc, color = Strain, shape =factor(BioRep)),size=4)+
  facet_wrap( ~ TimePoint, ncol = 3)+
  scale_y_log10( breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
  labs(title ="Pa->Sa")+
  theme_cowplot()

ggplot()+
  geom_point(data = combinedData %>% filter(Relation == "Sa->Sa"),aes(x=Distance,y=MeanPropOcc, color = Strain, shape =factor(BioRep) ),size=4)+
  facet_wrap( ~ TimePoint, ncol = 3)+
  scale_y_log10( breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
  labs(title ="Sa->Sa")+
  theme_cowplot()
```
```{r Plot comparing prop oc between time points}
ggplot()+ 
  geom_point(data = combinedData %>% filter(Relation == "Pa->Pa"), aes(x=Distance,y=MeanPropOcc, color = TimePoint) ,size=4)+
  scale_y_log10( breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
  facet_wrap(BioRep ~ Strain, ncol = 2)+
  labs(title ="Pa->Pa")+
  theme_cowplot()
ggplot()+
  geom_point(data = combinedData %>% filter(Relation == "Sa->Pa"), aes(x=Distance,y=MeanPropOcc, color = TimePoint) ,size=4)+
  scale_y_log10( breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
  facet_wrap(BioRep ~ Strain, ncol = 2)+
  labs(title ="Sa->Pa")+
  theme_cowplot()
ggplot()+
  geom_point(data = combinedData %>% filter(Relation == "Pa->Sa"), aes(x=Distance,y=MeanPropOcc, color = TimePoint) ,size=4)+
  scale_y_log10( breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
  facet_wrap(BioRep ~ Strain, ncol = 2)+
  labs(title ="Pa->Sa")+
  theme_cowplot() 
ggplot()+
  geom_point(data = combinedData %>% filter(Relation == "Sa->Sa"), aes(x=Distance,y=MeanPropOcc, color = TimePoint) ,size=4)+
  scale_y_log10( breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
  facet_wrap(BioRep ~ Strain, ncol = 2)+
  labs(title ="Sa->Sa")+
  theme_cowplot()
```
```{r Calculating empty space}
combinedDataEmptySpaceStaph<-combinedData %>% filter(source %in% c("finalRG", "finalRR")) %>% group_by(Distance, TimePoint, Strain, BioRep, RunRep) %>% mutate(EmptySpace =1-MeanPropOcc[source == "finalRG"]-MeanPropOcc[source == "finalRR"])

combinedDataEmptySpacePa<-combinedData %>% filter(source %in% c("finalGG", "finalGR")) %>% group_by(Distance, TimePoint, Strain, BioRep, RunRep) %>% mutate(EmptySpace =1-MeanPropOcc[source == "finalGG"]-MeanPropOcc[source == "finalGR"])

combinedDataEmptySpace<-bind_rows(combinedDataEmptySpaceStaph,combinedDataEmptySpacePa)
```
```{r Plot Empty space per condition}
ggplot()+
  geom_point(data = combinedDataEmptySpace %>% filter(FocusSpecies=="Pa"),aes(x=Distance,y=EmptySpace, color = Strain, shape =factor(BioRep)),size=4)+
  labs(title ="Empty Space Pa")+
  facet_wrap(~ TimePoint, ncol = 3)+
  theme_cowplot()

ggplot()+
  geom_point(data = combinedDataEmptySpace %>% filter(FocusSpecies=="Sa"),aes(x=Distance,y=EmptySpace, color = Strain, shape =factor(BioRep)),size=4)+
  labs(title ="Empty Space Sa")+
  facet_wrap(~ TimePoint, ncol = 3)+
  theme_cowplot()

```
```{r Plot Empty space over time}
ggplot()+
  geom_point(data = combinedDataEmptySpace %>% filter(FocusSpecies=="Pa"),aes(x=Distance,y=EmptySpace, color = TimePoint),size=4)+
  labs(title ="Empty Space Pa")+
  facet_wrap(BioRep~ Strain , ncol = 2)+
  theme_cowplot()

ggplot()+
  geom_point(data = combinedDataEmptySpace %>% filter(FocusSpecies=="Sa"),aes(x=Distance,y=EmptySpace, color = TimePoint),size=4)+
  labs(title ="Empty Space Sa")+
  facet_wrap(BioRep~ Strain, ncol = 2)+
  theme_cowplot()

```
```{r Plot occupancy based on focus}
ggplot()+
  geom_line(data = combinedDataEmptySpace %>% filter(FocusSpecies=="Pa" & Strain == "wt"),aes(x=Distance,y=MeanPropOcc, color = Interaction),size=1)+
  scale_y_log10( breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
  labs(title ="Occupied Space around Pa wt",subtitle = "Over time, per biological replicate")+
  facet_wrap(BioRep ~ Time , ncol = 6)+
  theme_minimal_grid()

ggplot()+
  geom_line(data = combinedDataEmptySpace %>% filter(FocusSpecies=="Pa" & Strain == "mut"),aes(x=Distance,y=MeanPropOcc, color = Interaction),size=1)+
  scale_y_log10( breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
  labs(title ="Occupied Space around Pa mut",subtitle = "Over time, per biological replicate")+
  facet_wrap(BioRep ~ Time , ncol = 6)+
  theme_minimal_grid()

ggplot()+
  geom_line(data = combinedDataEmptySpace %>% filter(FocusSpecies=="Sa" & Strain == "wt"),aes(x=Distance,y=MeanPropOcc, color = Interaction),size=1)+
  scale_y_log10( breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
  labs(title ="Occupied Space around Sa wt",subtitle = "Over time, per biological replicate")+
  facet_wrap(BioRep ~ Time , ncol = 6)+
  theme_minimal_grid()

ggplot()+
  geom_line(data = combinedDataEmptySpace %>% filter(FocusSpecies=="Sa" & Strain == "mut"),aes(x=Distance,y=MeanPropOcc, color = Interaction),size=1)+
  scale_y_log10( breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
  labs(title ="Occupied Space around Sa mut",subtitle = "Over time, per biological replicate")+
  facet_wrap(BioRep ~ Time , ncol = 6)+
  theme_minimal_grid()

```
```{r Plot empty space and proportional occupancy*}
#This is a good idea, but I will get back to it later @3/25/20
ggplot()+
  geom_point(data = combinedDataEmptySpace %>% filter(FocusSpecies=="Sa"),aes(x=Distance,y=MeanPropOcc, color = Strain, shape = Interaction),size=4)+
  geom_line(data = combinedDataEmptySpace %>% filter(FocusSpecies=="Sa"),aes(x=Distance,y=EmptySpace, color = Strain),size=4)+
  scale_y_log10( breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
  facet_wrap(~ TimePoint, ncol = 3)+
  labs(title ="title")+
  theme_cowplot()

```
# Statistical exploration of the data.
Three individual runs were performed independently on each of the experiments. The output of each of them is the mean proportional occupancy and it's SD. So, if the runs follow a normal distribution, their variance should be similar.
```{r Plot PropOc mean and SD}
PlotPropOcMeanSD <- function(df, name) {
  plot1<- ggplot()+
    geom_linerange(data=df%>% filter(RunRep==1), aes(x=Distance,ymax=MeanPropOcc+SDPropOcc,ymin=MeanPropOcc-SDPropOcc, color = Relation),size=1)+
    facet_wrap(Time~Relation, ncol = 4)+
    scale_y_log10( breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
    labs(title =paste0(name, " proportional occupancy mean +/- SD"))+
    theme_minimal_grid()+
    background_grid()
  ggsave(paste0(name,".png"),plot = plot1, width = 17, height = 10)
  }

PlotPropOcMeanSD(wt1, "wt1")
PlotPropOcMeanSD(wt2, "wt2")
PlotPropOcMeanSD(wt3, "wt3")
PlotPropOcMeanSD(mut1, "mut1")
PlotPropOcMeanSD(mut2, "mut2")
PlotPropOcMeanSD(mut3, "mut3")

PlotPropOcAllMeanSD <- function(relation) {
  plot1<- ggplot()+
    geom_linerange(data=combinedData %>% filter(Relation ==relation), 
                   aes(x=Distance,ymax=MeanPropOcc+SDPropOcc,ymin=MeanPropOcc-SDPropOcc, color = Strain, linetype =factor(BioRep), group = Experiment),
                   position = position_dodge(width =.8), size=.7)+
    facet_wrap(~Time, ncol = 3)+
    scale_y_log10( breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
    labs(title =paste0(relation, " proportional occupancy mean +/- SD"), linetype = "Biological Replicate")+
    theme_minimal_grid()+
    background_grid()+
    theme(plot.title = element_text(hjust = 0.5))
  ggsave(paste0(relation,".png"),plot = plot1, width = 20, height = 10)
}
PlotPropOcAllMeanSD("Pa->Pa")
PlotPropOcAllMeanSD("Pa->Sa")
PlotPropOcAllMeanSD("Sa->Sa")
PlotPropOcAllMeanSD("Sa->Pa")
```
Another metric used is the coefficient of variation, CV, which is the ratio of the standard deviation to the mean.So, let's also visualize that.
```{r Plot CV} 
PlotCVrelation <- function(relation){
  plot1<-ggplot()+ 
    geom_point(data=combinedData %>% filter(Relation =="Pa->Pa"), 
               aes(x=Distance,y = CV, color = Strain, shape = factor(BioRep), group = Experiment),
               position = position_dodge(width =.8), size=4)+
    geom_hline(yintercept = 1, linetype = "dashed")+
    facet_wrap( ~ Time, ncol = 3)+
    scale_y_log10( breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
    labs(title =paste0(relation, " proportional occupancy Coefficient of variation (SD/mean)"), linetype = "Biological Replicate")+
    theme_minimal_grid()+
    background_grid()+ 
    theme(plot.title = element_text(hjust = 0.5)) 
  ggsave(paste0(relation,"-CV.eps"),plot = plot1, width = 20, height = 10)
  ggsave(paste0(relation,"-CV.png"),plot = plot1, width = 20, height = 10)
  }
PlotCVrelation("Pa->Pa")
PlotCVrelation("Pa->Sa")
PlotCVrelation("Sa->Sa")
PlotCVrelation("Sa->Pa")
```
# Importing whole data sets to identify distribution of data
```{r read whole data sets}
ReadPropOc<-function(sampleName){
propOcData<-read.csv(paste0("/Volumes/raw_data/Confocal/Carolyn/2020/Chronic wounds/PropOc Data/", sampleName,".csv"),header = T)
data<-propOcData%>% filter(PropOc <1.02) %>% group_by(Distance, source) 
  dataList<-group_split(data)#split data fram into a list of dataframes with a single distance and from a single source
  histogramList<-map(dataList, HistogramDistance)#run the function on each item of the list created at the top
  output<-bind_rows(histogramList) #go back to a single dataframe 
  return(output)
}

HistogramDistance <- function(df) {
  #histogram<- hist(df$PropOc) 
  histogram<- hist(df$PropOc, breaks = seq.int(0,1.02,.01)) 
  #histogram<- hist(df$PropOc, breaks = c(0,lseq(.001,1.03,100)))
  #histogram<- hist(df$PropOc, breaks = c(0,lseq(.0001,1.03,100)))
  output<-data.frame(histogram$mids,histogram$counts, histogram$density)
  colnames(output)<-c("Value", "Frequency", "Density")
  output<-output %>% mutate(Distance = df$Distance[[1]]) %>% filter(!Frequency==0)
  output<-output %>% mutate(Source = df$source[[1]]) 
  return(output)
}

testReadPropOc<-ReadPropOc("mono_d1_01") #this is using seq(.0001,1.03,100)))
testReadPropOc1<-ReadPropOc("mono_d1_01") #this is using seq(.001,1.03,100)))
testReadPropOc2<-ReadPropOc("mono_d1_01") #this is using seq.int(0,1.02,.01)) 
testReadPropOc3<-ReadPropOc("mono_d1_01") #this is without specifying breaks

testReadPropOcLaptop<-ReadPropOc("mono_d1_01Laptop")

rawPropOcData<-read.csv(paste0("/Volumes/raw_data/Confocal/Carolyn/2020/Chronic wounds/PropOc Data/", "mono_d1_01Laptop",".csv"),header = T)

#QC for data:
countData<-rawPropOcData %>% group_by(source, Distance) %>% summarize(count = n()) %>% filter(count<1000) %>%ungroup() %>% summarise(MisingTotal = n()*1000-sum(count),TotalMedian = median(count), Mean = mean(count))
CheckPropOc<-rawPropOcData %>% filter(PropOc>1.05|PropOc<0)
ggplot()+
  geom_jitter(data = countData,aes(x=Distance,y=X, color = source ),size=4, height= .1)+
  #labs(title ="title")+
  #scale_y_log10(breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
  theme_cowplot()+
  theme(plot.title = element_text(hjust = 0.5))

```

```{r Original Whole PropOc frequency functions from mBio Paper}
GetAllHistPropOc <- function(df, timepoint){
  data.GG<-GetHistPropOc(df, timepoint, "finalGG")
  data.RG<-GetHistPropOc(df, timepoint, "finalRG")
  data.RR<-GetHistPropOc(df, timepoint, "finalRR")
  data.GR<-GetHistPropOc(df, timepoint, "finalGR")
  allData<- bind_rows(data.GG,data.RR,data.RG,data.GR)
return(allData)
}

GetHistPropOc <- function(df,timePoint, sources) {
  data<-df %>%  filter(TimePoint==timePoint) %>% filter(source==sources) %>% group_by(Distance, source) %>% filter(PropOc <1.02)
  dataList<-group_split(data)
  histogramList<-map(dataList, HistogramDistance)
  output<-bind_rows(histogramList)
  output<-output %>% mutate(Source = sources)
  return(output)
}
HistogramDistance <- function(df) {
  #histogram<- hist(df$PropOc, breaks = seq.int(0,1.02,.01)) 
  #histogram<- hist(df$PropOc) 
  #histogram<- hist(df$PropOc, breaks = c(0,lseq(.001,1.03,100)))
  histogram<- hist(df$PropOc, breaks = c(0,lseq(.0001,1.03,100)))
  output<-data.frame(histogram$mids,histogram$counts, histogram$density)
  colnames(output)<-c("Value", "Frequency", "Density")
  output<-output %>% mutate(Distance = df$Distance[[1]]) %>% filter(!Frequency==0)
  output<-output %>% mutate(Source = df$source[[1]]) 
  return(output)
}

#Get all of the distributions

```

```{r Whole PropOc frequency Figures}
PlotAllPropOcData <- function(df, relation ) {
  ggplot()+ 
    geom_point(data = df %>% filter(Source == relation),aes(x=Value,y=Frequency, color = Distance),size=2)+
    scale_y_log10( breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
    #scale_x_log10( breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
    #labs(title =paste( relation, timepoint))+
    #scale_color_viridis(option = "D")+
    scale_color_gradientn(colours = rainbow(5))+
    xlim(0,1)+
    theme_cowplot()+
    theme(plot.title = element_text(hjust = 0.5))
  #name<-paste0(relation, ".hour", timepoint,".png")
  #ggsave(paste0(name),plot = plot, width = 17, height = 10)
}

PlotAllPropOcData(testReadPropOc, "finalRR")
PlotAllPropOcData(testReadPropOc1, "finalRR")
PlotAllPropOcData(testReadPropOc2, "finalRR")
PlotAllPropOcData(testReadPropOc3, "finalRR")

#Honestly, they all look pretty much the same...
#let's try doing the bins in an exponential function...
PlotAllPropOcDatalog <- function(df, timepoint, relation ) {
  plot<-ggplot()+ 
    geom_point(data = df,aes(x=Value,y=Frequency, color = Distance),size=2)+
    scale_y_log10( breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)),limits = (c(1,1001)))+
    #scale_x_log10(breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
    scale_x_log10(breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)),limits = (c(0.0005,1)))+
    labs(title =paste( relation, timepoint))+
    #scale_color_viridis(option = "D")+
    scale_color_gradientn(colours = rainbow(5))+
    #xlim(0,1)+
    theme_cowplot()+
    theme(plot.title = element_text(hjust = 0.5))
  name<-paste0(relation, ".hour", timepoint,"(log).png")
  ggsave(paste0(name),plot = plot, width = 17, height = 10)
}

PlotAllPropOcDatalog(wt1.1Whole.5log %>% filter (Source == "finalRG"), 5, "Wt 1-1 SA->PA")
PlotAllPropOcDatalog(wt2.1Whole.5log %>% filter (Source == "finalRG"), 5, "Wt 2-1 SA->PA")
PlotAllPropOcDatalog(wt3.1Whole.5log %>% filter (Source == "finalRG"), 5, "Wt 3-1 SA->PA")

PlotAllPropOcDatalog(mut1.1Whole.5log %>% filter (Source == "finalRG"), 5, "Mut1-1 SA->PA")
PlotAllPropOcDatalog(mut2.1Whole.5log %>% filter (Source == "finalRG"), 5, "Mut2-1 SA->PA")
PlotAllPropOcDatalog(mut3.1Whole.5log %>% filter (Source == "finalRG"), 5, "Mut3-1 SA->PA")

PlotAllPropOcDatalog(wt1.1Whole.5log %>% filter (Source == "finalGR"), 5, "Wt 1-1 PA->SA")
PlotAllPropOcDatalog(wt2.1Whole.5log %>% filter (Source == "finalGR"), 5, "Wt 2-1 PA->SA")
PlotAllPropOcDatalog(wt3.1Whole.5log %>% filter (Source == "finalGR"), 5, "Wt 3-1 PA->SA")

PlotAllPropOcDatalog(mut1.1Whole.5log %>% filter (Source == "finalGR"), 5, "Mut1-1 PA->SA")
PlotAllPropOcDatalog(mut2.1Whole.5log %>% filter (Source == "finalGR"), 5, "Mut2-1 PA->SA")
PlotAllPropOcDatalog(mut3.1Whole.5log %>% filter (Source == "finalGR"), 5, "Mut3-1 PA->SA")

```

```{r Whole PropOc Data wrangling}
#So, I think the first thing to do would be to get a "mode", or the highest value for frequency of proportional occupancy per distance.
#at this point I can see at least if the zone of interest is the same for every sample.

GetMaxDensity <- function(df) {#this one is essentially the same as the one below, but this one doesnt allow repeated max density values
  df.summary<-df %>% mutate(Density = Frequency/1000) %>% #this is to make it be from 0 to 1
    group_by(Distance, Source) %>% select(Value, Distance,Density, Source) %>% summarise(DensestValue = Value [Density ==max(Density)], MaxDensity = max(Density))
  return(df.summary)
}

DensityCheck <- function(df) {
  df.summary<-df %>% 
    mutate(Density = Frequency/1000) %>% #this is to make it be from 0 to 1
    group_by(Distance, Source) %>% select(Value, Distance,Density, Source) %>% 
    mutate(MaxDensity = max(Density)) %>% 
    mutate(DensityCh = ifelse(Density ==max(Density), 1, 0 )) %>% filter(DensityCh==1) %>% ungroup()#find max density, check where it matches
  #df.summary<-df.summary %>% group_by(Distance, Source) %>% mutate(DoubledValues = sum(DensityCh))#this is just to find which values were repeated
  return(df.summary)
}

ProcessDensities <- function(histograms) {
histogramNames<- c("wt1.1","wt2.1","wt3.1","mut1.1","mut2.1","mut3.1")
mappedDensities<-map(histograms,DensityCheck)
namedMappedDensities<-map2(mappedDensities, histogramNames, ~.x %>% mutate(Sample = .y))
allDensities<-bind_rows(namedMappedDensities)
allDensities<-allDensities %>% ungroup() %>% 
  mutate(Strain = recode(allDensities$Sample, wt1.1="wt",wt2.1="wt",wt3.1="wt",mut1.1="mut",mut2.1="mut",mut3.1="mut"))
return(allDensities)}

histograms<- list(wt1.1Whole.5,wt2.1Whole.5,wt3.1Whole.5,mut1.1Whole.5,mut2.1Whole.5,mut3.1Whole.5)
histogramslog<- list(wt1.1Whole.5log,wt2.1Whole.5log,wt3.1Whole.5log,mut1.1Whole.5log,mut2.1Whole.5log,mut3.1Whole.5log)
histogramslog2<- list(wt1.1Whole.5log2,wt2.1Whole.5log2,wt3.1Whole.5log2,mut1.1Whole.5log2,mut2.1Whole.5log2,mut3.1Whole.5log2)

allDensitiesFunctions<-ProcessDensities(histograms)
allDensitiesLog<-ProcessDensities(histogramslog)
allDensitiesLog2<-ProcessDensities(histogramslog2)
```

```{r Whole Prop Freq Figures}
PlotMaxDensities <- function(df) {
  ggplot()+
    geom_jitter(data = df,aes(y=Value, color=Density,x = Distance, shape = Sample),size=2)+
    labs(title ="Maximum Density")+
    scale_y_log10(breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
    #scale_x_log10(breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
    facet_wrap( ~ Source, ncol = 2)+
    scale_color_gradientn(colours = rainbow(5))+
    scale_shape_manual(values=c(0,1,2, 15,16,17))+
    theme_cowplot()+
    theme(plot.title = element_text(hjust = 0.5))
}
PlotMaxDensities(allDensities)
PlotMaxDensities(allDensitiesFunctions %>% filter(Source=="finalRG"))
PlotMaxDensities(allDensitiesLog)
PlotMaxDensities(allDensitiesLog2)
```
#Calculating 50 percentile density.
```{r death curves Functions and data}
getDeathCurve<-function(df){
  totalFrequency = sum(df$Frequency)
  currentFrequency = 0
  for (i in 1 : nrow(df)){
    addedFrequency<-totalFrequency-currentFrequency
    df[i,6]<-addedFrequency
    currentFrequency = currentFrequency+df[i,2]
  }
  colnames(df)<-c("Value","Frequency","Density", "Distance", "Source","Decay")
  df<-df %>% mutate (normDecay = 100*(Decay - min(Decay)) / (max(Decay) - min(Decay)))
  return(df)
  }
processData<-function(df){
  allData<-df %>% group_by(Distance, Source)
  yas<- group_split(allData)
  mappedData<-map(yas, getDeathCurve)
  boundData<-bind_rows(mappedData)
}
GetPercentiles<-function(histograms){
  histogramNames<- c("wt1.1","wt2.1","wt3.1","mut1.1","mut2.1","mut3.1")
  mappedDensities<-map(histograms,processData)
  namedMappedDensities<-map2(mappedDensities, histogramNames, ~.x %>% mutate(Sample = .y))
  allDensities<-bind_rows(namedMappedDensities)
  allDensities<-allDensities %>% ungroup() %>% 
    mutate(Strain = recode(allDensities$Sample, wt1.1="wt",wt2.1="wt",wt3.1="wt",mut1.1="mut",mut2.1="mut",mut3.1="mut"))
return(allDensities)}

PlotPercentiles <- function(df) {
  ggplot()+
    geom_point(data = df,aes(y=Value, color=Percentile50,x = Distance, shape = Sample),size=2)+
    #geom_pointrange(data = df,aes(x = Distance,y=meanValue,ymax=meanValue+SdValue,ymin=meanValue-SdValue, color=Strain),size=2)+
    labs(title ="50 percentile Density")+
    scale_y_log10(breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
    #scale_x_log10(breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
    facet_wrap( ~ Source, ncol = 2)+
    scale_color_gradientn(colours = rainbow(5))+
    scale_shape_manual(values=c(0,1,2, 15,16,17))+
    theme_cowplot()+
    theme(plot.title = element_text(hjust = 0.5))
  }

allDeathCurvesLog2<-GetPercentiles(histogramslog2)
#there are, I believe, at least 3 ways to find the 50 percentile. one of them is finidng the closest value, regardless of where it comes from, whether it is higher or lower than 50 percentile. The other two are either taking the closest to 50, either exclusively larger or exclusively smaller than that. That's why there are 3 ways of doing this here:

#this is the closest to absolute value 50
allDeathCurvesLog2midAbs <- allDeathCurvesLog2 %>% group_by(Sample, Distance, Source) %>% 
  mutate(Percentile50 = min(abs(normDecay - 50)))%>% 
  mutate(DensityCh = ifelse(Percentile50 ==abs(normDecay - 50), 1, 0 )) %>% filter(DensityCh==1) %>% mutate(DoubledValues = sum(DensityCh)) %>% ungroup()#find max density, check where it matches

#this is coming from the highest value
allDeathCurvesLog2topAbs <- allDeathCurvesLog2 %>% group_by(Sample, Distance, Source) %>% 
  mutate(Percentile50 = (normDecay - 50)) %>% filter (Percentile50>0) %>% filter(Percentile50==min(Percentile50)) %>%  
  mutate(DensityCh = ifelse(Percentile50 ==(normDecay - 50), 1, 0 )) %>% filter(DensityCh==1) %>% 
  mutate(DoubledValues = sum(DensityCh)) %>% ungroup()#find max density, check where it matches

#this is coming from the lowest value
allDeathCurvesLog2bottomAbs <- allDeathCurvesLog2 %>% group_by(Sample, Distance, Source) %>% 
  mutate(Percentile50 = (50 -normDecay)) %>% filter (Percentile50>0) %>% filter(Percentile50==min(Percentile50)) %>%  
  mutate(DensityCh = ifelse(Percentile50 ==(50 - normDecay), 1, 0 )) %>% filter(DensityCh==1) %>% 
  mutate(DoubledValues = sum(DensityCh)) %>% ungroup()#find max density, check where it matches

#Plotting and comparing all 3
PlotPercentiles(allDeathCurvesLog2midAbs)
PlotPercentiles(allDeathCurvesLog2topAbs)
PlotPercentiles(allDeathCurvesLog2bottomAbs)
#they all look fine, so I'll just stick with the first one

#this looks kind of ok... what is the mean and sd?
allDeathCurvesLog2midAbsStats<-allDeathCurvesLog2midAbs %>% group_by(Strain, Distance, Source) %>% mutate(LogValue = log10(Value)) %>% mutate(meanValue = mean(Value), sdValue = sd(Value), meanLogValue = mean(LogValue),sdLogValue = sd(LogValue))
PlotPercentiles(allDeathCurvesLog2midAbsStats)

ggplot()+#linear
    #geom_point(data = df,aes(y=Value, color=Percentile50,x = Distance, shape = Sample),size=2)+
    geom_pointrange(data = allDeathCurvesLog2midAbsStats,aes(x = Distance,y=meanValue,ymax=meanValue+sdValue,ymin=meanValue-sdValue, color=Strain),size=.5)+
    labs(title ="50 percentile Density")+
    scale_y_log10(breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
    #scale_x_log10(breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
    facet_wrap( ~ Source, ncol = 2)+
    #scale_color_gradientn(colours = rainbow(5))+
    #scale_shape_manual(values=c(0,1,2, 15,16,17))+
    theme_cowplot()+
    theme(plot.title = element_text(hjust = 0.5))

allDeathCurvesLog2midAbsStats<-allDeathCurvesLog2midAbsStats%>% mutate(Relation = recode(Source, "finalGG" = "Pa->Pa","finalRG" = "Sa->Pa","finalRR" = "Sa->Sa","finalGR" = "Pa->Sa"))
ggplot()+#log transform
  geom_pointrange(data = allDeathCurvesLog2midAbsStats,aes(x = Distance,y=meanLogValue,ymax=meanLogValue+sdLogValue,ymin=meanLogValue-sdLogValue, color=Strain),size=.5)+
  facet_wrap( ~ Relation, ncol = 2)+
  scale_color_grey(name = "Strain", labels = c( "HQNO-","Wild Type"))+  
  theme_cowplot()+
  theme(plot.title = element_text(hjust = 0.5))
```
#Enrichment (distance at highest proportional occupancy)
```{r Enrichment}
#find the max proportional occupancy value from the 50 percentile

allDeathCurvesLog2midAbsEnrichment<- allDeathCurvesLog2midAbs %>% group_by(Sample, Source)%>%select(Value, Distance, Source,Sample, Strain, Percentile50) %>% mutate(Enrichment = max(Value)) %>%
  mutate(EnrichmentCh = ifelse(Enrichment == Value, 1, 0 )) %>% filter(EnrichmentCh==1) %>% mutate(DoubledValues = sum(EnrichmentCh)) %>% ungroup()#find max

PlotEnrichment <- function(df) {
ggplot()+#first run
    geom_point(data = df,aes(y=Distance, x = Sample, color = Enrichment, shape = Sample),size=2)+
    labs(title ="50 percentile Enrichment")+
    #scale_y_log10(breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
    #scale_x_log10(breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
    facet_wrap( ~ Source, ncol = 2)+
    scale_color_gradientn(colours = rainbow(5))+
    scale_shape_manual(values=c(0,1,2, 15,16,17))+
    theme_cowplot()+
    theme(plot.title = element_text(hjust = 0.5))
}

PlotDataEnrichmentEmphasis <- function(wholeData, EnrichmentData) {
ggplot()+#including rest of the data
  geom_point(data = wholeData,aes(y=Value, color=Percentile50,x = Distance, shape = Sample),size=2)+
  geom_point(data = EnrichmentData,aes(y=Value, color=Percentile50,x = Distance, shape = Sample),size=5)+
  labs(title ="50 percentile Density (Enrichment emphasis)")+
  scale_y_log10(breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
  #scale_x_log10(breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
  facet_wrap( ~ Source, ncol = 2)+
  scale_color_gradientn(colours = rainbow(5))+
  scale_shape_manual(values=c(0,1,2, 15,16,17))+
  theme_cowplot()+
  theme(plot.title = element_text(hjust = 0.5))
}

PlotEnrichment(allDeathCurvesLog2midAbsEnrichment)
PlotDataEnrichmentEmphasis(allDeathCurvesLog2midAbs,allDeathCurvesLog2midAbsEnrichment)

#That looks like a lot of the values are just at 0.5 distance, which I dont really care, I can make another argument about direct contact, so I'll filter those out...
allDeathCurvesLog2midAbsEnrichment2<- allDeathCurvesLog2midAbs %>% filter(!Distance ==0.5)%>% 
  group_by(Sample, Source) %>% select(Value, Distance, Source,Sample, Strain, Percentile50) %>% mutate(Enrichment = max(Value)) %>%
  mutate(EnrichmentCh = ifelse(Enrichment == Value, 1, 0 )) %>% filter(EnrichmentCh==1) %>% mutate(DoubledValues = sum(EnrichmentCh)) %>% ungroup()#find max

PlotEnrichment(allDeathCurvesLog2midAbsEnrichment2)
PlotDataEnrichmentEmphasis(allDeathCurvesLog2midAbs,allDeathCurvesLog2midAbsEnrichment2)

#This looks a little better... now get the mean per condition
allDeathCurvesLog2midAbsEnrichment2<-allDeathCurvesLog2midAbsEnrichment2 %>% group_by(Source, Sample) %>% mutate(EnrichmentDistance = mean(Distance)) %>% ungroup() %>% group_by(Source, Strain) %>% mutate(meanEnrichment = mean(EnrichmentDistance), sdEnrichment = sd(EnrichmentDistance))

allDeathCurvesLog2midAbsEnrichment2<-allDeathCurvesLog2midAbsEnrichment2 %>% mutate(Relation = recode(Source, "finalGG" = "Pa->Pa","finalRG" = "Sa->Pa","finalRR" = "Sa->Sa","finalGR" = "Pa->Sa"))

#this is the original figure I sent to Marvin
ggplot()+
  geom_point(data = allDeathCurvesLog2midAbsEnrichment2,aes(y=meanEnrichment, x = Strain, color = Strain),size=4)+
  geom_errorbar(data = allDeathCurvesLog2midAbsEnrichment2,
                aes(ymin = meanEnrichment-sdEnrichment,ymax = meanEnrichment+sdEnrichment, x = Strain, color = Strain),size=1)+
  geom_jitter(data = allDeathCurvesLog2midAbsEnrichment2,aes(y=Distance, x = Strain, color = Strain, shape = Sample),size=2)+
  facet_wrap( ~ Relation, ncol = 2)+
  scale_shape_manual(values=c(0,1,2, 15,16,17))+
  guides(shape = FALSE)+
  scale_color_grey(name = "Strain", labels = c("HQNO-","Wild Type"))+  
  theme_cowplot()+
  theme(plot.title = element_text(hjust = 0.5))
#Now I have to remove focus of Pa since there are too many of them
enrichmentDataFinal<-allDeathCurvesLog2midAbsEnrichment2 %>% filter(Relation %in% c("Sa->Pa", "Sa->Sa"))
enrichmentDataFinal$Strain <- factor(enrichmentDataFinal$Strain, levels = c("wt", "mut"))
```

```{r final figure for enrichment}
sa.paPlot<-ggplot()+
  geom_point(data = enrichmentDataFinal %>% filter(Relation == "Sa->Pa"),aes(y=meanEnrichment, x = Strain, shape = Strain),size=4)+
  geom_errorbar(data = enrichmentDataFinal %>% filter(Relation == "Sa->Pa"),
                aes(ymin = meanEnrichment-sdEnrichment,ymax = meanEnrichment+sdEnrichment, x = Strain),size=.2, width = .1)+
  labs( y = bquote(paste("Distance ("*mu*"m)")), x = "" ) +
  scale_shape_manual(values = c(1,2),name = "", limits=c("wt","mut"),labels = c(bquote(paste(italic('P. aeruginosa'), " wild-type")),
                                bquote(paste(italic('P. aeruginosa '), Delta*"pqsL"))))+
  scale_x_discrete(name ="", breaks = c("wt","mut"), labels =c("wild-type",expression(""*Delta*"pqsL")))+
  ylim(1, 9)+
  theme_cowplot()

sa.saPlot<-ggplot()+
  geom_point(data = enrichmentDataFinal %>% filter(Relation == "Sa->Sa"),aes(y=meanEnrichment, x = Strain, shape = Strain),size=4)+
  geom_errorbar(data = enrichmentDataFinal %>% filter(Relation == "Sa->Sa"),
                aes(ymin = meanEnrichment-sdEnrichment,ymax = meanEnrichment+sdEnrichment, x = Strain),size=.2, width = .1)+
  labs( y = bquote(paste("Distance ("*mu*"m)")), x = "" ) +
  scale_shape_manual(values = c(1,2),name = "", limits=c("wt","mut"),labels = c(bquote(paste(italic('P. aeruginosa'), " wild-type")),
                                bquote(paste(italic('P. aeruginosa '), Delta*"pqsL"))))+
  scale_x_discrete(name ="", breaks = c("wt","mut"), labels =c("wild-type",expression(""*Delta*"pqsL")))+
  ylim(1, 9)+
  theme_cowplot()

legendFigure3 <- get_legend(sa.saPlot + theme(legend.box.margin = margin(0, 0, 0, -10)))
figure3 <- plot_grid(sa.saPlot+theme(legend.position="none"),sa.paPlot+theme(legend.position="none"),
                      align='vh',labels = c("A", "B"),hjust = -1,nrow = 1)
plot_grid(figure3,legendFigure3,rel_widths = c(4, 1.7))
#plot_grid(sa.saPlot,sa.paPlot,align='vh',labels = c("A", "B"),hjust = -1,nrow = 1)

#p-value calculations
pvalueEnrichmentGR<- allDeathCurvesLog2midAbsEnrichment2 %>% filter(Source == "finalGR") %>% filter(!Distance == 6.5)%>% filter(!Distance == 10.5)

wtpvalueEnrichmentGR<-pvalueEnrichmentGR %>% filter(Strain=="wt")
mutpvalueEnrichmentGR<-pvalueEnrichmentGR %>% filter(Strain=="mut")
POTtest<-t.test(x = wtpvalueEnrichmentGR$EnrichmentDistance, y = mutpvalueEnrichmentGR$EnrichmentDistance, paired = T)
POTtest

pvalueEnrichmentRG<- allDeathCurvesLog2midAbsEnrichment2 %>% filter(Source == "finalRG") %>% filter(!Distance == 7.5)%>% filter(!Distance == 9.5) %>% filter(!Distance == 5.5) %>% filter(!Distance == 3.5) %>% ungroup() %>% slice(2:7)
wtpvalueEnrichmentRG<-pvalueEnrichmentRG %>% filter(Strain=="wt")
mutpvalueEnrichmentRG<-pvalueEnrichmentRG %>% filter(Strain=="mut")
POGRTtest<-t.test(x = wtpvalueEnrichmentRG$EnrichmentDistance, y = mutpvalueEnrichmentRG$EnrichmentDistance, paired = T)
POGRTtest

```

### 2021-07-18 R/PropOc Data 3D.Rmd
added quality control for raw data import

@@
 ```{r read whole data sets}
-ReadPropOc<-function(sampleName){
-propOcData<-read.csv(paste0("/Volumes/raw_data/Confocal/Carolyn/2020/Chronic wounds/PropOc Data/", sampleName,".csv"),header = T)
+
+ReadPropOcFile<-function(file){
+    propOcData<-read.csv(file,header = T)
+    fileName<-str_split(basename(file), "\\.")[[1]][1]#this selects the base file name and removes the ".csv"
+    print(paste0("Importing sample ", fileName))
+    attrList<-str_split(fileName,"_")[[1]]
+    propOcData<-propOcData %>% mutate(Condition = attrList[1], TimePoint = attrList[2], Replicate = attrList[3], SampleCode = fileName)
+    return(propOcData)
+    }
+
+propOcDatafolder<-'/Volumes/raw_data/Confocal/Carolyn/2020/Chronic wounds/PropOc Data'
+propOcDatafileList<-list.files(path = propOcDatafolder, full.names = TRUE)
+rawPropOcDataList<-map(propOcDatafileList,ReadPropOcFile)
+rawPropOcData<-bind_rows(rawPropOcDataList)
+rawPropOcData<-rawPropOcData %>% filter(!SampleCode=="mono_d1_01Slim") %>%  filter(!SampleCode=="mono_d1_02Slim")
+
+#QC for data:
+##How much data is just straight up missing?
+#####
+countData<-rawPropOcData %>% group_by(SampleCode, source, Distance) %>% summarize(count = n()) %>% filter(count<1000) %>%ungroup() %>% summarise(MisingTotal = n()*1000-sum(count),TotalMedian = median(count), Mean = mean(count))
+
+countData2<-rawPropOcData %>% group_by(SampleCode, source, Distance) %>% summarize(count = n()) %>% filter(count<1000) %>%ungroup() %>% group_by(SampleCode) %>% summarise(MisingTotal = n()*1000-sum(count),TotalMedian = median(count), Mean = mean(count)) %>% mutate(MissingPercent = (1000-Mean)/1000)
+##How much of the missing data matters?
+
+#first, remove the unnecessary conditions
+removablePropOc <- bind_rows(rawPropOcData %>% filter(Condition == "mono") %>% filter(!source == "finalRR"), #Pa in Sa mono culture
+                       rawPropOcData %>% filter(Condition == "papqsL") %>% filter(!source == "finalGG"),#Sa in all Pa mono cultures
+                       rawPropOcData %>% filter(Condition == "pawt") %>% filter(!source == "finalGG"),
+                       rawPropOcData %>% filter(Condition == "paphz") %>% filter(!source == "finalGG"))
+rawPropOcDataClean <- anti_join(rawPropOcData, removablePropOc)
+
+##then, bad samples
+rawPropOcDataClean<-rawPropOcDataClean %>% filter(!SampleCode == "mono_d1_03")
+rawPropOcDataClean<-rawPropOcDataClean %>% filter(!SampleCode == "phz_d4_14")
+rawPropOcDataClean<-rawPropOcDataClean %>% filter(!SampleCode == "pqsL_d4_02")
+rawPropOcDataClean<-rawPropOcDataClean %>% filter(!SampleCode == "pqsL_d4_04")
+rawPropOcDataClean<-rawPropOcDataClean %>% filter(!SampleCode == "pqsL_d4_10")
+rawPropOcDataClean<-rawPropOcDataClean %>% filter(!SampleCode == "wt_d4_07")
+rawPropOcDataClean<-rawPropOcDataClean %>% filter(!SampleCode == "papqsL_d4_02")
+rawPropOcDataClean<-rawPropOcDataClean %>% filter(!SampleCode == "pawt_d4_05")
+rawPropOcDataClean<-rawPropOcDataClean %>% filter(!SampleCode == "phz_d4_06")
+
+#Do it again
+countDataClean<-rawPropOcDataClean %>% group_by(SampleCode, source, Distance) %>% summarize(count = n()) %>% filter(count<1000) %>%ungroup() %>% summarise(MisingTotal = n()*1000-sum(count),TotalMedian = median(count), Mean = mean(count))
+
+countDataClean2<-rawPropOcDataClean %>% group_by(SampleCode, source, Distance) %>% summarize(count = n()) %>% filter(count<1000) %>%ungroup() %>% group_by(SampleCode) %>% summarise(MisingTotal = n()*1000-sum(count),TotalMedian = median(count), Mean = mean(count)) %>% mutate(MissingPercent = (1000-Mean)/1000)
+#it got a little better, but not that much...
+#####
+#How much of it is outside the ideal boundaries?
+
+CheckBenchmark<-function(benchmark){
+CheckPropOc<-rawPropOcDataClean %>% filter(PropOc>benchmark|PropOc<0)
+percentInbound<-length(CheckPropOc$SampleCode)/length(rawPropOcDataClean$SampleCode)*100
+return(percentInbound)}
+
+CheckBenchmark(1)
+
+ggplot()+
+  geom_jitter(data = countData,aes(x=Distance,y=X, color = source ),size=4, height= .1)+
+  #labs(title ="title")+
+  #scale_y_log10(breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
+  theme_cowplot()+
+  theme(plot.title = element_text(hjust = 0.5))
+
+GetHistograms<-function(sample){
+
 data<-propOcData%>% filter(PropOc <1.02) %>% group_by(Distance, source) 
@@
 
-rawPropOcData<-read.csv(paste0("/Volumes/raw_data/Confocal/Carolyn/2020/Chronic wounds/PropOc Data/", "mono_d1_01Laptop",".csv"),header = T)
-
-#QC for data:
-countData<-rawPropOcData %>% group_by(source, Distance) %>% summarize(count = n()) %>% filter(count<1000) %>%ungroup() %>% summarise(MisingTotal = n()*1000-sum(count),TotalMedian = median(count), Mean = mean(count))
-CheckPropOc<-rawPropOcData %>% filter(PropOc>1.05|PropOc<0)
-ggplot()+
-  geom_jitter(data = countData,aes(x=Distance,y=X, color = source ),size=4, height= .1)+
-  #labs(title ="title")+
-  #scale_y_log10(breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
-  theme_cowplot()+
-  theme(plot.title = element_text(hjust = 0.5))
+testrawPropOcData<-read.csv(paste0("/Volumes/raw_data/Confocal/Carolyn/2020/Chronic wounds/PropOc Data/", "mono_d1_01",".csv"),header = T)
 

### 2021-07-26 R/PropOc Data 3D.Rmd
exploring the missing data

@@
 #####
+#What are the observations missing?
+#####
+countDistancesALL<-rawPropOcDataClean %>% group_by(SampleCode,Condition, Distance) %>% summarise(count = n()) %>% ungroup() %>%group_by(Condition) %>%  mutate(difference = max(count)- count)
+countDistancesBadOnly<- countDistancesALL%>% filter(difference>0) %>% group_by(SampleCode) %>% summarise(missingDistantes = n()) %>% filter(missingDistantes == 30)
+countDistancesGoodOnly<- countDistancesALL%>% filter(difference==0) %>% group_by(SampleCode) %>% summarise(missingDistantes = 30-n()) %>% filter (missingDistantes==0)
+
+leftover<-anti_join(countDistancesALL,countDistancesBadOnly, by = "SampleCode")
+leftover<-anti_join(leftover,countDistancesGoodOnly, by = "SampleCode")
+
+#####
 #How much of it is outside the ideal boundaries?
-
+#####
 CheckBenchmark<-function(benchmark){
@@
 
-CheckBenchmark(1)
+CheckBenchmark(1.05)
+#the data outside the range should be primarily at really short distances, since this is where the calculation of voxels in the surrounding and sphere of potentially ocuppied space is the largest  
+#I think 1.05 is a good benchmark to observe this trend:
+CheckPropOc<-rawPropOcDataClean %>% filter(PropOc>1.05|PropOc<0)
 
 ggplot()+
-  geom_jitter(data = countData,aes(x=Distance,y=X, color = source ),size=4, height= .1)+
+  geom_jitter(data = CheckPropOc %>% filter(!source == "finalRR") %>% filter(!source == "finalGG") %>% filter(PropOc<1000),aes(x=Distance,y=PropOc, color = source ),size=2, height= .1)+
   #labs(title ="title")+
-  #scale_y_log10(breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
+  scale_y_log10(breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
   theme_cowplot()+
   theme(plot.title = element_text(hjust = 0.5))
+
+blah<-CheckPropOc %>% filter(!PropOc<0) %>% group_by(Distance) %>% summarise(counts = n())
+ggplot()+
+  geom_point(data = blah,aes(x=Distance,y=counts),size=4)+
+  scale_y_log10(breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
+  theme_cowplot()+
+  theme(plot.title = element_text(hjust = 0.5))
+#seems like the data outside the boundaries certainly tends to be at low distances, but the values themselves increase with distance
+#####
 

### 2021-08-14 R/PropOc Data 3D.Rmd
code for plotting missing data

@@
 #####
-countDistancesALL<-rawPropOcDataClean %>% group_by(SampleCode,Condition, Distance) %>% summarise(count = n()) %>% ungroup() %>%group_by(Condition) %>%  mutate(difference = max(count)- count)
-countDistancesBadOnly<- countDistancesALL%>% filter(difference>0) %>% group_by(SampleCode) %>% summarise(missingDistantes = n()) %>% filter(missingDistantes == 30)
-countDistancesGoodOnly<- countDistancesALL%>% filter(difference==0) %>% group_by(SampleCode) %>% summarise(missingDistantes = 30-n()) %>% filter (missingDistantes==0)
+countDistancesALL<-rawPropOcDataClean %>% group_by(SampleCode,Condition, source,Distance) %>% summarise(count = n()) %>% ungroup() %>%group_by(Condition) %>%  mutate(difference = max(count)- count)
 
-leftover<-anti_join(countDistancesALL,countDistancesBadOnly, by = "SampleCode")
-leftover<-anti_join(leftover,countDistancesGoodOnly, by = "SampleCode")
+countDistancesALLwt<- countDistancesALL %>% filter(Condition=="wt")
+countDistancesALLpqsL<- countDistancesALL %>% filter(Condition=="pqsL")
 
+ggplot()+
+  geom_point(data = countDistancesALLpqsL,aes(x=Distance,y=difference, shape = source, color = SampleCode),size=4)+
+  labs(title ="Prop Oc Analysis Sampling missing by Source and Distance(Original Run")+
+  facet_grid(.~source)+
+  theme_cowplot()+
+  theme(plot.title = element_text(hjust = 0.5))
 #####
@@
 CheckBenchmark<-function(benchmark){
-CheckPropOc<-rawPropOcDataClean %>% filter(PropOc>benchmark|PropOc<0)
+#CheckPropOc<-rawPropOcDataClean %>% filter(PropOc>benchmark|PropOc<0)
+CheckPropOc<-rawPropOcData %>% filter(PropOc<0)
 percentInbound<-length(CheckPropOc$SampleCode)/length(rawPropOcDataClean$SampleCode)*100
@@
 CheckBenchmark(1.05)
+CheckBenchmark(1.1)
+CheckBenchmark(1.2)
+
 #the data outside the range should be primarily at really short distances, since this is where the calculation of voxels in the surrounding and sphere of potentially ocuppied space is the largest  

### 2021-08-14 R/Prop Oc Data Clean.Rmd
new script looking only at prop Oc wt data

---
title: "Prop Oc Data Chronic Wounds"
author: "Juan P Barraza"
date: "8/14/2021"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
library(pixmap)
library(rtiff)
library(reshape2)
library(gplots)
library(gdata)
library(plyr)
library(dplyr)
library(ggplot2)
library(cowplot)
library(tidyr)
library(purrr)
library(plotrix)
library(ggsignif)
library(rdist)
library(stringr)

lseq <- function(from, to, length.out) {
  # logarithmic spaced sequence
  # blatantly stolen from library("emdbook"), because need only this
  exp(seq(log(from), log(to), length.out = length.out))}

source('/Users/jupabago/Documents/Whiteley/PROJECTS/Rpackage/PropOc Package/R/PropOcFunctions2.0.R')

ReadPropOcFile<-function(file){
    propOcData<-read.csv(file,header = T)
    fileName<-str_split(basename(file), "\\.")[[1]][1]#this selects the base file name and removes the ".csv"
    print(paste0("Importing sample ", fileName))
    attrList<-str_split(fileName,"_")[[1]]
    propOcData<-propOcData %>% mutate(Condition = attrList[1], TimePoint = attrList[2], Replicate = attrList[3], SampleCode = fileName)
    return(propOcData)
    }

propOcDatafolder<-'/Volumes/raw_data/Confocal/Carolyn/2020/Chronic wounds/PropOc Data1'
propOcDatafileList<-list.files(path = propOcDatafolder, full.names = TRUE)
rawPropOcDataList<-map(propOcDatafileList,ReadPropOcFile)
rawPropOcData<-bind_rows(rawPropOcDataList)
#rawPropOcData<-rawPropOcData %>% filter(!SampleCode=="mono_d1_01Slim") %>%  filter(!SampleCode=="mono_d1_02Slim")

#QC for data:
##How much data is just straight up missing?
#####
countData<-rawPropOcData %>% group_by(SampleCode, source, Distance) %>% summarize(count = n()) %>% filter(count<1000) %>%ungroup() %>% summarise(MisingTotal = n()*1000-sum(count),TotalMedian = median(count), Mean = mean(count))

countData2<-rawPropOcData %>% group_by(SampleCode, source, Distance) %>% summarize(count = n()) %>% ungroup() %>%filter(count<1000) %>%ungroup() %>% group_by(SampleCode) %>% summarise(MisingTotal = n()*1000-sum(count),TotalMedian = median(count), Mean = mean(count), N = n()) %>% mutate(MissingPercent = MisingTotal/120000*100)

countDistancesALL<-rawPropOcData %>% group_by(SampleCode,source, Distance) %>% summarise(count = n()) %>% ungroup() %>%  mutate(difference = max(count)- count)
ggplot()+
  geom_point(data = countDistancesALL,aes(x=Distance,y=difference, shape = source, color = SampleCode),size=4)+
  labs(title ="Prop Oc Analysis Sampling missing by Source and Distance")+
  facet_grid(.~source)+
  theme_cowplot()+
  theme(plot.title = element_text(hjust = 0.5))

#from 120 possible distance-source combinations, how many of those are missing? 
countDistancesBadOnly<- countDistancesALL%>% filter(difference>0) %>% group_by(SampleCode) %>%  summarise(missingDistantes = n())

#####
#How much of it is outside the ideal boundaries?
#####
CheckBenchmark<-function(benchmark){
#CheckPropOc<-rawPropOcData %>% filter(PropOc>benchmark|PropOc<0)
CheckPropOc<-rawPropOcData %>% filter(PropOc<0)
percentInbound<-length(CheckPropOc$SampleCode)/length(rawPropOcDataClean$SampleCode)*100
return(percentInbound)}

CheckBenchmark(1.5)
```

### 2021-08-17 R/PropOc Data 3D.Rmd
Added cumulative Density, 50 percentile and plots for mean 50 perecentile density per condition

--- 2021-07-18 R/PropOc Data 3D.Rmd
@@
 #####
-#How much of it is outside the ideal boundaries?
+#What are the observations missing?
+#####
+countDistancesALL<-rawPropOcDataClean %>% group_by(SampleCode,Condition, source,Distance) %>% summarise(count = n()) %>% ungroup() %>%group_by(Condition) %>%  mutate(difference = max(count)- count)
 
+countDistancesALLwt<- countDistancesALL %>% filter(Condition=="wt")
+countDistancesALLpqsL<- countDistancesALL %>% filter(Condition=="pqsL")
+
+ggplot()+
+  geom_point(data = countDistancesALLpqsL,aes(x=Distance,y=difference, shape = source, color = SampleCode),size=4)+
+  labs(title ="Prop Oc Analysis Sampling missing by Source and Distance(Original Run")+
+  facet_grid(.~source)+
+  theme_cowplot()+
+  theme(plot.title = element_text(hjust = 0.5))
+#####
+#How much of it is outside the 0 - 1 range?
+#####
 CheckBenchmark<-function(benchmark){
 CheckPropOc<-rawPropOcDataClean %>% filter(PropOc>benchmark|PropOc<0)
+#CheckPropOc<-rawPropOcData %>% filter(PropOc<0)
 percentInbound<-length(CheckPropOc$SampleCode)/length(rawPropOcDataClean$SampleCode)*100
@@
 
-CheckBenchmark(1)
+CheckBenchmark(1.05)
+CheckBenchmark(1.1)
+CheckBenchmark(1.2)
+CheckBenchmark(1.3)
+CheckBenchmark(1.4)
+CheckBenchmark(1.5)
+CheckBenchmark(1.6)
+CheckBenchmark(1.7)
+CheckBenchmark(1.8)
+CheckBenchmark(1.9)
+
+#the data outside the range should be primarily at really short distances, since this is where the calculation of voxels in the surrounding and sphere of potentially ocuppied space is the largest  
+#I think 1.05 is a good benchmark to observe this trend:
+CheckPropOc<-rawPropOcDataClean %>% filter(PropOc>1.5|PropOc<0)
 
 ggplot()+
-  geom_jitter(data = countData,aes(x=Distance,y=X, color = source ),size=4, height= .1)+
+  geom_jitter(data = CheckPropOc %>% filter(!source == "finalRR") %>% filter(!source == "finalGG") %>% filter(PropOc<1000),aes(x=Distance,y=PropOc, color = source ),size=2, height= .1)+
   #labs(title ="title")+
-  #scale_y_log10(breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
+  scale_y_log10(breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
   theme_cowplot()+
@@
 
-GetHistograms<-function(sample){
+blah<-CheckPropOc %>% filter(!PropOc<0) %>% group_by(Distance) %>% summarise(counts = n())
+ggplot()+
+  geom_point(data = blah,aes(x=Distance,y=counts),size=4)+
+  scale_y_log10(breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
+  theme_cowplot()+
+  theme(plot.title = element_text(hjust = 0.5))
 
-data<-propOcData%>% filter(PropOc <1.02) %>% group_by(Distance, source) 
+#seems like the data outside the boundaries certainly tends to be at low distances, but the values themselves increase with distance
+#####
+#Add New varaible to the data frame capping the value pf propOc to 1
+
+rawPropOcDataClean$PropOc1= rawPropOcDataClean$PropOc
+rawPropOcDataClean$PropOc1[rawPropOcDataClean$PropOc1>1] = 1
+rawPropOcDataClean$PropOc1[rawPropOcDataClean$PropOc1<0] = 0
+#make new data frame for downstream analysis
+PropOcDataFiltered<-rawPropOcDataClean %>% filter(PropOc<1.5) %>% filter(PropOc>=0)
+
+GetHistograms<-function(inputData){
+data<-inputData%>% group_by(SampleCode,Distance, source) 
   dataList<-group_split(data)#split data fram into a list of dataframes with a single distance and from a single source
@@
 }
-
 HistogramDistance <- function(df) {
   #histogram<- hist(df$PropOc) 
-  histogram<- hist(df$PropOc, breaks = seq.int(0,1.02,.01)) 
+  histogram<- hist(df$PropOc1, breaks = seq.int(0,1,.01)) 
   #histogram<- hist(df$PropOc, breaks = c(0,lseq(.001,1.03,100)))
@@
   output<-output %>% mutate(Source = df$source[[1]])
+  output<-output %>% mutate(Sample = df$SampleCode[[1]])
   return(output)
 }
+#Run histograms for data
+propOcHistogramData<-GetHistograms(PropOcDataFiltered)#from here what matters is the density since it is freq/total*#ofbins
+propOcHistogramData<-propOcHistogramData %>% group_by(Sample, Source, Distance) %>% mutate(count = sum(Frequency), NormDensity = Density/100) %>% ungroup()
 
-testReadPropOc<-ReadPropOc("mono_d1_01") #this is using seq(.0001,1.03,100)))
-testReadPropOc1<-ReadPropOc("mono_d1_01") #this is using seq(.001,1.03,100)))
-testReadPropOc2<-ReadPropOc("mono_d1_01") #this is using seq.int(0,1.02,.01)) 
-testReadPropOc3<-ReadPropOc("mono_d1_01") #this is without specifying breaks
+#plot distributions
+PlotAllPropOcData <- function(sample ) {
+  ggplot()+ 
+    geom_point(data = propOcHistogramData %>% filter(Sample ==sample),aes(x=Value,y=NormDensity, color = Distance),size=2)+
+    scale_y_log10( breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
+    scale_color_gradientn(colours = rainbow(5))+
+    facet_wrap(.~Source)+
+    theme_cowplot()+
+    theme(plot.title = element_text(hjust = 0.5))
+}
+PlotAllPropOcData("wt_d1_05")#looks cool, so let's keep going...
 
-testReadPropOcLaptop<-ReadPropOc("mono_d1_01Laptop")
+#now calculate the maximum frequency
+propOcMaxDensity<-propOcHistogramData %>% 
+    group_by(Sample, Distance, Source)%>% 
+    mutate(MaxDensity = max(NormDensity)) %>% 
+    mutate(DensityCh = ifelse(Density ==max(Density), 1, 0 )) %>% filter(DensityCh==1) %>% ungroup()#find max density, check where it matches
+  propOcMaxDensityDoubles<-propOcMaxDensity %>% group_by(Sample,Distance, Source) %>% mutate(DoubledValues = sum(DensityCh)) %>% filter (DoubledValues>1)#this is just to find which values were repeated
 
-testrawPropOcData<-read.csv(paste0("/Volumes/raw_data/Confocal/Carolyn/2020/Chronic wounds/PropOc Data/", "mono_d1_01",".csv"),header = T)
+  PlotMaxDensities <- function(sample) {
+  ggplot()+
+    geom_jitter(data = propOcMaxDensity %>% filter(Sample ==sample),aes(x=Value, y=Density,color = Distance),size=2)+
+    labs(title ="Maximum Density")+
+    scale_y_log10(breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
+    facet_wrap( ~ Source, ncol = 2)+
+    scale_color_gradientn(colours = rainbow(5))+
+    #scale_shape_manual(values=c(0,1,2, 15,16,17))+
+    theme_cowplot()+
+    theme(plot.title = element_text(hjust = 0.5))
+}
+PlotMaxDensities("wt_d1_05")
+  #maximum distribution isn't super representative, so for the distribution, I calculated the value at which 50% of the population is found
+
+#Median distribution
+getDeathCurve<-function(df){
+  currentDensity = 0
+  for (i in 1 : nrow(df)){
+    addeddensity<-1-currentDensity
+    df[i,9]<-addeddensity
+    df[i,10]<-currentDensity
+    currentDensity = currentDensity+df[i,8]
+  }
+  colnames(df)<-c("Value","Frequency","Density", "Distance", "Source","Sample", "count", "NormDensity", "Decay", "currentDens")
+  df<-df %>% mutate (normDecay = (Decay - min(Decay)) / (max(Decay) - min(Decay)), DeltaDens = abs(Decay-currentDens))
+  return(df)
+  }
+GetPercentiles<-function(input){
+  df<-input %>% group_by(Sample, Distance, Source)
+  yas<- group_split(df)
+  mappedData<-map(yas, getDeathCurve)
+  boundData<-bind_rows(mappedData)
+return(boundData)}
+
+#Calculate the cumulative density
+testGetPercentiles<-GetPercentiles(propOcHistogramData %>% filter(Sample == "wt_d1_05"))#test case for sample wt_d1_05
+propOcDensityData<-GetPercentiles(propOcHistogramData)#all data
+
+#Calculate the value at half density
+test50Percentile<-testGetPercentiles %>% group_by(Source, Sample, Distance) %>%filter(DeltaDens == min(DeltaDens))#test case for sample wt_d1_05
+propOcMidDensity<-propOcDensityData %>% group_by(Source, Sample, Distance) %>%filter(DeltaDens == min(DeltaDens))#all data
+
+PlotPercentiles <- function(df) {
+  ggplot()+
+    geom_point(data = df,aes(y=Value, color=normDecay,x = Distance, shape = Sample),size=2)+
+    #geom_pointrange(data = df,aes(x = Distance,y=meanValue,ymax=meanValue+SdValue,ymin=meanValue-SdValue, color=Strain),size=2)+
+    labs(title ="50 percentile Density")+
+    #scale_y_log10(breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
+    #scale_x_log10(breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
+    facet_wrap( ~ Source, ncol = 2)+
+    scale_color_gradientn(colours = rainbow(5))+
+    theme_cowplot()+
+    theme(plot.title = element_text(hjust = 0.5))
+  }
+PlotPercentiles(test50Percentile)#test case for sample wt_d1_05
+
+#Clean up data for plotting and doing stats
+##Recover conditions
+
+PropOcDataFiltered1<-PropOcDataFiltered %>% group_by(Condition,TimePoint,SampleCode) %>% summarise(None = n()) %>% mutate(Sample = SampleCode)
+
+propOcMidDensitylabeled <-merge(propOcMidDensity,PropOcDataFiltered1)
+
+##Make them factors
+propOcMidDensitylabeled$Condition <- factor(propOcMidDensitylabeled$Condition, levels = c("mono", "pawt","papqsL", "paphz", "wt", "pqsL", "phz"),labels = c('Sa mono', 'Pa wt mono','pqsL mono','phz mono','wt co', 'pqsL co', 'phz co'))
+propOcMidDensitylabeled$TimePoint <- factor(propOcMidDensitylabeled$TimePoint, levels = c("d1", "d4"),labels = c('Day 1','Day 4'))
+
+propOcMidDensitylabeled<-propOcMidDensitylabeled%>% mutate(Relation = recode(Source, "finalGG" = "Pa->Pa","finalRG" = "Sa->Pa","finalRR" = "Sa->Sa","finalGR" = "Pa->Sa"))
+
+propOcMidDensitylabeled<-propOcMidDensitylabeled%>% mutate(Culture = recode(Condition, 'Sa mono' = "mono", 'Pa wt mono' = "mono",'pqsL mono'= "mono",'phz mono'= "mono",'wt co'= "co", 'pqsL co'= "co", 'phz co'= "co"))
+
+propOcMidDensitylabeled<-propOcMidDensitylabeled%>% mutate(Strain = recode(Condition, 'Sa mono' = "Sa", 'Pa wt mono' = "wt",'pqsL mono'= "pqsL",'phz mono'= "phz",'wt co'= "wt", 'pqsL co'= "pqsL", 'phz co'= "phz"))
+
+propOcMidDensityStats<-propOcMidDensitylabeled %>% ungroup() %>% group_by(Condition,Culture,Strain,TimePoint, Distance, Relation) %>% summarize(meanValue = mean(Value), sdValue = sd(Value), medianValue = median(Value))
+
+ggplot()+#linear
+    geom_point(data = propOcMidDensityStats %>% filter(Relation== "Pa->Pa"),aes(y=meanValue, x = Distance,color=Condition, shape = "Mean"),size=2)+
+    geom_point(data = propOcMidDensityStats %>% filter(Relation== "Pa->Pa"),aes(y=medianValue, x = Distance,color=Condition,shape = "Median"),size=2)+
+    labs(title ="mean 50 percentile Density")+
+    #scale_y_log10(breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
+    #scale_x_log10(breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
+    facet_grid(Relation ~ TimePoint)+
+    #scale_color_gradientn(colours = rainbow(5))+
+    #scale_shape_manual(values=c(0,1,2, 15,16,17))+
+    scale_color_brewer(palette = "Set1")+
+    theme_cowplot()+
+    theme(plot.title = element_text(hjust = 0.5))
+
+ggplot()+#linear
+    geom_point(data = propOcMidDensityStats %>% filter(Relation== "Sa->Sa"),aes(y=meanValue, x = Distance,color=Culture, shape = "Mean"),size=2)+
+    geom_point(data = propOcMidDensityStats %>% filter(Relation== "Sa->Sa"),aes(y=medianValue, x = Distance,color=Culture,shape = "Median"),size=2)+
+    labs(title ="mean 50 percentile Density")+
+    #scale_y_log10(breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
+    #scale_x_log10(breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
+    facet_grid(Strain ~ TimePoint)+
+    #scale_color_gradientn(colours = rainbow(5))+
+    #scale_shape_manual(values=c(0,1,2, 15,16,17))+
+    scale_color_brewer(palette = "Set1")+
+    theme_cowplot()+
+    theme(plot.title = element_text(hjust = 0.5))
 
@@
 
-```{r Original Whole PropOc frequency functions from mBio Paper}
+```{r Original Whole PropOc frequency functions from mBio Paper -DONE}
 GetAllHistPropOc <- function(df, timepoint){
@@
 
-```{r Whole PropOc frequency Figures}
+```{r Whole PropOc frequency Figures -DONE}
 PlotAllPropOcData <- function(df, relation ) {
@@
 
-```{r Whole PropOc Data wrangling}
+```{r Whole PropOc Data wrangling -DONE}
 #So, I think the first thing to do would be to get a "mode", or the highest value for frequency of proportional occupancy per distance.
@@
 
-```{r Whole Prop Freq Figures}
+```{r Max Density Figures -DONE}
 PlotMaxDensities <- function(df) {
@@
 ```
+
 #Calculating 50 percentile density.
-```{r death curves Functions and data}
+```{r death curves Functions and data -DONE}
 getDeathCurve<-function(df){
@@
 ```
+
 #Enrichment (distance at highest proportional occupancy) 
@@
 
-allDeathCurvesLog2midAbsEnrichment<- allDeathCurvesLog2midAbs %>% group_by(Sample, Source)%>%select(Value, Distance, Source,Sample, Strain, Percentile50) %>% mutate(Enrichment = max(Value)) %>%
-  mutate(EnrichmentCh = ifelse(Enrichment == Value, 1, 0 )) %>% filter(EnrichmentCh==1) %>% mutate(DoubledValues = sum(EnrichmentCh)) %>% ungroup()#find max
+allDeathCurvesLog2midAbsEnrichment<- allDeathCurvesLog2midAbs %>% group_by(Sample, Source)%>%
+  select(Value, Distance, Source,Sample, Strain, Percentile50) %>% mutate(Enrichment = max(Value)) %>%
+  mutate(EnrichmentCh = ifelse(Enrichment == Value, 1, 0 )) %>% filter(EnrichmentCh==1) %>% 
+  mutate(DoubledValues = sum(EnrichmentCh)) %>% ungroup()#find max
 
@@
 #That looks like a lot of the values are just at 0.5 distance, which I dont really care, I can make another argument about direct contact, so I'll filter those out...
-allDeathCurvesLog2midAbsEnrichment2<- allDeathCurvesLog2midAbs %>% filter(!Distance ==0.5)%>% 
+allDeathCurvesLog2midAbsEnrichment2<-allDeathCurvesLog2midAbs %>% filter(!Distance ==0.5)%>% 
   group_by(Sample, Source) %>% select(Value, Distance, Source,Sample, Strain, Percentile50) %>% mutate(Enrichment = max(Value)) %>%

### 2021-08-18 R/Prop Oc Data Clean.Rmd
added calculation of enrichment from mean PO values

@@
 source('/Users/jupabago/Documents/Whiteley/PROJECTS/Rpackage/PropOc Package/R/PropOcFunctions2.0.R') 
+```
 
+```{r import data}
 ReadPropOcFile<-function(file){
@@
 
-propOcDatafolder<-'/Volumes/raw_data/Confocal/Carolyn/2020/Chronic wounds/PropOc Data1'
+propOcDatafolder<-'/Volumes/raw_data/Confocal/Carolyn/2020/Chronic wounds/PropOc Data'
 propOcDatafileList<-list.files(path = propOcDatafolder, full.names = TRUE)
@@
 rawPropOcData<-bind_rows(rawPropOcDataList)
-#rawPropOcData<-rawPropOcData %>% filter(!SampleCode=="mono_d1_01Slim") %>%  filter(!SampleCode=="mono_d1_02Slim")
+```
+```{r QC for data}
+#first, remove the unnecessary conditions
+removablePropOc <- bind_rows(rawPropOcData %>% filter(Condition == "mono") %>% filter(!source == "finalRR"), #Pa in Sa mono culture
+                       rawPropOcData %>% filter(Condition == "papqsL") %>% filter(!source == "finalGG"),#Sa in all Pa mono cultures
+                       rawPropOcData %>% filter(Condition == "pawt") %>% filter(!source == "finalGG"),
+                       rawPropOcData %>% filter(Condition == "paphz") %>% filter(!source == "finalGG"))
+rawPropOcDataClean <- anti_join(rawPropOcData, removablePropOc)
+
+lowCountSamples<-bind_rows(rawPropOcData %>% filter(Sample == "mono_d1_02"),
+                           rawPropOcData %>% filter(Sample == "phz_d4_08"),
+                           rawPropOcData %>% filter(Sample == "wt_d4_11") %>% filter(Source == "finalRG"))
+rawPropOcDataClean <- anti_join(rawPropOcDataClean, lowCountSamples)
+
+##then, bad samples
+rawPropOcDataClean<-rawPropOcDataClean %>% filter(!SampleCode == "mono_d1_03")
+rawPropOcDataClean<-rawPropOcDataClean %>% filter(!SampleCode == "phz_d4_14")
+rawPropOcDataClean<-rawPropOcDataClean %>% filter(!SampleCode == "pqsL_d4_02")
+rawPropOcDataClean<-rawPropOcDataClean %>% filter(!SampleCode == "pqsL_d4_04")
+rawPropOcDataClean<-rawPropOcDataClean %>% filter(!SampleCode == "pqsL_d4_10")
+rawPropOcDataClean<-rawPropOcDataClean %>% filter(!SampleCode == "wt_d4_07")
+rawPropOcDataClean<-rawPropOcDataClean %>% filter(!SampleCode == "papqsL_d4_02")
+rawPropOcDataClean<-rawPropOcDataClean %>% filter(!SampleCode == "pawt_d4_05")
+rawPropOcDataClean<-rawPropOcDataClean %>% filter(!SampleCode == "phz_d4_06")
 
@@
 
+#What are the observations missing?
 countDistancesALL<-rawPropOcData %>% group_by(SampleCode,source, Distance) %>% summarise(count = n()) %>% ungroup() %>%  mutate(difference = max(count)- count)
@@
 countDistancesBadOnly<- countDistancesALL%>% filter(difference>0) %>% group_by(SampleCode) %>%  summarise(missingDistantes = n())
-
+#dont know if this works
+#lowCountSamples<-bind_rows(rawPropOcDataClean %>% filter(Sample == "mono_d1_02"),
+#                           rawPropOcDataClean %>% filter(Sample == "phz_d4_08"),
+#                           rawPropOcDataClean %>% filter(Sample == "wt_d4_11") %>% filter(Source == "finalRG"))
+#rawPropOcDataClean <- anti_join(rawPropOcDataClean, lowCountSamples)
 #####
@@
 
-CheckBenchmark(1.5)
+CheckBenchmark(1.5)#This is the benchmark I picked
+
+#the data outside the range should be primarily at really short distances, since this is where the calculation of voxels in the surrounding and sphere of potentially ocuppied space is the largest  
+#I think 1.05 is a good benchmark to observe this trend:
+CheckPropOc<-rawPropOcDataClean %>% filter(PropOc>1.5|PropOc<0)
+
+ggplot()+
+  geom_jitter(data = CheckPropOc %>% filter(!source == "finalRR") %>% filter(!source == "finalGG") %>% filter(PropOc<1000),aes(x=Distance,y=PropOc, color = source ),size=2, height= .1)+
+  #labs(title ="title")+
+  scale_y_log10(breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
+  theme_cowplot()+
+  theme(plot.title = element_text(hjust = 0.5))
+
+blah<-CheckPropOc %>% filter(!PropOc<0) %>% group_by(Distance) %>% summarise(counts = n())
+ggplot()+
+  geom_point(data = blah,aes(x=Distance,y=counts),size=4)+
+  scale_y_log10(breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
+  theme_cowplot()+
+  theme(plot.title = element_text(hjust = 0.5))
+#seems like the data outside the boundaries certainly tends to be at low distances, but the values themselves increase with distance
+#####
 ```
+```{r wrangling clean Data}
+
+#Add New variaible to the data frame capping the value pf propOc to 1
+rawPropOcDataClean$PropOc1= rawPropOcDataClean$PropOc
+rawPropOcDataClean$PropOc1[rawPropOcDataClean$PropOc1>1] = 1
+rawPropOcDataClean$PropOc1[rawPropOcDataClean$PropOc1<0] = 0
+#make new data frame for downstream analysis
+PropOcDataFiltered<-rawPropOcDataClean %>% filter(PropOc<1.5) %>% filter(PropOc>=0)
+#make column factors 
+PropOcDataFiltered$SampleCode<-as.factor(PropOcDataFiltered$SampleCode)
+PropOcDataFiltered$TimePoint<-as.factor(PropOcDataFiltered$TimePoint)
+PropOcDataFiltered$Condition<-as.factor(PropOcDataFiltered$Condition)
+PropOcDataFiltered$source<-as.factor(PropOcDataFiltered$source)
+PropOcDataFiltered$Replicate<-as.factor(PropOcDataFiltered$Replicate)
+
+#From this point on there are at least two ways to move forward. The simplest one is to get the mean, mode and variance in the data
+meanPOData<-PropOcDataFiltered %>% group_by(SampleCode, TimePoint, source, Distance, Condition) %>% summarise(MeanPO = mean(PropOc1), MedianPO = median(PropOc1), SDPO = sd(PropOc1), SEPO = std.error(PropOc1))
+
+#label and merge with metadata for plotting, output of this is pOMeanMeta dataframe used for plots
+#####
+meanPOData$Condition <- factor(meanPOData$Condition, levels = c("mono", "pawt","papqsL", "paphz", "wt", "pqsL", "phz"),labels = c('Sa mono', 'Pa wt mono','pqsL mono','phz mono','wt co', 'pqsL co', 'phz co'))
+meanPOData$TimePoint <- factor(meanPOData$TimePoint, levels = c("d1", "d4"),labels = c('Day 1','Day 4'))
+meanPOData<-meanPOData%>% mutate(Relation = recode(source, "finalGG" = "Pa->Pa","finalRG" = "Sa->Pa","finalRR" = "Sa->Sa","finalGR" = "Pa->Sa"))
+meanPOData<-meanPOData%>% mutate(Culture = recode(Condition, 'Sa mono' = "mono", 'Pa wt mono' = "mono",'pqsL mono'= "mono",'phz mono'= "mono",'wt co'= "co", 'pqsL co'= "co", 'phz co'= "co"))
+meanPOData<-meanPOData%>% mutate(Strain = recode(Condition, 'Sa mono' = "Sa", 'Pa wt mono' = "wt",'pqsL mono'= "pqsL",'phz mono'= "phz",'wt co'= "wt", 'pqsL co'= "pqsL", 'phz co'= "phz"))
+
+metaData.df<-metaData.df %>% select(SampleCode, mouse, Position, size, Region, Zdim, xyDim,xySize)
+pOMeanMeta<-metaData.df %>%  merge(meanPOData, by = "SampleCode")
+pOMeanMeta <- pOMeanMeta %>% mutate(diffMean = MeanPO/MedianPO)
+pOMeanMeta$Region <- factor(pOMeanMeta$Region, levels = c("core", "edge",""))
+
+#####
+
+#Plot Mean PropOc
+#####
+PlotMeanPOs<-function(relation){
+  ggplot()+
+    geom_point(data =pOMeanMeta%>%filter(Relation == relation),aes(x=Distance,y=MeanPO,color = Region),size=2)+
+    #geom_pointrange(data =pOMeanMeta%>%filter(Relation == relation),aes(x=Distance,y=MeanPO,  ymax = MeanPO+SDPO,ymin = MeanPO-SDPO,color =Condition, shape = "Mean"),size=1)+
+    #geom_point(data =pOMeanMeta%>%filter(Relation == relation),aes(x=Distance,y = MedianPO,color = "Median"),size=2)+
+    labs(title =paste("Mean PO", relation))+
+    #facet_grid(Condition~TimePoint,scales = "free", space = "free")+
+    scale_color_brewer(palette = "Set1")+
+    facet_grid(Condition~TimePoint)+
+    theme_cowplot()+
+    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),plot.title = element_text(hjust = 0.5))
+}
+PlotMeanPOs("Pa->Sa")
+PlotMeanPOs("Sa->Pa")
+PlotMeanPOs("Sa->Sa")
+PlotMeanPOs("Pa->Pa")
+#####
+
+#Calculate the Enrichment
+pOcEnriMean<- pOMeanMeta %>% group_by(SampleCode,Relation)%>% mutate(Enrichment = max(MeanPO)) %>%
+  mutate(EnrichmentCh = ifelse(Enrichment == MeanPO, 1, 0 )) %>% filter(EnrichmentCh==1) %>% 
+  mutate(DoubledValues = sum(EnrichmentCh)) %>% ungroup()#find max
+###Sorry this is out of order
+lowCountSamples<-bind_rows(pOcEnriMean %>% filter(SampleCode == "mono_d1_02"),
+                           pOcEnriMean %>% filter(SampleCode == "phz_d4_08"),
+                           pOcEnriMean %>% filter(SampleCode == "wt_d4_11") %>% filter(source == "finalRG"))
+pOcEnriMean <- anti_join(pOcEnriMean, lowCountSamples)
+
+PlotEnrichmentMean<-function(relation){
+  ggplot()+
+    geom_point(data = pOcEnriMean %>% filter(Relation == relation),aes(y=MeanPO,x = SampleCode,shape = Region,  color =Condition),size=2)+
+    #geom_label(data = propOcEnrichment %>% filter(Relation == relation),aes(y=30, x = Sample, label = Value),size=2)+
+    labs(title =paste("50 percentile Enrichment", relation))+
+    facet_grid(.~TimePoint,scales = "free", space = "free")+
+    #scale_color_gradientn(colours = rainbow(5))+
+    #scale_shape_manual(values=c(0,1,2, 15,16,17))+
+    theme_cowplot()+
+    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),plot.title = element_text(hjust = 0.5))
+}
+PlotEnrichmentMean("Pa->Sa")
+PlotEnrichmentMean("Sa->Pa")
+PlotEnrichmentMean("Sa->Sa")
+PlotEnrichmentMean("Pa->Pa")
+
+#Get stats across samples
+pOMeanStatsRgn<-pOMeanMeta %>% ungroup() %>% group_by(Condition,Culture,Strain,TimePoint, Distance, Relation, Region) %>% summarize(meanValue = mean(MeanPO), sdValue = sd(MeanPO), medianValue = median(MeanPO))
+
+```

### 2021-08-18 Matlab/adaptiveThreshold.m
tested changes

@@ -15,7 +15,7 @@ Tiff2Data (rawTifPath,binTifPath,aggsFilePath,slicedAggsFilePath, xySize, zSize)
 end
 %}
 
-for sampleNumber = 1:10
+for sampleNumber = 
 iterateSamples('paphz_d4_',sampleNumber,.415,.52)
 end
 iterateSamples('papqsL_d4_',1,.208,.52)

### 2021-08-21 R/AggregateCounts.Rmd
Added the Macro Scale Region to biomass data and made plots

@@
 #agregate input functions
-ReadAggregateFile<-function(file, species, timepoint, condition, replicate, sampleCode){#make a dataframe of the aggregate size list and add experimental parameters
+ReadAggregateFile<-function(file, species, timepoint, condition, replicate,fileName, sampleCode){#make a dataframe of the aggregate size list and add experimental parameters
   print(file)
@@
    datos<-datos %>% mutate(SampleCode = sampleCode)
+   datos<-datos %>% mutate(FileName = fileName)
    datos$Species<-as.factor(datos$Species)
@@
    datos$TimePoint<-as.factor(datos$TimePoint)
+   datos$FileName<-as.factor(datos$FileName)
    datos$SampleCode<-as.factor(datos$SampleCode)
+
    return(datos)
@@
      attrList<-str_split(fileName,"_")[[1]]
-     growthDf<-rbind(growthDf,ReadAggregateFile(fileList[aggList],attrList[4],attrList[2],attrList[1],attrList[3], fileName))
-     }
+     sampleCode = paste0(attrList[1],"_",attrList[2],"_",attrList[3])
+     growthDf<-rbind(growthDf,ReadAggregateFile(fileList[aggList],attrList[4],attrList[2],attrList[1],attrList[3], fileName, sampleCode))}
    return(growthDf)
@@
 aggregateList<-GetAggregates()#this reads the data from Matlab
+
 #remove bad samples and irrelevant conditions
@@
 ##then, bad samples
-aggregateList<-aggregateList %>% filter(!SampleCode == "mono_d1_03_Pa" & !SampleCode == "mono_d1_03_Sa")
-aggregateList<-aggregateList %>% filter(!SampleCode == "phz_d4_14_Pa" & !SampleCode == "phz_d4_14_Sa")
-aggregateList<-aggregateList %>% filter(!SampleCode == "pqsL_d4_02_Pa" & !SampleCode == "pqsL_d4_02_Sa")
-aggregateList<-aggregateList %>% filter(!SampleCode == "pqsL_d4_04_Pa" & !SampleCode == "pqsL_d4_04_Sa")
-aggregateList<-aggregateList %>% filter(!SampleCode == "pqsL_d4_10_Pa" & !SampleCode == "pqsL_d4_10_Sa")
-aggregateList<-aggregateList %>% filter(!SampleCode == "wt_d4_07_Pa" & !SampleCode == "wt_d4_07_Sa")
-aggregateList<-aggregateList %>% filter(!SampleCode == "papqsL_d4_02_Pa" & !SampleCode == "papqsL_d4_02_Sa")
-aggregateList<-aggregateList %>% filter(!SampleCode == "pawt_d4_05_Pa" & !SampleCode == "pawt_d4_05_Sa")
-aggregateList<-aggregateList %>% filter(!SampleCode == "phz_d4_06_Pa" & !SampleCode == "phz_d4_06_Sa")
+aggregateList<-aggregateList %>% filter(!SampleCode == "mono_d1_03")
+aggregateList<-aggregateList %>% filter(!SampleCode == "phz_d4_14")
+aggregateList<-aggregateList %>% filter(!SampleCode == "pqsL_d4_02")
+aggregateList<-aggregateList %>% filter(!SampleCode == "pqsL_d4_04")
+aggregateList<-aggregateList %>% filter(!SampleCode == "pqsL_d4_10")
+aggregateList<-aggregateList %>% filter(!SampleCode == "wt_d4_07")
+aggregateList<-aggregateList %>% filter(!SampleCode == "papqsL_d4_02")
+aggregateList<-aggregateList %>% filter(!SampleCode == "pawt_d4_05")
+aggregateList<-aggregateList %>% filter(!SampleCode == "phz_d4_06")
 
@@
 aggregateList<-aggregateList%>% mutate(Strain = recode(Condition, 'Sa mono' = "Sa", 'Pa wt mono' = "wt",'pqsL mono'= "pqsL",'phz mono'= "phz",'wt co'= "wt", 'pqsL co'= "pqsL", 'phz co'= "phz"))
+#Adding the metadata
+metaData <-read.csv('/Volumes/raw_data/Confocal/Carolyn/2020/Chronic wounds/images metadata.csv', header = TRUE)
+metaData<-metaData %>% select(SampleCode, mouse, Position, size, Region, Zdim, xyDim,xySize)
+aggregateList<-metaData %>%  merge(aggregateList)
+aggregateList$Region<-as.factor(aggregateList$Region)
 
+#---This chunk creates 'aggregateList' data frame, which contains all the aggregates per sample and it is on the correct format
 ```
@@
 #Statistics from all aggregates
-
 #Get aggregate summary per sample
-aggregateListSummaryReplicate<-aggregateList%>% group_by(Species, Strain, Culture,TimePoint, Condition, Replicate) %>% 
+aggregateListSummaryReplicate<-aggregateList%>% group_by(SampleCode, Species, Strain, Culture,TimePoint, Condition, Replicate,Region) %>% 
   summarise(Aggs = n(), biomass = sum(Size), meanAggSize = mean(Size), seAggSize = std.error(Size), maxSize = max(Size), minSize = min(Size)) %>%
-  ungroup() %>% mutate(RatioMaxTotal = maxSize/biomass )
+  ungroup() %>% mutate(RatioMaxTotal = maxSize/biomass)
 
@@
 #####
-
 ggplot()+ 
@@
         strip.background = element_rect(color="black", fill="white", size=1, linetype="solid"))#facet background
+#####
+#Plot only biomass per Sample
+PlotBiomasPerSample<-function(df){
+ggplot()+ 
+    #this is for multiple conditions
+  #geom_point(data = df, aes(x = Strain, y= biomass, shape = Region, color = Culture),size = 3, position = position_dodge(width = .6))+
+  geom_point(data = df, aes(x = Culture, y= biomass, color= Species, shape = Region),size = 3, 
+             position = position_jitterdodge(jitter.height = 0, jitter.width = .3,dodge.width = 0.75))+
+    scale_y_log10( breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)), limits = c(1, 100000000))+
+      #this is for multiple conditions  
+    #facet_grid(Species~TimePoint, scales = "free", space = "free") +
+    #this is for only one mutant
+    facet_grid(.~TimePoint, scales = "free", space = "free") +
+  ggtitle('Total biomass per sample')+
+  labs(x = "",y = bquote(paste("Volume (", mu*"m"^3*")")))+
+  scale_color_brewer(palette = "Set1")+
+  scale_shape_manual(values=c(1, 2,0))+
+  theme_cowplot()+
+  panel_border() +
+  theme(plot.title = element_text(hjust = 0.5), 
+        strip.text = element_text(size = 11, face = "italic",margin = margin(.1,0,.1,0, "cm")),#this is for the facet text
+        strip.background = element_rect(color="black", fill="white", size=1, linetype="solid"))#facet background
+}
 
-#####
+PlotBiomasPerSample(aggregateListSummaryReplicate)
+#plotting only Sa and pa wt in mono and co-culture
+PlotBiomasPerSample(aggregateListSummaryReplicate %>% filter(Condition == "Sa mono" |Condition == "wt co"|Condition == "Pa wt mono"))
 
 #Get aggregate Summary per condition
-aggregateListSummary<-aggregateList %>% group_by(Species, Strain, Culture,TimePoint, Condition) %>% 
-  summarise(Aggs = n(), biomass = sum(Size), meanAggSize = mean(Size), seAggSize = std.error(Size), maxSize = max(Size), minSize = min(Size)) %>%
-  ungroup() %>% mutate(RatioMaxTotal = maxSize/biomass ) 
+aggregateListSummaryCondition<-aggregateListSummaryReplicate %>% group_by(Species, Strain, Culture,TimePoint, Condition, Region) %>% 
+  summarise(meanAggs= mean(Aggs), meanBiomassLog = mean(log10(biomass)), SEBiomassLog = std.error((log10(biomass))), meanAggSize = mean(meanAggSize), seAggSize = std.error(meanAggSize))%>%  mutate(meanBiomass =  meanBiomassLog^10, SEBiomass = SEBiomassLog^10)
 #plot agg summary per condition
 #####
-#Version 1
+PlotBiomassPerCondition<-function(df, metric, error){
 ggplot()+ 
-  geom_jitter(data = aggregateListSummary, aes(x = TimePoint, y= meanAggSize, color = Condition,shape = "MeanSize"),size = 3, height = 0, width = .3)+
-  geom_jitter(data = aggregateListSummary, aes(x = TimePoint, y= maxSize, color = Condition, shape = "MaxSize"),size = 3, height = 0, width = .3)+
-  geom_jitter(data = aggregateListSummary, aes(x = TimePoint, y= biomass, color = Condition, shape = "TotalBiomass"),size = 3, height = 0,width= .3)+
-  scale_y_log10( breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
-  facet_grid(. ~ Species, scales = "free", space = "free") +
-  ggtitle('Mean size and largest aggregate and total biomass per condition')+
+  geom_pointrange(data = df, aes(x = Culture, y= .data[[metric]],
+                                 ymax=.data[[metric]]+.data[[error]],ymin =.data[[metric]]-.data[[error]], color = Strain,shape = Region), 
+             position = position_jitterdodge(jitter.height = 0, jitter.width = .3,dodge.width = 0.75))+
+  scale_y_log10( breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)), limits = c(10000,1000000000))+
+  facet_grid(Species~TimePoint, scales = "free", space = "free") +
+  ggtitle('Mean size per condition and region')+
   labs(x = "",y = bquote(paste("Volume (", mu*"m"^3*")")))+
-  scale_shape_manual(name="Metric",values=c(MeanSize=1, MaxSize=2, TotalBiomass=17))+
+  #scale_shape_manual(name="Metric",values=c(MeanSize=1, MaxSize=2, TotalBiomass=17))+
   scale_color_brewer(palette = "Set1")+
@@
           strip.background = element_rect(color="black", fill="white", size=1, linetype="solid"))
-#Version 2
+}
+PlotBiomassPerCondition(aggregateListSummaryCondition,"meanBiomass", "SEBiomass")
+PlotBiomassPerCondition(aggregateListSummary,"biomass")
+#####
+#combining all 
+PlotBiomasPerSampleAndConditionWT<-function(df1,df2){
 ggplot()+ 
-  geom_jitter(data = aggregateListSummary, aes(x = TimePoint, y= meanAggSize, color = Strain,shape = "MeanSize"),size = 3, height = 0, width = .3)+
-  geom_jitter(data = aggregateListSummary, aes(x = TimePoint, y= maxSize, color = Strain, shape = "MaxSize"),size = 3, height = 0, width = .3)+
-  geom_jitter(data = aggregateListSummary, aes(x = TimePoint, y= biomass, color = Strain, shape = "TotalBiomass"),size = 3, height = 0,width= .3)+
-  scale_y_log10( breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
-  facet_grid(Species~Culture, scales = "free", space = "free") +
-  ggtitle('Mean size and largest aggregate and total biomass per condition')+
-  labs(x = "",y = bquote(paste("Volume (", mu*"m"^3*")")))+
-  scale_shape_manual(name="Metric",values=c(MeanSize=1, MaxSize=2, TotalBiomass=17))+
+    geom_point(data = df1, aes(x = Culture, y= meanBiomassLog,color = Species,shape = Region), 
+             position = position_jitterdodge(jitter.height = 0, jitter.width = .3,dodge.width = 0.75), size = 4)+
+  geom_point(data = df2, aes(x = Culture, y= log10(biomass), color= Species, shape = Region),size = 1, 
+             position = position_jitterdodge(jitter.height = 0, jitter.width = .3,dodge.width = 0.75))+
+    #scale_y_log10( breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)), limits = c(1, 100000000))+
+      facet_grid(.~TimePoint, scales = "free", space = "free") +
+  ggtitle('Biomass per sample')+
+  labs(x = "",y = bquote(paste("Volume (log10", mu*"m"^3*")")))+
   scale_color_brewer(palette = "Set1")+
+  scale_shape_manual(values=c(16, 1))+
+  ylim(0,8)+
     theme_cowplot()+
-  theme(plot.title = element_text(hjust = 0.5),strip.text = element_text(size = 11, face = "italic",margin = margin(.1,0,.1,0, "cm")),#this is for the facets
-          strip.background = element_rect(color="black", fill="white", size=1, linetype="solid"))
+  panel_border() +
+  theme(plot.title = element_text(hjust = 0.5), 
+        strip.text = element_text(size = 11, face = "italic",margin = margin(.1,0,.1,0, "cm")),#this is for the facet text
+        strip.background = element_rect(color="black", fill="white", size=1, linetype="solid"))#facet background
+}
+PlotBiomasPerSampleAndConditionWT(aggregateListSummaryCondition%>% filter(Condition == "Sa mono" |Condition == "wt co"|Condition == "Pa wt mono"),
+                                aggregateListSummaryReplicate %>% filter(Condition == "Sa mono" |Condition == "wt co"|Condition == "Pa wt mono"))
+PlotBiomasPerSampleAndCondition<-function(df1,df2){
+ggplot()+ 
+    geom_point(data = df1, aes(x = Culture, y= meanBiomassLog,color = Strain,shape = Region), 
+             position = position_jitterdodge(jitter.height = 0, jitter.width = .3,dodge.width = 0.75), size = 4)+
+  geom_point(data = df2, aes(x = Culture, y= log10(biomass), color= Strain, shape = Region),size = 1, 
+             position = position_jitterdodge(jitter.height = 0, jitter.width = .3,dodge.width = 0.75))+
+    #scale_y_log10( breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)), limits = c(1, 100000000))+
+      facet_grid(Species~TimePoint, scales = "free", space = "free") +
+  ggtitle('Biomass per sample')+
+  labs(x = "",y = bquote(paste("Volume (log10", mu*"m"^3*")")))+
+  scale_color_brewer(palette = "Set1")+
+  scale_shape_manual(values=c(4,16, 1))+
+  ylim(0,8)+
+    theme_cowplot()+
+  panel_border() +
+  theme(plot.title = element_text(hjust = 0.5), 
+        strip.text = element_text(size = 11, face = "italic",margin = margin(.1,0,.1,0, "cm")),#this is for the facet text
+        strip.background = element_rect(color="black", fill="white", size=1, linetype="solid"))#facet background
+}
+PlotBiomasPerSampleAndCondition(aggregateListSummaryCondition,aggregateListSummaryReplicate)
 
-#####
 ```

### 2021-08-22 R/Prop Oc Data Clean.Rmd

@@
 
-#Add New variaible to the data frame capping the value pf propOc to 1
+#Add New variable to the data frame capping the value pf propOc to 1
 rawPropOcDataClean$PropOc1= rawPropOcDataClean$PropOc
@@
 #From this point on there are at least two ways to move forward. The simplest one is to get the mean, mode and variance in the data
+```
+
+```{r meanPO}
 meanPOData<-PropOcDataFiltered %>% group_by(SampleCode, TimePoint, source, Distance, Condition) %>% summarise(MeanPO = mean(PropOc1), MedianPO = median(PropOc1), SDPO = sd(PropOc1), SEPO = std.error(PropOc1))
@@
 
-#Calculate the Enrichment
+###Moving forward I could calculate the mean PO for all samples and then get the enrichment from there or calculate the enrichment and then get mean enrichment for all samples.
+I'll do the former first:
+
+#---Mean, then enrichment
+#####
+#Get the mean meanPO across samples
+##Group including Region
+pOMeanStatsRgn<-pOMeanMeta %>% ungroup() %>% group_by(Condition,Culture,Strain,TimePoint, Distance, Relation, Region) %>% summarize(meanValue = mean(MeanPO), sdValue = sd(MeanPO), medianValue = median(MeanPO))
+##Group without region
+pOMeanStatsNoRgn<-pOMeanMeta %>% ungroup() %>% group_by(Condition,Culture,Strain,TimePoint, Distance, Relation) %>% summarize(meanValue = mean(MeanPO), sdValue = sd(MeanPO), medianValue = median(MeanPO))
+
+PlotMeanMeanPO<-function(df,relation){
+  ggplot()+
+    #geom_point(data = df %>% filter(Relation == relation),aes(y=meanValue,x = Distance,shape = Region,  color =Condition),size=2)+
+    #geom_pointrange(data = df %>% filter(Relation == relation),aes(y=meanValue,ymax=meanValue+sdValue,ymin=meanValue-sdValue,x = Distance,shape = Region,  color =Condition))+
+    geom_pointrange(data = df %>% filter(Relation == relation),aes(y=meanValue,ymax=meanValue+sdValue,ymin=meanValue-sdValue,x = Distance,color =Culture, shape = Region), position = position_dodge(width = .5))+
+    #geom_label(data = propOcEnrichment %>% filter(Relation == relation),aes(y=30, x = Sample, label = Value),size=2)+
+    labs(title =paste("Mean MeanPO", relation))+
+    facet_grid(Strain~TimePoint,scales = "free", space = "free")+
+    #scale_color_gradientn(colours = rainbow(5))+
+    #scale_shape_manual(values=c(0,1,2, 15,16,17))+
+    theme_cowplot()+
+    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),plot.title = element_text(hjust = 0.5))
+}
+PlotMeanMeanPO(pOMeanStatsRgn, "Pa->Sa")
+PlotMeanMeanPO(pOMeanStatsNoRgn, "Pa->Sa")
+PlotMeanMeanPO(pOMeanStatsRgn,"Sa->Pa")
+PlotMeanMeanPO(pOMeanStatsNoRgn,"Sa->Pa")
+PlotMeanMeanPO(pOMeanStatsRgn,"Sa->Sa")
+PlotMeanMeanPO(pOMeanStatsNoRgn,"Sa->Sa")
+PlotMeanMeanPO(pOMeanStatsRgn,"Pa->Pa")
+PlotMeanMeanPO(pOMeanStatsNoRgn,"Pa->Pa")
+
+pOMeanEnri<- pOMeanStatsRgn %>% group_by(Condition,Culture, Strain, TimePoint,Relation, Region)%>% 
+  mutate(Enrichment = max(meanValue)) %>%
+  mutate(EnrichmentCh = ifelse(Enrichment == meanValue, 1, 0 )) %>% filter(EnrichmentCh==1) %>% 
+  mutate(DoubledValues = sum(EnrichmentCh)) %>% ungroup()#find max
+
+#PlotMeanEnrichment<-function(relation){
+  ggplot()+
+    geom_point(data = pOMeanEnri,aes(y=Distance,x = Condition,color = Region),position = position_dodge(width = .5),size=2)+
+    #geom_label(data = propOcEnrichment %>% filter(Relation == relation),aes(y=30, x = Sample, label = Value),size=2)+
+    labs(title =paste("Enrichment from mean PO"))+
+    facet_grid(TimePoint~Relation,scales = "free", space = "free")+
+    #scale_color_gradientn(colours = rainbow(5))+
+    #scale_shape_manual(values=c(0,1,2, 15,16,17))+
+    theme_cowplot()+
+    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),plot.title = element_text(hjust = 0.5))+
+    panel_border() 
+#}
+
+#####
+#---Enrichment, then mean
+#####
+  #Calculate the Enrichment for all samples
 pOcEnriMean<- pOMeanMeta %>% group_by(SampleCode,Relation)%>% mutate(Enrichment = max(MeanPO)) %>%
@@
 PlotEnrichmentMean("Pa->Pa")
-
-#Get stats across samples
-pOMeanStatsRgn<-pOMeanMeta %>% ungroup() %>% group_by(Condition,Culture,Strain,TimePoint, Distance, Relation, Region) %>% summarize(meanValue = mean(MeanPO), sdValue = sd(MeanPO), medianValue = median(MeanPO))
-
+#####
 ```

### 2021-08-22 R/PropOc Data 3D.Rmd

@@
 ```
-# Importing whole data sets to identify distribution of data
+Importing whole data sets to identify distribution of data
+the chunk below is the only one aplicable to the SaPa chronic wounds project, all the other ones are just for reference
+
 ```{r read whole data sets}
-
 ReadPropOcFile<-function(file){
@@
 
+#Functions to make histograms of proportional occupancy values
+#####
 GetHistograms<-function(inputData){
@@
   histogram<- hist(df$PropOc1, breaks = seq.int(0,1,.01)) 
-  #histogram<- hist(df$PropOc, breaks = c(0,lseq(.001,1.03,100)))
-  #histogram<- hist(df$PropOc, breaks = c(0,lseq(.0001,1.03,100)))
+  #histogram<- hist(df$PropOc1, breaks = c(0,lseq(.001,1.03,100)))
+  #histogram<- hist(df$PropOc1, breaks = c(0,lseq(.0001,1.03,100)))
   output<-data.frame(histogram$mids,histogram$counts, histogram$density)
@@
 }
+#####
 #Run histograms for data
@@
 propOcHistogramData<-propOcHistogramData %>% group_by(Sample, Source, Distance) %>% mutate(count = sum(Frequency), NormDensity = Density/100) %>% ungroup()
+#Some Quality control by removing samples with low counts:
+#Quality control for low counts
+lowcounts<-propOcHistogramData %>% filter(count<500)
+lowcountssummary<-lowcounts %>% group_by(Sample, Source) %>% summarize(Lowcounts = n(), meanCounts = mean(count))
+
+lowsamples<-unique(lowcounts$Sample)
+
+ggplot()+
+  geom_point(data = lowcounts,aes(x=Sample,y=count, color = Distance, shape = Source))+
+  theme_cowplot()+
+  theme(plot.title = element_text(hjust = 0.5))
+
+lowCountSamples<-bind_rows(propOcHistogramData %>% filter(Sample == "mono_d1_02"),
+                           propOcHistogramData %>% filter(Sample == "phz_d4_08"),
+                           propOcHistogramData %>% filter(Sample == "wt_d4_11") %>% filter(Source == "finalRG"))
+propOcHistogramData <- anti_join(propOcHistogramData, lowCountSamples)
 
@@
   ggplot()+ 
-    geom_point(data = propOcHistogramData %>% filter(Sample ==sample),aes(x=Value,y=NormDensity, color = Distance),size=2)+
+    geom_point(data = propOcHistogramData %>% filter(Sample ==sample),aes(x=Value,y=NormDensity, color = Distance),size=2, shape = 1)+
     scale_y_log10( breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
     scale_color_gradientn(colours = rainbow(5))+
+    labs(title =sample)+
     facet_wrap(.~Source)+
@@
 }
-PlotAllPropOcData("wt_d1_05")#looks cool, so let's keep going...
+PlotAllPropOcData("wt_d4_05")#looks cool, so let's keep going...
 
 #now calculate the maximum frequency
+#####
 propOcMaxDensity<-propOcHistogramData %>% 
@@
 }
-PlotMaxDensities("wt_d1_05")
+PlotMaxDensities("pqsL_d4_03")
+#####
 #maximum distribution isn't super representative, so for the distribution, I calculated the value at which 50% of the population is found
@@
 #Median distribution
+#####
 getDeathCurve<-function(df){
@@
 PlotPercentiles(test50Percentile)#test case for sample wt_d1_05
+PlotPercentiles(propOcMidDensity %>% filter(Sample == "wt_d4_05", Source == "finalGR"))
 
@@
 
-ggplot()+#linear
-    geom_point(data = propOcMidDensityStats %>% filter(Relation== "Pa->Pa"),aes(y=meanValue, x = Distance,color=Condition, shape = "Mean"),size=2)+
-    geom_point(data = propOcMidDensityStats %>% filter(Relation== "Pa->Pa"),aes(y=medianValue, x = Distance,color=Condition,shape = "Median"),size=2)+
+ggplot()+
+    geom_point(data = propOcMidDensityStats %>% filter(Relation== "Pa->Sa"),aes(y=meanValue, x = Distance,color=Condition, shape = "Mean"),size=2)+
+    geom_point(data = propOcMidDensityStats %>% filter(Relation== "Pa->Sa"),aes(y=medianValue, x = Distance,color=Condition,shape = "Median"),size=2)+
     labs(title ="mean 50 percentile Density")+
-    #scale_y_log10(breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
-    #scale_x_log10(breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
     facet_grid(Relation ~ TimePoint)+
+    scale_color_brewer(palette = "Set1")+
+    theme_cowplot()+
+    theme(plot.title = element_text(hjust = 0.5))
+
+ggplot()+#Pa->Pa
+    geom_point(data = propOcMidDensityStats %>% filter(Relation== "Pa->Pa"),aes(y=meanValue, x = Distance,color=Culture, shape = "Mean"),size=2)+
+    geom_point(data = propOcMidDensityStats %>% filter(Relation== "Pa->Pa"),aes(y=medianValue, x = Distance,color=Culture,shape = "Median"),size=2)+
+    labs(title ="mean 50 percentile Density")+
+    facet_grid(Strain ~ TimePoint)+
+    scale_color_brewer(palette = "Set1")+
+    theme_cowplot()+
+    theme(plot.title = element_text(hjust = 0.5))
+
+#Calculate Enrichment
+propOcEnrichment<- propOcMidDensitylabeled %>% group_by(SampleCode,Relation)%>%
+  select(Value, Density, Distance, Relation,Sample, Strain,TimePoint, Condition, Culture, Strain,SampleCode) %>% mutate(Enrichment = max(Value)) %>%
+  mutate(EnrichmentCh = ifelse(Enrichment == Value, 1, 0 )) %>% filter(EnrichmentCh==1) %>% 
+  mutate(DoubledValues = sum(EnrichmentCh)) %>% ungroup()#find max
+propOcEnrichment$SampleCode<-as.factor(propOcEnrichment$SampleCode)#make samples a factor
+
+metaData.df <-read.csv('/Volumes/raw_data/Confocal/Carolyn/2020/Chronic wounds/images metadata.csv', header = TRUE)
+metaData.df$SampleCode<-as.factor(metaData.df$SampleCode)
+
+metaData.df<-metaData.df %>% select(SampleCode, mouse, Position, size, Region, Zdim, xyDim,xySize)
+pOEnrMeta<-metaData.df %>%  merge(propOcEnrichment, by = "SampleCode")
+
+#Plotting Enrichment per Relation
+PlotEnrichment<-function(relation){
+  ggplot()+
+    geom_point(data = pOEnrMeta %>% filter(Relation == relation),aes(y=Distance,x = Sample,shape = Region, color =Condition),size=2)+
+    geom_point(data = pOEnrMeta %>% filter(Relation == relation),aes(y=WmeanDist, x = Sample, shape = Region), color ="BLACK",size=2)+
+    labs(title =paste("50 percentile Enrichment", relation))+
+    facet_grid(.~TimePoint,scales = "free", space = "free")+
     #scale_color_gradientn(colours = rainbow(5))+
     #scale_shape_manual(values=c(0,1,2, 15,16,17))+
-    scale_color_brewer(palette = "Set1")+
-    theme_cowplot()+
-    theme(plot.title = element_text(hjust = 0.5))
-
-ggplot()+#linear
-    geom_point(data = propOcMidDensityStats %>% filter(Relation== "Sa->Sa"),aes(y=meanValue, x = Distance,color=Culture, shape = "Mean"),size=2)+
-    geom_point(data = propOcMidDensityStats %>% filter(Relation== "Sa->Sa"),aes(y=medianValue, x = Distance,color=Culture,shape = "Median"),size=2)+
-    labs(title ="mean 50 percentile Density")+
-    #scale_y_log10(breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
-    #scale_x_log10(breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
-    facet_grid(Strain ~ TimePoint)+
-    #scale_color_gradientn(colours = rainbow(5))+
-    #scale_shape_manual(values=c(0,1,2, 15,16,17))+
-    scale_color_brewer(palette = "Set1")+
-    theme_cowplot()+
-    theme(plot.title = element_text(hjust = 0.5))
+    ylim(0,30)+
+    theme_cowplot()+
+    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),plot.title = element_text(hjust = 0.5))+
+    panel_border() 
+}
+PlotEnrichment("Pa->Sa")
+PlotEnrichment("Sa->Pa")
+PlotEnrichment("Sa->Sa")
+PlotEnrichment("Pa->Pa")
+
+#It's unclear how to deal with the issue of multiple enrichment distances, but I think doing a weighted mean makes the most sense:
+pOEnrMetaClean<-pOEnrMeta %>% group_by(SampleCode,Condition,TimePoint, Region, Relation)%>%summarise(WmeanDist =weighted.mean(Distance, Density))
+#now calculate the Mean per condition:
+pOEnrMetaStatsRegion<-pOEnrMetaClean %>% group_by(Condition,TimePoint, Region, Relation) %>%
+  summarise(meanED = mean(WmeanDist),medianED = median(WmeanDist), SDED = sd(WmeanDist), SEED = std.error(WmeanDist),per25 = quantile(WmeanDist, .25), per75 = quantile(WmeanDist, .75))
+
+pOEnrMetaStats<-pOEnrMetaClean %>% group_by(Condition,TimePoint, Relation) %>%
+  summarise(meanED = mean(WmeanDist),medianED = median(WmeanDist), SDED = sd(WmeanDist), SEED = std.error(WmeanDist), per25 = quantile(WmeanDist, .25), per75 = quantile(WmeanDist, .75))
+
+#plot mean, weighted mean Enrichment distance from 50 percentile PO
+##First using region
+PlotMeanEnrichment50percent<-function(df1,df2){
+  ggplot()+
+    geom_pointrange(data = df1,aes(y=meanED,ymax=meanED+SEED,ymin=meanED-SEED, x = Condition,shape = Region),position = position_dodge(width = .5),size = .7)+
+  geom_point(data = df2,aes(y=WmeanDist,x = Condition, group = Region),position = position_dodge(width = .5),size=1, shape = 1)+
+    labs(y = expression(atop("Enrichment distance ("*mu*"m)",paste(italic("P. aeruginosa ") %->% italic("S. aureus"))))) +
+    #facet_grid(.~Relation,scales = "free", space = "free")+
+    theme_cowplot()+
+    #theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),plot.title = element_text(hjust = 0.5))+
+    theme(plot.title = element_text(hjust = 0.5),
+          strip.text = element_text(size = 12, face = "italic",margin = margin(.1,0,.1,0, "cm")),#this is for the facets
+          strip.background = element_rect(color="black", fill="white", size=.5, linetype="solid"))
+}
+PlotMeanEnrichment50percent(pOEnrMetaStatsRegion %>% filter(TimePoint == "Day 4", Relation == "Pa->Sa", TimePoint == "Day 4"),
+                            pOEnrMetaClean %>% filter(TimePoint == "Day 4", Relation == "Pa->Sa", TimePoint == "Day 4"))
+
+PlotMedianEnrichment50percent<-function(df1,df2){
+  ggplot()+
+    geom_pointrange(data = df1,aes(y=medianED,ymax=per25,ymin=per75, x = Condition,shape = Region),position = position_dodge(width = .5),size = .7)+
+  geom_jitter(data = df2,aes(y=WmeanDist,x = Condition),width = .5, height = 0,size=1, shape = 1)+
+    labs(y = expression(atop("Enrichment distance ("*mu*"m)",paste(italic("P. aeruginosa ") %->% italic("S. aureus"))))) +
+    #facet_grid(.~Relation,scales = "free", space = "free")+
+    theme_cowplot()+
+    #theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),plot.title = element_text(hjust = 0.5))+
+    theme(plot.title = element_text(hjust = 0.5),
+          strip.text = element_text(size = 12, face = "italic",margin = margin(.1,0,.1,0, "cm")),#this is for the facets
+          strip.background = element_rect(color="black", fill="white", size=.5, linetype="solid"))
+}
+PlotMedianEnrichment50percent(pOEnrMetaStatsRegion %>% filter(TimePoint == "Day 4", Relation == "Pa->Sa", TimePoint == "Day 4"),
+                            pOEnrMetaClean %>% filter(TimePoint == "Day 4", Relation == "Pa->Sa", TimePoint == "Day 4"))
+#then without region
+PlotMedianEnrichment50percentNRegion<-function(df1,df2){
+  ggplot()+
+    geom_pointrange(data = df1,aes(y=medianED,ymax=per25,ymin=per75, x = Condition),size = .7)+
+  geom_jitter(data = df2,aes(y=WmeanDist,x = Condition),width = .2, height = 0,size=1, shape = 1)+
+    labs(y = expression(atop("Enrichment distance ("*mu*"m)",paste(italic("P. aeruginosa ") %->% italic("S. aureus"))))) +
+    #facet_grid(.~Relation,scales = "free", space = "free")+
+    theme_cowplot()+
+    #theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),plot.title = element_text(hjust = 0.5))+
+    theme(plot.title = element_text(hjust = 0.5),
+          strip.text = element_text(size = 12, face = "italic",margin = margin(.1,0,.1,0, "cm")),#this is for the facets
+          strip.background = element_rect(color="black", fill="white", size=.5, linetype="solid"))
+}
+PlotMeanEnrichment50percentNRegion<-function(df1,df2){
+  ggplot()+
+    geom_pointrange(data = df1,aes(y=meanED,ymax=meanED+SEED,ymin=meanED-SEED, x = Condition),size = .7)+
+  geom_jitter(data = df2,aes(y=WmeanDist,x = Condition, group = Region),width = .2, height = 0,size=1, shape = 1)+
+    labs(y = expression(atop("Enrichment distance ("*mu*"m)",paste(italic("P. aeruginosa ") %->% italic("S. aureus"))))) +
+    #facet_grid(.~Relation,scales = "free", space = "free")+
+    theme_cowplot()+
+    #theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),plot.title = element_text(hjust = 0.5))+
+    theme(plot.title = element_text(hjust = 0.5),
+          strip.text = element_text(size = 12, face = "italic",margin = margin(.1,0,.1,0, "cm")),#this is for the facets
+          strip.background = element_rect(color="black", fill="white", size=.5, linetype="solid"))
+}
+PlotMeanEnrichment50percentNRegion(pOEnrMetaStats %>% filter(TimePoint == "Day 4", Relation == "Pa->Sa", TimePoint == "Day 4"),
+                            pOEnrMetaClean %>% filter(TimePoint == "Day 4", Relation == "Pa->Sa", TimePoint == "Day 4"))
+PlotMedianEnrichment50percentNRegion(pOEnrMetaStats %>% filter(TimePoint == "Day 4", Relation == "Pa->Sa", TimePoint == "Day 4"),
+                            pOEnrMetaClean %>% filter(TimePoint == "Day 4", Relation == "Pa->Sa", TimePoint == "Day 4"))
+
+#original figure 
+ggplot()+
+    geom_pointrange(data = pOEnrMetaStats,aes(y=meanED,ymax=meanED+SEED,ymin=meanED-SEED, x = Condition),position = position_dodge(width = .5))+
+  geom_jitter(data = pOEnrMetaClean,aes(y=WmeanDist,x = Condition),size=1, shape = 1, height = 0, width = .2)+
+    labs(y = expression("Enrichment distance ("*mu*"m)")) +
+    facet_grid(TimePoint~Relation,scales = "free", space = "free")+
+    theme_cowplot()+
+    theme(plot.title = element_text(hjust = 0.5),
+          strip.text = element_text(size = 12, margin = margin(.1,0,.1,0, "cm")),#this is for the facets
+          strip.background = element_rect(color="black", fill="white", size=.5, linetype="solid"))+
+    panel_border()
+
+ggplot()+
+    geom_pointrange(data = pOEnrMetaStatsRegion,aes(y=meanED,ymax=meanED+SEED,ymin=meanED-SEED, shape = Region,x = Condition),
+                    position = position_dodge(width = .5))+
+    geom_point(data = pOEnrMetaClean,aes(y=WmeanDist,x = Condition, group = Region),position = position_dodge(width = .5),size=1, shape = 1)+
+    labs(y = expression("Enrichment distance ("*mu*"m)")) +
+    facet_grid(TimePoint~Relation,scales = "free", space = "free")+
+    theme_cowplot()+
+    theme(plot.title = element_text(hjust = 0.5),
+          strip.text = element_text(size = 12,margin = margin(.1,0,.1,0, "cm")),#this is for the facets
+          strip.background = element_rect(color="black", fill="white", size=.5, linetype="solid"))+
+    panel_border()
 
@@
 PlotEnrichment <- function(df) {
-ggplot()+#first run
+ggplot()+
     geom_point(data = df,aes(y=Distance, x = Sample, color = Enrichment, shape = Sample),size=2)+
     labs(title ="50 percentile Enrichment")+
-    #scale_y_log10(breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
-    #scale_x_log10(breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
     facet_wrap( ~ Source, ncol = 2)+

### 2021-08-31 R/AggregateCounts.Rmd
Changed bin sizes, added jitter_dodge to plots, and made more functions for z-slices

@@
 library(EBImage) #for rtiff
+
 ```
@@
 aggregateList$Condition <- factor(aggregateList$Condition, levels = c("mono", "pawt","papqsL", "paphz", "wt", "pqsL", "phz"),
-                                  labels = c('Sa mono', 'Pa wt mono','pqsL mono','phz mono','wt co', 'pqsL co', 'phz co'))
+                                  labels = c('Sa mono', 'wt mono','pqsL mono','phz mono','wt co', 'pqsL co', 'phz co'))
 aggregateList$TimePoint <- factor(aggregateList$TimePoint, levels = c("d1", "d4"),labels = c('Day 1','Day 4'))
 
-aggregateList<-aggregateList %>% mutate(Culture = recode(Condition, 'Sa mono' = "mono", 'Pa wt mono' = "mono",'pqsL mono'= "mono",'phz mono'= "mono",'wt co'= "co", 'pqsL co'= "co", 'phz co'= "co"))
-aggregateList<-aggregateList%>% mutate(Strain = recode(Condition, 'Sa mono' = "Sa", 'Pa wt mono' = "wt",'pqsL mono'= "pqsL",'phz mono'= "phz",'wt co'= "wt", 'pqsL co'= "pqsL", 'phz co'= "phz"))
+aggregateList<-aggregateList %>% mutate(Culture = recode(Condition, 'Sa mono' = "mono", 'wt mono' = "mono",'pqsL mono'= "mono",'phz mono'= "mono",'wt co'= "co", 'pqsL co'= "co", 'phz co'= "co"))
+aggregateList<-aggregateList%>% mutate(Strain = recode(Condition, 'Sa mono' = "Sa", 'wt mono' = "wt",'pqsL mono'= "pqsL",'phz mono'= "phz",'wt co'= "wt", 'pqsL co'= "pqsL", 'phz co'= "phz"))
+aggregateList<-aggregateList%>% mutate(SaStrain = recode(Condition, 'Sa mono' = "Sa mono", 'wt mono' = "wt",'pqsL mono'= "pqsL",'phz mono'= "phz",'wt co'= "co-wt", 'pqsL co'= "co-pqsL", 'phz co'= "co-phz"))
+
 #Adding the metadata
@@
 #Get aggregate summary per sample
-aggregateListSummaryReplicate<-aggregateList%>% group_by(SampleCode, Species, Strain, Culture,TimePoint, Condition, Replicate,Region) %>% 
+aggregateListSummaryReplicate<-aggregateList%>% group_by(SampleCode, Species,SaStrain, Strain, Culture,TimePoint, Condition, Replicate,Region) %>% 
   summarise(Aggs = n(), biomass = sum(Size), meanAggSize = mean(Size), seAggSize = std.error(Size), maxSize = max(Size), minSize = min(Size)) %>%
   ungroup() %>% mutate(RatioMaxTotal = maxSize/biomass)
+
+#Get aggregate Summary per condition
+aggregateListSummaryCondNoRegion<-aggregateListSummaryReplicate %>% group_by(Species,SaStrain, Strain, Culture,TimePoint, Condition) %>% 
+  summarise(meanAggs= mean(Aggs), meanBiomassLog = mean(log10(biomass)), SEBiomassLog = std.error((log10(biomass))), meanAggSize = mean(meanAggSize), seAggSize = std.error(meanAggSize))%>%  mutate(meanBiomass =  meanBiomassLog^10, SEBiomass = SEBiomassLog^10)
+
+#Get aggregate Summary per condition and region
+aggregateListSummaryCondition<-aggregateListSummaryReplicate %>% group_by(Species, SaStrain,Strain, Culture,TimePoint, Condition, Region) %>% 
+  summarise(meanAggs= mean(Aggs), meanBiomassLog = mean(log10(biomass)), SEBiomassLog = std.error((log10(biomass))), meanAggSize = mean(meanAggSize), seAggSize = std.error(meanAggSize))%>%  mutate(meanBiomass =  meanBiomassLog^10, SEBiomass = SEBiomassLog^10)
 
@@
 #Plot only biomass per Sample
+#####
 PlotBiomasPerSample<-function(df){
@@
 
+#plotting all conditions
 PlotBiomasPerSample(aggregateListSummaryReplicate)
@@
 PlotBiomasPerSample(aggregateListSummaryReplicate %>% filter(Condition == "Sa mono" |Condition == "wt co"|Condition == "Pa wt mono"))
+#####
 
-#Get aggregate Summary per condition
-aggregateListSummaryCondition<-aggregateListSummaryReplicate %>% group_by(Species, Strain, Culture,TimePoint, Condition, Region) %>% 
-  summarise(meanAggs= mean(Aggs), meanBiomassLog = mean(log10(biomass)), SEBiomassLog = std.error((log10(biomass))), meanAggSize = mean(meanAggSize), seAggSize = std.error(meanAggSize))%>%  mutate(meanBiomass =  meanBiomassLog^10, SEBiomass = SEBiomassLog^10)
-#plot agg summary per condition
+#plot agg summary per condition#this shows both contition and replicate
 #####
@@
 }
+
 PlotBiomassPerCondition(aggregateListSummaryCondition,"meanBiomass", "SEBiomass")
-PlotBiomassPerCondition(aggregateListSummary,"biomass")
 #####
-#combining all 
-PlotBiomasPerSampleAndConditionWT<-function(df1,df2){
+
+#Plotting mean and all samples
+PlotBiomasPerSampleAndConditionWT<-function(df1,df2, df3){
 ggplot()+ 
-    geom_point(data = df1, aes(x = Culture, y= meanBiomassLog,color = Species,shape = Region), 
+    geom_point(data = df1 %>% filter(TimePoint=="Day 4"), aes(x = Culture, y= meanBiomassLog,shape = Region), 
              position = position_jitterdodge(jitter.height = 0, jitter.width = .3,dodge.width = 0.75), size = 4)+
-  geom_point(data = df2, aes(x = Culture, y= log10(biomass), color= Species, shape = Region),size = 1, 
+  geom_point(data = df2%>% filter(TimePoint=="Day 4"), aes(x = Culture, y= log10(biomass), shape = Region),size = 1, 
              position = position_jitterdodge(jitter.height = 0, jitter.width = .3,dodge.width = 0.75))+
+    geom_point(data = df3 %>% filter(TimePoint=="Day 4"), aes(x = Culture, y= meanBiomassLog),shape = 3,size = 4)+
     #scale_y_log10( breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)), limits = c(1, 100000000))+
-      facet_grid(.~TimePoint, scales = "free", space = "free") +
+      facet_grid(.~Species, scales = "free", space = "free") +
   ggtitle('Biomass per sample')+
+  labs(x = "",y = bquote(paste("log10 Volume (", mu*"m"^3*")")))+
+  scale_color_brewer(palette = "Set1")+
+  scale_shape_manual(values=c(16, 1))+
+  ylim(0,8)+
+    theme_cowplot()+
+  panel_border() +
+  theme(plot.title = element_text(hjust = 0.5), 
+        strip.text = element_text(size = 11, face = "italic",margin = margin(.1,0,.1,0, "cm")),#this is for the facet text
+        strip.background = element_rect(color="black", fill="white", size=1, linetype="solid"))#facet background
+}
+
+#WT only
+PlotBiomasPerSampleAndConditionWT(aggregateListSummaryCondition%>% filter(Condition == "Sa mono" |Condition == "wt co"|Condition == "Pa wt mono"),
+                                aggregateListSummaryReplicate %>% filter(Condition == "Sa mono" |Condition == "wt co"|Condition == "Pa wt mono"), 
+                                aggregateListSummaryCondNoRegion%>% filter(Condition == "Sa mono" |Condition == "wt co"|Condition == "Pa wt mono"))
+
+PlotBiomasPerSampleAndCondition<-function(df1,df2, df3, species){
+ggplot()+ 
+    geom_point(data = df1 %>% filter(TimePoint=="Day 4") %>% filter(Species==species), aes(x = SaStrain, y= meanBiomassLog,shape = Region), 
+             position = position_jitterdodge(jitter.height = 0, jitter.width = .3,dodge.width = 0.75), size = 4)+
+  geom_point(data = df2%>% filter(TimePoint=="Day 4") %>% filter(Species==species), aes(x = SaStrain, y= log10(biomass), shape = Region),size = 1, 
+             position = position_jitterdodge(jitter.height = 0, jitter.width = .3,dodge.width = 0.75))+ 
+  geom_point(data = df3 %>% filter(TimePoint=="Day 4") %>% filter(Species==species), aes(x = SaStrain, y= meanBiomassLog), shape = 3, size = 4)+
+    #scale_y_log10( breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)), limits = c(1, 100000000))+
+      facet_grid(.~Species, scales = "free", space = "free") +
+  ggtitle('Total Biomass')+
   labs(x = "",y = bquote(paste("Volume (log10", mu*"m"^3*")")))+
@@
 }
-PlotBiomasPerSampleAndConditionWT(aggregateListSummaryCondition%>% filter(Condition == "Sa mono" |Condition == "wt co"|Condition == "Pa wt mono"),
-                                aggregateListSummaryReplicate %>% filter(Condition == "Sa mono" |Condition == "wt co"|Condition == "Pa wt mono"))
-PlotBiomasPerSampleAndCondition<-function(df1,df2){
+PlotBiomasPerSampleAndCondition(aggregateListSummaryCondition,
+                                aggregateListSummaryReplicate,
+                                aggregateListSummaryCondNoRegion, "S. aureus")
+
+PlotMeanAggsPerSampleAndConditionWT<-function(df1,df2, df3){
 ggplot()+ 
-    geom_point(data = df1, aes(x = Culture, y= meanBiomassLog,color = Strain,shape = Region), 
+    geom_point(data = df1 %>% filter(TimePoint=="Day 4"), aes(x = Culture, y= meanAggs,shape = Region), 
              position = position_jitterdodge(jitter.height = 0, jitter.width = .3,dodge.width = 0.75), size = 4)+
-  geom_point(data = df2, aes(x = Culture, y= log10(biomass), color= Strain, shape = Region),size = 1, 
+  geom_point(data = df2%>% filter(TimePoint=="Day 4"), aes(x = Culture, y= Aggs, shape = Region),size = 1, 
              position = position_jitterdodge(jitter.height = 0, jitter.width = .3,dodge.width = 0.75))+
-    #scale_y_log10( breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)), limits = c(1, 100000000))+
-      facet_grid(Species~TimePoint, scales = "free", space = "free") +
-  ggtitle('Biomass per sample')+
-  labs(x = "",y = bquote(paste("Volume (log10", mu*"m"^3*")")))+
+    geom_point(data = df3 %>% filter(TimePoint=="Day 4"), aes(x = Culture, y= meanAggs),shape = 3,size = 4)+
+    scale_y_log10( breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)), limits = c(10, 100000))+
+      facet_grid(.~Species, scales = "free", space = "free") +
+  ggtitle('Number of groups of bacteria')+
+  labs(x = "",y = "")+
   scale_color_brewer(palette = "Set1")+
-  scale_shape_manual(values=c(4,16, 1))+
-  ylim(0,8)+
+  scale_shape_manual(values=c(16, 1))+
+  #ylim(0,8)+
     theme_cowplot()+
@@
 }
-PlotBiomasPerSampleAndCondition(aggregateListSummaryCondition,aggregateListSummaryReplicate)
+PlotMeanAggsPerSampleAndConditionWT(aggregateListSummaryCondition%>% filter(Condition == "Sa mono" |Condition == "wt co"|Condition == "Pa wt mono"),
+                                aggregateListSummaryReplicate %>% filter(Condition == "Sa mono" |Condition == "wt co"|Condition == "Pa wt mono"), 
+                                aggregateListSummaryCondNoRegion%>% filter(Condition == "Sa mono" |Condition == "wt co"|Condition == "Pa wt mono"))
 
+PlotMeanAggsPerSampleAndCondition<-function(df1,df2, df3,species){
+ggplot()+ 
+    geom_point(data = df1 %>% filter(TimePoint=="Day 4") %>% filter(Species == species), aes(x = SaStrain, y= meanAggs,shape = Region), 
+             position = position_jitterdodge(jitter.height = 0, jitter.width = .3,dodge.width = 0.75), size = 4)+
+  geom_point(data = df2%>% filter(TimePoint=="Day 4")%>% filter(Species == species), aes(x = SaStrain, y= Aggs, shape = Region),size = 1, 
+             position = position_jitterdodge(jitter.height = 0, jitter.width = .3,dodge.width = 0.75))+
+    geom_point(data = df3 %>% filter(TimePoint=="Day 4")%>% filter(Species == species), aes(x = SaStrain, y= meanAggs),shape = 3,size = 4)+
+    scale_y_log10( breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)), limits = c(10, 100000))+
+      #facet_grid(, scales = "free", space = "free") +
+  ggtitle('Number of groups of bacteria')+
+  labs(x = "",y = "")+
+  scale_color_brewer(palette = "Set1")+
+  scale_shape_manual(values=c(16, 1))+
+  #ylim(0,8)+
+    theme_cowplot()+
+  panel_border() +
+  theme(plot.title = element_text(hjust = 0.5), 
+        strip.text = element_text(size = 11, face = "italic",margin = margin(.1,0,.1,0, "cm")),#this is for the facet text
+        strip.background = element_rect(color="black", fill="white", size=1, linetype="solid"))#facet background
+}
+PlotMeanAggsPerSampleAndCondition(aggregateListSummaryCondition,
+                                aggregateListSummaryReplicate, 
+                                aggregateListSummaryCondNoRegion, "S. aureus")
+
+PlotMeanAggsPerSampleAndConditionPa<-function(df1,df2, df3,species){
+ggplot()+ 
+    geom_point(data = df1 %>% filter(TimePoint=="Day 4") %>% filter(Species == species), aes(x = Strain, y= meanAggs,shape = Region, color= Region), 
+             position = position_jitterdodge(jitter.height = 0, jitter.width = .3,dodge.width = 0.75),
+             fill = "black", size = 4)+
+  geom_point(data = df2%>% filter(TimePoint=="Day 4")%>% filter(Species == species), aes(x = Strain, y= Aggs, shape = Region, color = Region),size = 1, fill = "black", 
+             position = position_jitterdodge(jitter.height = 0, jitter.width = .3,dodge.width = 0.75))+
+    geom_point(data = df3 %>% filter(TimePoint=="Day 4")%>% filter(Species == species), aes(x = Strain, y= meanAggs),shape = 3,size = 4)+
+    scale_y_log10( breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)), limits = c(10, 100000))+
+      facet_grid(.~Culture, scales = "free", space = "free") +
+  ggtitle('Number of groups of bacteria')+
+  labs(x = "",y = "")+
+  #scale_color_brewer(palette = "Set1")+
+  scale_color_manual(values = c("white", "black"))+
+  scale_shape_manual(values=c(21, 1))+
+  #ylim(0,8)+
+    theme_cowplot()+
+  panel_border() +
+  theme(plot.title = element_text(hjust = 0.5), 
+        strip.text = element_text(size = 11, face = "italic",margin = margin(.1,0,.1,0, "cm")),#this is for the facet text
+        strip.background = element_rect(color="black", fill="white", size=1, linetype="solid"))#facet background
+}
+
+```
+```{r figures 1A,1B and 2A, 2B}
+#Biomass wt
+PlotBiomasPerSampleAndConditionWT(aggregateListSummaryCondition%>% filter(Condition == "Sa mono" |Condition == "wt co"|Condition == "Pa wt mono"),
+                                aggregateListSummaryReplicate %>% filter(Condition == "Sa mono" |Condition == "wt co"|Condition == "Pa wt mono"), 
+                                aggregateListSummaryCondNoRegion%>% filter(Condition == "Sa mono" |Condition == "wt co"|Condition == "Pa wt mono"))
+#Biomass Sa and mutants
+PlotBiomasPerSampleAndCondition(aggregateListSummaryCondition,
+                                aggregateListSummaryReplicate,
+                                aggregateListSummaryCondNoRegion, "S. aureus")
+
+PlotBiomasPerSampleAndCondition(aggregateListSummaryCondition,
+                                aggregateListSummaryReplicate,
+                                aggregateListSummaryCondNoRegion, "P. aeruginosa")
+
+#Number of aggregates wt
+PlotMeanAggsPerSampleAndConditionWT(aggregateListSummaryCondition%>% filter(Condition == "Sa mono" |Condition == "wt co"|Condition == "Pa wt mono"),
+                                aggregateListSummaryReplicate %>% filter(Condition == "Sa mono" |Condition == "wt co"|Condition == "Pa wt mono"), 
+                                aggregateListSummaryCondNoRegion%>% filter(Condition == "Sa mono" |Condition == "wt co"|Condition == "Pa wt mono"))
+
+#Number of aggregates Sa and mutants
+PlotMeanAggsPerSampleAndCondition(aggregateListSummaryCondition,
+                                aggregateListSummaryReplicate, 
+                                aggregateListSummaryCondNoRegion, "S. aureus")
+
+PlotMeanAggsPerSampleAndConditionPa(aggregateListSummaryCondition,
+                                aggregateListSummaryReplicate, 
+                                aggregateListSummaryCondNoRegion, "P. aeruginosa")
 ```
@@
 #First per replicate:
-HistReplicate<-aggregateList %>% mutate(LogBin = case_when(Size <= 5 ~ 5,
-                        Size<= 10 ~ 10,
-                        Size<= 100    ~ 100,
-                        Size<= 1000   ~ 1000,
-                        Size<= 10000  ~ 10000,
-                        Size<= 100000 ~ 100000,
-                        Size > 100000 ~ 1000000)) %>% group_by(Species,Culture,Strain, Condition,TimePoint, Replicate)%>% 
+#####
+HistReplicate<-aggregateList %>% mutate(LogBin = case_when(Size <= 5 ~ "(.5, 5]",
+                        Size<= 10 ~ "(5, 10]",
+                        Size<= 100    ~ "(10, 100]",
+                        Size<= 1000   ~ "(100, 1000]",
+                        Size> 1000  ~ paste0("(1000, ",bquote("\U221E"), ")"))) %>% 
+  group_by(SampleCode)%>% 
   mutate(TotalBiomass = sum(Size), TotalFrequency = n()) %>% ungroup() %>% 
-  group_by(Species,Culture,Strain, Condition,TimePoint, Replicate, LogBin)%>%
+  group_by(SampleCode, LogBin)%>%
   mutate(BinBiomass = sum(Size), BinFrequency = n()) %>% ungroup() %>%
@@
 
+HistReplicate$LogBin <- factor(HistReplicate$LogBin, levels = c("(.5, 5]", "(5, 10]","(10, 100]", "(100, 1000]", paste0("(1000, ",bquote("\U221E"), ")")),labels = c(levels = c("(.5, 5]", "(5, 10]","(10, 100]", "(100, 1000]", paste0("(1000, ",bquote("\U221E"), ")"))))
+
 #This is weird, but I want to have the histogram above with all the data, and the one below with only the bins
 HistReplicateSummary<-HistReplicate %>% 
-  group_by(Species,Culture,Strain, Condition,TimePoint, Replicate, LogBin,NormalizedFrequency,NormalizedBiomass) %>% summarize() %>%
-  unique()%>%ungroup() %>%  group_by(Species,Culture,Condition,TimePoint, Replicate) %>% 
+  group_by(Species,Culture,SaStrain, Strain,Region,Condition,TimePoint, Replicate,SampleCode, LogBin,NormalizedFrequency,NormalizedBiomass) %>% summarize() %>%
+  unique()%>%ungroup() %>%  group_by(Species,Strain, SaStrain,Culture,Condition,TimePoint, Replicate, SampleCode) %>% 
   mutate(checkSumFreq =sum(NormalizedFrequency), checkSumBiomass = sum(NormalizedBiomass))
+#####
+#Now per condition. The difference is int the "group_by" part
+#####
+HistCondition<-aggregateList %>% mutate(LogBin = case_when(Size <= 5 ~ "(.5, 5]",
+                        Size<= 10 ~ "(5, 10]",
+                        Size<= 100    ~ "(10, 100]",
+                        Size<= 1000   ~ "(100, 1000]",
+                        Size> 1000  ~ paste0("(1000, ",bquote("\U221E"), ")"))) %>% 
+  group_by(Species,Condition,TimePoint)%>% 
+  mutate(TotalBiomass = sum(Size), TotalFrequency = n()) %>% ungroup() %>%
+  group_by(Species, Condition,TimePoint,LogBin)%>%
+  mutate(BinBiomass = sum(Size), BinFrequency = n()) %>% ungroup() %>%
+  mutate(NormalizedFrequency = BinFrequency/TotalFrequency*100, NormalizedBiomass = BinBiomass/TotalBiomass*100)
+HistCondition$LogBin <- factor(HistCondition$LogBin, levels = c("(.5, 5]", "(5, 10]","(10, 100]", "(100, 1000]", paste0("(1000, ",bquote("\U221E"), ")")),labels = c(levels = c("(.5, 5]", "(5, 10]","(10, 100]", "(100, 1000]", paste0("(1000, ",bquote("\U221E"), ")"))))
 
-#Now per condition. The difference is int the "group_by" part
-HistCondition<-aggregateList %>% mutate(LogBin = case_when(Size <= 5 ~ 5,
-                        Size<= 10 ~ 10,
-                        Size<= 100    ~ 100,
-                        Size<= 1000   ~ 1000,
-                        Size<= 10000  ~ 10000,
-                        Size<= 100000 ~ 100000,
-                        Size > 100000 ~ 1000000)) %>% group_by(Species,Culture,Strain, Condition,TimePoint)%>% 
+#Summary data frame
+HistConditionSummary<-HistCondition %>%
+  group_by(Species,Culture,SaStrain, Strain, Condition,TimePoint,LogBin,NormalizedFrequency,NormalizedBiomass) %>% 
+  summarize() %>% unique()%>%ungroup() %>%
+  group_by(Species,Culture,Strain,SaStrain, Condition,TimePoint) %>% 
+  mutate(checkSumFreq =sum(NormalizedFrequency), checkSumBiomass = sum(NormalizedBiomass))
+#####
+
+#Now per condition including region. The difference is int the "group_by" part
+#####
+HistConditionRegin<-aggregateList %>% mutate(LogBin = case_when(Size <= 5 ~ "(.5, 5]",
+                        Size<= 10 ~ "(5, 10]",
+                        Size<= 100    ~ "(10, 100]",
+                        Size<= 1000   ~ "(100, 1000]",
+                        Size> 1000  ~ paste0("(1000, ",bquote("\U221E"), ")"))) %>% 
+  group_by(Species,Condition,TimePoint, Region)%>% 
   mutate(TotalBiomass = sum(Size), TotalFrequency = n()) %>% ungroup() %>%
-  group_by(Species,Culture,Strain, Condition,TimePoint,LogBin)%>%
+  group_by(Species, Condition,TimePoint, Region,LogBin)%>%
   mutate(BinBiomass = sum(Size), BinFrequency = n()) %>% ungroup() %>%
@@
 
+HistConditionRegin$LogBin <- factor(HistConditionRegin$LogBin, levels = c("(.5, 5]", "(5, 10]","(10, 100]", "(100, 1000]", paste0("(1000, ",bquote("\U221E"), ")")),labels = c(levels = c("(.5, 5]", "(5, 10]","(10, 100]", "(100, 1000]", paste0("(1000, ",bquote("\U221E"), ")"))))
+
 #Summary data frame
-HistConditionSummary<-HistCondition %>%
-  group_by(Species,Culture,Strain, Condition,TimePoint,LogBin,NormalizedFrequency,NormalizedBiomass) %>% summarize() %>% 
-  unique()%>%ungroup() %>%  group_by(Species,Culture,Condition,TimePoint) %>% 
+HistCondRegionSum<-HistConditionRegin %>%
+  group_by(Species,Culture,SaStrain, Strain, Condition,TimePoint, Region,LogBin,NormalizedFrequency,NormalizedBiomass) %>% 
+  summarize() %>% unique()%>%ungroup() %>%
+  group_by(Species,Culture,Strain,SaStrain, Condition,TimePoint, Region) %>% 
   mutate(checkSumFreq =sum(NormalizedFrequency), checkSumBiomass = sum(NormalizedBiomass))
+#####
 
@@
 #this isn't useful as the normalized Frequency changes with replicate, so it's better to pool all samples together
-PlotHistSum<-function(rep.df,cond.df, y_var, title){
+PlotHistSum<-function(rep.df,cond.df,region.df, y_var, title, species, colorStrain){
 ggplot()+
-    geom_jitter(data = rep.df,aes(x=as.factor(LogBin),y=.data[[y_var]],  color =Condition),size=3, height = 0, width = .2, shape = 1)+
-    geom_point(data = cond.df,aes(x=as.factor(LogBin),y=.data[[y_var]],  color =Condition,group = Condition),size=4, shape = 16, position = position_dodge(width = .5) )+
-    scale_y_log10(breaks = c(100, 10, 1, .1, .01), labels = c(100, 10, 1, .1, .01))+
-    facet_grid(Species~TimePoint)+
+    geom_point(data = rep.df %>% filter(TimePoint=="Day 4")%>% filter(Species == species),
+                aes(x=as.factor(LogBin),y=.data[[y_var]], color =.data[[colorStrain]], shape = Region),
+               position = position_jitterdodge(jitter.height = 0, jitter.width = .3,dodge.width = 0.75),size=1)+
+    geom_point(data = region.df%>% filter(TimePoint=="Day 4")%>% filter(Species == species),
+               aes(x=as.factor(LogBin),y=.data[[y_var]], color =.data[[colorStrain]],shape = Region),
+               size=3, position = position_dodge(width = .75) )+
+    geom_point(data = cond.df%>% filter(TimePoint=="Day 4") %>% filter(Species == species),
+               aes(x=as.factor(LogBin),y=.data[[y_var]],  color =.data[[colorStrain]]),size=4, shape = 3,position = position_dodge(width = .75) )+
+    #scale_y_log10(breaks = c(100, 10, 1, .1, .01), labels = c(100, 10, 1, .1, .01))+
+    facet_grid(.~Species)+
+    scale_shape_manual(values=c(16, 1))+
     ggtitle(title)+
@@
 }
+PlotHistSum(HistReplicateSummary,HistConditionSummary,HistCondRegionSum,"NormalizedFrequency", "Normalized Frequency all sizes", "S. aureus")
 
-PlotHistSum(HistReplicateSummary,HistConditionSummary,"NormalizedFrequency", "Normalized Frequency all sizes")
+####---Figure 1C
+PlotHistSum(HistReplicateSummary %>% filter(SaStrain %in% c("Sa mono", "co-wt")),
+            HistConditionSummary%>% filter(SaStrain %in% c("Sa mono", "co-wt")),
+            HistCondRegionSum%>% filter(SaStrain %in% c("Sa mono", "co-wt")),
+            "NormalizedFrequency", "Normalized Frequency all sizes", "S. aureus", "Culture")
 
-PlotHistSum(HistReplicateSummary,HistConditionSummary,"NormalizedBiomass", "Normalized Biomass all sizes")
+PlotHistSum(HistReplicateSummary %>% filter(Strain %in% c("wt")),
+            HistConditionSummary%>% filter(Strain %in% c("wt")),
+            HistCondRegionSum%>% filter(Strain %in% c("wt")),
+            "NormalizedFrequency", "Normalized Frequency all sizes", "P. aeruginosa", "Culture")
+
+PlotHistSum(HistReplicateSummary,
+            HistConditionSummary,
+            HistCondRegionSum,
+            "NormalizedFrequency", "Normalized Frequency all sizes", "S. aureus", "SaStrain")
+
+PlotHistSum(HistReplicateSummary,HistCondRegionSum,HistConditionSummary,"NormalizedBiomass", "Normalized Biomass all sizes")
 
@@
 #####
-#now only aggregates 5 microns or larger
+#Now only aggregates 5 microns or larger
+
+##Separating the replicates
 #####
-#Separating the replicates
 aggsHistRep<-aggregateList %>% mutate(LogBin = case_when(Size <= 5 ~ 5,
@@
                         Size<= 100000 ~ 100000,
-                        Size > 100000 ~ 1000000)) %>% filter(!LogBin == 5) %>% group_by(Species,Culture,Strain,Condition,TimePoint, Replicate)%>% 
-  mutate(TotalBiomass = sum(Size), TotalFrequency = n()) %>% ungroup() %>% group_by(Species,Culture,Strain,Condition,TimePoint, Replicate, LogBin)%>%
+                        Size > 100000 ~ 1000000)) %>% filter(!LogBin == 5) %>%
+  group_by(Species,Culture,Strain,Condition,TimePoint, Replicate)%>% 
+  mutate(TotalBiomass = sum(Size), TotalFrequency = n()) %>% ungroup() %>% 
+  group_by(Species,Culture,Strain,Condition,TimePoint, Replicate, LogBin)%>%
   mutate(BinBiomass = sum(Size), BinFrequency = n()) %>% ungroup() %>%
@@
 aggsHistRepSum<-aggsHistRep %>% group_by(Species,Culture,Strain,Condition,TimePoint, Replicate, LogBin,NormalizedFrequency,NormalizedBiomass) %>% summarize() %>%  unique()%>%ungroup() %>%  group_by(Species,Culture,Strain,Condition,TimePoint, Replicate) %>% mutate(checkSumFreq =sum(NormalizedFrequency), checkSumBiomass = sum(NormalizedBiomass))
-
-#Pooling replicates together
+#####
+##Pooling replicates together
+#####
 aggsHistCond<-aggregateList %>% mutate(LogBin = case_when(Size <= 5 ~ 5,
@@
                         Size<= 100000 ~ 100000,
-                        Size > 100000 ~ 1000000)) %>% filter(!LogBin == 5) %>% group_by(Species,Culture,Strain,Condition,TimePoint)%>% 
-  mutate(TotalBiomass=sum(Size),TotalFrequency=n()) %>% ungroup() %>% group_by(Species,Culture,Strain,Condition,TimePoint, LogBin)%>%
+                        Size > 100000 ~ 1000000)) %>% filter(!LogBin == 5) %>%
+  group_by(Species,Culture,Strain,Condition,TimePoint)%>% 
+  mutate(TotalBiomass=sum(Size),TotalFrequency=n()) %>% ungroup() %>% 
+  group_by(Species,Culture,Strain,Condition,TimePoint, LogBin)%>%
   mutate(BinBiomass = sum(Size), BinFrequency = n()) %>% ungroup() %>%
@@
 ##Summary df
-aggsHistCondSum<-aggsHistCond %>% group_by(Species,Culture,Strain,Condition,TimePoint, Replicate, LogBin,NormalizedFrequency,NormalizedBiomass) %>% summarize() %>%  unique()%>%ungroup() %>%  group_by(Species,Culture,Strain,Condition,TimePoint, Replicate) %>% mutate(checkSumFreq =sum(NormalizedFrequency), checkSumBiomass = sum(NormalizedBiomass))%>%ungroup()
+aggsHistCondSum<-aggsHistCond %>% 
+  group_by(Species,Culture,Strain,Condition,TimePoint, LogBin,NormalizedFrequency,NormalizedBiomass) %>%
+  summarize() %>%  unique()%>%ungroup() %>%
+  group_by(Species,Culture,Strain,Condition,TimePoint) %>%
+  mutate(checkSumFreq =sum(NormalizedFrequency), checkSumBiomass = sum(NormalizedBiomass))%>%ungroup()
 
@@
 #####
+
 #Planktonic vs aggregates
@@
 ##Normalize using replicates
-HistReplicate<-HistReplicate %>%  mutate(Aggregation = case_when(LogBin == 5 ~"Planktonic",LogBin>5 ~ "Aggregate")) %>%
-  group_by(Species,Culture,Condition,Strain,TimePoint, Replicate, Aggregation)%>% 
+HistReplicate<-HistReplicate %>%  mutate(Aggregation = if_else(LogBin == "(.5, 5]" ,"Planktonic", "Aggregate")) %>%
+  group_by(Species,SampleCode, Aggregation)%>% 
   mutate(AgPlBiomass = sum(Size), AgPlFreq = n()) %>% ungroup() %>%
@@
 #Collapse to only values per replicate
-plankAggHistRep<-HistReplicate %>% group_by(Species,Culture,Condition,Strain,TimePoint, Replicate, Aggregation,AgPlNormFrequency,AgPlNormBiomass) %>% summarize() %>%  unique()%>%ungroup() %>%  group_by(Species,Culture,Strain,Condition,TimePoint, Replicate) %>% mutate(checkAggFreq =sum(AgPlNormFrequency), checkAggBiomass = sum(AgPlNormBiomass))
+plankAggHistRep<-HistReplicate %>% 
+  group_by(Species,Culture,Condition,Strain,TimePoint, Replicate, SaStrain, Region, Aggregation,AgPlNormFrequency,AgPlNormBiomass) %>% 
+  summarize() %>%  unique()%>%ungroup() %>%  
+  group_by(Species,Culture,Condition,Strain,TimePoint, Replicate, SaStrain, Region) %>% mutate(checkAggFreq =sum(AgPlNormFrequency), checkAggBiomass = sum(AgPlNormBiomass))
 
-##Normalize using Condition
-HistCondition<-HistCondition %>%  mutate(Aggregation = case_when(LogBin == 5 ~"Planktonic",LogBin>5 ~ "Aggregate")) %>%
-  group_by(Species,Culture,Condition,Strain, TimePoint, Aggregation)%>% 
+##Normalize using Condition and region
+HistConditionRegin<-HistConditionRegin %>%  mutate(Aggregation = if_else(LogBin == "(.5, 5]", "Planktonic", "Aggregate")) %>%
+  group_by(Species,Culture,Condition,Strain, TimePoint,Region, SaStrain, Aggregation)%>% 
   mutate(AgPlBiomass = sum(Size), AgPlFreq = n()) %>% ungroup() %>%
@@
 #Collapse to only values per replicate
-plankAggHistCond<-HistCondition %>% group_by(Species,Culture,Condition,Strain,TimePoint, Aggregation,AgPlNormFrequency,AgPlNormBiomass) %>% summarize() %>%  unique()%>%ungroup() %>%  group_by(Species,Culture,Strain, Condition,TimePoint) %>% mutate(checkAggFreq =sum(AgPlNormFrequency), checkAggBiomass = sum(AgPlNormBiomass))
+plankAggHistCondReg<-HistConditionRegin %>% 
+  group_by(Species,Culture,Condition,SaStrain, Region,Strain,TimePoint, Aggregation,AgPlNormFrequency,AgPlNormBiomass) %>%
+  summarize() %>%  unique()%>%ungroup() %>%
+  group_by(Species,Culture,Condition,SaStrain, Region,Strain,TimePoint) %>% mutate(checkAggFreq =sum(AgPlNormFrequency), checkAggBiomass = sum(AgPlNormBiomass))
+
+##Normalize using Condition 
+HistCondition<-HistCondition %>%  mutate(Aggregation = if_else(LogBin == "(.5, 5]", "Planktonic", "Aggregate")) %>%
+  group_by(Species,Culture,Condition,SaStrain, TimePoint,Strain, Aggregation)%>% 
+  mutate(AgPlBiomass = sum(Size), AgPlFreq = n()) %>% ungroup() %>%
+  mutate(AgPlNormFrequency = AgPlFreq/TotalFrequency*100, AgPlNormBiomass = AgPlBiomass/TotalBiomass*100)
+#Collapse to only values per replicate
+plankAggHistCond<-HistCondition %>% 
+  group_by(Species,Culture,Condition,Strain,SaStrain,TimePoint, Aggregation,AgPlNormFrequency,AgPlNormBiomass) %>%
+  summarize() %>%  unique()%>%ungroup() %>%  
+  group_by(Species,Culture,Condition,Strain,SaStrain,TimePoint) %>% mutate(checkAggFreq =sum(AgPlNormFrequency), checkAggBiomass = sum(AgPlNormBiomass))
 
 #Plot Frequency
+PlotAggPlank<-function(rep.df,cond.df,region.df, y_var, title, species, colorStrain){
+ggplot()+
+    geom_point(data = rep.df %>% filter(TimePoint=="Day 4")%>% filter(Species == species),
+                aes(x=as.factor(Aggregation),y=.data[[y_var]], color =.data[[colorStrain]], shape = Region),
+               position = position_jitterdodge(jitter.height = 0, jitter.width = .3,dodge.width = 0.75),size=1)+
+    geom_point(data = region.df%>% filter(TimePoint=="Day 4")%>% filter(Species == species),
+               aes(x=as.factor(Aggregation),y=.data[[y_var]], color =.data[[colorStrain]],shape = Region),
+               size=3, position = position_dodge(width = .75) )+
+    geom_point(data = cond.df%>% filter(TimePoint=="Day 4") %>% filter(Species == species),
+               aes(x=as.factor(Aggregation),y=.data[[y_var]],  color =.data[[colorStrain]]),size=4, shape = 3,position = position_dodge(width = .75) )+
+    scale_y_log10(breaks = c(100, 10, 1, .1, .01), labels = c(100, 10, 1, .1, .01))+
+    facet_grid(.~Species)+
+    scale_shape_manual(values=c(16, 1))+
+    ggtitle(title)+
+    labs(y = paste(y_var,"(%)"),x = bquote(paste("Aggregate Volume (", mu*"m"^3*")")))+
+    scale_color_brewer(palette = "Set1")+
+    theme_cowplot()+
+    panel_border() +
+    theme(plot.title = element_text(hjust = 0.5), 
+        strip.text = element_text(size = 11, face = "italic",margin = margin(.1,0,.1,0, "cm")),#this is for the facet text
+        strip.background = element_rect(color="black", fill="white", size=1, linetype="solid"))#facet background
+}
+###---Figure 1D
+PlotAggPlank(plankAggHistRep%>% filter(SaStrain %in% c("Sa mono", "co-wt")),
+             plankAggHistCond%>% filter(SaStrain %in% c("Sa mono", "co-wt")),
+             plankAggHistCondReg%>% filter(SaStrain %in% c("Sa mono", "co-wt")),
+             "AgPlNormBiomass", "Normalized Biomass", "S. aureus", "Culture")
+
+PlotAggPlank(plankAggHistRep,
+             plankAggHistCond,
+             plankAggHistCondReg,
+             "AgPlNormBiomass", "Normalized Biomass", "S. aureus", "SaStrain")
+
 ggplot()+
@@
 ggplot()+
-  geom_jitter(data = plankAggHistRep,aes(x=as.factor(Aggregation),y=AgPlNormBiomass,  color =Condition ),size=2, height = 0, width = .2, shape = 1)+
-  geom_point(data = plankAggHistCond,aes(x=as.factor(Aggregation),y=AgPlNormBiomass,  color =Condition),size=5, shape = 16, position = position_dodge2(width = .5)) +
+  geom_jitter(data = plankAggHistRep,
+              aes(x=as.factor(Aggregation),y=AgPlNormBiomass,  color =Condition ),size=2, height = 0, width = .2, shape = 1)+
+  geom_point(data = plankAggHistCond,
+             aes(x=as.factor(Aggregation),y=AgPlNormBiomass,  color =Condition),size=5, shape = 16, position = position_dodge2(width = .5)) +
   facet_grid(Species~TimePoint)+
@@
 #Plot using the code from the paper
-
 PlotAggregateBiomassContribution<-function(species){
@@
 PlotBiomassAggregateSize2("S. aureus")
-
 #####
@@
 #rename variables
-sliceDataMeta$Channel <- factor(sliceDataMeta$Channel, levels = c(1, 2, 3),labels = c('S. aureus','P. aeruginosa','host'))
+sliceDataMeta<-sliceDataMeta %>% mutate(Species = recode(Channel,"1" ='S. aureus',"2" ='P. aeruginosa',"3" ='host'))
 sliceDataMeta$Condition<- factor(sliceDataMeta$Condition, levels = c("mono", "pawt","papqsL", "paphz", "wt", "pqsL", "phz"),
@@
 sliceDataMeta<-sliceDataMeta%>% mutate(Strain = recode(Condition, 'Sa mono' = "Sa", 'Pa wt mono' = "wt",'pqsL mono'= "pqsL",'phz mono'= "phz",'wt co'= "wt", 'pqsL co'= "pqsL", 'phz co'= "phz"))
+#add useful metrics
+sliceDataMeta<-sliceDataMeta%>% filter(!Channel == "3") %>% mutate(Height = Zdim*Slice) %>% group_by(SampleCode)%>% mutate(MaxHeight = max(Height)) 
+#calculate relative biomass
+##For all samples
 
-#calculate relative biomass
-sliceDataMeta<-sliceDataMeta%>% filter(!Channel == "host") %>% mutate(Height = Zdim*Slice) %>% group_by(SampleCode, Channel) %>% mutate(TotalBiomass = sum(Biomass)) %>% ungroup() %>% mutate(NormBiomass = Biomass/TotalBiomass*100)
+sliceDataMetaAll<-sliceDataMeta%>% group_by(SampleCode, Channel) %>% mutate(TotalBiomass = sum(Biomass)) %>% ungroup() %>% mutate(NormBiomass = Biomass/TotalBiomass*100)
+
+sliceDataSumary<-sliceDataMeta %>% group_by(SampleCode, TimePoint, Strain, Culture, MaxHeight)%>% summarise() %>% unique()
+
+sliceDataClean<-sliceDataMeta %>% filter(MaxHeight>60) %>% filter(Height<60) %>% filter(TimePoint=="Day 4") %>% group_by(SampleCode, Channel) %>% mutate(TotalBiomass = sum(Biomass)) %>% ungroup() %>% mutate(NormBiomass = Biomass/TotalBiomass*100)
 
@@
 #####  
-sliceDataSum<-sliceDataMeta %>% group_by(SampleCode) %>% mutate(MaxHeight = max(Height)) %>% ungroup()
+  #graph the samples height
+  ggplot()+
+    geom_col(data = sliceDataSumary %>% filter(TimePoint=="Day 4"),aes(x=SampleCode,y=MaxHeight, color = Strain, fill =Culture ),size=2)+
+    geom_hline(yintercept = 50)+
+    labs(title ="title")+
+    scale_color_brewer(palette = "Set2")+
+    scale_fill_brewer(palette = "Set1")+
+    theme_cowplot()+
+    theme(plot.title = element_text(hjust = 0.5))
 
+PlotZsliceSa<-function(){  
   ggplot()+
-  geom_smooth(data = sliceDataSum %>% filter(MaxHeight>50 & MaxHeight<120) ,aes(y=NormBiomass,x=Height, color = Strain, linetype = Culture),size=2)+
+    geom_smooth(data = sliceDataClean %>% filter(Species == "S. aureus"),aes(y=NormBiomass,x=Height, color = Region),size=2, alpha = .1)+
+    #geom_point(data = sliceDataClean%>% filter(Species == species),aes(y=NormBiomass,x=Height, color = Region),size=1, alpha = .5)+
     geom_hline(yintercept = 0, linetype = "dashed", color = "gray")+
@@
     scale_color_brewer(palette = "Set1")+
-  facet_grid(Channel~TimePoint)+
+    facet_grid(Strain~.)+
+    scale_shape_manual(values = c(1, 3))+
     panel_border() +
     coord_flip()+
-  theme(plot.title = element_text(hjust = 0.5))
+    theme(plot.title = element_text(hjust = 0.5))}
+PlotZslicePa<-function(){  
+  ggplot()+
+    geom_smooth(data = sliceDataClean %>% filter(Species == "P. aeruginosa") %>% filter(Culture=="co"),aes(y=NormBiomass,x=Height, color = Region),size=2, alpha = .1)+
+    #geom_point(data = sliceDataClean%>% filter(Species == species),aes(y=NormBiomass,x=Height, color = Region),size=1, alpha = .5)+
+    geom_hline(yintercept = 0, linetype = "dashed", color = "gray")+
+    theme_cowplot()+
+    scale_color_brewer(palette = "Set1")+
+    facet_grid(Strain~.)+
+    scale_shape_manual(values = c(1, 3))+
+    panel_border() +
+    coord_flip()+
+    theme(plot.title = element_text(hjust = 0.5))}
+PlotZslicePa()
+
+PlotZsliceSa()
 

### 2021-09-04 R/AggregateCounts.Rmd
Re-ran it from scratch and fixed some grouping errors

@@
 
-```{r aggregate wrangling and overview plots}
+```{r aggregate wrangling}
 #Statistics from all aggregates
 #Get aggregate summary per sample
-aggregateListSummaryReplicate<-aggregateList%>% group_by(SampleCode, Species,SaStrain, Strain, Culture,TimePoint, Condition, Replicate,Region) %>% 
-  summarise(Aggs = n(), biomass = sum(Size), meanAggSize = mean(Size), seAggSize = std.error(Size), maxSize = max(Size), minSize = min(Size)) %>%
-  ungroup() %>% mutate(RatioMaxTotal = maxSize/biomass)
+aggregateListSummaryReplicate<-aggregateList%>% group_by(SampleCode,Species,SaStrain,Strain,Culture,TimePoint,Condition,Replicate,Region) %>% 
+  summarise(Aggs = n(), Biomass = sum(Size), MeanAggSize = mean(Size), SEAggSize = std.error(Size), MaxSize = max(Size), MinSize = min(Size)) %>%
+  ungroup() %>% mutate(RatioMaxTotal = MaxSize/Biomass)
 
 #Get aggregate Summary per condition
-aggregateListSummaryCondNoRegion<-aggregateListSummaryReplicate %>% group_by(Species,SaStrain, Strain, Culture,TimePoint, Condition) %>% 
-  summarise(meanAggs= mean(Aggs), meanBiomassLog = mean(log10(biomass)), SEBiomassLog = std.error((log10(biomass))), meanAggSize = mean(meanAggSize), seAggSize = std.error(meanAggSize))%>%  mutate(meanBiomass =  meanBiomassLog^10, SEBiomass = SEBiomassLog^10)
+aggregateListSummaryCondNoRegion<-aggregateListSummaryReplicate %>% group_by(Species,SaStrain,Strain,Culture,TimePoint,Condition) %>% 
+  summarise(MeanAggs= mean(Aggs), MeanBiomassLog = mean(log10(Biomass)), SEBiomassLog = std.error((log10(Biomass))), MeanMeanAggSize = mean(MeanAggSize), SEMeanAggSize = std.error(MeanAggSize))
 
 #Get aggregate Summary per condition and region
-aggregateListSummaryCondition<-aggregateListSummaryReplicate %>% group_by(Species, SaStrain,Strain, Culture,TimePoint, Condition, Region) %>% 
-  summarise(meanAggs= mean(Aggs), meanBiomassLog = mean(log10(biomass)), SEBiomassLog = std.error((log10(biomass))), meanAggSize = mean(meanAggSize), seAggSize = std.error(meanAggSize))%>%  mutate(meanBiomass =  meanBiomassLog^10, SEBiomass = SEBiomassLog^10)
-
+aggregateListSummaryCondition<-aggregateListSummaryReplicate %>% group_by(Species,SaStrain,Strain,Culture,TimePoint,Condition,Region) %>% summarise(MeanAggs= mean(Aggs), MeanBiomassLog = mean(log10(Biomass)), SEBiomassLog = std.error((log10(Biomass))), MeanMeanAggSize = mean(MeanAggSize), SEMeanAggSize = std.error(MeanAggSize))
+```
+```{r Overview Plots}
 #Plot agg summary per sample
@@
                         Size> 1000  ~ paste0("(1000, ",bquote("\U221E"), ")"))) %>% 
-  group_by(SampleCode)%>% 
+  group_by(SampleCode,Species)%>% 
   mutate(TotalBiomass = sum(Size), TotalFrequency = n()) %>% ungroup() %>% 
-  group_by(SampleCode, LogBin)%>%
+  group_by(SampleCode,Species,LogBin)%>%
   mutate(BinBiomass = sum(Size), BinFrequency = n()) %>% ungroup() %>%
@@
 HistReplicateSummary<-HistReplicate %>% 
-  group_by(Species,Culture,SaStrain, Strain,Region,Condition,TimePoint, Replicate,SampleCode, LogBin,NormalizedFrequency,NormalizedBiomass) %>% summarize() %>%
-  unique()%>%ungroup() %>%  group_by(Species,Strain, SaStrain,Culture,Condition,TimePoint, Replicate, SampleCode) %>% 
+  group_by(SampleCode,Species,SaStrain,Strain,Culture,TimePoint,Condition,Replicate,Region,LogBin,NormalizedFrequency,NormalizedBiomass) %>% summarize() %>%
+  unique()%>%ungroup() %>%  group_by(SampleCode,Species,SaStrain,Strain,Culture,TimePoint,Condition,Replicate,Region) %>% 
   mutate(checkSumFreq =sum(NormalizedFrequency), checkSumBiomass = sum(NormalizedBiomass))
@@
   mutate(TotalBiomass = sum(Size), TotalFrequency = n()) %>% ungroup() %>% 
-  group_by(Species, Condition,TimePoint,LogBin)%>%
+  group_by(Species,Condition,TimePoint,LogBin)%>%
   mutate(BinBiomass = sum(Size), BinFrequency = n()) %>% ungroup() %>%
@@
 HistConditionSummary<-HistCondition %>%
-  group_by(Species,Culture,SaStrain, Strain, Condition,TimePoint,LogBin,NormalizedFrequency,NormalizedBiomass) %>% 
+  group_by(Species,SaStrain,Strain,Culture,TimePoint,Condition,LogBin,NormalizedFrequency,NormalizedBiomass) %>% 
   summarize() %>% unique()%>%ungroup() %>%
-  group_by(Species,Culture,Strain,SaStrain, Condition,TimePoint) %>% 
+  group_by(Species,SaStrain,Strain,Culture,TimePoint,Condition) %>% 
   mutate(checkSumFreq =sum(NormalizedFrequency), checkSumBiomass = sum(NormalizedBiomass))
@@
                         Size> 1000  ~ paste0("(1000, ",bquote("\U221E"), ")"))) %>% 
-  group_by(Species,Condition,TimePoint, Region)%>% 
+  group_by(Species,Condition,TimePoint,Region)%>% 
   mutate(TotalBiomass = sum(Size), TotalFrequency = n()) %>% ungroup() %>%
-  group_by(Species, Condition,TimePoint, Region,LogBin)%>%
+  group_by(Species,Condition,TimePoint,Region,LogBin)%>%
   mutate(BinBiomass = sum(Size), BinFrequency = n()) %>% ungroup() %>%
@@
 HistConditionRegin$LogBin <- factor(HistConditionRegin$LogBin, levels = c("(.5, 5]", "(5, 10]","(10, 100]", "(100, 1000]", paste0("(1000, ",bquote("\U221E"), ")")),labels = c(levels = c("(.5, 5]", "(5, 10]","(10, 100]", "(100, 1000]", paste0("(1000, ",bquote("\U221E"), ")"))))
-
 #Summary data frame
 HistCondRegionSum<-HistConditionRegin %>%
-  group_by(Species,Culture,SaStrain, Strain, Condition,TimePoint, Region,LogBin,NormalizedFrequency,NormalizedBiomass) %>% 
+  group_by(Species,SaStrain,Strain,Culture,TimePoint,Condition,Region,LogBin,NormalizedFrequency,NormalizedBiomass) %>% 
   summarize() %>% unique()%>%ungroup() %>%
-  group_by(Species,Culture,Strain,SaStrain, Condition,TimePoint, Region) %>% 
+  group_by(Species,SaStrain,Strain,Culture,TimePoint,Condition,Region) %>% 
   mutate(checkSumFreq =sum(NormalizedFrequency), checkSumBiomass = sum(NormalizedBiomass))
 #####
-
+```
+
+```{r Plot Aggregate size bins}
 #Plot Normalized Frequency
@@
 
-PlotHistSum(HistReplicateSummary,HistCondRegionSum,HistConditionSummary,"NormalizedBiomass", "Normalized Biomass all sizes")
+PlotHistSum(HistReplicateSummary%>% filter(Culture =="co"),
+            HistConditionSummary%>% filter(Culture =="co"),
+            HistCondRegionSum%>% filter(Culture =="co"),
+            "NormalizedFrequency", "Normalized Frequency all sizes", "P. aeruginosa", "Strain")
 
@@
 PlotHistRepBioTrend(HistReplicateSummary, "S. aureus")
-
+```
+
+```{Aggregates Only, Not currently in use}
 #####
@@
 #####
-
+```
+```{r Aggregates vs Planktonics}
 #Planktonic vs aggregates
@@
 plankAggHistRep<-HistReplicate %>% 
-  group_by(Species,Culture,Condition,Strain,TimePoint, Replicate, SaStrain, Region, Aggregation,AgPlNormFrequency,AgPlNormBiomass) %>% 
+  group_by(SampleCode,Species,SaStrain,Strain,Culture,TimePoint,Condition,Replicate,Region,Aggregation,AgPlNormFrequency,AgPlNormBiomass) %>% 
   summarize() %>%  unique()%>%ungroup() %>%  
-  group_by(Species,Culture,Condition,Strain,TimePoint, Replicate, SaStrain, Region) %>% mutate(checkAggFreq =sum(AgPlNormFrequency), checkAggBiomass = sum(AgPlNormBiomass))
-
-##Normalize using Condition and region
-HistConditionRegin<-HistConditionRegin %>%  mutate(Aggregation = if_else(LogBin == "(.5, 5]", "Planktonic", "Aggregate")) %>%
-  group_by(Species,Culture,Condition,Strain, TimePoint,Region, SaStrain, Aggregation)%>% 
-  mutate(AgPlBiomass = sum(Size), AgPlFreq = n()) %>% ungroup() %>%
-  mutate(AgPlNormFrequency = AgPlFreq/TotalFrequency*100, AgPlNormBiomass = AgPlBiomass/TotalBiomass*100)
-#Collapse to only values per replicate
-plankAggHistCondReg<-HistConditionRegin %>% 
-  group_by(Species,Culture,Condition,SaStrain, Region,Strain,TimePoint, Aggregation,AgPlNormFrequency,AgPlNormBiomass) %>%
-  summarize() %>%  unique()%>%ungroup() %>%
-  group_by(Species,Culture,Condition,SaStrain, Region,Strain,TimePoint) %>% mutate(checkAggFreq =sum(AgPlNormFrequency), checkAggBiomass = sum(AgPlNormBiomass))
+  group_by(SampleCode,Species,SaStrain,Strain,Culture,TimePoint,Condition,Replicate,Region) %>% mutate(checkAggFreq =sum(AgPlNormFrequency), checkAggBiomass = sum(AgPlNormBiomass))
 
@@
 HistCondition<-HistCondition %>%  mutate(Aggregation = if_else(LogBin == "(.5, 5]", "Planktonic", "Aggregate")) %>%
-  group_by(Species,Culture,Condition,SaStrain, TimePoint,Strain, Aggregation)%>% 
+  group_by(Species,Condition,TimePoint,Aggregation)%>% 
   mutate(AgPlBiomass = sum(Size), AgPlFreq = n()) %>% ungroup() %>%
@@
 plankAggHistCond<-HistCondition %>% 
-  group_by(Species,Culture,Condition,Strain,SaStrain,TimePoint, Aggregation,AgPlNormFrequency,AgPlNormBiomass) %>%
+  group_by(Species,SaStrain,Strain,Culture,TimePoint,Condition,Aggregation,AgPlNormFrequency,AgPlNormBiomass) %>%
   summarize() %>%  unique()%>%ungroup() %>%  
-  group_by(Species,Culture,Condition,Strain,SaStrain,TimePoint) %>% mutate(checkAggFreq =sum(AgPlNormFrequency), checkAggBiomass = sum(AgPlNormBiomass))
+  group_by(Species,SaStrain,Strain,Culture,TimePoint,Condition) %>% mutate(checkAggFreq =sum(AgPlNormFrequency), checkAggBiomass = sum(AgPlNormBiomass))
+
+##Normalize using Condition and region
+HistConditionRegin<-HistConditionRegin %>%  mutate(Aggregation = if_else(LogBin == "(.5, 5]", "Planktonic", "Aggregate")) %>%
+  group_by(Species,SaStrain,Strain,Culture,TimePoint,Condition,Region,Aggregation)%>% 
+  mutate(AgPlBiomass = sum(Size), AgPlFreq = n()) %>% ungroup() %>%
+  mutate(AgPlNormFrequency = AgPlFreq/TotalFrequency*100, AgPlNormBiomass = AgPlBiomass/TotalBiomass*100)
+#Collapse to only values per condition and Replicate
+plankAggHistCondReg<-HistConditionRegin %>% 
+  group_by(Species,SaStrain,Strain,Culture,TimePoint,Condition,Region,Aggregation,AgPlNormFrequency,AgPlNormBiomass) %>%
+  summarize() %>%  unique()%>%ungroup() %>%
+  group_by(Species,SaStrain,Strain,Culture,TimePoint,Condition,Region) %>% mutate(checkAggFreq =sum(AgPlNormFrequency), checkAggBiomass = sum(AgPlNormBiomass))
+```
+
+```{r Plot Aggregate vs planktonics}
 
 #Plot Frequency
-PlotAggPlank<-function(rep.df,cond.df,region.df, y_var, title, species, colorStrain){
+PlotAggPlank<-function(rep.df,cond.df,region.df, y_var, title, species, colorStrain, facet){
 ggplot()+
@@
     scale_y_log10(breaks = c(100, 10, 1, .1, .01), labels = c(100, 10, 1, .1, .01))+
-    facet_grid(.~Species)+
+    facet_grid(.~.data[[facet]])+
     scale_shape_manual(values=c(16, 1))+
@@
              plankAggHistCondReg%>% filter(SaStrain %in% c("Sa mono", "co-wt")),
-             "AgPlNormBiomass", "Normalized Biomass", "S. aureus", "Culture")
+             "AgPlNormBiomass", "Normalized Biomass", "S. aureus", "Culture", "Species")
 
@@
              plankAggHistCondReg,
-             "AgPlNormBiomass", "Normalized Biomass", "S. aureus", "SaStrain")
-
-ggplot()+
-  geom_jitter(data = plankAggHistRep,aes(x=as.factor(Aggregation),y=AgPlNormFrequency,  color =Condition ),size=3, height = 0, width = .2, shape = 1)+ 
-  geom_point(data = plankAggHistCond,aes(x=as.factor(Aggregation),y=AgPlNormFrequency,  color =Condition,group = Condition),size=4, shape = 16, position = position_dodge(width = .3) )+
-  facet_grid(Species~TimePoint)+
-  ggtitle("Normalized Frequency (%) Aggs vs Plank")+
-  labs(y = "Normalized Frequency (%)",x = bquote(paste("Aggregate Volume (", mu*"m"^3*")")))+
-  theme_half_open()+
-  panel_border() +
-  scale_color_brewer(palette = "Set1")+
-  theme(plot.title = element_text(hjust = 0.5)) 
+             "AgPlNormBiomass", "Normalized Biomass", "S. aureus", "SaStrain","Species")
+
+PlotAggPlank(plankAggHistRep,
+             plankAggHistCond,
+             plankAggHistCondReg,
+             "AgPlNormBiomass", "Normalized Biomass", "P. aeruginosa", "Strain","Culture")
+
 #Plot Biomass
@@
 PlotZslicePa()
-
 PlotZsliceSa()
+
+PlotZsliceBth<-function(){  
+  ggplot()+
+    geom_smooth(data = sliceDataClean,aes(y=NormBiomass,x=Height, color = Species ),size=2, alpha = .1)+
+    #geom_point(data = sliceDataClean%>% filter(Species == species),aes(y=NormBiomass,x=Height, color = Region),size=1, alpha = .5)+
+    geom_hline(yintercept = 0, linetype = "dashed", color = "gray")+
+    theme_cowplot()+
+    scale_color_brewer(palette = "Set1")+
+    facet_grid(Strain~Region)+
+    scale_shape_manual(values = c(1, 3))+
+    panel_border() +
+    coord_flip()+
+    theme(plot.title = element_text(hjust = 0.5))}
+
+PlotZsliceBth()
 

### 2021-09-06 R/PropOc Data 3D.Rmd

@@
 ```
-Importing whole data sets to identify distribution of data
-the chunk below is the only one aplicable to the SaPa chronic wounds project, all the other ones are just for reference
-
-```{r read whole data sets}
+
+The chunk below is the only one aplicable to the SaPa chronic wounds project, all the other ones are just for reference
+
+```{r SAPA Chorinc wounds paper chunk}
 ReadPropOcFile<-function(file){
@@
 #####
-#maximum distribution isn't super representative, so for the distribution, I calculated the value at which 50% of the population is found
+#maximum frequency isn't super representative, so for the distribution, I calculated the value at which 50% of the population is found
 
@@
 
-PropOcDataFiltered1<-PropOcDataFiltered %>% group_by(Condition,TimePoint,SampleCode) %>% summarise(None = n()) %>% mutate(Sample = SampleCode)
-
-propOcMidDensitylabeled <-merge(propOcMidDensity,PropOcDataFiltered1)
+PropOcDataFiltered1<-PropOcDataFiltered %>% group_by(Condition,TimePoint,Region,SampleCode) %>% summarise(None = n()) %>% mutate(Sample = SampleCode)
+
+propOcMidDensitylabeled <-merge(propOcMidDensity,PropOcDataFiltered1)#Add condition and timepoint
 
@@
 
-propOcMidDensityStats<-propOcMidDensitylabeled %>% ungroup() %>% group_by(Condition,Culture,Strain,TimePoint, Distance, Relation) %>% summarize(meanValue = mean(Value), sdValue = sd(Value), medianValue = median(Value))
-
-ggplot()+
-    geom_point(data = propOcMidDensityStats %>% filter(Relation== "Pa->Sa"),aes(y=meanValue, x = Distance,color=Condition, shape = "Mean"),size=2)+
-    geom_point(data = propOcMidDensityStats %>% filter(Relation== "Pa->Sa"),aes(y=medianValue, x = Distance,color=Condition,shape = "Median"),size=2)+
+#add region
+metaData.df <-read.csv('/Volumes/raw_data/Confocal/Carolyn/2020/Chronic wounds/images metadata.csv', header = TRUE)
+metaData.df$SampleCode<-as.factor(metaData.df$SampleCode)
+metaData.df<-metaData.df %>% select(SampleCode, mouse, Position, size, Region, Zdim, xyDim,xySize)#
+propOcMidDensMetaLabel<-metaData.df %>%  merge(propOcMidDensitylabeled, by = "SampleCode")
+
+#include Region
+propOcMidDensityStatsRegion<-propOcMidDensMetaLabel %>% ungroup() %>% group_by(Condition,Culture,Strain,TimePoint,Region, Distance, Relation) %>% summarize(meanValue = mean(Value), sdValue = std.error(Value), medianValue = median(Value))
+#exclude region
+propOcMidDensityStats<-propOcMidDensMetaLabel %>% ungroup() %>% group_by(Condition,Culture,Strain,TimePoint,Distance, Relation) %>% summarize(meanValue = mean(Value), sdValue = std.error(Value), medianValue = median(Value))
+
+PlotMeanMidDensityPORegion<-function(relation){
+  ggplot()+
+    geom_pointrange(data = propOcMidDensityStatsRegion %>% filter(TimePoint == "Day 4", Relation== relation),aes(y=meanValue,ymin= meanValue-(sdValue/2), ymax = meanValue+(sdValue/2), x = Distance,color=Condition, shape = Region),size=1, position = position_dodge(width = .6))+
+    #geom_point(data = propOcMidDensityStats %>% filter(Relation== "Pa->Sa"),aes(y=medianValue, x = Distance,color=Condition,shape = "Median"),size=2)+
+    #scale_y_log10(breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
     labs(title ="mean 50 percentile Density")+
-    facet_grid(Relation ~ TimePoint)+
+    facet_grid(Relation ~ .)+
     scale_color_brewer(palette = "Set1")+
@@
     theme(plot.title = element_text(hjust = 0.5))
-
-ggplot()+#Pa->Pa
-    geom_point(data = propOcMidDensityStats %>% filter(Relation== "Pa->Pa"),aes(y=meanValue, x = Distance,color=Culture, shape = "Mean"),size=2)+
-    geom_point(data = propOcMidDensityStats %>% filter(Relation== "Pa->Pa"),aes(y=medianValue, x = Distance,color=Culture,shape = "Median"),size=2)+
+}
+#Including Edge
+PlotMeanMidDensityPORegion("Pa->Sa")
+PlotMeanMidDensityPORegion("Sa->Pa")#this is log exponential
+PlotMeanMidDensityPORegion("Pa->Pa")
+PlotMeanMidDensityPORegion("Sa->Sa")
+
+PlotMeanMidDensityPO<-function(relation){
+  ggplot()+
+    geom_pointrange(data = propOcMidDensityStats %>% filter(TimePoint == "Day 4", Relation== relation),aes(y=meanValue,ymin= meanValue-(sdValue/2), ymax = meanValue+(sdValue/2), x = Distance,color=Condition),size=1, position = position_dodge(width = .6))+
+    #geom_point(data = propOcMidDensityStats %>% filter(Relation== "Pa->Sa"),aes(y=medianValue, x = Distance,color=Condition,shape = "Median"),size=2)+
+    #scale_y_log10(breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
     labs(title ="mean 50 percentile Density")+
-    facet_grid(Strain ~ TimePoint)+
+    facet_grid(Relation ~ .)+
     scale_color_brewer(palette = "Set1")+
@@
     theme(plot.title = element_text(hjust = 0.5))
+}
+PlotMeanMidDensityPO("Pa->Sa")
+PlotMeanMidDensityPO("Sa->Pa")#this is log exponential
+PlotMeanMidDensityPO("Pa->Pa")
+PlotMeanMidDensityPO("Sa->Sa")
+#this wat combines the data accroding to the focus species
+PlotMeanMidDensityPOCenter<-function(){
+  ggplot()+
+    geom_pointrange(data = propOcMidDensityStats %>% filter(TimePoint == "Day 4", Culture == "co") %>% filter(Relation%in%c("Sa->Sa","Sa->Pa")),
+    #geom_pointrange(data = propOcMidDensityStats %>% filter(TimePoint == "Day 4", Culture == "co") %>% filter(Relation%in%c("Pa->Sa","Pa->Pa")),
+                      aes(y=meanValue,ymin= meanValue-(sdValue/2), ymax = meanValue+(sdValue/2), x = Distance,color=Relation),size=1, position = position_dodge(width = .6))+
+    #geom_point(data = propOcMidDensityStats %>% filter(Relation== "Pa->Sa"),aes(y=medianValue, x = Distance,color=Condition,shape = "Median"),size=2)+
+    #scale_y_log10(breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
+    labs(title ="mean 50 percentile Density")+
+    facet_grid(.~Condition )+
+    scale_color_brewer(palette = "Set1")+
+    theme_cowplot()+
+    theme(plot.title = element_text(hjust = 0.5))
+}
+PlotMeanMidDensityPOCenter()
+PlotMeanMidDensityPOCenterRegion<-function(){
+  ggplot()+
+    #geom_pointrange(data = propOcMidDensityStatsRegion %>% filter(TimePoint == "Day 4", Culture == "co") %>% filter(Relation%in%c("Sa->Sa","Sa->Pa")),
+    geom_pointrange(data = propOcMidDensityStatsRegion %>% filter(TimePoint == "Day 4", Culture == "co") %>% filter(Relation%in%c("Pa->Sa","Pa->Pa")),
+                      aes(y=meanValue,ymin= meanValue-(sdValue/2), ymax = meanValue+(sdValue/2), x = Distance,shape = Region,color=Relation),
+    size=1, position = position_dodge(width = .6))+
+    #geom_point(data = propOcMidDensityStats %>% filter(Relation== "Pa->Sa"),aes(y=medianValue, x = Distance,color=Condition,shape = "Median"),size=2)+
+    #scale_y_log10(breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
+    labs(title ="mean 50 percentile Density")+
+    facet_grid(.~Condition )+
+    scale_color_brewer(palette = "Set1")+
+    theme_cowplot()+
+    theme(plot.title = element_text(hjust = 0.5))
+}
+PlotMeanMidDensityPOCenterRegion()
+#Calculate empty space
+
+emptySpaceRgn<-propOcMidDensityStatsRegion %>% mutate(Focus = recode(Relation, "Pa->Sa" = "Pa","Pa->Pa" = "Pa","Sa->Sa" = "Sa","Sa->Pa" = "Sa")) %>% group_by(Focus, Distance, Condition, TimePoint, Region) %>% mutate(EmptySpace = 1-(sum(meanValue)), SDEmptySpace = sum(sdValue))
+
+emptySpace<-propOcMidDensityStats %>% mutate(Focus = recode(Relation, "Pa->Sa" = "Pa","Pa->Pa" = "Pa","Sa->Sa" = "Sa","Sa->Pa" = "Sa")) %>% group_by(Focus, Distance, Condition, TimePoint) %>% mutate(EmptySpace = 1-(sum(meanValue)), SDEmptySpace = sum(sdValue))
+PlotEmptySpace<-function(focus){
+  ggplot()+
+    geom_pointrange(data = emptySpace %>% filter(TimePoint == "Day 4", Focus== focus),aes(y=EmptySpace,ymin= EmptySpace-(SDEmptySpace/2), ymax = EmptySpace+(SDEmptySpace/2), x = Distance,color=Strain),size=1, position = position_dodge(width = .6))+
+    #geom_point(data = propOcMidDensityStats %>% filter(Relation== "Pa->Sa"),aes(y=medianValue, x = Distance,color=Condition,shape = "Median"),size=2)+
+    #scale_y_log10(breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
+    labs(title ="mean 50 percentile Density")+
+    facet_grid( .~Culture)+
+    scale_color_brewer(palette = "Set1")+
+    theme_cowplot()+
+    theme(plot.title = element_text(hjust = 0.5))
+}
+PlotEmptySpace("Pa")
+PlotEmptySpace("Sa")
+
+PlotEmptySpaceRegion<-function(focus){
+  ggplot()+
+    geom_pointrange(data = emptySpaceRgn %>% filter(TimePoint == "Day 4", Focus== focus),
+                    aes(y=EmptySpace,ymin= EmptySpace-(SDEmptySpace/2), ymax = EmptySpace+(SDEmptySpace/2), x = Distance,color=Strain, shape = Region),size=1, position = position_dodge(width = .6))+
+    #geom_point(data = propOcMidDensityStats %>% filter(Relation== "Pa->Sa"),aes(y=medianValue, x = Distance,color=Condition,shape = "Median"),size=2)+
+    #scale_y_log10(breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
+    labs(title ="mean 50 percentile Density")+
+    facet_grid( .~Culture)+
+    scale_color_brewer(palette = "Set1")+
+    theme_cowplot()+
+    theme(plot.title = element_text(hjust = 0.5))
+}
+PlotEmptySpaceRegion("Pa")
+PlotEmptySpaceRegion("Sa")
 
@@
 }
+
 PlotMeanEnrichment50percentNRegion(pOEnrMetaStats %>% filter(TimePoint == "Day 4", Relation == "Pa->Sa", TimePoint == "Day 4"),
@@
     panel_border() 
-
 ```
@@
 #Enrichment (distance at highest proportional occupancy) 
-```{r Enrichment}
+```{r Enrichment -DONE}
 #find the max proportional occupancy value from the 50 percentile

### 2021-09-07 R/AggregateCounts.Rmd
added plots with factes for species. Finalized first version of figures for chapter

@@
 
-PlotBiomasPerSampleAndCondition<-function(df1,df2, df3, species){
-ggplot()+ 
-    geom_point(data = df1 %>% filter(TimePoint=="Day 4") %>% filter(Species==species), aes(x = SaStrain, y= meanBiomassLog,shape = Region), 
+PlotBiomasPerSampleAndCondition<-function(df1,df2, df3,xAxis){
+ggplot()+ 
+    geom_point(data = df1 %>% filter(TimePoint=="Day 4") , aes(x = .data[[xAxis]], y= meanBiomassLog,shape = Region), 
              position = position_jitterdodge(jitter.height = 0, jitter.width = .3,dodge.width = 0.75), size = 4)+
-  geom_point(data = df2%>% filter(TimePoint=="Day 4") %>% filter(Species==species), aes(x = SaStrain, y= log10(biomass), shape = Region),size = 1, 
+  geom_point(data = df2%>% filter(TimePoint=="Day 4") , aes(x = .data[[xAxis]], y= log10(biomass), shape = Region),size = 1, 
              position = position_jitterdodge(jitter.height = 0, jitter.width = .3,dodge.width = 0.75))+ 
-  geom_point(data = df3 %>% filter(TimePoint=="Day 4") %>% filter(Species==species), aes(x = SaStrain, y= meanBiomassLog), shape = 3, size = 4)+
+  geom_point(data = df3 %>% filter(TimePoint=="Day 4"), aes(x = .data[[xAxis]], y= meanBiomassLog), shape = 3, size = 4)+
     #scale_y_log10( breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)), limits = c(1, 100000000))+
@@
 }
-PlotBiomasPerSampleAndCondition(aggregateListSummaryCondition,
-                                aggregateListSummaryReplicate,
-                                aggregateListSummaryCondNoRegion, "S. aureus")
 
@@
 }
-PlotMeanAggsPerSampleAndConditionWT(aggregateListSummaryCondition%>% filter(Condition == "Sa mono" |Condition == "wt co"|Condition == "Pa wt mono"),
-                                aggregateListSummaryReplicate %>% filter(Condition == "Sa mono" |Condition == "wt co"|Condition == "Pa wt mono"), 
-                                aggregateListSummaryCondNoRegion%>% filter(Condition == "Sa mono" |Condition == "wt co"|Condition == "Pa wt mono"))
-
-PlotMeanAggsPerSampleAndCondition<-function(df1,df2, df3,species){
-ggplot()+ 
-    geom_point(data = df1 %>% filter(TimePoint=="Day 4") %>% filter(Species == species), aes(x = SaStrain, y= meanAggs,shape = Region), 
+
+PlotMeanAggsPerSampleAndCondition<-function(df1,df2, df3, xAxis){
+ggplot()+ 
+    geom_point(data = df1 %>% filter(TimePoint=="Day 4") , aes(x = .data[[xAxis]], y= meanAggs,shape = Region), 
              position = position_jitterdodge(jitter.height = 0, jitter.width = .3,dodge.width = 0.75), size = 4)+
-  geom_point(data = df2%>% filter(TimePoint=="Day 4")%>% filter(Species == species), aes(x = SaStrain, y= Aggs, shape = Region),size = 1, 
+  geom_point(data = df2%>% filter(TimePoint=="Day 4"), aes(x = .data[[xAxis]], y= Aggs, shape = Region),size = 1, 
              position = position_jitterdodge(jitter.height = 0, jitter.width = .3,dodge.width = 0.75))+
-    geom_point(data = df3 %>% filter(TimePoint=="Day 4")%>% filter(Species == species), aes(x = SaStrain, y= meanAggs),shape = 3,size = 4)+
-    scale_y_log10( breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)), limits = c(10, 100000))+
-      #facet_grid(, scales = "free", space = "free") +
+    geom_point(data = df3 %>% filter(TimePoint=="Day 4"), aes(x = .data[[xAxis]], y= meanAggs),shape = 3,size = 4)+
+    scale_y_log10( breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)), limits = c(1, 100000))+
+      facet_grid(.~Species, scales = "free", space = "free") +
   ggtitle('Number of groups of bacteria')+
@@
 }
-PlotMeanAggsPerSampleAndCondition(aggregateListSummaryCondition,
-                                aggregateListSummaryReplicate, 
-                                aggregateListSummaryCondNoRegion, "S. aureus")
 
@@
 #Biomass Sa and mutants
-PlotBiomasPerSampleAndCondition(aggregateListSummaryCondition,
-                                aggregateListSummaryReplicate,
-                                aggregateListSummaryCondNoRegion, "S. aureus")
-
-PlotBiomasPerSampleAndCondition(aggregateListSummaryCondition,
-                                aggregateListSummaryReplicate,
-                                aggregateListSummaryCondNoRegion, "P. aeruginosa")
+PlotBiomasPerSampleAndCondition(aggregateListSummaryCondition%>% filter(Culture=="co"),
+                                aggregateListSummaryReplicate%>% filter(Culture=="co"),
+                                aggregateListSummaryCondNoRegion%>% filter(Culture=="co"),"SaStrain")
 
@@
 #Number of aggregates Sa and mutants
-PlotMeanAggsPerSampleAndCondition(aggregateListSummaryCondition,
-                                aggregateListSummaryReplicate, 
-                                aggregateListSummaryCondNoRegion, "S. aureus")
-
-PlotMeanAggsPerSampleAndConditionPa(aggregateListSummaryCondition,
-                                aggregateListSummaryReplicate, 
-                                aggregateListSummaryCondNoRegion, "P. aeruginosa")
+PlotMeanAggsPerSampleAndCondition(aggregateListSummaryCondition%>% filter(Condition == "Sa mono" |Condition == "wt co"|Condition == "Pa wt mono"),
+                                aggregateListSummaryReplicate%>% filter(Condition == "Sa mono" |Condition == "wt co"|Condition == "Pa wt mono"), 
+                                aggregateListSummaryCondNoRegion%>% filter(Condition == "Sa mono" |Condition == "wt co"|Condition == "Pa wt mono"), "Culture")
+
+PlotMeanAggsPerSampleAndCondition(aggregateListSummaryCondition %>% filter(Culture=="co"),
+                                aggregateListSummaryReplicate%>% filter(Culture=="co"), 
+                                aggregateListSummaryCondNoRegion%>% filter(Culture=="co"),"SaStrain")
 ```
@@
 #First including all sizes
-#####
 
@@
 #####
-
 #Now per condition including region. The difference is int the "group_by" part
@@
 #this isn't useful as the normalized Frequency changes with replicate, so it's better to pool all samples together
-PlotHistSum<-function(rep.df,cond.df,region.df, y_var, title, species, colorStrain){
-ggplot()+
-    geom_point(data = rep.df %>% filter(TimePoint=="Day 4")%>% filter(Species == species),
+PlotHistSum<-function(rep.df,cond.df,region.df, y_var, title, colorStrain){
+ggplot()+
+    geom_point(data = rep.df %>% filter(TimePoint=="Day 4"),
                 aes(x=as.factor(LogBin),y=.data[[y_var]], color =.data[[colorStrain]], shape = Region),
                position = position_jitterdodge(jitter.height = 0, jitter.width = .3,dodge.width = 0.75),size=1)+
-    geom_point(data = region.df%>% filter(TimePoint=="Day 4")%>% filter(Species == species),
+    geom_point(data = region.df%>% filter(TimePoint=="Day 4"),
                aes(x=as.factor(LogBin),y=.data[[y_var]], color =.data[[colorStrain]],shape = Region),
                size=3, position = position_dodge(width = .75) )+
-    geom_point(data = cond.df%>% filter(TimePoint=="Day 4") %>% filter(Species == species),
+    geom_point(data = cond.df%>% filter(TimePoint=="Day 4"),
                aes(x=as.factor(LogBin),y=.data[[y_var]],  color =.data[[colorStrain]]),size=4, shape = 3,position = position_dodge(width = .75) )+
@@
     ggtitle(title)+
-    labs(y = paste(y_var,"(%)"),x = bquote(paste("Aggregate Volume (", mu*"m"^3*")")))+
+    labs(y = paste("Frequency (%)"),x = bquote(paste("Aggregate Volume (", mu*"m"^3*")")))+
     scale_color_brewer(palette = "Set1")+
@@
 ####---Figure 1C
-PlotHistSum(HistReplicateSummary %>% filter(SaStrain %in% c("Sa mono", "co-wt")),
-            HistConditionSummary%>% filter(SaStrain %in% c("Sa mono", "co-wt")),
-            HistCondRegionSum%>% filter(SaStrain %in% c("Sa mono", "co-wt")),
-            "NormalizedFrequency", "Normalized Frequency all sizes", "S. aureus", "Culture")
-
-PlotHistSum(HistReplicateSummary %>% filter(Strain %in% c("wt")),
-            HistConditionSummary%>% filter(Strain %in% c("wt")),
-            HistCondRegionSum%>% filter(Strain %in% c("wt")),
-            "NormalizedFrequency", "Normalized Frequency all sizes", "P. aeruginosa", "Culture")
-
-PlotHistSum(HistReplicateSummary,
-            HistConditionSummary,
-            HistCondRegionSum,
-            "NormalizedFrequency", "Normalized Frequency all sizes", "S. aureus", "SaStrain")
+PlotHistSum(HistReplicateSummary%>% filter(Condition == "Sa mono" |Condition == "wt co"|Condition == "wt mono"),
+            HistConditionSummary%>% filter(Condition == "Sa mono" |Condition == "wt co"|Condition == "wt mono"),
+            HistCondRegionSum%>% filter(Condition == "Sa mono" |Condition == "wt co"|Condition == "wt mono"),
+            "NormalizedFrequency", "Normalized Frequency per size",  "Culture")
 
@@
             HistCondRegionSum%>% filter(Culture =="co"),
-            "NormalizedFrequency", "Normalized Frequency all sizes", "P. aeruginosa", "Strain")
+            "NormalizedFrequency", "Normalized Frequency per size bin", "Strain")
+#To Show the mono for Pa, one way to do it is to include the species in the filtering and do one plot per species. I dont thnink it's reasonable to do it all in one plot
 
@@
 
-```{r Plot Aggregate vs planktonics}
+```{r figures 1D and 2D Plot Aggregate vs planktonics}
 
 #Plot Frequency
-PlotAggPlank<-function(rep.df,cond.df,region.df, y_var, title, species, colorStrain, facet){
+PlotAggPlankSpecies<-function(rep.df,cond.df,region.df, y_var, title, species, colorStrain, facet){
 ggplot()+
@@
     ggtitle(title)+
-    labs(y = paste(y_var,"(%)"),x = bquote(paste("Aggregate Volume (", mu*"m"^3*")")))+
+    labs(y = paste("Biomass Contribution (%)"),x = bquote(paste("Aggregate Volume (", mu*"m"^3*")")))+
     scale_color_brewer(palette = "Set1")+
@@
 }
+PlotAggPlank<-function(rep.df,cond.df,region.df, y_var, title, colorStrain, facet){
+ggplot()+
+    geom_point(data = rep.df %>% filter(TimePoint=="Day 4"),
+                aes(x=as.factor(Aggregation),y=.data[[y_var]], color =.data[[colorStrain]], shape = Region),
+               position = position_jitterdodge(jitter.height = 0, jitter.width = .3,dodge.width = 0.75),size=1)+
+    geom_point(data = region.df%>% filter(TimePoint=="Day 4"),
+               aes(x=as.factor(Aggregation),y=.data[[y_var]], color =.data[[colorStrain]],shape = Region),
+               size=3, position = position_dodge(width = .75) )+
+    geom_point(data = cond.df%>% filter(TimePoint=="Day 4"),
+               aes(x=as.factor(Aggregation),y=.data[[y_var]],  color =.data[[colorStrain]]),size=4, shape = 3,position = position_dodge(width = .75) )+
+    scale_y_log10(breaks = c(100, 10, 1, .1, .01), labels = c(100, 10, 1, .1, .01))+
+    facet_grid(.~.data[[facet]])+
+    scale_shape_manual(values=c(16, 1))+
+    ggtitle(title)+
+    labs(y = paste("Biomass contribution (%)"),x = bquote(paste("Aggregate Volume (", mu*"m"^3*")")))+
+    scale_color_brewer(palette = "Set1")+
+    theme_cowplot()+
+    panel_border() +
+    theme(plot.title = element_text(hjust = 0.5), 
+        strip.text = element_text(size = 11, face = "italic",margin = margin(.1,0,.1,0, "cm")),#this is for the facet text
+        strip.background = element_rect(color="black", fill="white", size=1, linetype="solid"))#facet background
+}
+
 ###---Figure 1D
-PlotAggPlank(plankAggHistRep%>% filter(SaStrain %in% c("Sa mono", "co-wt")),
+#this is the current version but the ones below mmight also work if I want to show Pa monos and not facetting the species
+PlotAggPlank(plankAggHistRep%>% filter(Condition == "Sa mono" |Condition == "wt co"|Condition == "wt mono"),
+             plankAggHistCond%>% filter(Condition == "Sa mono" |Condition == "wt co"|Condition == "wt mono"),
+             plankAggHistCondReg%>% filter(Condition == "Sa mono" |Condition == "wt co"|Condition == "wt mono"),
+             "AgPlNormBiomass", "Normalized Biomass Contribution", "Culture","Species")
+
+PlotAggPlank(plankAggHistRep%>% filter(Culture == "co"),
+             plankAggHistCond%>% filter(Culture == "co"),
+             plankAggHistCondReg%>% filter(Culture == "co"),
+             "AgPlNormBiomass", "Normalized Biomass Contribution", "Strain","Species")
+
+#these are the other versions
+PlotAggPlankSpecies(plankAggHistRep%>% filter(SaStrain %in% c("Sa mono", "co-wt")),
              plankAggHistCond%>% filter(SaStrain %in% c("Sa mono", "co-wt")),
@@
 
-PlotAggPlank(plankAggHistRep,
+PlotAggPlankSpecies(plankAggHistRep,
              plankAggHistCond,
@@
     theme(plot.title = element_text(hjust = 0.5))
-
+#####
 PlotZsliceSa<-function(){  
@@
 
+sliceDataClean$Strain <- factor(sliceDataClean$Strain, levels = c("Sa","wt","pqsL","phz"),labels = c("Sa", "wild-type", paste0(bquote(Delta),"pqsL"), expression(paste(alpha,"phz"))))
 PlotZsliceBth<-function(){  
   ggplot()+
-    geom_smooth(data = sliceDataClean,aes(y=NormBiomass,x=Height, color = Species ),size=2, alpha = .1)+
+    geom_smooth(data = sliceDataClean %>% filter(Culture=="co"),aes(y=NormBiomass,x=Height, color = Species ),size=2, alpha = .1)+
     #geom_point(data = sliceDataClean%>% filter(Species == species),aes(y=NormBiomass,x=Height, color = Region),size=1, alpha = .5)+
@@
     theme_cowplot()+
-    scale_color_brewer(palette = "Set1")+
+    scale_color_brewer(palette = "Set1",breaks=c("P. aeruginosa","S. aureus"), 
+                   labels = c(bquote(paste(italic("P. aeruginosa"))), bquote(paste(italic("S. aureus")))))+
+    labs(color ="", y = "Percent Biomass", x = bquote(paste("Height (", mu*"m)")))+
     facet_grid(Strain~Region)+
@@
     coord_flip()+
-    theme(plot.title = element_text(hjust = 0.5))}
-
+    theme(plot.title = element_text(hjust = 0.5),strip.background = element_rect(color="black", fill="white", size=1, linetype="solid"))#facet background
+}
+labels = c(bquote(paste(italic("P. aeruginosa"), " wt")), bquote(paste(italic(Delta*"pqsL"))))
+paste0("(1000, ",bquote("\U221E"), ")")
 PlotZsliceBth()

### 2021-09-07 R/PropOc Data 3D.Rmd
minimal changes to adaptive threshold, PropOc Data and PropOC functions

@@
 library(gganimate)#gifs for ggplot
+library(stringr)
 

### 2021-09-07 Matlab/adaptiveThreshold.m

@@ -13,7 +13,7 @@ xySize = .415; %.208 or .132
 zSize = .52; %.365 or .361
 Tiff2Data (rawTifPath,binTifPath,aggsFilePath,slicedAggsFilePath, xySize, zSize);
 end
-%}
+%
 
 for sampleNumber = 1:10
 iterateSamples('paphz_d4_',sampleNumber,.415,.52)
@@ -26,13 +26,19 @@ end
 for sampleNumber = 1:9
 iterateSamples('pawt_d4_',sampleNumber,.208,.52)
 end
-
+%}
+iterateSamples('phz_d4_',14,.208,.52)
 function iterateSamples(sampleName, sampleNum,xy,z)
-
-rawTifPathBase = '/run/user/937561/gvfs/smb-share:server=130.207.66.142,share=raw_data/Confocal/Carolyn/2020/Chronic wounds/Tiff Stacks New/';
+rawTifPathBase = '/Volumes/raw_data/Confocal/Carolyn/2020/Chronic wounds/Tiff Stacks New/';%Laptop
+binTifPathBase = '/Volumes/raw_data/Confocal/Carolyn/2020/Chronic wounds/Binary Images/';
+aggsFilePathBase = '/Volumes/raw_data/Confocal/Carolyn/2020/Chronic wounds/Aggregate lists/'; %names are different
+slicedAggsFilePathBase = '/Volumes/raw_data/Confocal/Carolyn/2020/Chronic wounds/Results per slice/'; %names are different
+%{
+rawTifPathBase = '/run/user/937561/gvfs/smb-share:server=130.207.66.142,share=raw_data/Confocal/Carolyn/2020/Chronic wounds/Tiff Stacks New/';%Thor
 binTifPathBase = '/run/user/937561/gvfs/smb-share:server=130.207.66.142,share=raw_data/Confocal/Carolyn/2020/Chronic wounds/Binary Images/';
 aggsFilePathBase = '/run/user/937561/gvfs/smb-share:server=130.207.66.142,share=raw_data/Confocal/Carolyn/2020/Chronic wounds/Aggregate lists/'; %names are different
 slicedAggsFilePathBase = '/run/user/937561/gvfs/smb-share:server=130.207.66.142,share=raw_data/Confocal/Carolyn/2020/Chronic wounds/Results per slice/'; %names are different
+%}
 rawTifPath = [rawTifPathBase,sampleName,GetNum(sampleNum),'/'];
 binTifPath = [binTifPathBase,sampleName,GetNum(sampleNum),'/'];
[…]

### 2021-09-07 R/PropOcFunctions2.1.R

@@ -4,7 +4,7 @@
 #'
 #'these functions were optimized for capped spheres on 10/14/19
 #'
-SlicesTo3D<-function(filesList,channel,side){
+SlicesTo3D<-function(filesList){
   image1<-readTiff(filesList[1])#read first image to get its dimensions
   image3D <- array(0, c(image1@size[1], image1@size[2], length(filesList)))#preallocate array for image given using image dimensions
   for(i in 1:length(filesList)){#keep in mind that it is not zero-index

### 2021-09-09 R/AggregateCounts.Rmd
added stats and simplified figure 1D and 2D

@@
 aggregateListSummaryCondition<-aggregateListSummaryReplicate %>% group_by(Species,SaStrain,Strain,Culture,TimePoint,Condition,Region) %>% summarise(MeanAggs= mean(Aggs), MeanBiomassLog = mean(log10(Biomass)), SEBiomassLog = std.error((log10(Biomass))), MeanMeanAggSize = mean(MeanAggSize), SEMeanAggSize = std.error(MeanAggSize))
-```
-```{r Overview Plots}
+
+#T-tests for biomass and Aggs
+TtestTable<-name <- function(dataPoint) {data <-data.frame(dataPoint$data.name, dataPoint$p.value)}
+##WT co vs mono comparisons
+###Biomass and Aggs of Pa mono vs co
+PaWtmono<-aggregateListSummaryReplicate %>% filter(Species == "P. aeruginosa" & TimePoint == "Day 4", Strain == "wt", Culture == "mono")
+PaWtco<-aggregateListSummaryReplicate %>% filter(Species == "P. aeruginosa" & TimePoint == "Day 4", Strain == "wt", Culture == "co")
+PaWtonovsCoBiomassTtest<-t.test(x = PaWtmono$biomass, y = PaWtco$biomass, paired = F)
+PaWtonovsCoAggsTtest<-t.test(x = PaWtmono$Aggs, y = PaWtco$Aggs, paired = F)
+###Biomass and Aggs of Sa mono vs co
+SaWtmono<-aggregateListSummaryReplicate %>% filter(Species == "S. aureus" & TimePoint == "Day 4", Strain == "Sa", Culture == "mono")
+SaWtco<-aggregateListSummaryReplicate %>% filter(Species == "S. aureus" & TimePoint == "Day 4", Strain == "wt", Culture == "co")
+SaWtonovsCoBiomassTtest<-t.test(x = SaWtmono$biomass, y = SaWtco$biomass, paired = F)
+SaWtonovsCoAggsTtest<-t.test(x = SaWtmono$Aggs, y = SaWtco$Aggs, paired = F)
+###Biomass and Aggs of Pa core vs edge co-culture
+PaWtCoEdge<-aggregateListSummaryReplicate %>% filter(Species == "P. aeruginosa"&TimePoint =="Day 4",Strain == "wt",Culture == "co",Region == "edge")
+PaWtcoCore<-aggregateListSummaryReplicate %>% filter(Species == "P. aeruginosa"&TimePoint =="Day 4",Strain == "wt",Culture == "co",Region == "core")
+PaWtCoEdgevsCoreBiomassTtest<-t.test(x = PaWtCoEdge$biomass, y = PaWtcoCore$biomass, paired = F)
+PaWtCoEdgevsCoreAggsTtest<-t.test(x = PaWtCoEdge$Aggs, y = PaWtcoCore$Aggs, paired = F)
+###Biomass and Aggs of Sa core vs edge co-culture
+SaWtCoEdge<-aggregateListSummaryReplicate %>% filter(Species == "S. aureus"&TimePoint =="Day 4",Strain == "wt",Culture == "co",Region == "edge")
+SaWtcoCore<-aggregateListSummaryReplicate %>% filter(Species == "S. aureus"&TimePoint =="Day 4",Strain == "wt",Culture == "co",Region == "core")
+SaWtCoEdgevsCoreBiomassTtest<-t.test(x = SaWtCoEdge$biomass, y = SaWtcoCore$biomass, paired = F)
+SaWtCoEdgevsCoreAggsTtest<-t.test(x = SaWtCoEdge$Aggs, y = SaWtcoCore$Aggs, paired = F)
+
+tTestFigs1ABData<-list(PaWtonovsCoBiomassTtest,PaWtonovsCoAggsTtest,PaWtCoEdgevsCoreBiomassTtest,PaWtCoEdgevsCoreAggsTtest,
+                       SaWtonovsCoBiomassTtest,SaWtonovsCoAggsTtest,SaWtCoEdgevsCoreBiomassTtest,SaWtCoEdgevsCoreAggsTtest)
+tTestFigs1ABTable<-bind_rows(map(tTestFigs1ABData, TtestTable))
+##co wt vs mutants
+###Biomass and Aggs of Pa wt vs mutants
+PaBiomassAov <- aov(biomass ~ Strain, data = aggregateListSummaryReplicate %>% 
+                           filter(Species == "P. aeruginosa" & TimePoint == "Day 4", Culture == "co"))
+PaAggsAov <- aov(Aggs ~ Strain, data = aggregateListSummaryReplicate %>% 
+                           filter(Species == "P. aeruginosa" & TimePoint == "Day 4", Culture == "co"))
+###Biomass and Aggs of Sa wt vs mutants
+SaBiomassAov <- aov(biomass ~ Strain, data = aggregateListSummaryReplicate %>% 
+                           filter(Species == "S. aureus" & TimePoint == "Day 4", Culture == "co"))
+SaAggsAov <- aov(Aggs ~ Strain, data = aggregateListSummaryReplicate %>% 
+                           filter(Species == "S. aureus" & TimePoint == "Day 4", Culture == "co"))
+summary(PaAggsAov)
+TukeyHSD(PaAggsAov)#wt~pqsL p = 0.06, wt~phz p = 0.003
+summary(SaAggsAov)
+TukeyHSD(SaAggsAov)#wt~pqsL p = 0.03
+
+```
+
+```{r biomass, aggregate number and mean size Plots}
 #Plot agg summary per sample
@@
 ```
+
 ```{r figures 1A,1B and 2A, 2B}
@@
 #####
+
+#Stats for aggregates
+##Mono vs Co
+PaMono5<-HistReplicateSummary %>% filter(Species == "P. aeruginosa" & TimePoint == "Day 4", Strain == "wt", Culture == "mono",LogBin == "(.5, 5]")
+PaCo5<-HistReplicateSummary %>% filter(Species == "P. aeruginosa" & TimePoint == "Day 4", Strain == "wt", Culture == "co",LogBin == "(.5, 5]")
+PaMono10<-HistReplicateSummary %>% filter(Species == "P. aeruginosa" & TimePoint == "Day 4", Strain == "wt", Culture == "mono",LogBin == "(5, 10]")
+PaCo10<-HistReplicateSummary %>% filter(Species == "P. aeruginosa" & TimePoint == "Day 4", Strain == "wt", Culture == "co",LogBin == "(5, 10]")
+PaMono100<-HistReplicateSummary %>% filter(Species == "P. aeruginosa" & TimePoint == "Day 4", Strain == "wt", Culture == "mono",LogBin == "(10, 100]")
+PaCo100<-HistReplicateSummary %>% filter(Species == "P. aeruginosa" & TimePoint == "Day 4", Strain == "wt", Culture == "co",LogBin == "(10, 100]")
+
+PaMonoCo5BiomassTtest <-t.test(x = PaMono5$NormalizedBiomass, y = PaCo5$NormalizedBiomass, paired = F)
+PaMonoCo5FreqTtest    <-t.test(x = PaMono5$NormalizedFrequency, y = PaCo5$NormalizedFrequency, paired = F)
+PaMonoCo10FreqTtest   <-t.test(x = PaMono10$NormalizedFrequency, y = PaCo10$NormalizedFrequency, paired = F)
+PaMonoCo100FreqTtest  <-t.test(x = PaMono100$NormalizedFrequency, y = PaCo100$NormalizedFrequency, paired = F)
+
+SaMono5<-HistReplicateSummary %>% filter(Species == "S. aureus",TimePoint =="Day 4",Strain == "Sa",Culture == "mono",LogBin == "(.5, 5]")
+SaCo5<-HistReplicateSummary %>% filter(Species == "S. aureus"&TimePoint =="Day 4",Strain == "wt",Culture == "co",LogBin == "(.5, 5]")
+SaMono10<-HistReplicateSummary %>% filter(Species == "S. aureus",TimePoint =="Day 4",Strain == "Sa",Culture == "mono",LogBin == "(5, 10]")
+SaCo10<-HistReplicateSummary %>% filter(Species == "S. aureus"&TimePoint =="Day 4",Strain == "wt",Culture == "co",LogBin == "(5, 10]")
+SaMono100<-HistReplicateSummary %>% filter(Species == "S. aureus",TimePoint =="Day 4",Strain == "Sa",Culture == "mono",LogBin == "(10, 100]")
+SaCo100<-HistReplicateSummary %>% filter(Species == "S. aureus"&TimePoint =="Day 4",Strain == "wt",Culture == "co",LogBin == "(10, 100]")
+
+SaMonoCo5BiomassTtest <-t.test(x = SaMono5$NormalizedBiomass, y = SaCo5$NormalizedBiomass, paired = F)
+SaMonoCo5FreqTtest    <-t.test(x = SaMono5$NormalizedFrequency, y = SaCo5$NormalizedFrequency, paired = F)
+SaMonoCo10FreqTtest   <-t.test(x = SaMono10$NormalizedFrequency, y = SaCo10$NormalizedFrequency, paired = F)
+SaMonoCo100FreqTtest  <-t.test(x = SaMono100$NormalizedFrequency, y = SaCo100$NormalizedFrequency, paired = F)
+
+tTestFigs1CDData<-list(PaMonoCo5BiomassTtest,PaMonoCo5FreqTtest,PaMonoCo10FreqTtest,PaMonoCo100FreqTtest,
+                       SaMonoCo5BiomassTtest,SaMonoCo5FreqTtest,SaMonoCo10FreqTtest,SaMonoCo100FreqTtest)
+tTestFigs1CDTable<-bind_rows(map(tTestFigs1CDData, TtestTable))
+### Edge vs Core
+Pawt5E<-HistReplicateSummary%>% filter(Species=="P. aeruginosa",TimePoint=="Day 4",Strain == "wt", Culture == "co",LogBin == "(.5, 5]",Region == "edge")
+Pawt5C<-HistReplicateSummary%>% filter(Species=="P. aeruginosa",TimePoint== "Day 4",Strain == "wt",Culture == "co",LogBin == "(.5, 5]",Region == "core")
+Pawt10E<-HistReplicateSummary%>% filter(Species=="P. aeruginosa",TimePoint== "Day 4",Strain== "wt",Culture == "co",LogBin == "(5, 10]",Region == "edge")
+Pawt10C<-HistReplicateSummary%>% filter(Species=="P. aeruginosa",TimePoint== "Day 4",Strain== "wt",Culture == "co",LogBin == "(5, 10]",Region == "core")
+Pawt100E<-HistReplicateSummary%>% filter(Species=="P. aeruginosa",TimePoint== "Day 4",Strain=="wt",Culture=="co",LogBin == "(10, 100]",Region == "edge")
+Pawt100C<-HistReplicateSummary%>% filter(Species=="P. aeruginosa",TimePoint== "Day 4",Strain=="wt",Culture=="co",LogBin == "(10, 100]",Region == "core")
+
+Sawt5E<-HistReplicateSummary%>%filter(Species == "S. aureus",TimePoint == "Day 4", Strain == "wt", Culture=="co",LogBin =="(.5, 5]",Region == "edge")
+Sawt5C<-HistReplicateSummary%>%filter(Species == "S. aureus",TimePoint == "Day 4", Strain == "wt", Culture=="co",LogBin =="(.5, 5]",Region == "core")
+Sawt10E<-HistReplicateSummary%>%filter(Species == "S. aureus",TimePoint == "Day 4", Strain == "wt", Culture == "co",LogBin == "(5, 10]",Region == "edge")
+Sawt10C<-HistReplicateSummary%>%filter(Species == "S. aureus",TimePoint == "Day 4", Strain == "wt", Culture == "co",LogBin == "(5, 10]",Region == "core")
+Sawt100E<-HistReplicateSummary%>%filter(Species == "S. aureus",TimePoint == "Day 4",Strain == "wt", Culture=="co",LogBin=="(10, 100]",Region== "edge")
+Sawt100C<-HistReplicateSummary %>% filter(Species == "S. aureus",TimePoint=="Day 4",Strain=="wt",Culture == "co",LogBin == "(10, 100]",Region == "core")
+
+Pawt5CorEdBioTtest     <-t.test(x = Pawt5E$NormalizedBiomass, y = Pawt5C$NormalizedBiomass, paired = F)
+Pawt5CorEdFreqTtest    <-t.test(x = Pawt5E$NormalizedFrequency, y = Pawt5C$NormalizedFrequency, paired = F)
+Pawt10CorEdFreqTtest   <-t.test(x = Pawt10E$NormalizedFrequency, y = Pawt10C$NormalizedFrequency, paired = F)
+Pawt100CorEdFreqTtest  <-t.test(x = Pawt100E$NormalizedFrequency, y = Pawt100C$NormalizedFrequency, paired = F)
+
+Sawt5CorEdBioTtest     <-t.test(x = Sawt5E$NormalizedBiomass, y = Sawt5C$NormalizedBiomass, paired = F)
+Sawt5CorEdFreqTtest    <-t.test(x = Sawt5E$NormalizedFrequency, y = Sawt5C$NormalizedFrequency, paired = F)
+Sawt10CorEdFreqTtest   <-t.test(x = Sawt10E$NormalizedFrequency, y = Sawt10C$NormalizedFrequency, paired = F)
+Sawt100CorEdFreqTtest  <-t.test(x = Sawt100E$NormalizedFrequency, y = Sawt100C$NormalizedFrequency, paired = F)
+
+tTestFigs2ABDataCorEdge<-list(Pawt5CorEdBioTtest,Pawt5CorEdFreqTtest,Pawt10CorEdFreqTtest,Pawt100CorEdFreqTtest,
+                       Sawt5CorEdBioTtest,Sawt5CorEdFreqTtest,Sawt10CorEdFreqTtest,Sawt100CorEdFreqTtest)
+
+tTestFigs2ABTableCorEdge<-bind_rows(map(tTestFigs2ABDataCorEdge, TtestTable))
+
+##wt vs mutants
+# Compute the analysis of variance 
+Pabiomass5Aov <- aov(NormalizedBiomass ~ Strain, data = HistReplicateSummary%>%
+                     filter(Species == "P. aeruginosa",TimePoint == "Day 4",Culture == "co",LogBin == "(.5, 5]"))
+Pafrequency5Aov <- aov(NormalizedFrequency ~ Strain, data = HistReplicateSummary%>%
+                       filter(Species == "P. aeruginosa",TimePoint == "Day 4",Culture == "co",LogBin == "(.5, 5]"))
+Pafrequency10Aov <- aov(NormalizedFrequency ~ Strain, data = HistReplicateSummary%>%
+                       filter(Species == "P. aeruginosa",TimePoint == "Day 4",Culture == "co",LogBin == "(5, 10]"))
+Pafrequency100Aov <- aov(NormalizedFrequency ~ Strain, data = HistReplicateSummary%>%
+                       filter(Species == "P. aeruginosa",TimePoint == "Day 4",Culture == "co",LogBin == "(10, 100]"))
+##None of the Pa are significant
+Sabiomass5Aov <- aov(NormalizedBiomass ~ Strain, data = HistReplicateSummary%>%
+                     filter(Species == "S. aureus",TimePoint == "Day 4",Culture == "co",LogBin == "(.5, 5]")) 
+Safrequency5Aov <- aov(NormalizedFrequency ~ Strain, data = HistReplicateSummary%>%
+                       filter(Species == "S. aureus",TimePoint == "Day 4",Culture == "co",LogBin == "(.5, 5]"))
+Safrequency10Aov <- aov(NormalizedFrequency ~ Strain, data = HistReplicateSummary%>%
+                       filter(Species == "S. aureus",TimePoint == "Day 4",Culture == "co",LogBin == "(5, 10]"))
+Safrequency100Aov <- aov(NormalizedFrequency ~ Strain, data = HistReplicateSummary%>%
+                       filter(Species == "S. aureus",TimePoint == "Day 4",Culture == "co",LogBin == "(10, 100]"))
+
+summary(Pabiomass5Aov)
+TukeyHSD(Pabiomass5Aov)
+# Summary of the analysis
+summary(Sabiomass5Aov)#*p = 0.07
+TukeyHSD(Sabiomass5Aov)#*p pqsL-wt 0.077
+summary(Safrequency10Aov)#*p = 0.005
+TukeyHSD(Safrequency10Aov)#*p pqsL-wt 0.003
+
+#now compute comparison edge vs core
+PaPhz5E<-HistReplicateSummary%>% filter(Species=="P. aeruginosa",TimePoint=="Day 4",Strain == "phz", Culture == "co",LogBin == "(.5, 5]",Region == "edge")
+PaPhz5C<-HistReplicateSummary%>% filter(Species=="P. aeruginosa",TimePoint== "Day 4",Strain == "phz",Culture == "co",LogBin == "(.5, 5]",Region == "core")
+PaPhz10E<-HistReplicateSummary%>% filter(Species=="P. aeruginosa",TimePoint== "Day 4",Strain== "phz",Culture == "co",LogBin == "(5, 10]",Region == "edge")
+PaPhz10C<-HistReplicateSummary%>% filter(Species=="P. aeruginosa",TimePoint== "Day 4",Strain== "phz",Culture == "co",LogBin == "(5, 10]",Region == "core")
+PaPhz100E<-HistReplicateSummary%>% filter(Species=="P. aeruginosa",TimePoint== "Day 4",Strain=="phz",Culture=="co",LogBin == "(10, 100]",Region == "edge")
+PaPhz100C<-HistReplicateSummary%>% filter(Species=="P. aeruginosa",TimePoint== "Day 4",Strain=="phz",Culture=="co",LogBin == "(10, 100]",Region == "core")
+PaPqsL5E<-HistReplicateSummary%>% filter(Species=="P. aeruginosa",TimePoint== "Day 4",Strain=="pqsL",Culture == "co",LogBin == "(.5, 5]",Region == "edge")
+PaPqsL5C<-HistReplicateSummary%>% filter(Species=="P. aeruginosa",TimePoint== "Day 4",Strain=="pqsL",Culture == "co",LogBin == "(.5, 5]",Region == "core")
+PaPqsL10E<-HistReplicateSummary%>% filter(Species=="P. aeruginosa",TimePoint=="Day 4",Strain=="pqsL",Culture == "co",LogBin == "(5, 10]",Region == "edge")
+PaPqsL10C<-HistReplicateSummary%>% filter(Species=="P. aeruginosa",TimePoint=="Day 4",Strain =="pqsL",Culture =="co",LogBin == "(5, 10]",Region == "core")
+PaPqsL100E<-HistReplicateSummary%>% filter(Species=="P. aeruginosa",TimePoint=="Day 4",Strain=="pqsL",Culture=="co",LogBin =="(10, 100]",Region == "edge")
+PaPqsL100C<-HistReplicateSummary%>% filter(Species=="P. aeruginosa",TimePoint== "Day 4",Strain=="pqsL",Culture=="co",LogBin=="(10, 100]",Region == "core")
+
+PaPhz5CorEdBioTtest     <-t.test(x = PaPhz5E$NormalizedBiomass, y = PaPhz5C$NormalizedBiomass, paired = F)
+PaPhz5CorEdFreqTtest    <-t.test(x = PaPhz5E$NormalizedFrequency, y = PaPhz5C$NormalizedFrequency, paired = F)
+PaPhz10CorEdFreqTtest   <-t.test(x = PaPhz10E$NormalizedFrequency, y = PaPhz10C$NormalizedFrequency, paired = F)
+PaPhz100CorEdFreqTtest  <-t.test(x = PaPhz100E$NormalizedFrequency, y = PaPhz100C$NormalizedFrequency, paired = F)
+PaPqsL5CorEdBioTtest     <-t.test(x = PaPqsL5E$NormalizedBiomass, y = PaPqsL5C$NormalizedBiomass, paired = F)
+PaPqsL5CorEdFreqTtest    <-t.test(x = PaPqsL5E$NormalizedFrequency, y = PaPqsL5C$NormalizedFrequency, paired = F)
+PaPqsL10CorEdFreqTtest   <-t.test(x = PaPqsL10E$NormalizedFrequency, y = PaPqsL10C$NormalizedFrequency, paired = F)
+PaPqsL100CorEdFreqTtest  <-t.test(x = PaPqsL100E$NormalizedFrequency, y = PaPqsL100C$NormalizedFrequency, paired = F)
+
+SaPhz5E<-HistReplicateSummary %>% filter(Species == "S. aureus" & TimePoint == "Day 4", Strain == "phz", Culture=="co",LogBin =="(.5, 5]",Region == "edge")
+SaPhz5C<-HistReplicateSummary %>% filter(Species == "S. aureus" & TimePoint == "Day 4", Strain == "phz", Culture=="co",LogBin =="(.5, 5]",Region == "core")                                        
+SaPqsL5E<-HistReplicateSummary %>% filter(Species == "S. aureus" & TimePoint == "Day 4", Strain == "pqsL", Culture == "co",LogBin == "(.5, 5]",Region == "edge")
+SaPqsL5C<-HistReplicateSummary %>% filter(Species == "S. aureus" & TimePoint == "Day 4", Strain == "pqsL", Culture == "co",LogBin == "(.5, 5]",Region == "core")
+SaPhz10E<-HistReplicateSummary %>% filter(Species == "S. aureus" & TimePoint == "Day 4", Strain == "phz", Culture == "co",LogBin == "(5, 10]",Region == "edge")
+SaPhz10C<-HistReplicateSummary %>% filter(Species == "S. aureus" & TimePoint == "Day 4", Strain == "phz", Culture == "co",LogBin == "(5, 10]",Region == "core")
+SaPqsL10E<-HistReplicateSummary %>% filter(Species == "S. aureus" & TimePoint == "Day 4", Strain == "pqsL", Culture == "co",LogBin == "(5, 10]",Region == "edge")
+SaPqsL10C<-HistReplicateSummary %>% filter(Species == "S. aureus" & TimePoint == "Day 4", Strain == "pqsL", Culture == "co",LogBin == "(5, 10]",Region == "core")
+SaPhz100E<-HistReplicateSummary %>% filter(Species == "S. aureus" & TimePoint == "Day 4", Strain == "phz", Culture == "co",LogBin == "(10, 100]",Region == "edge")
+SaPhz100C<-HistReplicateSummary %>% filter(Species == "S. aureus" & TimePoint == "Day 4", Strain == "phz", Culture == "co",LogBin == "(10, 100]",Region == "core")
+SaPqsL100E<-HistReplicateSummary %>% filter(Species == "S. aureus" & TimePoint == "Day 4", Strain == "pqsL", Culture == "co",LogBin == "(10, 100]",Region == "edge")
+SaPqsL100C<-HistReplicateSummary %>% filter(Species == "S. aureus" & TimePoint == "Day 4", Strain == "pqsL", Culture == "co",LogBin == "(10, 100]",Region == "core")
+SaPhz5CorEdBioTtest     <-t.test(x = SaPhz5E$NormalizedBiomass, y = SaPhz5C$NormalizedBiomass, paired = F)
+SaPhz5CorEdFreqTtest    <-t.test(x = SaPhz5E$NormalizedFrequency, y = SaPhz5C$NormalizedFrequency, paired = F)
+SaPhz10CorEdFreqTtest   <-t.test(x = SaPhz10E$NormalizedFrequency, y = SaPhz10C$NormalizedFrequency, paired = F)
+SaPhz100CorEdFreqTtest  <-t.test(x = SaPhz100E$NormalizedFrequency, y = SaPhz100C$NormalizedFrequency, paired = F)
+SaPqsL5CorEdBioTtest     <-t.test(x = SaPqsL5E$NormalizedBiomass, y = SaPqsL5C$NormalizedBiomass, paired = F)
+SaPqsL5CorEdFreqTtest    <-t.test(x = SaPqsL5E$NormalizedFrequency, y = SaPqsL5C$NormalizedFrequency, paired = F)
+SaPqsL10CorEdFreqTtest   <-t.test(x = SaPqsL10E$NormalizedFrequency, y = SaPqsL10C$NormalizedFrequency, paired = F)
+SaPqsL100CorEdFreqTtest  <-t.test(x = SaPqsL100E$NormalizedFrequency, y = SaPqsL100C$NormalizedFrequency, paired = F)
+
+tTestFigs2CDData<-list(PaPhz5CorEdBioTtest,PaPhz5CorEdFreqTtest,PaPhz10CorEdFreqTtest,PaPhz100CorEdFreqTtest,
+                       PaPqsL5CorEdBioTtest,PaPqsL5CorEdFreqTtest,PaPqsL10CorEdFreqTtest,PaPqsL100CorEdFreqTtest,
+                       SaPhz5CorEdBioTtest,SaPhz5CorEdFreqTtest,SaPhz10CorEdFreqTtest,SaPhz100CorEdFreqTtest,
+                       SaPqsL5CorEdBioTtest,SaPqsL5CorEdFreqTtest,SaPqsL10CorEdFreqTtest,SaPqsL100CorEdFreqTtest)
+
+tTestFigs2CDTable<-bind_rows(map(tTestFigs2CDData, TtestTable))
+
 ```
@@
 ggplot()+
-    geom_point(data = rep.df %>% filter(TimePoint=="Day 4"),
-                aes(x=as.factor(Aggregation),y=.data[[y_var]], color =.data[[colorStrain]], shape = Region),
+    geom_point(data = rep.df %>% filter(TimePoint=="Day 4" & Aggregation == "Planktonic"),
+                aes(x=.data[[facet]],y=.data[[y_var]], color =.data[[colorStrain]], shape = Region),
                position = position_jitterdodge(jitter.height = 0, jitter.width = .3,dodge.width = 0.75),size=1)+
-    geom_point(data = region.df%>% filter(TimePoint=="Day 4"),
-               aes(x=as.factor(Aggregation),y=.data[[y_var]], color =.data[[colorStrain]],shape = Region),
+    geom_point(data = region.df%>% filter(TimePoint=="Day 4"& Aggregation == "Planktonic"),
+               aes(x=.data[[facet]],y=.data[[y_var]], color =.data[[colorStrain]],shape = Region),
                size=3, position = position_dodge(width = .75) )+
-    geom_point(data = cond.df%>% filter(TimePoint=="Day 4"),
-               aes(x=as.factor(Aggregation),y=.data[[y_var]],  color =.data[[colorStrain]]),size=4, shape = 3,position = position_dodge(width = .75) )+
+    geom_point(data = cond.df%>% filter(TimePoint=="Day 4"& Aggregation == "Planktonic"),
+               aes(x=.data[[facet]],y=.data[[y_var]],  color =.data[[colorStrain]]),size=4, shape = 3,position = position_dodge(width = .75) )+
     scale_y_log10(breaks = c(100, 10, 1, .1, .01), labels = c(100, 10, 1, .1, .01))+
-    facet_grid(.~.data[[facet]])+
+    #facet_grid(.~.data[[facet]])+
     scale_shape_manual(values=c(16, 1))+
     ggtitle(title)+
-    labs(y = paste("Biomass contribution (%)"),x = bquote(paste("Aggregate Volume (", mu*"m"^3*")")))+
+    labs(y = expression(atop("Planktonic cells", "biomass contribution (%)")))+
+    scale_x_discrete(name ="", breaks = c("P. aeruginosa","S. aureus"), 
+                   labels = c(expression(italic("P. aeruginosa")), 
+                              expression(italic("S. aureus"))))+
     scale_color_brewer(palette = "Set1")+
@@
              plankAggHistCondReg%>% filter(Condition == "Sa mono" |Condition == "wt co"|Condition == "wt mono"),
-             "AgPlNormBiomass", "Normalized Biomass Contribution", "Culture","Species")
+             "AgPlNormBiomass", "Biomass from planktonic cells", "Culture","Species")
 
@@
              plankAggHistCondReg%>% filter(Culture == "co"),
-             "AgPlNormBiomass", "Normalized Biomass Contribution", "Strain","Species")
+             "AgPlNormBiomass", "Biomass from planktonic cells", "Strain","Species")
 

### 2021-09-09 R/PropOc Data 3D.Rmd
Enrichment Distance Stats

@@
 propOcMidDensMetaLabel<-metaData.df %>%  merge(propOcMidDensitylabeled, by = "SampleCode")
-
-#include Region
+#####
+#Calculate Stats
+##include Region
 propOcMidDensityStatsRegion<-propOcMidDensMetaLabel %>% ungroup() %>% group_by(Condition,Culture,Strain,TimePoint,Region, Distance, Relation) %>% summarize(meanValue = mean(Value), sdValue = std.error(Value), medianValue = median(Value))
-#exclude region
+##exclude region
 propOcMidDensityStats<-propOcMidDensMetaLabel %>% ungroup() %>% group_by(Condition,Culture,Strain,TimePoint,Distance, Relation) %>% summarize(meanValue = mean(Value), sdValue = std.error(Value), medianValue = median(Value))
@@
 PlotMeanMidDensityPOCenterRegion()
+#####
 #Calculate empty space
@@
 
+#####
 #Calculate Enrichment
@@
 #It's unclear how to deal with the issue of multiple enrichment distances, but I think doing a weighted mean makes the most sense:
+#THIS is the one used for stats
 pOEnrMetaClean<-pOEnrMeta %>% group_by(SampleCode,Condition,TimePoint, Region, Relation)%>%summarise(WmeanDist =weighted.mean(Distance, Density))
+pOEnrMetaClean$CondRegion <- paste0(pOEnrMetaClean$Condition, "-",pOEnrMetaClean$Region)
+#####
+#Stats
+PaSaEnDi.Aov <- aov(WmeanDist ~ Condition, data = pOEnrMetaClean%>%
+                     filter(Relation == "Pa->Sa",TimePoint == "Day 4"))
+SaPaEnDi.Aov <- aov(WmeanDist ~ Condition, data = pOEnrMetaClean%>%
+                       filter(Relation == "Sa->Pa",TimePoint == "Day 4"))
+
+PaSaEnDiRgn.Aov <- aov(WmeanDist ~ CondRegion, data = pOEnrMetaClean%>%
+                       filter(Relation == "Pa->Sa",TimePoint == "Day 4"))
+SapaEnDiRgn.Aov <- aov(WmeanDist ~ CondRegion, data = pOEnrMetaClean%>%
+                       filter(Relation == "Sa->Pa",TimePoint == "Day 4"))
+# Summary of the analysis #only showing significant values
+summary(PaSaEnDi.Aov)#*p = 0.03
+TukeyHSD(PaSaEnDi.Aov)#p wt~pqsL = 0.03
+summary(SaPaEnDi.Aov)#nope
+summary(PaSaEnDiRgn.Aov)#*p = 0.08
+TukeyHSD(PaSaEnDiRgn.Aov)#p wt-edge~pqsL-core = 0.04
+summary(SapaEnDiRgn.Aov)#nope!
+
 #now calculate the Mean per condition:
@@
                             pOEnrMetaClean %>% filter(TimePoint == "Day 4", Relation == "Pa->Sa", TimePoint == "Day 4"))
-
-#original figure 
+#####
+#original figures
+##no region
 ggplot()+
@@
     panel_border() 
-
+##include Region
 ggplot()+

### 2021-09-09 R/AggregateCounts.Rmd
Finished stats and sent to Marvin

@@
 TukeyHSD(SaAggsAov)#wt~pqsL p = 0.03
+###Core vs edge within mutants
+PaPqsLmassE<-aggregateListSummaryReplicate %>% filter(Species =="P. aeruginosa",TimePoint =="Day 4",Strain == "pqsL",Culture == "co",Region == "edge")
+PaPqsLmassC<-aggregateListSummaryReplicate %>% filter(Species =="P. aeruginosa",TimePoint =="Day 4",Strain == "pqsL",Culture == "co",Region == "core")
+PaPhzmassE<-aggregateListSummaryReplicate %>% filter(Species == "P. aeruginosa",TimePoint =="Day 4",Strain == "phz",Culture == "co",Region == "edge")
+PaPhzmassC<-aggregateListSummaryReplicate %>% filter(Species == "P. aeruginosa",TimePoint =="Day 4",Strain == "phz",Culture == "co",Region == "core")
+
+SaPqsLmassE<-aggregateListSummaryReplicate %>% filter(Species =="S. aureus",TimePoint =="Day 4",Strain == "pqsL",Culture == "co",Region == "edge")
+SaPqsLmassC<-aggregateListSummaryReplicate %>% filter(Species =="S. aureus",TimePoint =="Day 4",Strain == "pqsL",Culture == "co",Region == "core")
+SaPhzmassE<-aggregateListSummaryReplicate %>% filter(Species == "S. aureus",TimePoint =="Day 4",Strain == "phz",Culture == "co",Region == "edge")
+SaPhzmassC<-aggregateListSummaryReplicate %>% filter(Species == "S. aureus",TimePoint =="Day 4",Strain == "phz",Culture == "co",Region == "core")
+
+PaPqsLCoEdgevsCoreBiomassTtest<-t.test(x = PaPqsLmassE$biomass, y = PaPqsLmassC$biomass, paired = F)
+PaPqsLCoEdgevsCoreAggsTtest<-t.test(x = PaPqsLmassE$Aggs, y = PaPqsLmassC$Aggs, paired = F)
+PaPhzCoEdgevsCoreBiomassTtest<-t.test(x = PaPhzmassE$biomass, y = PaPhzmassC$biomass, paired = F)
+PaPhzCoEdgevsCoreAggsTtest<-t.test(x = PaPhzmassE$Aggs, y = PaPhzmassC$Aggs, paired = F)
+
+SaPqsLCoEdgevsCoreBiomassTtest<-t.test(x = SaPqsLmassE$biomass, y = SaPqsLmassC$biomass, paired = F)
+SaPqsLCoEdgevsCoreAggsTtest<-t.test(x = SaPqsLmassE$Aggs, y = SaPqsLmassC$Aggs, paired = F)
+SaPhzCoEdgevsCoreBiomassTtest<-t.test(x = SaPhzmassE$biomass, y = SaPhzmassC$biomass, paired = F)
+SaPhzCoEdgevsCoreAggsTtest<-t.test(x = SaPhzmassE$Aggs, y = SaPhzmassC$Aggs, paired = F)
+
+tTestFigs2ABDataCvsE<-list(PaPqsLCoEdgevsCoreBiomassTtest,PaPqsLCoEdgevsCoreAggsTtest,PaPhzCoEdgevsCoreBiomassTtest,PaPhzCoEdgevsCoreAggsTtest,
+                           SaPqsLCoEdgevsCoreBiomassTtest,SaPqsLCoEdgevsCoreAggsTtest,SaPhzCoEdgevsCoreBiomassTtest,SaPhzCoEdgevsCoreAggsTtest)
+tTestFigs2ABTableCvsE<-bind_rows(map(tTestFigs1ABDataCvsE, TtestTable))
 
@@
 
-#Stats for aggregates
+#Stats for aggregate frequency and biomass
+#####
 ##Mono vs Co
+###
 PaMono5<-HistReplicateSummary %>% filter(Species == "P. aeruginosa" & TimePoint == "Day 4", Strain == "wt", Culture == "mono",LogBin == "(.5, 5]")
@@
 tTestFigs1CDTable<-bind_rows(map(tTestFigs1CDData, TtestTable))
-### Edge vs Core
+### Edge vs Core only co-cultures
+#####
 Pawt5E<-HistReplicateSummary%>% filter(Species=="P. aeruginosa",TimePoint=="Day 4",Strain == "wt", Culture == "co",LogBin == "(.5, 5]",Region == "edge")
@@
 
-tTestFigs2ABDataCorEdge<-list(Pawt5CorEdBioTtest,Pawt5CorEdFreqTtest,Pawt10CorEdFreqTtest,Pawt100CorEdFreqTtest,
+tTestFigs1CDDataCorEdge<-list(Pawt5CorEdBioTtest,Pawt5CorEdFreqTtest,Pawt10CorEdFreqTtest,Pawt100CorEdFreqTtest,
                        Sawt5CorEdBioTtest,Sawt5CorEdFreqTtest,Sawt10CorEdFreqTtest,Sawt100CorEdFreqTtest)
 
-tTestFigs2ABTableCorEdge<-bind_rows(map(tTestFigs2ABDataCorEdge, TtestTable))
+tTestFigs1CDTableCorEdge<-bind_rows(map(tTestFigs1CDDataCorEdge, TtestTable))
 
@@
 
-summary(Pabiomass5Aov)
-TukeyHSD(Pabiomass5Aov)
-# Summary of the analysis
+# Summary of the analysis #only showing significant values
 summary(Sabiomass5Aov)#*p = 0.07
@@
 
+#bundling up bin and edge
+HistReplicateSummary$StrainRegion <- paste(HistReplicateSummary$Region, "-", HistReplicateSummary$Strain)
+
+Pabiomass5AovSR <- aov(NormalizedBiomass ~ StrainRegion, data = HistReplicateSummary%>%
+                     filter(Species == "P. aeruginosa",TimePoint == "Day 4",Culture == "co",LogBin == "(.5, 5]"))
+Pafrequency5AovSR <- aov(NormalizedFrequency ~ StrainRegion, data = HistReplicateSummary%>%
+                       filter(Species == "P. aeruginosa",TimePoint == "Day 4",Culture == "co",LogBin == "(.5, 5]"))
+Pafrequency10AovSR <- aov(NormalizedFrequency ~ StrainRegion, data = HistReplicateSummary%>%
+                       filter(Species == "P. aeruginosa",TimePoint == "Day 4",Culture == "co",LogBin == "(5, 10]"))
+Pafrequency100AovSR <- aov(NormalizedFrequency ~ StrainRegion, data = HistReplicateSummary%>%
+                       filter(Species == "P. aeruginosa",TimePoint == "Day 4",Culture == "co",LogBin == "(10, 100]"))
+##None of the Pa are significant
+Sabiomass5AovSR <- aov(NormalizedBiomass ~ StrainRegion, data = HistReplicateSummary%>%
+                     filter(Species == "S. aureus",TimePoint == "Day 4",Culture == "co",LogBin == "(.5, 5]")) 
+Safrequency5AovSR <- aov(NormalizedFrequency ~ StrainRegion, data = HistReplicateSummary%>%
+                       filter(Species == "S. aureus",TimePoint == "Day 4",Culture == "co",LogBin == "(.5, 5]"))
+Safrequency10AovSR <- aov(NormalizedFrequency ~ StrainRegion, data = HistReplicateSummary%>%
+                       filter(Species == "S. aureus",TimePoint == "Day 4",Culture == "co",LogBin == "(5, 10]"))
+Safrequency100AovSR <- aov(NormalizedFrequency ~ StrainRegion, data = HistReplicateSummary%>%
+                       filter(Species == "S. aureus",TimePoint == "Day 4",Culture == "co",LogBin == "(10, 100]"))
+summary(Sabiomass5AovSR)#
+TukeyHSD(Sabiomass5AovSR)#*p core wt vs core pqsL 0.08, edge phz vs core pqsL 0.04, edge wt core pqsL .08
+summary(Safrequency5AovSR)# nope
+summary(Safrequency10AovSR)#yup
+TukeyHSD(Safrequency10AovSR)# core pqsL VS core wt 0.01, vs edge phz 0.03 edge pqsL 0.06, edge wt 0.03 
+summary(Safrequency100AovSR)
+
 #now compute comparison edge vs core
+##Pa
 PaPhz5E<-HistReplicateSummary%>% filter(Species=="P. aeruginosa",TimePoint=="Day 4",Strain == "phz", Culture == "co",LogBin == "(.5, 5]",Region == "edge")
@@
 PaPqsL100CorEdFreqTtest  <-t.test(x = PaPqsL100E$NormalizedFrequency, y = PaPqsL100C$NormalizedFrequency, paired = F)
-
+##Sa
 SaPhz5E<-HistReplicateSummary %>% filter(Species == "S. aureus" & TimePoint == "Day 4", Strain == "phz", Culture=="co",LogBin =="(.5, 5]",Region == "edge")
@@
 
-tTestFigs2CDTable<-bind_rows(map(tTestFigs2CDData, TtestTable))
+tTestFigs2CDTableCorevsEdge<-bind_rows(map(tTestFigs2CDData, TtestTable))
 
@@
 
+plankAggHistRepStats<-plankAggHistRep %>%
+  group_by(Species,SaStrain,Strain,Culture,TimePoint,Condition,Aggregation)%>%
+  summarize(MeanFreq = mean(AgPlNormFrequency), MeanBiomass = mean(AgPlNormBiomass))
+
 ##Normalize using Condition 
@@
 }
-PlotAggPlank<-function(rep.df,cond.df,region.df, y_var, title, colorStrain, facet){
+PlotAggPlank<-function(rep.df, y_var, title, colorStrain, facet){
 ggplot()+
@@
                position = position_jitterdodge(jitter.height = 0, jitter.width = .3,dodge.width = 0.75),size=1)+
-    geom_point(data = region.df%>% filter(TimePoint=="Day 4"& Aggregation == "Planktonic"),
-               aes(x=.data[[facet]],y=.data[[y_var]], color =.data[[colorStrain]],shape = Region),
-               size=3, position = position_dodge(width = .75) )+
-    geom_point(data = cond.df%>% filter(TimePoint=="Day 4"& Aggregation == "Planktonic"),
-               aes(x=.data[[facet]],y=.data[[y_var]],  color =.data[[colorStrain]]),size=4, shape = 3,position = position_dodge(width = .75) )+
-    scale_y_log10(breaks = c(100, 10, 1, .1, .01), labels = c(100, 10, 1, .1, .01))+
+    #geom_point(data = region.df%>% filter(TimePoint=="Day 4"& Aggregation == "Planktonic"),
+    #           aes(x=.data[[facet]],y=.data[[y_var]], color =.data[[colorStrain]],shape = Region),
+    #           size=3, position = position_dodge(width = .75) )+
+    #geom_point(data = cond.df%>% filter(TimePoint=="Day 4"& Aggregation == "Planktonic"),
+    #           aes(x=.data[[facet]],y=.data[[y_var]],  color =.data[[colorStrain]]),size=4, shape = 3,position = position_dodge(width = .75) )+
+    #scale_y_log10(breaks = c(100, 10, 1, .1, .01), labels = c(100, 10, 1, .1, .01))+
     #facet_grid(.~.data[[facet]])+
@@
 PlotAggPlank(plankAggHistRep%>% filter(Condition == "Sa mono" |Condition == "wt co"|Condition == "wt mono"),
-             plankAggHistCond%>% filter(Condition == "Sa mono" |Condition == "wt co"|Condition == "wt mono"),
-             plankAggHistCondReg%>% filter(Condition == "Sa mono" |Condition == "wt co"|Condition == "wt mono"),
+             #plankAggHistCond%>% filter(Condition == "Sa mono" |Condition == "wt co"|Condition == "wt mono"),
+             #plankAggHistCondReg%>% filter(Condition == "Sa mono" |Condition == "wt co"|Condition == "wt mono"),
              "AgPlNormBiomass", "Biomass from planktonic cells", "Culture","Species")
+
+test<-plankAggHistRep%>% filter(Condition == "Sa mono" |Condition == "wt co"|Condition == "wt mono") %>% filter(TimePoint=="Day 4" & Aggregation == "Planktonic")
 

### 2021-09-20 R/AggregateCounts.Rmd
added figures for columns instead of scatter plots

@@
 
+PlotHistSumCols<- function(df, df2, fill){
+ggplot()+
+  geom_col(data = df,aes(x=as.factor(LogBin),y=NormalizedFrequency, fill = .data[[fill]]),
+           size=3,position = position_dodge( width = .9))+
+  geom_point(data = df2,
+                aes(x=as.factor(LogBin),y=NormalizedFrequency, fill = .data[[fill]]),
+               position = position_jitterdodge(jitter.height = 0, jitter.width = .3,dodge.width = 0.75),size=1, shape = 1,show.legend = FALSE)+
+  scale_y_continuous(limits = c(0,103),expand = expand_scale(mult = c(0, 0)))+
+  facet_grid(.~Species)+
+  scale_fill_grey()+
+  labs(y = paste("Frequency (%)"),x = bquote(paste("Aggregate Volume (", mu*"m"^3*")")))+
+  theme_cowplot()+
+  theme(plot.title = element_text(hjust = 0.5),strip.text = element_text(size = 9, face = "italic",margin = margin(.1,0,.1,0, "cm")),
+        strip.background = element_rect(color="black", fill="white", size=.5, linetype="solid"),
+        axis.title.x = element_text(margin = margin(0,0,0,0),size=13),axis.text.x = element_text(margin = margin(1,0,0,0),size=13),
+        axis.title.y = element_text(margin = margin(0,4,0,0),size=13),axis.text.y = element_text(margin = margin(0,0,2,0),size=11))
+}
+
+PlotHistSumCols(HistCondRegionSum%>% filter(Condition == "Sa mono" |Condition == "wt co"|Condition == "wt mono") %>% filter(TimePoint=="Day 4"),
+                  HistReplicateSummary%>% filter(Condition == "Sa mono" |Condition == "wt co"|Condition == "wt mono") %>%  
+                    filter(TimePoint=="Day 4"), "Culture")#for mono vs co
+PlotHistSumCols(HistCondRegionSum%>% filter(Culture == "co") %>% filter(TimePoint=="Day 4"),
+                  HistReplicateSummary%>% filter(Culture == "co")%>%  filter(TimePoint=="Day 4"), "Strain")#for mono vs co
+
 #Plot normalized Biomass per sample
@@
 
+#this is for the defense presentation
+PlotAggsPlankcols<- function(df, df2, fill){
+ggplot()+
+  geom_col(data = df,aes(x=Aggregation,y=AgPlNormBiomass, fill = .data[[fill]]),
+           size=3,position = position_dodge( width = .9))+
+  geom_point(data = df2,
+                aes(x=Aggregation,y=AgPlNormBiomass, fill = .data[[fill]]),
+               position = position_jitterdodge(jitter.height = 0, jitter.width = .3,dodge.width = 0.75),size=1, shape = 1,show.legend = FALSE)+
+  scale_y_continuous(limits = c(0,103),expand = expand_scale(mult = c(0, 0)))+
+  facet_grid(.~Species)+
+  scale_fill_grey()+
+  labs(title = '', x = "", y = "Biomass contribution (%)")+
+  theme_cowplot()+
+  theme(plot.title = element_text(hjust = 0.5),strip.text = element_text(size = 9, face = "italic",margin = margin(.1,0,.1,0, "cm")),
+        strip.background = element_rect(color="black", fill="white", size=.5, linetype="solid"),
+        axis.title.x = element_text(margin = margin(0,0,0,0),size=13),axis.text.x = element_text(margin = margin(1,0,0,0),size=13),
+        axis.title.y = element_text(margin = margin(0,4,0,0),size=13),axis.text.y = element_text(margin = margin(0,0,2,0),size=11))
+}
+
+PlotAggsPlankcols(plankAggHistCondReg%>% filter(Condition == "Sa mono" |Condition == "wt co"|Condition == "wt mono") %>% filter(TimePoint=="Day 4"),
+                  plankAggHistRep%>% filter(Condition == "Sa mono" |Condition == "wt co"|Condition == "wt mono") %>%  
+                    filter(TimePoint=="Day 4"), "Culture")#for mono vs co
+PlotAggsPlankcols(plankAggHistCondReg%>% filter(Culture == "co") %>% filter(TimePoint=="Day 4"),
+                  plankAggHistRep%>% filter(Culture == "co")%>%  filter(TimePoint=="Day 4"), "Strain")#for mono vs co
+
 #these are the other versions

### 2021-11-29 R/AggregateCounts.Rmd
Transfered z-slice data to DeepSpatialAnalysis script

@@
 
-```{r biomass per slice}
-#this was taken from "Microscopy data clean.Rmd" 
-GetSliceData<-function(){#import all experiments at once
-  folder<- '/Volumes/raw_data/Confocal/Carolyn/2020/Chronic wounds/Results per slice'
-   fileList<-list.files(path = folder, full.names = TRUE)
-   growthDf<-data.frame()
-   for (aggList in 1:length(fileList)){
-     fileName<-str_split(basename(fileList[aggList]), "\\.")[[1]][1]#this selects the base file name and removes the ".csv"
-     attrList<-str_split(fileName,"_")[[1]]
-     growthDf<-rbind(growthDf,ReadSliceFile(fileList[aggList],attrList[2],attrList[1],attrList[3], fileName))
-     }
-   return(growthDf)
-}
-
-ReadSliceFile<-function(file, timepoint, condition, replicate, sampleCode){#make a dataframe of the aggregate size list and add experimental parameters
-  print(file)
-   datos <-read.csv(file, header = F)  
-   colnames(datos)<-c('Biomass', 'Channel', 'Slice') 
-   datos<-datos %>% mutate(TimePoint = timepoint) 
-   datos<-datos %>% mutate(Condition = condition)
-   datos<-datos %>% mutate(Replicate = replicate)
-   datos<-datos %>% mutate(SampleCode = sampleCode)
-   datos$Replicate<-as.factor(datos$Replicate)
-   datos$Condition<-as.factor(datos$Condition)
-   datos$TimePoint<-as.factor(datos$TimePoint)
-   datos$SampleCode<-as.factor(datos$SampleCode)
-   return(datos)
-}
-
-#Input data
-#####
-#get data from csv file
-slicedData<-GetSliceData()
- #get metadata
-metaData.df <-read.csv('/Volumes/raw_data/Confocal/Carolyn/2020/Chronic wounds/images metadata.csv', header = TRUE)
-metaData.df$SampleCode<-as.factor(metaData.df$SampleCode)
-
-#merge files
-metaData.df<-metaData.df %>% select(SampleCode, mouse, Position, size, Region, Zdim, xyDim,xySize)
-sliceDataMeta<-metaData.df %>%  merge(slicedData, by = "SampleCode")
-#clean up
-remove <- bind_rows(sliceDataMeta %>% filter(Channel == 2 & Condition == "mono"),
-                    sliceDataMeta %>% filter(Channel == 1 & Condition == "pawt"),
-                    sliceDataMeta %>% filter(Channel == 1 & Condition == "paphz"),
-                    sliceDataMeta %>% filter(Channel == 1 & Condition == "papqsL"))
-
-sliceDataMeta <- anti_join(sliceDataMeta, remove)
-
-sliceDataMeta<-sliceDataMeta %>% filter(!SampleCode == "mono_d1_03")
-sliceDataMeta<-sliceDataMeta %>% filter(!SampleCode == "phz_d4_14") #didnt make it to this dataset but still making sure
-sliceDataMeta<-sliceDataMeta %>% filter(!SampleCode == "pqsL_d4_02")
-sliceDataMeta<-sliceDataMeta %>% filter(!SampleCode == "pqsL_d4_04")
-sliceDataMeta<-sliceDataMeta %>% filter(!SampleCode == "pqsL_d4_10")
-sliceDataMeta<-sliceDataMeta %>% filter(!SampleCode == "wt_d4_07")
-sliceDataMeta<-sliceDataMeta %>% filter(!SampleCode == "papqsL_d4_02")
-sliceDataMeta<-sliceDataMeta %>% filter(!SampleCode == "pawt_d4_05")
-sliceDataMeta<-sliceDataMeta %>% filter(!SampleCode == "phz_d4_06")
-
-#rename variables
-sliceDataMeta<-sliceDataMeta %>% mutate(Species = recode(Channel,"1" ='S. aureus',"2" ='P. aeruginosa',"3" ='host'))
-sliceDataMeta$Condition<- factor(sliceDataMeta$Condition, levels = c("mono", "pawt","papqsL", "paphz", "wt", "pqsL", "phz"),
-                                  labels = c('Sa mono', 'Pa wt mono','pqsL mono','phz mono','wt co', 'pqsL co', 'phz co'))
-sliceDataMeta$TimePoint <- factor(sliceDataMeta$TimePoint, levels = c("d1", "d4"),labels = c('Day 1','Day 4'))
-sliceDataMeta<-sliceDataMeta %>% mutate(Culture = recode(Condition, 'Sa mono' = "mono", 'Pa wt mono' = "mono",'pqsL mono'= "mono",'phz mono'= "mono",'wt co'= "co", 'pqsL co'= "co", 'phz co'= "co"))
-sliceDataMeta<-sliceDataMeta%>% mutate(Strain = recode(Condition, 'Sa mono' = "Sa", 'Pa wt mono' = "wt",'pqsL mono'= "pqsL",'phz mono'= "phz",'wt co'= "wt", 'pqsL co'= "pqsL", 'phz co'= "phz"))
-#add useful metrics
-sliceDataMeta<-sliceDataMeta%>% filter(!Channel == "3") %>% mutate(Height = Zdim*Slice) %>% group_by(SampleCode)%>% mutate(MaxHeight = max(Height)) 
-#calculate relative biomass
-##For all samples
-
-sliceDataMetaAll<-sliceDataMeta%>% group_by(SampleCode, Channel) %>% mutate(TotalBiomass = sum(Biomass)) %>% ungroup() %>% mutate(NormBiomass = Biomass/TotalBiomass*100)
-
-sliceDataSumary<-sliceDataMeta %>% group_by(SampleCode, TimePoint, Strain, Culture, MaxHeight)%>% summarise() %>% unique()
-
-sliceDataClean<-sliceDataMeta %>% filter(MaxHeight>60) %>% filter(Height<60) %>% filter(TimePoint=="Day 4") %>% group_by(SampleCode, Channel) %>% mutate(TotalBiomass = sum(Biomass)) %>% ungroup() %>% mutate(NormBiomass = Biomass/TotalBiomass*100)
-
-#####
-#Plot Data
-#####
-ggplot()+
-  #geom_point(data = sliceDataMeta ,aes(y=NormBiomass,x=Height, color = Condition, group = Replicate),size=.5)+
-  geom_smooth(data = sliceDataMeta ,aes(y=NormBiomass,x=Height, color =Condition),size=2)+
-  geom_hline(yintercept = 0, linetype = "dashed", color = "gray")+
-  theme_cowplot()+
-  scale_color_brewer(palette = "Set1")+
-  ylim(0,26)+
-  facet_grid(Channel~TimePoint)+
-  panel_border() +
-  coord_flip()
-  theme(plot.title = element_text(hjust = 0.5))
-#####
-#Filter by Max height of the sample
-#####  
-  #graph the samples height
-  ggplot()+
-    geom_col(data = sliceDataSumary %>% filter(TimePoint=="Day 4"),aes(x=SampleCode,y=MaxHeight, color = Strain, fill =Culture ),size=2)+
-    geom_hline(yintercept = 50)+
-    labs(title ="title")+
-    scale_color_brewer(palette = "Set2")+
-    scale_fill_brewer(palette = "Set1")+
-    theme_cowplot()+
-    theme(plot.title = element_text(hjust = 0.5))
-#####
-PlotZsliceSa<-function(){  
-  ggplot()+
-    geom_smooth(data = sliceDataClean %>% filter(Species == "S. aureus"),aes(y=NormBiomass,x=Height, color = Region),size=2, alpha = .1)+
-    #geom_point(data = sliceDataClean%>% filter(Species == species),aes(y=NormBiomass,x=Height, color = Region),size=1, alpha = .5)+
-    geom_hline(yintercept = 0, linetype = "dashed", color = "gray")+
-    theme_cowplot()+
-    scale_color_brewer(palette = "Set1")+
-    facet_grid(Strain~.)+
-    scale_shape_manual(values = c(1, 3))+
-    panel_border() +
-    coord_flip()+
-    theme(plot.title = element_text(hjust = 0.5))}
-PlotZslicePa<-function(){  
-  ggplot()+
-    geom_smooth(data = sliceDataClean %>% filter(Species == "P. aeruginosa") %>% filter(Culture=="co"),aes(y=NormBiomass,x=Height, color = Region),size=2, alpha = .1)+
-    #geom_point(data = sliceDataClean%>% filter(Species == species),aes(y=NormBiomass,x=Height, color = Region),size=1, alpha = .5)+
-    geom_hline(yintercept = 0, linetype = "dashed", color = "gray")+
-    theme_cowplot()+
-    scale_color_brewer(palette = "Set1")+
-    facet_grid(Strain~.)+
-    scale_shape_manual(values = c(1, 3))+
-    panel_border() +
-    coord_flip()+
-    theme(plot.title = element_text(hjust = 0.5))}
-PlotZslicePa()
-PlotZsliceSa()
-
-sliceDataClean$Strain <- factor(sliceDataClean$Strain, levels = c("Sa","wt","pqsL","phz"),labels = c("Sa", "wild-type", paste0(bquote(Delta),"pqsL"), expression(paste(alpha,"phz"))))
-PlotZsliceBth<-function(){  
-  ggplot()+
-    geom_smooth(data = sliceDataClean %>% filter(Culture=="co"),aes(y=NormBiomass,x=Height, color = Species ),size=2, alpha = .1)+
-    #geom_point(data = sliceDataClean%>% filter(Species == species),aes(y=NormBiomass,x=Height, color = Region),size=1, alpha = .5)+
-    geom_hline(yintercept = 0, linetype = "dashed", color = "gray")+
-    theme_cowplot()+
-    scale_color_brewer(palette = "Set1",breaks=c("P. aeruginosa","S. aureus"), 
-                   labels = c(bquote(paste(italic("P. aeruginosa"))), bquote(paste(italic("S. aureus")))))+
-    labs(color ="", y = "Percent Biomass", x = bquote(paste("Height (", mu*"m)")))+
-    facet_grid(Strain~Region)+
-    scale_shape_manual(values = c(1, 3))+
-    panel_border() +
-    coord_flip()+
-    theme(plot.title = element_text(hjust = 0.5),strip.background = element_rect(color="black", fill="white", size=1, linetype="solid"))#facet background
-}
-labels = c(bquote(paste(italic("P. aeruginosa"), " wt")), bquote(paste(italic(Delta*"pqsL"))))
-paste0("(1000, ",bquote("\U221E"), ")")
-PlotZsliceBth()
-
-```
-
 ```{r Metadata info}

### 2021-11-29 R/DeepSpatialAnalysis.Rmd
Transfered z-slice data to DeepSpatialAnalysis script

---
title: "DeepSpatialAnalysis"
author: "Juan P Barraza"
date: "11/29/2021"
output: html_document
---
In here I am aiming to do a more in depth analysis of the spatial data
```{r setup, include=FALSE}
```{r biomass per slice}
#this was taken from "Microscopy data clean.Rmd" 
GetSliceData<-function(){#import all experiments at once
  folder<- '/Volumes/raw_data/Confocal/Carolyn/2020/Chronic wounds/Results per slice'
   fileList<-list.files(path = folder, full.names = TRUE)
   growthDf<-data.frame()
   for (aggList in 1:length(fileList)){
     fileName<-str_split(basename(fileList[aggList]), "\\.")[[1]][1]#this selects the base file name and removes the ".csv"
     attrList<-str_split(fileName,"_")[[1]]
     growthDf<-rbind(growthDf,ReadSliceFile(fileList[aggList],attrList[2],attrList[1],attrList[3], fileName))
     }
   return(growthDf)
}

ReadSliceFile<-function(file, timepoint, condition, replicate, sampleCode){#make a dataframe of the aggregate size list and add experimental parameters
  print(file)
   datos <-read.csv(file, header = F)  
   colnames(datos)<-c('Voxels', 'Channel', 'Slice') 
   datos<-datos %>% mutate(TimePoint = timepoint) 
   datos<-datos %>% mutate(Condition = condition)
   datos<-datos %>% mutate(Replicate = replicate)
   datos<-datos %>% mutate(SampleCode = sampleCode)
   datos$Replicate<-as.factor(datos$Replicate)
   datos$Condition<-as.factor(datos$Condition)
   datos$TimePoint<-as.factor(datos$TimePoint)
   datos$SampleCode<-as.factor(datos$SampleCode)
   return(datos)
}

#Input data
#####
#get data from csv file
slicedData<-GetSliceData()
#get metadata
metaData.df <-read.csv('/Volumes/raw_data/Confocal/Carolyn/2020/Chronic wounds/images metadata.csv', header = TRUE)
metaData.df$SampleCode<-as.factor(metaData.df$SampleCode)

#merge files
metaData.df<-metaData.df %>% select(SampleCode, Position, Region, Zdim, xyDim,xySize)
sliceDataMeta<-metaData.df %>%  merge(slicedData, by = "SampleCode")
#clean up
remove <- bind_rows(sliceDataMeta %>% filter(Channel == 2 & Condition == "mono"),
                    sliceDataMeta %>% filter(Channel == 1 & Condition == "pawt"),
                    sliceDataMeta %>% filter(Channel == 1 & Condition == "paphz"),
                    sliceDataMeta %>% filter(Channel == 1 & Condition == "papqsL"))

sliceDataMeta <- anti_join(sliceDataMeta, remove)

sliceDataMeta<-sliceDataMeta %>% filter(!SampleCode == "mono_d1_03")
sliceDataMeta<-sliceDataMeta %>% filter(!SampleCode == "phz_d4_14") #didnt make it to this dataset but still making sure
sliceDataMeta<-sliceDataMeta %>% filter(!SampleCode == "pqsL_d4_02")
sliceDataMeta<-sliceDataMeta %>% filter(!SampleCode == "pqsL_d4_04")
sliceDataMeta<-sliceDataMeta %>% filter(!SampleCode == "pqsL_d4_10")
sliceDataMeta<-sliceDataMeta %>% filter(!SampleCode == "wt_d4_07")
sliceDataMeta<-sliceDataMeta %>% filter(!SampleCode == "papqsL_d4_02")
sliceDataMeta<-sliceDataMeta %>% filter(!SampleCode == "pawt_d4_05")
sliceDataMeta<-sliceDataMeta %>% filter(!SampleCode == "phz_d4_06")

#rename or add variables
sliceDataMeta<-sliceDataMeta %>% mutate(Species = recode(Channel,"1" ='S. aureus',"2" ='P. aeruginosa',"3" ='Host'))
sliceDataMeta$Condition<- factor(sliceDataMeta$Condition, levels = c("mono", "pawt","papqsL", "paphz", "wt", "pqsL", "phz"),
                                  labels = c('Sa mono', 'Pa wt mono','pqsL mono','phz mono','wt co', 'pqsL co', 'phz co'))
sliceDataMeta$TimePoint <- factor(sliceDataMeta$TimePoint, levels = c("d1", "d4"),labels = c('Day 1','Day 4'))
sliceDataMeta<-sliceDataMeta %>% mutate(Culture = recode(Condition, 'Sa mono' = "mono", 'Pa wt mono' = "mono",'pqsL mono'= "mono",'phz mono'= "mono",'wt co'= "co", 'pqsL co'= "co", 'phz co'= "co"))
sliceDataMeta<-sliceDataMeta%>% mutate(Strain = recode(Condition, 'Sa mono' = "Sa", 'Pa wt mono' = "wt",'pqsL mono'= "pqsL",'phz mono'= "phz",'wt co'= "wt", 'pqsL co'= "pqsL", 'phz co'= "phz"))

#remove host channel, add Height (current), Total Heightuseful metrics
sliceDataMeta<-sliceDataMeta%>% filter(!Channel == "3") %>% mutate(CurrentHeight = Zdim*Slice, Biomass = Voxels*Zdim*xyDim*xyDim) %>% group_by(SampleCode)%>% mutate(TotalHeight = max(CurrentHeight))%>%ungroup() %>% group_by(SampleCode, Species) %>% mutate(SpeciesBiomass = sum(Biomass)) %>% ungroup()
sliceDataMeta<-sliceDataMeta %>% group_by(SampleCode)%>% mutate(TotalVolume = TotalHeight*xySize*xySize, TotalBiomass = sum(Biomass)) %>% ungroup() %>% 
  mutate(TotalRatio = TotalBiomass/TotalVolume, SpeciesRatio = SpeciesBiomass/TotalVolume, currentRatio = Biomass/(CurrentHeight*xySize*xySize))

sliceDataSumary<-sliceDataMeta %>% group_by(SampleCode,Species,TimePoint, Strain, Culture,TotalBiomass,TotalVolume,TotalRatio)%>% summarise() %>% unique()
#SpeciesBiomass is separated by species, TotalBiomass is for both

ggplot()+
  geom_point(data = sliceDataSumary,aes(x=SampleCode,y=TotalRatio, color = Culture, shape = Strain),size=4)+
  geom_hline(aes(yintercept = 0.5))+
  geom_hline(aes(yintercept = 0.1))+
  geom_hline(aes(yintercept = 0.01))+
  scale_y_log10(breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
  theme_cowplot()+
  theme(plot.title = element_text(hjust = 0.5))

#calculate relative biomass
##For all samples

sliceDataMetaAll<-sliceDataMeta%>% group_by(SampleCode, Channel) %>% mutate(TotalBiomass = sum(Biomass)) %>% ungroup() %>% mutate(NormBiomass = Biomass/TotalBiomass*100)

sliceDataSumary<-sliceDataMeta %>% group_by(SampleCode, TimePoint, Strain, Culture, MaxHeight)%>% summarise() %>% unique()

sliceDataClean<-sliceDataMeta %>% filter(MaxHeight>60) %>% filter(Height<60) %>% filter(TimePoint=="Day 4") %>% group_by(SampleCode, Channel) %>% mutate(TotalBiomass = sum(Biomass)) %>% ungroup() %>% mutate(NormBiomass = Biomass/TotalBiomass*100)

#####
#Plot Data
#####
ggplot()+
  #geom_point(data = sliceDataMeta ,aes(y=NormBiomass,x=Height, color = Condition, group = Replicate),size=.5)+
  geom_smooth(data = sliceDataMeta ,aes(y=NormBiomass,x=Height, color =Condition),size=2)+
  geom_hline(yintercept = 0, linetype = "dashed", color = "gray")+
  theme_cowplot()+
  scale_color_brewer(palette = "Set1")+
  ylim(0,26)+
  facet_grid(Channel~TimePoint)+
  panel_border() +
  coord_flip()
  theme(plot.title = element_text(hjust = 0.5))
#####
#Filter by Max height of the sample
#####  
  #graph the samples height
  ggplot()+
    geom_col(data = sliceDataSumary %>% filter(TimePoint=="Day 4"),aes(x=SampleCode,y=MaxHeight, color = Strain, fill =Culture ),size=2)+
    geom_hline(yintercept = 50)+
    labs(title ="title")+
    scale_color_brewer(palette = "Set2")+
    scale_fill_brewer(palette = "Set1")+
    theme_cowplot()+
    theme(plot.title = element_text(hjust = 0.5))
#####
PlotZsliceSa<-function(){  
  ggplot()+
    geom_smooth(data = sliceDataClean %>% filter(Species == "S. aureus"),aes(y=NormBiomass,x=Height, color = Region),size=2, alpha = .1)+
    #geom_point(data = sliceDataClean%>% filter(Species == species),aes(y=NormBiomass,x=Height, color = Region),size=1, alpha = .5)+
    geom_hline(yintercept = 0, linetype = "dashed", color = "gray")+
    theme_cowplot()+
    scale_color_brewer(palette = "Set1")+
    facet_grid(Strain~.)+
    scale_shape_manual(values = c(1, 3))+
    panel_border() +
    coord_flip()+
    theme(plot.title = element_text(hjust = 0.5))}
PlotZslicePa<-function(){  
  ggplot()+
    geom_smooth(data = sliceDataClean %>% filter(Species == "P. aeruginosa") %>% filter(Culture=="co"),aes(y=NormBiomass,x=Height, color = Region),size=2, alpha = .1)+
    #geom_point(data = sliceDataClean%>% filter(Species == species),aes(y=NormBiomass,x=Height, color = Region),size=1, alpha = .5)+
    geom_hline(yintercept = 0, linetype = "dashed", color = "gray")+
    theme_cowplot()+
    scale_color_brewer(palette = "Set1")+
    facet_grid(Strain~.)+
    scale_shape_manual(values = c(1, 3))+
    panel_border() +
    coord_flip()+
    theme(plot.title = element_text(hjust = 0.5))}
PlotZslicePa()
PlotZsliceSa()

sliceDataClean$Strain <- factor(sliceDataClean$Strain, levels = c("Sa","wt","pqsL","phz"),labels = c("Sa", "wild-type", paste0(bquote(Delta),"pqsL"), expression(paste(alpha,"phz"))))
PlotZsliceBth<-function(){  
  ggplot()+
    geom_smooth(data = sliceDataClean %>% filter(Culture=="co", Strain == "wt"),aes(y=NormBiomass,x=Height, color = Species ),size=2, alpha = .1)+
    #geom_point(data = sliceDataClean%>% filter(Species == species),aes(y=NormBiomass,x=Height, color = Region),size=1, alpha = .5)+
    geom_hline(yintercept = 0, linetype = "dashed", color = "gray")+
    theme_cowplot()+
    scale_color_brewer(palette = "Set1",breaks=c("P. aeruginosa","S. aureus"), 
                   labels = c(bquote(paste(italic("P. aeruginosa"))), bquote(paste(italic("S. aureus")))))+
    labs(color ="", y = "Percent Biomass", x = bquote(paste("Height (", mu*"m)")))+
    facet_grid(.~Region)+
    scale_shape_manual(values = c(1, 3))+
    panel_border() +
    coord_flip()+
    theme(plot.title = element_text(hjust = 0.5),strip.background = element_rect(color="black", fill="white", size=1, linetype="solid"))#facet background
}
labels = c(bquote(paste(italic("P. aeruginosa"), " wt")), bquote(paste(italic(Delta*"pqsL"))))
paste0("(1000, ",bquote("\U221E"), ")")
PlotZsliceBth()

```

### 2022-01-25 R/PaperFigures.Rmd
First few figures

---
title: "SaPaFigures"
author: "Juan P Barraza"
date: "1/14/2022"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
library(pixmap)
library(rtiff)
library(reshape2)
library(gplots)
library(gdata)
library(plyr)
library(dplyr)
library(ggplot2)
library(cowplot)
library(tidyr)
library(purrr)
library(plotrix)
library(ggsignif)
library(rdist)
library(stringr)

```

```{r figure 1}
#CFU data from Carolyn
CFUdata<-read.csv("/Users/jupabago/Documents/Whiteley/PROJECTS/SaPa Chronic Wounds/Data/CFU_wound_All_dataTidy.csv",header = TRUE)
CFUdata$Condition<-as.factor(CFUdata$Condition)
   CFUdata$Day<-as.factor(CFUdata$Day)
   CFUdata$Species<-as.factor(CFUdata$Species)
   CFUdata$Strain<-as.factor(CFUdata$Strain)
CFUdata$Condition <- factor(CFUdata$Condition, levels = c("mono", "co-wt", "co-pqsL"))
CFUstats<-CFUdata%>%group_by(Species,Condition,Strain,Day) %>% mutate(MeanCFU = mean(CFU), SECFU = std.error(CFU))
CFUstats$Condition <- factor(CFUstats$Condition, levels = c("mono", "co-wt", "co-pqsL"))
PlotCFUs<- function(){
ggplot()+
  geom_col(data = CFUstats %>% filter(Day == "4", Condition %in% c("mono", "co-wt"), Strain == "wt"),aes(x=Species,y=MeanCFU, fill = Condition),
           size=3,position = position_dodge( width = .9))+

  geom_errorbar(data = CFUstats %>% filter(Day == "4", Condition %in% c("mono", "co-wt"), Strain == "wt"),
                aes(x=Species,ymin=(MeanCFU-SECFU), ymax = (MeanCFU+SECFU), group = Condition),width = 0, size=.5,position = position_dodge(width = .9))+

    scale_y_log10(breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)),expand = expand_scale(mult = c(0, 0)))+
  #facet_grid(.~Species)+
  scale_fill_grey(labels = c("Mono-culture","Co-culture"))+
  #labs(x = "", y = expression(paste(Log[10], " CFU")), linetype = "")+
    labs(x = "", y = "CFU per wound")+
  theme_cowplot()+
  theme(plot.title = element_text(hjust = 0.5),strip.text = element_text(size = 9, face = "italic",margin = margin(.1,0,.1,0, "cm")),
        strip.background = element_rect(color="black", fill="white", size=.5, linetype="solid"),
        axis.title.x = element_text(margin = margin(0,0,0,0),size=13),axis.text.x = element_text(face = "italic",margin = margin(1,0,0,0),size=13),
        axis.title.y = element_text(margin = margin(0,4,0,0),size=13),axis.text.y = element_text(margin = margin(0,0,2,0),size=11))
}
figure1A<-PlotCFUs()
figure1A

CFUdataWT<-CFUdata %>% filter(Day == "4", Condition %in% c("mono", "co-wt"), Strain == "wt")

PlotCFUs2<- function(){
  ggplot()+
    geom_jitter(data = CFUdata %>% filter(Day == "4", Condition %in% c("mono", "co-wt"), Strain == "wt"),
                aes(x=Species,y=CFU, color = Condition),size=3,position = position_jitterdodge(jitter.height = 0,jitter.width = 0.6, dodge.width = .9))+
    geom_errorbar(data = CFUstats %>% filter(Day == "4", Condition %in% c("mono", "co-wt"), Strain == "wt"),
                aes(x=Species,ymin=(MeanCFU), ymax = (MeanCFU), group = Condition),width = .4,position = position_dodge(width = .9))+
    scale_color_grey(labels = c("Mono-culture","Co-culture"))+
    scale_y_log10(breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)),expand = expand_scale(mult = c(0, 0)), limits = c(1,10^11))+
  #labs(x = "", y = expression(paste(Log[10], " CFU")), linetype = "")+
    labs(x = "", y = "CFU per wound")+
  theme_cowplot()+
  theme(plot.title = element_text(hjust = 0.5),strip.text = element_text(size = 9, face = "italic",margin = margin(.1,0,.1,0, "cm")),
        strip.background = element_rect(color="black", fill="white", size=.5, linetype="solid"),
        axis.title.x = element_text(margin = margin(0,0,0,0),size=13),axis.text.x = element_text(face = "italic",margin = margin(1,0,0,0),size=13),
        axis.title.y = element_text(margin = margin(0,4,0,0),size=13),axis.text.y = element_text(margin = margin(0,0,2,0),size=11))
}  
figure1A2<-PlotCFUs2()
figure1A2

#I am taking this code from Aggregate counts.RMD, but the biomass is lower case on the df that I have
BiomassData<-aggregateList%>% group_by(SampleCode,Species,SaStrain,Strain,Culture,TimePoint,Condition,Replicate,Region) %>% 
  summarise(Aggs = n(), Biomass = sum(Size), MeanAggSize = mean(Size), SEAggSize = std.error(Size), MaxSize = max(Size), MinSize = min(Size)) %>%
  ungroup() %>% mutate(RatioMaxTotal = MaxSize/Biomass)

BiomassDataStats<-BiomassData %>% 
  group_by(Species,SaStrain,Strain,Culture,TimePoint,Condition) %>% 
  summarise(MeanAggs= mean(Aggs),MeanBiomass = mean(Biomass), SEBiomass = std.error(Biomass), MeanBiomassLog = mean(log10(Biomass)), SEBiomassLog = std.error((log10(Biomass))), MeanMeanAggSize = mean(MeanAggSize), SEMeanAggSize = std.error(MeanAggSize))

biomassWTData = BiomassDataStats%>% filter(Condition == "Sa mono" |Condition == "wt co"|Condition == "wt mono") %>% filter(TimePoint == "Day 4" )

PlotBiomass<- function(){
  ggplot()+
    geom_col(data = biomassWTData,aes(x=Species,y=MeanBiomass, fill = Culture),
             size=3,position = position_dodge( width = .9))+
    geom_errorbar(data = biomassWTData, aes(x=Species,ymin=(MeanBiomass-SEBiomass), ymax = (MeanBiomass+SEBiomass), group = Culture)
                ,width = 0, size=.5,position = position_dodge(width = .9))+
    scale_y_log10(breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)),expand = expand_scale(mult = c(0, 0)))+
    scale_fill_grey(labels = c("Mono-culture","Co-culture"))+
    labs(x = "",y = bquote(paste("Biomass per wound (", mu*"m"^3*")")))+
    theme_cowplot()+
    theme(plot.title = element_text(hjust = 0.5),strip.text = element_text(size = 9, face = "italic",margin = margin(.1,0,.1,0, "cm")),
          strip.background = element_rect(color="black", fill="white", size=.5, linetype="solid"),
          axis.title.x = element_text(margin = margin(0,0,0,0),size=13),axis.text.x = element_text(face = "italic",margin = margin(1,0,0,0),size=13),
          axis.title.y = element_text(margin = margin(0,4,0,0),size=13),axis.text.y = element_text(margin = margin(0,0,2,0),size=11))
}

figure1B<-PlotBiomass()
figure1B

```
#####

```{r figure 2 Core vs Edge}

#Figure 2A: Percent CFU inner wound
##### 
CFUInOutData<-read.csv("/Users/jupabago/Documents/Whiteley/PROJECTS/SaPa Chronic Wounds/Data/Inside_Outside_CFUcm2_Day4Tidy.csv",header = TRUE)
CFUInOutData<-Filter(function(x)!all(is.na(x)), CFUInOutData)#this is to remove columns with NA
CFUInOutData <- na.omit(CFUInOutData) #removing rows with NA
CFUInOutData$Condition<-as.factor(CFUInOutData$Condition)
CFUInOutData$Sample<-as.factor(CFUInOutData$Sample)
CFUInOutData$Species<-as.factor(CFUInOutData$Species)
CFUInOutData$Strain<-as.factor(CFUInOutData$Strain)

CFUInOutDataPost<-CFUInOutData %>% mutate(CFU.Inside = Inside.Bandage+Inside.Tissue, CFU.Outside = Outside.Tissue+Outside.Bandage) %>% mutate(PercentIn = 100*CFU.Outside/(CFU.Inside+CFU.Outside))

CFUInOutStats<-CFUInOutDataPost%>% group_by(Species,Strain,Condition) %>% summarise(meanInPercent = mean(PercentIn), SEInPercent = std.error(PercentIn))
CFUInOutStatsWt<-CFUInOutStats %>% filter(!Condition=="co-pqsL") %>% filter(Strain == "wt")
CFUInOutStatsWt$Condition <- factor(CFUInOutStatsWt$Condition, levels = c("mono", "co-wt"))

PlotInCFUs<- function(){
  ggplot()+
    geom_col(data = CFUInOutStatsWt,aes(x=Species,y=meanInPercent, fill = Condition),size=3,position = position_dodge( width = .9))+
    geom_errorbar(data = CFUInOutStatsWt,aes(x=Species,ymin=(meanInPercent-SEInPercent), ymax = (meanInPercent+SEInPercent), group = Condition),width = 0, size=.5,position = position_dodge(width = .9))+
    scale_fill_grey(labels = c("Mono-culture","Co-culture"))+
    scale_y_continuous(expand = expand_scale(mult = c(0, 0)))+
  #labs(x = "", y = expression(paste(Log[10], " CFU")), linetype = "")+
    labs(x = "",y = bquote(paste("% CFU/", "cm"^2*" in healing edge")))+
  theme_cowplot()+
  theme(plot.title = element_text(hjust = 0.5),strip.text = element_text(size = 9, face = "italic",margin = margin(.1,0,.1,0, "cm")),
        strip.background = element_rect(color="black", fill="white", size=.5, linetype="solid"),
        axis.title.x = element_text(margin = margin(0,0,0,0),size=13),axis.text.x = element_text(face = "italic",margin = margin(1,0,0,0),size=13),
        axis.title.y = element_text(margin = margin(0,4,0,0),size=13),axis.text.y = element_text(margin = margin(0,0,2,0),size=11))
  }
figure2A<-PlotInCFUs()
figure2A

#now with geom_point
CFUInOutPostWt<-CFUInOutDataPost %>% filter(!Condition=="co-pqsL") %>% filter(Strain == "wt")
CFUInOutPostWt$Condition <- factor(CFUInOutPostWt$Condition, levels = c("mono", "co-wt"))

PlotInCFUs2<- function(){
  ggplot()+
    geom_jitter(data = CFUInOutPostWt,aes(x=Species,y=PercentIn, color = Condition),size=3,position = position_jitterdodge(jitter.height = 0,jitter.width = 0.2, dodge.width = .9))+
    geom_errorbar(data = CFUInOutStatsWt,aes(x=Species,ymin=(meanInPercent), ymax = (meanInPercent), group = Condition),width = .4, size=.5,position = position_dodge(width = .9))+
    scale_color_grey(labels = c("Mono-culture","Co-culture"))+
    scale_y_continuous(expand = expand_scale(mult = c(0, 0)), limits = c(0,75))+
  #labs(x = "", y = expression(paste(Log[10], " CFU")), linetype = "")+
    labs(x = "",y = bquote(paste("% CFU/", "cm"^2*" in healing edge")))+
  theme_cowplot()+
  theme(plot.title = element_text(hjust = 0.5),strip.text = element_text(size = 9, face = "italic",margin = margin(.1,0,.1,0, "cm")),
        strip.background = element_rect(color="black", fill="white", size=.5, linetype="solid"),
        axis.title.x = element_text(margin = margin(0,0,0,0),size=13),axis.text.x = element_text(face = "italic",margin = margin(1,0,0,0),size=13),
        axis.title.y = element_text(margin = margin(0,4,0,0),size=13),axis.text.y = element_text(margin = margin(0,0,2,0),size=11))
}  
figure2A2<-PlotInCFUs2()
figure2A2
#####

#Figure 2B
#Aggregation inner vs outer region
#####
PlotAggCore<-function(rep.df,region.df, y_var, title,colorStrain, facet){
ggplot()+
    geom_point(data = rep.df %>% filter(TimePoint=="Day 4"),
                aes(x=Region,y=.data[[y_var]], color =.data[[colorStrain]]),
               position = position_jitterdodge(jitter.height = 0, jitter.width = .3,dodge.width = 0.75),size=3)+
    geom_errorbar(data = region.df%>% filter(TimePoint=="Day 4"),
               aes(x=Region,ymin=.data[[y_var]],ymax=.data[[y_var]], group =.data[[colorStrain]]),
               size=.5,width = 0.5, position = position_dodge(width = .75) )+
    #geom_point(data = cond.df%>% filter(TimePoint=="Day 4"),
     #          aes(x=Region,y=.data[[y_var]],  color =.data[[colorStrain]]),size=4, shape = 3,position = position_dodge(width = .75) )+
    scale_y_log10(breaks = c(100, 10, 1, .1, .01), labels = c(100, 10, 1, .1, .01))+
    facet_grid(.~.data[[facet]])+
    scale_shape_manual(values=c(16, 1))+
    scale_color_grey(labels = c("Mono-culture","Co-culture"))+
    ggtitle(title)+
    labs(y = paste("Planktonic Biomass Contribution (%)"))+
    theme_cowplot()+
    panel_border() +
    theme(plot.title = element_text(hjust = 0.5), 
        strip.text = element_text(size = 11, face = "italic",margin = margin(.1,0,.1,0, "cm")),#this is for the facet text
        strip.background = element_rect(color="black", fill="white", size=1, linetype="solid"))#facet background
}

PlotAggCore(plankAggHistRep%>% filter(Strain %in% c("Sa", "wt")) %>% filter(Aggregation=="Planktonic"),
             plankAggHistCondReg%>% filter(Strain %in% c("Sa", "wt"))%>% filter(Aggregation=="Planktonic"),
             "AgPlNormBiomass", "", "Culture", "Species")

```

```{r Figure 4}
#Antibiotic data
ReadAbData<-function(){
df<-read.csv("/Users/jupabago/Documents/Whiteley/PROJECTS/SaPa Chronic Wounds/Data/AntibioticTreatment_percentofuntreatedTidy.csv",header = TRUE)
df<-Filter(function(x)!all(is.na(x)), df)#this is to remove columns with NA
df <- na.omit(df) #removing rows with NA
df$Condition<-as.factor(df$Condition)
df$Sample<-as.factor(df$Sample)
df$Species<-as.factor(df$Species)
df$Treatment<-as.factor(df$Treatment)
df$Structure<-as.factor(df$Structure)
return(df)
}
AbData<-ReadAbData()
AbData$Condition <- factor(AbData$Condition, levels = c("mono", "co-wt", "co-pqsL"))
AbData<-AbData %>% group_by(Structure, Species, Condition, Sample) %>%  mutate(SurvivalFinal = mean(Survival)) %>% filter(!Treatment=="Treated1")
AbData<-AbData %>% mutate(SurvivalRatio = SurvivalFinal/100)
AbDataStats<-AbData %>% group_by(Species, Structure,Condition) %>% summarise(MeanSurvival = mean(SurvivalFinal), SESurvival = std.error(SurvivalFinal), 
                                                                             MeanSurRatio = mean(SurvivalRatio), SESurRatio = std.error(SurvivalRatio)) %>% ungroup()

PlotAbData<-function(df,xaxis,yaxis, error, fill){
ggplot()+
  geom_col(data = df%>% filter(Species == "S. aureus"),aes(x=.data[[xaxis]],y=.data[[yaxis]], fill = .data[[fill]]),size=3,position = position_dodge( width = .9))+
  geom_errorbar(data = df%>% filter(Species == "S. aureus"),aes(x=.data[[xaxis]],ymin=(.data[[yaxis]]-.data[[error]]), ymax = (.data[[yaxis]]+.data[[error]]), group = .data[[fill]]),
                width = 0, size=.5,position = position_dodge(width = .9))+
  scale_y_continuous(expand = expand_scale(mult = c(0, 0)))+
  #scale_y_log10(limits = c(.0001,100))+
  #facet_grid(.~Species)+
  scale_fill_grey(labels = c("Mono-culture","Co-culture wt", "Co-culture pqsL"))+
  #labs(x = "", y = expression(paste(Log[10], " CFU")), linetype = "")+
  labs(x = "", y = expression(paste(italic(S.aureus )," % Survival" )))+
  theme_cowplot()+
  theme(plot.title = element_text(hjust = 0.5),strip.text = element_text(size = 9, face = "italic",margin = margin(.1,0,.1,0, "cm")),
        strip.background = element_rect(color="black", fill="white", size=.5, linetype="solid"),
        axis.title.x = element_text(margin = margin(0,0,0,0),size=13),axis.text.x = element_text(face = "italic",margin = margin(1,0,0,0),size=13),
        axis.title.y = element_text(margin = margin(0,4,0,0),size=13),axis.text.y = element_text(margin = margin(0,0,2,0),size=11))
}
PlotAbData(AbDataStats,"Structure","MeanSurvival","SESurvival", "Condition")

PlotAbData2<-function(){
ggplot()+
  geom_jitter(data = AbData %>% filter(Species == "S. aureus"),aes(x=Structure,y=SurvivalRatio, shape = Sample, color = Condition, group = Condition),size=3,
              position = position_jitterdodge(jitter.height = 0,jitter.width = 0.2, dodge.width = .9))+
  geom_errorbar(data = AbDataStats %>% filter(Species == "S. aureus"),aes(x=Structure,ymin=(MeanSurRatio), ymax = (MeanSurRatio), group = Condition),
                width = .5, size=.5,position = position_dodge(width = .9))+
  #facet_grid(.~Species)+
  scale_color_grey(labels = c("Mono-culture","Co-culture wt", "Co-culture pqsL"))+
  #labs(x = "", y = expression(paste(Log[10], " CFU")), linetype = "")+
    #scale_y_log10(breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
  labs(x = "", y = expression(paste(italic(S.aureus )," Survival fraction" )))+
  theme_cowplot()+
  theme(plot.title = element_text(hjust = 0.5),strip.text = element_text(size = 9, face = "italic",margin = margin(.1,0,.1,0, "cm")),
        strip.background = element_rect(color="black", fill="white", size=.5, linetype="solid"),
        axis.title.x = element_text(margin = margin(0,0,0,0),size=13),axis.text.x = element_text(margin = margin(1,0,0,0),size=13),
        axis.title.y = element_text(margin = margin(0,4,0,0),size=13),axis.text.y = element_text(margin = margin(0,0,2,0),size=11))
}
PlotAbData2()

#This doesn't really gets the point across, so get the ratio of survival in treated vs untreated
AbData<-AbData %>% ungroup() %>% group_by(Sample, Species, Condition) %>% mutate(SurvivalRatioStructure = SurvivalRatio/SurvivalRatio[Structure=="Unstructured"],SurvivalDifferenceStructure = SurvivalFinal[Structure=="Unstructured"]-SurvivalFinal )
#now we redo AbDataStats:
AbDataUnstructureStats<-AbData %>% filter(Structure == "Structured") %>% group_by(Species, Condition) %>%
  summarise(MeanRatio = mean(SurvivalRatioStructure), SESurvival = std.error(SurvivalRatioStructure),
            MeanDifference = mean(SurvivalDifferenceStructure), SEDifference = std.error(SurvivalDifferenceStructure))%>% ungroup()

PlotAbData3<-function(df,xaxis,yaxis, error, fill){
ggplot()+
  geom_col(data = df %>% filter(Species == "S. aureus"),aes(x=.data[[xaxis]],y=.data[[yaxis]], fill = .data[[fill]]),size=3,position = position_dodge( width = .9))+
  geom_errorbar(data = df%>% filter(Species == "S. aureus"),aes(x=.data[[xaxis]],ymin=(.data[[yaxis]]-.data[[error]]), ymax = (.data[[yaxis]]+.data[[error]]), group = .data[[fill]]),
                width = 0, size=.5,position = position_dodge(width = .9))+
  scale_y_continuous(expand = expand_scale(mult = c(0, 0)))+
  #scale_y_log10(expand = expand_scale(mult = c(0, 0)))+
  #facet_grid(.~Species)+
  scale_fill_grey(labels = c("Mono-culture","Co-culture wt", "Co-culture pqsL"))+
  #labs(x = "", y = expression(paste(Log[10], " CFU")), linetype = "")+
  labs(x = "", y = "Survival fraction Structured/Unstructured")+
  theme_cowplot()+
  theme(plot.title = element_text(hjust = 0.5),strip.text = element_text(size = 9, face = "italic",margin = margin(.1,0,.1,0, "cm")),
        strip.background = element_rect(color="black", fill="white", size=.5, linetype="solid"),
        axis.title.x = element_text(margin = margin(0,0,0,0),size=13),axis.text.x = element_text(face = "italic",margin = margin(1,0,0,0),size=13),
        axis.title.y = element_text(margin = margin(0,4,0,0),size=13),axis.text.y = element_text(margin = margin(0,0,2,0),size=11))
}
PlotAbData3(AbDataUnstructureStats,"Species","MeanRatio","SESurvival", "Condition")
PlotAbData3(AbDataUnstructureStats,"Species","MeanDifference","SEDifference", "Condition")
#now using the jittel points

PlotAbData4<-function(){
ggplot()+
  geom_jitter(data = AbData %>% filter(Species == "S. aureus") %>% filter(Structure == "Structured") ,
              aes(x=Species,y=SurvivalRatioStructure, color = Condition, group = Condition, shape = Sample),size=3,
              position = position_jitterdodge(jitter.height = 0,jitter.width = 0.2, dodge.width = .9))+
  geom_errorbar(data = AbDataUnstructureStats %>% filter(Species == "S. aureus"),
                aes(x=Species,ymin=(MeanRatio), ymax = (MeanRatio), group = Condition),
                width = .5, size=.5,position = position_dodge(width = .9))+
  #facet_grid(.~Species)+
  scale_color_grey(labels = c("Mono-culture","Co-culture wt", "Co-culture pqsL"))+
  labs(x = "", y = expression(paste(italic(S.aureus )," survival fraction Structured/Unstructured" )))+
    scale_y_log10(breaks = c(1,10,100,1000), labels = c(1,10,100,1000), limits = c(1, 10000))+
  theme_cowplot()+
  theme(plot.title = element_text(hjust = 0.5),strip.text = element_text(size = 9, face = "italic",margin = margin(.1,0,.1,0, "cm")),
        strip.background = element_rect(color="black", fill="white", size=.5, linetype="solid"),
        axis.title.x = element_text(margin = margin(0,0,0,0),size=13),axis.text.x = element_text(margin = margin(1,0,0,0),size=13),
        axis.title.y = element_text(margin = margin(0,4,0,0),size=13),axis.text.y = element_text(margin = margin(0,0,2,0),size=11))
}
PlotAbData4()

```

### 2022-02-22 R/PaperFigures.Rmd
new computer first commit

@@
 library(pixmap)
-library(rtiff)
 library(reshape2)
@@
 ```{r figure 1}
+#Figure 1A CFU data wt
+#####
 #CFU data from Carolyn
@@
 
+#####
+
+#Figure 1B
+#####
 #I am taking this code from Aggregate counts.RMD, but the biomass is lower case on the df that I have
@@
 
+BiomassDataWt = BiomassData%>% filter(Condition == "Sa mono" |Condition == "wt co"|Condition == "wt mono") %>% filter(TimePoint == "Day 4" )
 biomassWTData = BiomassDataStats%>% filter(Condition == "Sa mono" |Condition == "wt co"|Condition == "wt mono") %>% filter(TimePoint == "Day 4" )
+#Carolyn wanted to play with the data so here it is:
+write.csv(BiomassDataWt,"/Users/jupabago/Documents/Whiteley/PROJECTS/SaPa Chronic Wounds/Data/CSV exports/BiomassWT.csv", row.names = T)
 
@@
     scale_fill_grey(labels = c("Mono-culture","Co-culture"))+
-    labs(x = "",y = bquote(paste("Biomass per wound (", mu*"m"^3*")")))+
+    labs(x = "",y = bquote(paste("Biomass per image (", mu*"m"^3*")")))+
     theme_cowplot()+
@@
 figure1B
+
+PlotBiomassPoints<- function(){
+  ggplot()+
+    geom_jitter(data = BiomassDataWt,aes(x=Species,y=Biomass, color = Culture),size=3,position = position_jitterdodge(jitter.height = 0,jitter.width = 0.2, dodge.width = .9))+
+    geom_errorbar(data = biomassWTData, aes(x=Species,ymin=(MeanBiomass), ymax = (MeanBiomass), group = Culture)
+                ,width = .4, size=.5,position = position_dodge(width = .9))+
+    scale_y_log10(breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)),
+                  limits = c(100, 10e7), expand = expand_scale(mult = c(0, 0)))+
+    scale_color_grey(labels = c("Mono-culture","Co-culture"))+
+    labs(x = "",y = bquote(paste("Biomass per image (", mu*"m"^3*")")))+
+    theme_cowplot()+
+    theme(plot.title = element_text(hjust = 0.5),strip.text = element_text(size = 9, face = "italic",margin = margin(.1,0,.1,0, "cm")),
+          strip.background = element_rect(color="black", fill="white", size=.5, linetype="solid"),
+          axis.title.x = element_text(margin = margin(0,0,0,0),size=13),axis.text.x = element_text(face = "italic",margin = margin(1,0,0,0),size=13),
+          axis.title.y = element_text(margin = margin(0,4,0,0),size=13),axis.text.y = element_text(margin = margin(0,0,2,0),size=11))
+}
+PlotBiomassPoints()
+#####
 
@@
 figure2A2
+
+#With the mutants
+
 #####
+#Figure 2B
+#####
+#this is taken from AggregateCounts.Rmd section Plot Aggregagte size bins
 
-#Figure 2B
+PlotHistSumFinal<-function(rep.df,cond.df,region.df, y_var, colorStrain){
+ggplot()+
+    geom_point(data = rep.df %>% filter(TimePoint=="Day 4"),
+                aes(x=as.factor(LogBin),y=.data[[y_var]], color =.data[[colorStrain]], shape = Region),
+               position = position_jitterdodge(jitter.height = 0, jitter.width = .3,dodge.width = 0.75),size=1)+
+    geom_point(data = region.df%>% filter(TimePoint=="Day 4"),
+               aes(x=as.factor(LogBin),y=.data[[y_var]], color =.data[[colorStrain]],shape = Region),
+               size=3, position = position_dodge(width = .75) )+
+    geom_errorbar(data = cond.df%>% filter(TimePoint=="Day 4"),
+               aes(x=as.factor(LogBin),ymin=.data[[y_var]],ymax=.data[[y_var]], group =.data[[colorStrain]]),width = .5,position = position_dodge(width = .75) )+
+    facet_grid(.~Species)+
+    scale_shape_manual(values=c(16, 1))+
+    scale_color_grey(labels = c("Mono-culture","Co-culture"))+
+    scale_x_discrete(labels = c("Planktonic", "5-10", "10-100", "100-1000", ">1000"))+
+    labs(y = paste("Frequency (%)"),x = bquote(paste("Aggregate Volume (", mu*"m"^3*")")))+
+    theme_cowplot()+
+    panel_border() +
+    theme(plot.title = element_text(hjust = 0.5), 
+        strip.text = element_text(size = 11, face = "italic",margin = margin(.1,0,.1,0, "cm")),#this is for the facet text
+        strip.background = element_rect(color="black", fill="white", size=1, linetype="solid"))#facet background
+}
+
+PlotHistSumFinal(HistReplicateSummary%>% filter(Condition == "Sa mono" |Condition == "wt co"|Condition == "wt mono"),
+            HistConditionSummary%>% filter(Condition == "Sa mono" |Condition == "wt co"|Condition == "wt mono"),
+            HistCondRegionSum%>% filter(Condition == "Sa mono" |Condition == "wt co"|Condition == "wt mono"),
+            "NormalizedFrequency", "Culture")
+
+#only difference between these two should be "scale_color_grey"
+PlotHistSumFinalStrains<-function(rep.df,cond.df,region.df, y_var, colorStrain){
+ggplot()+
+    geom_point(data = rep.df %>% filter(TimePoint=="Day 4"),
+                aes(x=as.factor(LogBin),y=.data[[y_var]], color =.data[[colorStrain]], shape = Region),
+               position = position_jitterdodge(jitter.height = 0, jitter.width = .3,dodge.width = 1),size=2)+
+    geom_point(data = region.df%>% filter(TimePoint=="Day 4"),
+               aes(x=as.factor(LogBin),y=.data[[y_var]], color =.data[[colorStrain]],shape = Region),
+               size=5, position = position_dodge(width = 1) )+
+    geom_errorbar(data = cond.df%>% filter(TimePoint=="Day 4"),
+               aes(x=as.factor(LogBin),ymin=.data[[y_var]],ymax=.data[[y_var]], group =.data[[colorStrain]]),width = .8,position = position_dodge(width = 1) )+
+    facet_grid(.~Species)+
+    scale_shape_manual(values=c(16, 1))+
+    scale_color_grey(labels = c(bquote(paste(italic('S. aureus + P. aeruginosa '))),
+                                bquote(paste(italic('S. aureus + P. aeruginosa '*Delta*"pqsL"))), 
+                                bquote(paste(italic('S. aureus + P. aeruginosa '*Delta*"phz")))))+
+    scale_x_discrete(labels = c("Planktonic", "5-10", "10-100", "100-1000", ">1000"))+
+    labs(y = paste("Frequency (%)"),x = bquote(paste("Aggregate Volume (", mu*"m"^3*")")), color = "Condition")+
+    theme_cowplot()+
+    panel_border() +
+    theme(plot.title = element_text(hjust = 0.5), 
+        strip.text = element_text(size = 11, face = "italic",margin = margin(.1,0,.1,0, "cm")),#this is for the facet text
+        strip.background = element_rect(color="black", fill="white", size=1, linetype="solid"))#facet background
+}#only difference between these two should be "scale_color_grey
+PlotHistSumFinalStrains(HistReplicateSummary%>% filter(Culture =="co"),
+            HistConditionSummary%>% filter(Culture =="co"),
+            HistCondRegionSum%>% filter(Culture =="co"),
+            "NormalizedFrequency","Strain")
+
+#####
+#Figure 2C
 #Aggregation inner vs outer region
@@
     ggtitle(title)+
-    labs(y = paste("Planktonic Biomass Contribution (%)"))+
+    labs(y = paste("Planktonic Biomass Contribution (%)"), x = "")+
     theme_cowplot()+
@@
              "AgPlNormBiomass", "", "Culture", "Species")
+
+#Figure 2D
+##Marvin suggested doing the enrichment distance for those samples, but I guess there is nothing to compare, unless I do core vs edge
+##ggplot code from PropOc Data 3D
+PlotwtED<-function(){
+df1<-pOEnrMetaStatsRegion %>% filter(Relation == "Pa->Sa", TimePoint=="Day 4", Condition == "wt co")
+df2<-pOEnrMetaClean %>% filter(Relation == "Pa->Sa", TimePoint=="Day 4", Condition == "wt co")
+  ggplot()+
+    geom_errorbar(data = df1,aes(y=meanED,ymax=meanED,ymin=meanED, group = Region,x = Condition),
+                    position = position_dodge(width = .75), width = 0.5)+
+    geom_point(data = df2,aes(y=WmeanDist,x = Condition, shape = Region),position = position_jitterdodge(jitter.height = 0, jitter.width = .3,dodge.width = 0.75),size=3)+
+    labs(y = expression("Enrichment distance ("*mu*"m)"), x = "") +
+    scale_color_grey()+
+    scale_x_discrete(labels = c(""))+
+    scale_shape_manual(values=c(16, 1))+
+    theme_cowplot()+
+    theme(plot.title = element_text(hjust = 0.5),
+          strip.text = element_text(size = 12,margin = margin(.1,0,.1,0, "cm")),#this is for the facets
+          strip.background = element_rect(color="black", fill="white", size=.5, linetype="solid"))+
+    panel_border() 
+}
+
+PlotwtED()
+
+#Figure 2E
+PlotEDvsDensityFinal<-function(df, yAxis,tittle){
+  ggplot()+
+    geom_point(data = df,aes(y=WmeanDist,x=.data[[yAxis]], shape =Region ),size=4)+
+    #geom_smooth(data = df,aes(y=WmeanDist,x=.data[[yAxis]],color = Strain, shape =Region ),size=4)+
+    geom_abline(intercept = 10.683, slope = 44.416, color = "Black")+
+    #geom_text(x=.3, y=30, label= bquote(paste("R"^2*"=0.3368")))+
+    #geom_text(x=.3, y=10, label= "bl")+
+    annotate(geom="text", x=.3, y=10, label=bquote(paste("R"^2*"=0.3368")))+
+    #geom_abline(intercept = 9.011, slope = 37.488, color = "Green")+
+    #geom_abline(intercept = 9.519, slope = 50.800, color = "Red")+
+    labs(title =tittle, y = "Mean Enrichment Distance", x = "Bacterial Density")+
+    scale_shape_manual(values=c(16, 1))+
+    theme_cowplot()+
+    theme(plot.title = element_text(hjust = 0.5))
+}
+PlotEDvsDensityFinal(EdSlice %>% filter(Strain == "wt"), "TotalRatio","")
 

### 2022-02-23 R/PaperFigures.Rmd
gbg

@@
 library(pixmap)
+library(rtiff)
 library(reshape2)
@@
 ```
-#####
 
@@
 figure2A2
-
-#With the mutants
-
 #####
@@
     scale_color_grey(labels = c("Mono-culture","Co-culture"))+
-    scale_x_discrete(labels = c("Planktonic", "5-10", "10-100", "100-1000", ">1000"))+
     labs(y = paste("Frequency (%)"),x = bquote(paste("Aggregate Volume (", mu*"m"^3*")")))+
@@
 
-#only difference between these two should be "scale_color_grey"
-PlotHistSumFinalStrains<-function(rep.df,cond.df,region.df, y_var, colorStrain){
-ggplot()+
-    geom_point(data = rep.df %>% filter(TimePoint=="Day 4"),
-                aes(x=as.factor(LogBin),y=.data[[y_var]], color =.data[[colorStrain]], shape = Region),
-               position = position_jitterdodge(jitter.height = 0, jitter.width = .3,dodge.width = 1),size=2)+
-    geom_point(data = region.df%>% filter(TimePoint=="Day 4"),
-               aes(x=as.factor(LogBin),y=.data[[y_var]], color =.data[[colorStrain]],shape = Region),
-               size=5, position = position_dodge(width = 1) )+
-    geom_errorbar(data = cond.df%>% filter(TimePoint=="Day 4"),
-               aes(x=as.factor(LogBin),ymin=.data[[y_var]],ymax=.data[[y_var]], group =.data[[colorStrain]]),width = .8,position = position_dodge(width = 1) )+
-    facet_grid(.~Species)+
-    scale_shape_manual(values=c(16, 1))+
-    scale_color_grey(labels = c(bquote(paste(italic('S. aureus + P. aeruginosa '))),
-                                bquote(paste(italic('S. aureus + P. aeruginosa '*Delta*"pqsL"))), 
-                                bquote(paste(italic('S. aureus + P. aeruginosa '*Delta*"phz")))))+
-    scale_x_discrete(labels = c("Planktonic", "5-10", "10-100", "100-1000", ">1000"))+
-    labs(y = paste("Frequency (%)"),x = bquote(paste("Aggregate Volume (", mu*"m"^3*")")), color = "Condition")+
-    theme_cowplot()+
-    panel_border() +
-    theme(plot.title = element_text(hjust = 0.5), 
-        strip.text = element_text(size = 11, face = "italic",margin = margin(.1,0,.1,0, "cm")),#this is for the facet text
-        strip.background = element_rect(color="black", fill="white", size=1, linetype="solid"))#facet background
-}#only difference between these two should be "scale_color_grey
-PlotHistSumFinalStrains(HistReplicateSummary%>% filter(Culture =="co"),
+PlotHistSum(HistReplicateSummary%>% filter(Culture =="co"),
             HistConditionSummary%>% filter(Culture =="co"),
@@
 PlotAbData3(AbDataUnstructureStats,"Species","MeanDifference","SEDifference", "Condition")
-#now using the jittel points
+#now using the jitter points
 

### 2022-02-23 R/PaperFigures.Rmd
Added correct labels to inner vs outer

--- 2022-02-22 R/PaperFigures.Rmd
@@
 #CFU data from Carolyn
-CFUdata<-read.csv("/Users/jupabago/Documents/Whiteley/PROJECTS/SaPa Chronic Wounds/Data/CFU_wound_All_dataTidy.csv",header = TRUE)
+CFUdata<-read.csv("/Users/jupabago/Documents/Whiteley/PROJECTS/SaPa Chronic Wounds/Data/From Carolyn/CFU_wound_All_dataTidy.csv",header = TRUE)
 CFUdata$Condition<-as.factor(CFUdata$Condition)
@@
 CFUstats$Condition <- factor(CFUstats$Condition, levels = c("mono", "co-wt", "co-pqsL"))
+
 PlotCFUs<- function(){
@@
 ##### 
-CFUInOutData<-read.csv("/Users/jupabago/Documents/Whiteley/PROJECTS/SaPa Chronic Wounds/Data/Inside_Outside_CFUcm2_Day4Tidy.csv",header = TRUE)
+CFUInOutData<-read.csv("/Users/jupabago/Documents/Whiteley/PROJECTS/SaPa Chronic Wounds/Data/From Carolyn/Inside_Outside_CFUcm2_Day4Tidy.csv",header = TRUE)
 CFUInOutData<-Filter(function(x)!all(is.na(x)), CFUInOutData)#this is to remove columns with NA
@@
 
-CFUInOutDataPost<-CFUInOutData %>% mutate(CFU.Inside = Inside.Bandage+Inside.Tissue, CFU.Outside = Outside.Tissue+Outside.Bandage) %>% mutate(PercentIn = 100*CFU.Outside/(CFU.Inside+CFU.Outside))
+CFUInOutDataPost<-CFUInOutData %>% mutate(CFU.Inside = Inside.Bandage+Inside.Tissue, CFU.Outside = Outside.Tissue+Outside.Bandage) %>% mutate(PercentIn = 100*CFU.Inside/(CFU.Inside+CFU.Outside))
 
@@
   #labs(x = "", y = expression(paste(Log[10], " CFU")), linetype = "")+
-    labs(x = "",y = bquote(paste("% CFU/", "cm"^2*" in healing edge")))+
+    labs(x = "",y = bquote(paste("% CFU/", "cm"^2*" in wound core")))+
   theme_cowplot()+
@@
     scale_color_grey(labels = c("Mono-culture","Co-culture"))+
-    scale_y_continuous(expand = expand_scale(mult = c(0, 0)), limits = c(0,75))+
+    scale_y_continuous(expand = expand_scale(mult = c(0, 0)), limits = c(0,100))+
   #labs(x = "", y = expression(paste(Log[10], " CFU")), linetype = "")+

### 2022-03-15 R/PaperFigures.Rmd
added aggregate size distribution figures for mutants, both dots and violin plots

@@
 
-```{r figure 1}
+```{r figure 1 and 3}
 #Figure 1A CFU data wt
@@
 BiomassDataWt = BiomassData%>% filter(Condition == "Sa mono" |Condition == "wt co"|Condition == "wt mono") %>% filter(TimePoint == "Day 4" )
+BiomassDataMut = BiomassData%>% filter(Culture == "co")  %>% filter(TimePoint == "Day 4" )
 biomassWTData = BiomassDataStats%>% filter(Condition == "Sa mono" |Condition == "wt co"|Condition == "wt mono") %>% filter(TimePoint == "Day 4" )
+biomassMutData = BiomassDataStats%>% filter(Culture == "co")  %>% filter(TimePoint == "Day 4" )
+
 #Carolyn wanted to play with the data so here it is:
 write.csv(BiomassDataWt,"/Users/jupabago/Documents/Whiteley/PROJECTS/SaPa Chronic Wounds/Data/CSV exports/BiomassWT.csv", row.names = T)
+write.csv(HistReplicateSummary,"/Users/jpb/Library/Mobile Documents/com~apple~CloudDocs/Documents/Whiteley/PROJECTS/SaPa Chronic Wounds/Data/CSV exports/ReplicateData.csv", row.names = T)
+write.csv(HistConditionSummary,"/Users/jpb/Library/Mobile Documents/com~apple~CloudDocs/Documents/Whiteley/PROJECTS/SaPa Chronic Wounds/Data/CSV exports/ConditionData.csv", row.names = T)
+write.csv(HistCondRegionSum,"/Users/jpb/Library/Mobile Documents/com~apple~CloudDocs/Documents/Whiteley/PROJECTS/SaPa Chronic Wounds/Data/CSV exports/RegionData.csv", row.names = T)
 
@@
 PlotBiomassPoints()
+
+PlotBiomassPointsMutants<- function(){
+  ggplot()+
+    geom_jitter(data = BiomassDataMut,aes(x=Species,y=Biomass, color = Strain),size=3,position = position_jitterdodge(jitter.height = 0,jitter.width = 0.2, dodge.width = .9))+
+    geom_errorbar(data = biomassMutData, aes(x=Species,ymin=(MeanBiomass), ymax = (MeanBiomass), group = Strain)
+                ,width = .4, size=.5,position = position_dodge(width = .9))+
+    scale_y_log10(breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)),
+                  limits = c(1, 10e7), expand = expand_scale(mult = c(0, 0)))+
+    scale_color_brewer(palette = "Set1",
+      labels = c(bquote(paste(italic('S. aureus + P. aeruginosa '))),
+                                bquote(paste(italic('S. aureus + P. aeruginosa '*Delta*"pqsL"))), 
+                                bquote(paste(italic('S. aureus + P. aeruginosa '*Delta*"phz")))))+
+
+    labs(x = "",y = bquote(paste("Biomass per image (", mu*"m"^3*")")), color = "Condition")+
+    theme_cowplot()+
+    theme(plot.title = element_text(hjust = 0.5),strip.text = element_text(size = 9, face = "italic",margin = margin(.1,0,.1,0, "cm")),
+          strip.background = element_rect(color="black", fill="white", size=.5, linetype="solid"),
+          axis.title.x = element_text(margin = margin(0,0,0,0),size=13),axis.text.x = element_text(face = "italic",margin = margin(1,0,0,0),size=13),
+          axis.title.y = element_text(margin = margin(0,4,0,0),size=13),axis.text.y = element_text(margin = margin(0,0,2,0),size=11))
+}
+PlotBiomassPointsMutantsViolin<- function(){
+  ggplot()+
+    geom_violin(data = BiomassDataMut,aes(x=Species,y=Biomass, color = Strain))+
+    geom_errorbar(data = biomassMutData, aes(x=Species,ymin=(MeanBiomass), ymax = (MeanBiomass), group = Strain)
+                ,width = .4, size=.5,position = position_dodge(width = .9))+
+    scale_y_log10(breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)),
+                  limits = c(1, 10e7), expand = expand_scale(mult = c(0, 0)))+
+    scale_color_brewer(palette = "Set1",
+      labels = c(bquote(paste(italic('S. aureus + P. aeruginosa '))),
+                                bquote(paste(italic('S. aureus + P. aeruginosa '*Delta*"pqsL"))), 
+                                bquote(paste(italic('S. aureus + P. aeruginosa '*Delta*"phz")))))+
+
+    labs(x = "",y = bquote(paste("Biomass per image (", mu*"m"^3*")")), color = "Condition")+
+    theme_cowplot()+
+    theme(plot.title = element_text(hjust = 0.5),strip.text = element_text(size = 9, face = "italic",margin = margin(.1,0,.1,0, "cm")),
+          strip.background = element_rect(color="black", fill="white", size=.5, linetype="solid"),
+          axis.title.x = element_text(margin = margin(0,0,0,0),size=13),axis.text.x = element_text(face = "italic",margin = margin(1,0,0,0),size=13),
+          axis.title.y = element_text(margin = margin(0,4,0,0),size=13),axis.text.y = element_text(margin = margin(0,0,2,0),size=11))
+}
+PlotBiomassPointsMutants()
+PlotBiomassPointsMutantsViolin()
 #####
@@
 PlotHistSumFinalStrains(HistReplicateSummary%>% filter(Culture =="co"),
+            HistConditionSummary%>% filter(Culture =="co"),
+            HistCondRegionSum%>% filter(Culture =="co"),
+            "NormalizedFrequency","Strain")
+
+PlotHistSumFinalStrainsViolin<-function(rep.df,cond.df,region.df, y_var, colorStrain){#doesn't include region
+ggplot()+
+    geom_violin(data = rep.df %>% filter(TimePoint=="Day 4"),
+                scale = "width", trim = F,
+                aes(x=as.factor(LogBin),y=.data[[y_var]], color =.data[[colorStrain]]))+
+    geom_point(data = region.df%>% filter(TimePoint=="Day 4"),
+               aes(x=as.factor(LogBin),y=.data[[y_var]], color =.data[[colorStrain]],shape = Region),
+               size=5, position = position_dodge(width = 1) )+
+    geom_errorbar(data = cond.df%>% filter(TimePoint=="Day 4"),
+               aes(x=as.factor(LogBin),ymin=.data[[y_var]],ymax=.data[[y_var]], group =.data[[colorStrain]]),width = .8,position = position_dodge(width = 1) )+
+    facet_grid(.~Species)+
+    scale_shape_manual(values=c(16, 1))+
+    scale_color_brewer(palette = "Set1",
+                       labels = c(bquote(paste(italic('S. aureus + P. aeruginosa '))),
+                                bquote(paste(italic('S. aureus + P. aeruginosa '*Delta*"pqsL"))), 
+                                bquote(paste(italic('S. aureus + P. aeruginosa '*Delta*"phz")))))+
+    scale_x_discrete(labels = c("Planktonic", "5-10", "10-100", "100-1000", ">1000"))+
+    labs(y = paste("Frequency (%)"),x = bquote(paste("Aggregate Volume (", mu*"m"^3*")")), color = "Condition")+
+    theme_cowplot()+
+    panel_border() +
+    theme(plot.title = element_text(hjust = 0.5), 
+        strip.text = element_text(size = 11, face = "italic",margin = margin(.1,0,.1,0, "cm")),#this is for the facet text
+        strip.background = element_rect(color="black", fill="white", size=1, linetype="solid"))#facet background
+}#only difference between these two should be "scale_color_grey
+PlotHistSumFinalStrainsViolin(HistReplicateSummary%>% filter(Culture =="co"),
             HistConditionSummary%>% filter(Culture =="co"),

### 2022-03-16 R/PaperFigures.Rmd
Added the updated color palete, changed the wtED, added plotAggCoreMut

@@
                   limits = c(1, 10e7), expand = expand_scale(mult = c(0, 0)))+
-    scale_color_brewer(palette = "Set1",
+    scale_color_manual(values=c("#000000", "#3964C3", "#D34328"),
       labels = c(bquote(paste(italic('S. aureus + P. aeruginosa '))),
@@
 
+PlotHistSumFinalViolin<-function(rep.df,cond.df,region.df, y_var, colorStrain){
+ggplot()+
+    geom_violin(data = rep.df %>% filter(TimePoint=="Day 4"),
+                scale = "width", trim = F,
+                aes(x=as.factor(LogBin),y=.data[[y_var]], color =.data[[colorStrain]]))+
+    geom_point(data = region.df%>% filter(TimePoint=="Day 4"),
+               aes(x=as.factor(LogBin),y=.data[[y_var]], color =.data[[colorStrain]],shape = Region),
+               size=3, position = position_dodge(width = .75) )+
+    geom_errorbar(data = cond.df%>% filter(TimePoint=="Day 4"),
+               aes(x=as.factor(LogBin),ymin=.data[[y_var]],ymax=.data[[y_var]], group =.data[[colorStrain]]),width = .5,position = position_dodge(width = .75) )+
+    facet_grid(.~Species)+
+    scale_shape_manual(values=c(16, 1))+
+    scale_color_grey(labels = c("Mono-culture","Co-culture"))+
+    scale_x_discrete(labels = c("Planktonic", "5-10", "10-100", "100-1000", ">1000"))+
+    labs(y = paste("Frequency (%)"),x = bquote(paste("Aggregate Volume (", mu*"m"^3*")")))+
+    theme_cowplot()+
+    panel_border() +
+    theme(plot.title = element_text(hjust = 0.5), 
+        strip.text = element_text(size = 11, face = "italic",margin = margin(.1,0,.1,0, "cm")),#this is for the facet text
+        strip.background = element_rect(color="black", fill="white", size=1, linetype="solid"))#facet background
+}
+
+PlotHistSumFinalViolin(HistReplicateSummary%>% filter(Condition == "Sa mono" |Condition == "wt co"|Condition == "wt mono"),
+            HistConditionSummary%>% filter(Condition == "Sa mono" |Condition == "wt co"|Condition == "wt mono"),
+            HistCondRegionSum%>% filter(Condition == "Sa mono" |Condition == "wt co"|Condition == "wt mono"),
+            "NormalizedFrequency", "Culture")
+
 #only difference between these two should be "scale_color_grey"
@@
     geom_violin(data = rep.df %>% filter(TimePoint=="Day 4"),
-                scale = "width", trim = F,
+                scale = "width", trim = T,
                 aes(x=as.factor(LogBin),y=.data[[y_var]], color =.data[[colorStrain]]))+
@@
     scale_shape_manual(values=c(16, 1))+
-    scale_color_brewer(palette = "Set1",
+    scale_color_manual(values=c("#000000", "#3964C3", "#D34328"),
                        labels = c(bquote(paste(italic('S. aureus + P. aeruginosa '))),
@@
 #####
-#Figure 2C
+#Figure 2D
 #Aggregation inner vs outer region
@@
     geom_point(data = rep.df %>% filter(TimePoint=="Day 4"),
-                aes(x=Region,y=.data[[y_var]], color =.data[[colorStrain]]),
-               position = position_jitterdodge(jitter.height = 0, jitter.width = .3,dodge.width = 0.75),size=3)+
+                aes(x=.data[[colorStrain]],y=.data[[y_var]], shape = Region, color =.data[[colorStrain]]),
+               position = position_jitterdodge(jitter.height = 0, jitter.width = .3,dodge.width = 0.75),size=3, show.legend = F)+
     geom_errorbar(data = region.df%>% filter(TimePoint=="Day 4"),
-               aes(x=Region,ymin=.data[[y_var]],ymax=.data[[y_var]], group =.data[[colorStrain]]),
+               aes(x=.data[[colorStrain]],ymin=.data[[y_var]],ymax=.data[[y_var]], group =Region),
                size=.5,width = 0.5, position = position_dodge(width = .75) )+
@@
     scale_color_grey(labels = c("Mono-culture","Co-culture"))+
+    scale_x_discrete(labels = c("Mono-culture","Co-culture"))+
     ggtitle(title)+
@@
 
-#Figure 2D
+PlotAggCoreMut<-function(rep.df,region.df, y_var, title,colorStrain, facet){
+ggplot()+
+    geom_point(data = rep.df %>% filter(TimePoint=="Day 4"),
+                aes(x=Region,y=.data[[y_var]], shape = Region, color =.data[[colorStrain]]),
+               position = position_jitterdodge(jitter.height = 0, jitter.width = .3,dodge.width = 0.75),size=3)+
+    geom_errorbar(data = region.df%>% filter(TimePoint=="Day 4"),
+               aes(x=Region,ymin=.data[[y_var]],ymax=.data[[y_var]], group =Strain),
+               size=.5,width = 0.5, position = position_dodge(width = .75) )+
+    #geom_point(data = cond.df%>% filter(TimePoint=="Day 4"),
+     #          aes(x=Region,y=.data[[y_var]],  color =.data[[colorStrain]]),size=4, shape = 3,position = position_dodge(width = .75) )+
+    scale_y_log10(breaks = c(100, 10, 1, .1, .01), labels = c(100, 10, 1, .1, .01))+
+    facet_grid(.~.data[[facet]])+
+    scale_shape_manual(values=c(16, 1))+
+    scale_color_manual(values=c("#000000", "#3964C3", "#D34328"),
+                       labels = c(bquote(paste(italic('S. aureus + P. aeruginosa '))),
+                                bquote(paste(italic('S. aureus + P. aeruginosa '*Delta*"pqsL"))), 
+                                bquote(paste(italic('S. aureus + P. aeruginosa '*Delta*"phz")))))+
+    ggtitle(title)+
+    labs(y = paste("Planktonic Biomass Contribution (%)"), x = "")+
+    theme_cowplot()+
+    panel_border() +
+    theme(plot.title = element_text(hjust = 0.5), 
+        strip.text = element_text(size = 11, face = "italic",margin = margin(.1,0,.1,0, "cm")),#this is for the facet text
+        strip.background = element_rect(color="black", fill="white", size=1, linetype="solid"))#facet background
+}
+
+PlotAggCoreMut(plankAggHistRep%>% filter(Culture=="co") %>% filter(Aggregation=="Planktonic"),
+             plankAggHistCondReg%>% filter(Culture=="co")%>% filter(Aggregation=="Planktonic"),
+             "AgPlNormBiomass", "", "Strain", "Species")
+
+#####
+
+#Figure 2E
+## Enrichment distance
+#####
 ##Marvin suggested doing the enrichment distance for those samples, but I guess there is nothing to compare, unless I do core vs edge
@@
     geom_point(data = df2,aes(y=WmeanDist,x = Condition, shape = Region),position = position_jitterdodge(jitter.height = 0, jitter.width = .3,dodge.width = 0.75),size=3)+
-    labs(y = expression("Enrichment distance ("*mu*"m)"), x = "") +
+    labs(y = expression(atop("Enrichment distance ("*mu*"m)",paste(italic("S. aureus") %->% italic("S. aureus ")))), x = "") +
     scale_color_grey()+
@@
 PlotwtED()
+#In this case, i want an actual x axis, but the top may work for reference
+PlotwtED2<-function(){
+df1<-pOEnrMetaStatsRegion %>% filter(Relation == "Pa->Sa", TimePoint=="Day 4", Condition == "wt co")
+df2<-pOEnrMetaClean %>% filter(Relation == "Pa->Sa", TimePoint=="Day 4", Condition == "wt co")
+  ggplot()+
+    geom_errorbar(data = df1,aes(y=meanED,ymax=meanED,ymin=meanED, x = Region), width = .5)+
+    geom_point(data = df2,aes(y=WmeanDist,x = Region, shape = Region),position = position_jitter(height = 0, width = .2),size=3, show.legend = F)+
+    labs(y = expression(atop("Enrichment distance ("*mu*"m)",paste(italic("S. aureus") %->% italic("S. aureus ")))), x = "") +
+    scale_color_grey()+
+    scale_shape_manual(values=c(16, 1))+
+    theme_cowplot()+
+    theme(plot.title = element_text(hjust = 0.5),
+          strip.text = element_text(size = 12,margin = margin(.1,0,.1,0, "cm")),#this is for the facets
+          strip.background = element_rect(color="black", fill="white", size=.5, linetype="solid"))+
+    panel_border() 
+}
 
-#Figure 2E
+PlotwtED2()
+#####
+#Figure 2F
 PlotEDvsDensityFinal<-function(df, yAxis,tittle){

### 2022-03-17 R/PaperFigures.Rmd
worked on finishing figures 2C, 2D, 2f AND 3E

@@
 BiomassDataWt = BiomassData%>% filter(Condition == "Sa mono" |Condition == "wt co"|Condition == "wt mono") %>% filter(TimePoint == "Day 4" )
-BiomassDataMut = BiomassData%>% filter(Culture == "co")  %>% filter(TimePoint == "Day 4" )
+BiomassDataMut = BiomassData %>% filter(TimePoint == "Day 4" )
 biomassWTData = BiomassDataStats%>% filter(Condition == "Sa mono" |Condition == "wt co"|Condition == "wt mono") %>% filter(TimePoint == "Day 4" )
-biomassMutData = BiomassDataStats%>% filter(Culture == "co")  %>% filter(TimePoint == "Day 4" )
+biomassMutData = BiomassDataStats  %>% filter(TimePoint == "Day 4" )
 
 #Carolyn wanted to play with the data so here it is:
-write.csv(BiomassDataWt,"/Users/jupabago/Documents/Whiteley/PROJECTS/SaPa Chronic Wounds/Data/CSV exports/BiomassWT.csv", row.names = T)
+write.csv(BiomassDataWt,"/Users/jpb/Library/Mobile Documents/com~apple~CloudDocs/Documents/Whiteley/PROJECTS/SaPa Chronic Wounds/Data/CSV exports/BiomassWT.csv", row.names = T)
+write.csv(BiomassDataMut,"/Users/jpb/Library/Mobile Documents/com~apple~CloudDocs/Documents/Whiteley/PROJECTS/SaPa Chronic Wounds/Data/CSV exports/BiomassMut.csv", row.names = T)
+write.csv(biomassMutData,"/Users/jpb/Library/Mobile Documents/com~apple~CloudDocs/Documents/Whiteley/PROJECTS/SaPa Chronic Wounds/Data/CSV exports/BiomassMutStats.csv", row.names = T)
+
 write.csv(HistReplicateSummary,"/Users/jpb/Library/Mobile Documents/com~apple~CloudDocs/Documents/Whiteley/PROJECTS/SaPa Chronic Wounds/Data/CSV exports/ReplicateData.csv", row.names = T)
@@
 
-#Figure 2A: Percent CFU inner wound
+#Figure 2B: Percent CFU inner wound
 ##### 
@@
 #####
-#Figure 2B
+#Figure 2C
 #####
@@
     geom_violin(data = rep.df %>% filter(TimePoint=="Day 4"),
-                scale = "width", trim = F,
-                aes(x=as.factor(LogBin),y=.data[[y_var]], color =.data[[colorStrain]]))+
+                scale = "width", trim = T, position = position_dodge(width = .85) ,
+                aes(x=as.factor(LogBin),y=.data[[y_var]], linetype =.data[[colorStrain]]))+
     geom_point(data = region.df%>% filter(TimePoint=="Day 4"),
-               aes(x=as.factor(LogBin),y=.data[[y_var]], color =.data[[colorStrain]],shape = Region),
-               size=3, position = position_dodge(width = .75) )+
+               aes(x=as.factor(LogBin),y=.data[[y_var]], group =.data[[colorStrain]],shape = CultureRegion),
+               size=3, position = position_jitterdodge(jitter.height = 0, jitter.width = .3,dodge.width = .75))+
     geom_errorbar(data = cond.df%>% filter(TimePoint=="Day 4"),
-               aes(x=as.factor(LogBin),ymin=.data[[y_var]],ymax=.data[[y_var]], group =.data[[colorStrain]]),width = .5,position = position_dodge(width = .75) )+
+               aes(x=as.factor(LogBin),ymin=.data[[y_var]],ymax=.data[[y_var]], group =.data[[colorStrain]]),width = .6,position = position_dodge(width = .75) )+
     facet_grid(.~Species)+
-    scale_shape_manual(values=c(16, 1))+
-    scale_color_grey(labels = c("Mono-culture","Co-culture"))+
+    scale_shape_manual(values=c( 16,17,1,2))+
+    scale_linetype_manual(values=c( "dashed","solid"),labels = c("Mono-infection","Co-infection"))+
     scale_x_discrete(labels = c("Planktonic", "5-10", "10-100", "100-1000", ">1000"))+
@@
             "NormalizedFrequency", "Culture")
+HistCondRegionSum = HistCondRegionSum %>% unite(CultureRegion, Culture, Region, sep = " ", remove = FALSE)
 
@@
 
+# Violin Plots
+## 2 versions, one with the species as a facet and the other one with species as x-axis
+### Mono vs co
+#####
+plankAggHistCondReg= plankAggHistCondReg %>% unite(CultureRegion, Culture, Region, sep = " ", remove = FALSE)#this is for the shapes fill and triangle vs circle
+
+PlotAggCoreViolinFacet<-function(rep.df,region.df, cond.df,y_var,colorStrain, facet){
+ggplot()+
+    geom_violin(data = rep.df %>% filter(TimePoint=="Day 4"),
+                aes(x=.data[[colorStrain]],y=.data[[y_var]], linetype =.data[[colorStrain]]),
+               position = position_dodge(width = 0.75),show.legend = T)+
+    geom_errorbar(data =cond.df %>% filter(TimePoint=="Day 4"),
+               aes(x=.data[[colorStrain]],ymin=.data[[y_var]],ymax=.data[[y_var]]),
+               size=.5,width = 0.5, position = position_dodge(width = .75) )+
+    geom_point(data = region.df%>% filter(TimePoint=="Day 4"),
+               aes(x=.data[[colorStrain]],y=.data[[y_var]],  shape =CultureRegion),size=4, position = position_dodge(width = .75) )+
+    scale_y_log10(breaks = c(100, 10, 1, .1, .01), labels = c(100, 10, 1, .1, .01))+
+    facet_grid(.~.data[[facet]])+
+    scale_shape_manual(values=c( 16,17,1,2))+
+    #scale_color_grey(labels = c("Mono-culture","Co-culture"))+
+    scale_x_discrete(labels = c("Mono-infection","Co-infection"))+
+    scale_linetype_manual(values=c( "dashed","solid"),labels = c("Mono-infection","Co-infection"))+
+    labs(y = paste("Planktonic Biomass Contribution (%)"), x = "")+
+    theme_cowplot()+
+    panel_border() +
+    theme(plot.title = element_text(hjust = 0.5), 
+        strip.text = element_text(size = 11, face = "italic",margin = margin(.1,0,.1,0, "cm")),#this is for the facet text
+        strip.background = element_rect(color="black", fill="white", size=1, linetype="solid"))#facet background
+}
+PlotAggCoreViolinFacet(plankAggHistRep%>% filter(Strain %in% c("Sa", "wt")) %>% filter(Aggregation=="Planktonic"),
+             plankAggHistCondReg%>% filter(Strain %in% c("Sa", "wt"))%>% filter(Aggregation=="Planktonic"),
+             plankAggHistCond%>% filter(Strain %in% c("Sa", "wt"))%>% filter(Aggregation=="Planktonic"),
+             "AgPlNormBiomass", "Culture", "Species")
+
+PlotAggCoreViolin<-function(rep.df,region.df, cond.df,y_var,colorStrain, facet){
+ggplot()+
+    geom_violin(data = rep.df %>% filter(TimePoint=="Day 4"),
+                aes(x=.data[[facet]],y=.data[[y_var]], linetype =.data[[colorStrain]]),
+               position = position_dodge(width = 0.75),show.legend = T)+
+    geom_errorbar(data =cond.df %>% filter(TimePoint=="Day 4"),
+               aes(x=.data[[facet]],ymin=.data[[y_var]],ymax=.data[[y_var]], group = Culture),
+               size=.5,width = 0.5, position = position_dodge(width = .75) )+
+    geom_point(data = region.df%>% filter(TimePoint=="Day 4"),
+               aes(x=.data[[facet]],y=.data[[y_var]],  group= Culture, shape =CultureRegion),size=4, 
+               position = position_jitterdodge(jitter.height = 0, jitter.width = .2,dodge.width = .75) )+
+    scale_y_log10(breaks = c(100, 10, 1, .1, .01), labels = c(100, 10, 1, .1, .01))+
+    #facet_grid(.~.data[[facet]])+
+    scale_shape_manual(values=c( 16,17,1,2))+
+    #scale_color_grey(labels = c("Mono-infection","Co-culture"))+
+    scale_x_discrete(labels = c(bquote(italic('P. aeruginosa')),bquote(italic('S. aureus'))))+
+    scale_linetype_manual(values=c( "dashed","solid"),labels = c("Mono-infection","Co-infection"))+
+    labs(y = paste("Planktonic Biomass Contribution (%)"), x = "")+
+    theme_cowplot()+
+    panel_border() +
+    theme(plot.title = element_text(hjust = 0.5), 
+        strip.text = element_text(size = 11, face = "italic",margin = margin(.1,0,.1,0, "cm")),#this is for the facet text
+        strip.background = element_rect(color="black", fill="white", size=1, linetype="solid"))#facet background
+}
+PlotAggCoreViolin(plankAggHistRep%>% filter(Strain %in% c("Sa", "wt")) %>% filter(Aggregation=="Planktonic"),
+             plankAggHistCondReg%>% filter(Strain %in% c("Sa", "wt"))%>% filter(Aggregation=="Planktonic"),
+             plankAggHistCond%>% filter(Strain %in% c("Sa", "wt"))%>% filter(Aggregation=="Planktonic"),
+             "AgPlNormBiomass", "Culture", "Species")
+#####
+### Mutants
 PlotAggCoreMut<-function(rep.df,region.df, y_var, title,colorStrain, facet){
@@
              plankAggHistCondReg%>% filter(Culture=="co")%>% filter(Aggregation=="Planktonic"),
+             plankAggHistCond%>% filter(Culture=="co")%>% filter(Aggregation=="Planktonic"),
              "AgPlNormBiomass", "", "Strain", "Species")
@@
 ##ggplot code from PropOc Data 3D
+## sending these to Carolyn for plotting
+
+write.csv(pOEnrMetaClean %>% filter(Relation == "Pa->Sa", TimePoint=="Day 4"),"/Users/jpb/Library/Mobile Documents/com~apple~CloudDocs/Documents/Whiteley/PROJECTS/SaPa Chronic Wounds/Data/CSV exports/EDData.csv", row.names = T)
+write.csv(pOEnrMetaStatsRegion %>% filter(Relation == "Pa->Sa", TimePoint=="Day 4"),"/Users/jpb/Library/Mobile Documents/com~apple~CloudDocs/Documents/Whiteley/PROJECTS/SaPa Chronic Wounds/Data/CSV exports/EDStats.csv", row.names = T)
+
 PlotwtED<-function(){
@@
 df2<-pOEnrMetaClean %>% filter(Relation == "Pa->Sa", TimePoint=="Day 4", Condition == "wt co")
+
   ggplot()+
@@
   ggplot()+
-    geom_point(data = df,aes(y=WmeanDist,x=.data[[yAxis]], shape =Region ),size=4)+
+    geom_point(data = df,aes(y=WmeanDist,x=.data[[yAxis]], color= Strain, shape =Region ),size=4)+
     #geom_smooth(data = df,aes(y=WmeanDist,x=.data[[yAxis]],color = Strain, shape =Region ),size=4)+
@@
     annotate(geom="text", x=.3, y=10, label=bquote(paste("R"^2*"=0.3368")))+
+    scale_color_manual(values=c("#000000", "#3964C3", "#D34328"),
+                       labels = c(bquote(paste(italic('S. aureus + P. aeruginosa '))),
+                                bquote(paste(italic('S. aureus + P. aeruginosa '*Delta*"pqsL"))), 
+                                bquote(paste(italic('S. aureus + P. aeruginosa '*Delta*"phz")))))+
     #geom_abline(intercept = 9.011, slope = 37.488, color = "Green")+
@@
     labs(title =tittle, y = "Mean Enrichment Distance", x = "Bacterial Density")+
-    scale_shape_manual(values=c(16, 1))+
+    scale_shape_manual(values=c(16, 17))+
     theme_cowplot()+
@@
 PlotEDvsDensityFinal(EdSlice %>% filter(Strain == "wt"), "TotalRatio","")
+PlotEDvsDensityFinal2<-function(df, yAxis,tittle){
+  ggplot()+
+    geom_point(data = df,aes(y=WmeanDist,x=.data[[yAxis]], color= Strain, shape =Region ),size=4)+
+    #geom_smooth(data = df,aes(y=WmeanDist,x=.data[[yAxis]],color = Strain, shape =Region ),size=4)+
+    #geom_abline(intercept = 10.683, slope = 44.416, color = "Black")+
+    #geom_text(x=.3, y=30, label= bquote(paste("R"^2*"=0.3368")))+
+    #geom_text(x=.3, y=10, label= "bl")+
+    #annotate(geom="text", x=.3, y=10, label=bquote(paste("R"^2*"=0.3368")))+
+    scale_color_manual(values=c("#000000", "#D34328", "#3964C3"),
+                       labels = c(bquote(paste(italic('S. aureus + P. aeruginosa '))),
+                                bquote(paste(italic('S. aureus + P. aeruginosa '*Delta*"pqsL"))), 
+                                bquote(paste(italic('S. aureus + P. aeruginosa '*Delta*"phz")))))+
+    #geom_abline(intercept = 9.011, slope = 37.488, color = "Green")+
+    #geom_abline(intercept = 9.519, slope = 50.800, color = "Black")+
+    labs(title =tittle, y = "Mean Enrichment Distance", x = "Bacterial Density")+
+    scale_shape_manual(values=c(16, 17))+
+    theme_cowplot()+
+    theme(plot.title = element_text(hjust = 0.5))
+}
+
+PlotEDvsDensityFinal2(EdSlice, "TotalRatio","")
 

### 2022-03-25 R/PaperFigures.Rmd
saved figures for paper as EPS

@@
 
+HistCondRegionSum = HistCondRegionSum %>% unite(CultureRegion, Culture, Region, sep = " ", remove = FALSE)
 PlotHistSumFinalViolin<-function(rep.df,cond.df,region.df, y_var, colorStrain){
@@
     scale_shape_manual(values=c( 16,17,1,2))+
-    scale_linetype_manual(values=c( "dashed","solid"),labels = c("Mono-infection","Co-infection"))+
+    scale_linetype_manual(values=c( "solid","solid"),labels = c("Mono-infection","Co-infection"))+
     scale_x_discrete(labels = c("Planktonic", "5-10", "10-100", "100-1000", ">1000"))+
     labs(y = paste("Frequency (%)"),x = bquote(paste("Aggregate Volume (", mu*"m"^3*")")))+
+
     theme_cowplot()+
@@
         strip.text = element_text(size = 11, face = "italic",margin = margin(.1,0,.1,0, "cm")),#this is for the facet text
-        strip.background = element_rect(color="black", fill="white", size=1, linetype="solid"))#facet background
+        strip.background = element_rect(color="black", fill="white", size=1, linetype="solid"),#facet background
+        axis.title.x = element_text(margin = margin(0,0,0,0),size=13 ),axis.text.x = element_text(margin = margin(1,0,2,0),size=11),
+        axis.title.y = element_text(margin = margin(0,0,0,0),size=13),axis.text.y = element_text(margin = margin(0,0,0,0),size=11))
 }
 
-PlotHistSumFinalViolin(HistReplicateSummary%>% filter(Condition == "Sa mono" |Condition == "wt co"|Condition == "wt mono"),
+Figure2C<-PlotHistSumFinalViolin(HistReplicateSummary%>% filter(Condition == "Sa mono" |Condition == "wt co"|Condition == "wt mono"),
             HistConditionSummary%>% filter(Condition == "Sa mono" |Condition == "wt co"|Condition == "wt mono"),
@@
             "NormalizedFrequency", "Culture")
-HistCondRegionSum = HistCondRegionSum %>% unite(CultureRegion, Culture, Region, sep = " ", remove = FALSE)
+
+ggsave(plot = Figure2C,
+       file="/Users/jpb/Library/Mobile Documents/com~apple~CloudDocs/Documents/Whiteley/PROJECTS/SaPa Chronic Wounds/Data/EPS Figures/Figure2C.EPS",
+device = cairo_ps, 
+width = 25,
+height = 10, 
+units = "cm")
 
@@
     scale_x_discrete(labels = c("Mono-infection","Co-infection"))+
-    scale_linetype_manual(values=c( "dashed","solid"),labels = c("Mono-infection","Co-infection"))+
+    scale_linetype_manual(values=c( "solid","solid"),labels = c("Mono-infection","Co-infection"))+
     labs(y = paste("Planktonic Biomass Contribution (%)"), x = "")+
@@
     scale_x_discrete(labels = c(bquote(italic('P. aeruginosa')),bquote(italic('S. aureus'))))+
-    scale_linetype_manual(values=c( "dashed","solid"),labels = c("Mono-infection","Co-infection"))+
+    scale_linetype_manual(values=c( "solid","solid"),labels = c("Mono-infection","Co-infection"))+
     labs(y = paste("Planktonic Biomass Contribution (%)"), x = "")+
@@
         strip.text = element_text(size = 11, face = "italic",margin = margin(.1,0,.1,0, "cm")),#this is for the facet text
-        strip.background = element_rect(color="black", fill="white", size=1, linetype="solid"))#facet background
+        strip.background = element_rect(color="black", fill="white", size=1, linetype="solid"),#facet background
+        axis.title.x = element_text(margin = margin(0,0,0,0),size=13 ),axis.text.x = element_text(margin = margin(1,0,2,0),size=11),
+        axis.title.y = element_text(margin = margin(0,0,0,0),size=13),axis.text.y = element_text(margin = margin(0,0,0,0),size=11))
 }
-PlotAggCoreViolin(plankAggHistRep%>% filter(Strain %in% c("Sa", "wt")) %>% filter(Aggregation=="Planktonic"),
+Figure2D<-PlotAggCoreViolin(plankAggHistRep%>% filter(Strain %in% c("Sa", "wt")) %>% filter(Aggregation=="Planktonic"),
              plankAggHistCondReg%>% filter(Strain %in% c("Sa", "wt"))%>% filter(Aggregation=="Planktonic"),
@@
              "AgPlNormBiomass", "Culture", "Species")
+
+ggsave(Figure2D, file="/Users/jpb/Library/Mobile Documents/com~apple~CloudDocs/Documents/Whiteley/PROJECTS/SaPa Chronic Wounds/Data/EPS Figures/Figure2D.EPS", device="eps", width = 5.5, height = 4.5)
 #####
@@
 
-PlotAggCoreMut(plankAggHistRep%>% filter(Culture=="co") %>% filter(Aggregation=="Planktonic"),
+PlotAggCoreMut(plankAggHistRep %>% filter(Aggregation=="Planktonic"),
+             plankAggHistCondReg%>% filter(Aggregation=="Planktonic"),
+             plankAggHistCond%>% filter(Aggregation=="Planktonic"),
+             "AgPlNormBiomass", "", "Strain", "Species")
+
+PlotAggCoreViolinFacetMut<-function(rep.df,region.df, cond.df,y_var,colorStrain, facet){
+ggplot()+
+    geom_violin(data = rep.df %>% filter(TimePoint=="Day 4"),
+                aes(x=.data[[colorStrain]],y=.data[[y_var]], color =.data[[colorStrain]]),
+               position = position_dodge(width = 0.75),show.legend = T)+
+    geom_errorbar(data =cond.df %>% filter(TimePoint=="Day 4"),
+               aes(x=.data[[colorStrain]],ymin=.data[[y_var]],ymax=.data[[y_var]]),
+               size=.5,width = 0.5, position = position_dodge(width = .75) )+
+    geom_point(data = region.df%>% filter(TimePoint=="Day 4"),
+               aes(x=.data[[colorStrain]],y=.data[[y_var]],  color = .data[[colorStrain]],shape =Region),size=4, position = position_dodge(width = .75) )+
+    scale_y_log10(breaks = c(100, 10, 1, .1, .01), labels = c(100, 10, 1, .1, .01))+
+    facet_grid(.~.data[[facet]])+
+    scale_shape_manual(values=c( 16,17,1,2))+
+    scale_color_manual(values=c("#000000", "#D34328", "#3964C3"),
+                       labels = c(bquote(paste(italic('S. aureus + P. aeruginosa '))),
+                                bquote(paste(italic('S. aureus + P. aeruginosa '*Delta*"pqsL"))), 
+                                bquote(paste(italic('S. aureus + P. aeruginosa '*Delta*"phz")))))+
+    scale_x_discrete(labels = c("","",""))+
+    #scale_linetype_manual(values=c( "dashed","solid"),labels = c("Mono-infection","Co-infection"))+
+    labs(y = paste("Planktonic Biomass Contribution (%)"), x = "")+
+    theme_cowplot()+
+    panel_border() +
+    theme(plot.title = element_text(hjust = 0.5), 
+        strip.text = element_text(size = 11, face = "italic",margin = margin(.1,0,.1,0, "cm")),#this is for the facet text
+        strip.background = element_rect(color="black", fill="white", size=1, linetype="solid"),#facet background
+        axis.title.x = element_text(margin = margin(0,0,0,0),size=13 ),axis.text.x = element_text(margin = margin(1,0,2,0),size=11),
+        axis.title.y = element_text(margin = margin(0,0,0,0),size=13),axis.text.y = element_text(margin = margin(0,0,0,0),size=11))
+}
+
+Figure3C<-PlotAggCoreViolinFacetMut(plankAggHistRep%>% filter(Culture=="co") %>% filter(Aggregation=="Planktonic"),
              plankAggHistCondReg%>% filter(Culture=="co")%>% filter(Aggregation=="Planktonic"),
              plankAggHistCond%>% filter(Culture=="co")%>% filter(Aggregation=="Planktonic"),
-             "AgPlNormBiomass", "", "Strain", "Species")
+             "AgPlNormBiomass", "Strain", "Species")
+
+ggsave(Figure3C, file="/Users/jpb/Library/Mobile Documents/com~apple~CloudDocs/Documents/Whiteley/PROJECTS/SaPa Chronic Wounds/Data/EPS Figures/Figure3C.EPS", device="eps", width = 7.5, height = 4.5)
 
@@
 PlotEDvsDensityFinal(EdSlice %>% filter(Strain == "wt"), "TotalRatio","")
-PlotEDvsDensityFinal2<-function(df, yAxis,tittle){
+
+PlotEDvsDensityFinal2<-function(df, xAxis,tittle){
   ggplot()+
-    geom_point(data = df,aes(y=WmeanDist,x=.data[[yAxis]], color= Strain, shape =Region ),size=4)+
+    geom_point(data = df,aes(x=.data[[xAxis]],y=WmeanDist, color= Strain, shape =Region ),size=4)+
     #geom_smooth(data = df,aes(y=WmeanDist,x=.data[[yAxis]],color = Strain, shape =Region ),size=4)+
@@
 PlotEDvsDensityFinal2(EdSlice, "TotalRatio","")
+write.csv(EdSlice,"/Users/jpb/Library/Mobile Documents/com~apple~CloudDocs/Documents/Whiteley/PROJECTS/SaPa Chronic Wounds/Data/CSV exports/BacterialSaturationData.csv", row.names = T)
 
